### 2021-11-05 Test.Rmd
Add test file

---
title: "Test"
author: "Anthony Zeimbekakis"
date: "11/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-11-08 Manuscript/manuscript.tex
Updated the manuscript template for this topic. Deleted unnecessary files.

\documentclass[12pt, letterpaper, titlepage]{article}

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor = blue}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{setspace}

\usepackage[pagewise]{lineno}
\linenumbers*[1]
% %% patches to make lineno work better with amsmath
\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
 \expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
 \expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
 \renewenvironment{#1}%
 {\linenomath\csname old#1\endcsname}%
 {\csname oldend#1\endcsname\endlinenomath}}%
\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
 \patchAmsMathEnvironmentForLineno{#1}%
 \patchAmsMathEnvironmentForLineno{#1*}}%

\AtBeginDocument{%
 \patchBothAmsMathEnvironmentsForLineno{equation}%
 \patchBothAmsMathEnvironmentsForLineno{align}%
 \patchBothAmsMathEnvironmentsForLineno{flalign}%
 \patchBothAmsMathEnvironmentsForLineno{alignat}%
 \patchBothAmsMathEnvironmentsForLineno{gather}%
 \patchBothAmsMathEnvironmentsForLineno{multline}%
}

\title{Survey of Misuses of the KS-Test}

\author{Anthony Zeimbekakis and Jun Yan\\
\href{mailto:anthony.zeimbekakis@uconn.edu}{\nolinkurl{anthony.zeimbekakis@uconn.edu}}\\
Department of Statistics, University of Connecticut}
\date{November 8, 2021}

\begin{document}
\maketitle

\doublespace

\begin{abstract}
Abstract here.
\end{abstract}

\hypertarget{sec:intro}{%
\section{Introduction}\label{sec:intro}}

Introuction here.

\hypertarget{sec:litrev}{%
\section{Problem Under Serial Dependence}\label{sec:litrev}}

Problem Under Serial Dependence here.

\hypertarget{sec:data}{%
\section{Simulation}\label{sec:data}}

Simulation here.

\hypertarget{sec:methods}{%
\section{Real Data Analysis}\label{sec:methods}}

Real Data Analysis here.

\hypertarget{sec:disc}{%
\section{Conclusion}\label{sec:disc}}

Conclusion here.

\bibliographystyle{chicago}
\bibliography{citations.bib}

\end{document}

### 2021-12-02 Code/Simulation.Rmd
Added tests for assumptions of KS-Test. Added Weiss reference. Added rough abstract.

---
title: "R Notebook"
output: html_notebook
---

```{r}
library(faux)
library(MASS)
library(xtable)
```

```{r}
# Testing a simple random normal distribution
test_normal <- function(n_tests, n_samples) {
  results <- numeric(n_tests)
  for(i in 1:n_tests) {
    data <- rnorm(n_samples)
    results[i] <- ks.test(data, "pnorm")$p.value
  }
  power_level <- 1 - sum(results < 0.05) / n_tests
  cat("Number of tests:", n_tests, "\n")
  cat("Number of samples:", n_samples, "\n")
  cat("Power level:", power_level, "\n")
}

test_normal(10000, 10)
test_normal(10000, 100)
test_normal(10000, 1000)
test_normal(10, 10000)
test_normal(100, 10000)
test_normal(1000, 10000)
```

```{r}
test_rounded <- function(n_tests, n_samples, rounded) {
  results <- numeric(n_tests)
  for(i in 1:n_tests) {
    data <- round(rnorm(n_samples), rounded)
    results[i] <- ks.test(data, "pnorm")$p.value
  }
  power_level <- 1 - sum(results < 0.05) / n_tests
  cat("Number of tests:", n_tests, "\n")
  cat("Number of samples:", n_samples, "\n")
  cat("Number of decimals:", rounded, "\n")
  cat("Power level:", power_level, "\n")
}

suppressWarnings(test_rounded(1000, 10000, 3))
suppressWarnings(test_rounded(1000, 10000, 2))
suppressWarnings(test_rounded(1000, 10000, 1))
```

```{r}
test_correlation <- function(n_tests, ars) {
  results <- numeric(length(ars))
  for(i in 1:length(ars)) {
    ar_results <- numeric(n_tests)
    for(j in 1:n_tests) {
      data <- arima.sim(model = list(ar = ars[i]), rand.gen = rnorm, n = 500)
      ar_results[j] <- round(ks.test(data, "pnorm")$p.value, 5)
    }
    results[i] <- sum(ar_results < 0.05) / n_tests
  }
  return(results)
}
ars <- seq(-0.95, 0.95, by = 0.025)
results <- suppressWarnings(test_correlation(1000, ars))
```

```{r}
plot(x = ars, y = results, xlab = "ar", ylab = "Type I Error Rate", col = ifelse(results < 0.05,'red','black'))
lines(x = ars, y = rep(c(0.05), times = length(ars)), lty = 2)
```

```{r}
test_table <- function(n_tests, n_samples) {
  results <- numeric(n_tests)
  for(i in 1:n_tests) {
    data <- rnorm(n_samples)
    results[i] <- ks.test(data, "pnorm")$p.value
  }
  power_level <- 1 - sum(results < 0.05) / n_tests
  return(power_level)
}
Tests_Samples <- c("10000, 10", "10000, 100", "10000, 1000", "10, 10000", "100, 10000", "1000, 10000")
Power_Level <- c(0, 0, 0, 0, 0, 0)
tab <- data.frame(Tests_Samples, Power_Level)
tab[1, "Power_Level"] <- test_table(10000, 10)
tab[2, "Power_Level"] <- test_table(10000, 100)
tab[3, "Power_Level"] <- test_table(10000, 1000)
tab[4, "Power_Level"] <- test_table(10, 10000)
tab[5, "Power_Level"] <- test_table(100, 10000)
tab[6, "Power_Level"] <- test_table(1000, 10000)
tab <- xtable(tab)
tab
```

### 2021-12-02 Manuscript/manuscript.tex
Added to the reference folder and fixed a bibliography issue where it would not appear in the manuscript
Added tests for assumptions of KS-Test. Added Weiss reference. Added rough abstract.

@@
 \begin{abstract}
-Abstract here.
+The Kolmogorov–Smirnov (KS) test is one the most popular goodness-of-fit tests for comparing a sample with a hypothesized parametric distribution.
+Nevertheless, it has often been misused.
+The standard one-sample KS test applies to independent, continuous data with a hypothesized distribution that is completely specified.
+It is not uncommon, however, to see in the literature that it was applied to dependent, discrete, or rounded data, with hypothesized distributions containing estimated parameters.
+For example, it has been “discovered” multiple times that the test is too conservative when the parameters are estimated [e.g., 39].
+This paper aims to survey the misuses of the KS test, demonstrate their consequences through simulation, and provide remedies as needed.
 \end{abstract}
@@
 Problem Under Serial Dependence here.
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rlr}
+  \hline
+ & Tests\_Samples & Power\_Level \\ 
+  \hline
+1 & 10000, 10 & 0.95 \\ 
+  2 & 10000, 100 & 0.96 \\ 
+  3 & 10000, 1000 & 0.95 \\ 
+  4 & 10, 10000 & 0.90 \\ 
+  5 & 100, 10000 & 0.92 \\ 
+  6 & 1000, 10000 & 0.94 \\ 
+   \hline
+\end{tabular}
+\end{table}
 
@@
 
+Here is an example citation: \citet{Steinskog}
+
 \bibliographystyle{chicago}

### 2021-12-06 Code/Simulation.Rmd
Added p-value histograms for all tests. Correctly test correlated data.

@@
 ```{r}
-library(faux)
-library(MASS)
 library(xtable)
+library(dgof)
 ```
@@
   }
-  power_level <- 1 - sum(results < 0.05) / n_tests
-  cat("Number of tests:", n_tests, "\n")
-  cat("Number of samples:", n_samples, "\n")
-  cat("Power level:", power_level, "\n")
+  #power_level <- 1 - sum(results < 0.05) / n_tests
+  hist_title <- paste("P-values for n =", n_samples, "and", n_tests, "replicate tests")
+  hist(results, main = hist_title, xlab = "P-value")
 }
 
+par(mfrow=c(3,2))
 test_normal(10000, 10)
@@
   }
-  power_level <- 1 - sum(results < 0.05) / n_tests
-  cat("Number of tests:", n_tests, "\n")
-  cat("Number of samples:", n_samples, "\n")
-  cat("Number of decimals:", rounded, "\n")
-  cat("Power level:", power_level, "\n")
+  #power_level <- 1 - sum(results < 0.05) / n_tests
+  hist_title <- paste("P-values with", rounded, "rounded decimals")
+  hist(results, main = hist_title, xlab = "P-value")
 }
 
+par(mfrow=c(2,2))
+suppressWarnings(test_rounded(1000, 10000, 4))
 suppressWarnings(test_rounded(1000, 10000, 3))
@@
 test_correlation <- function(n_tests, ars) {
-  results <- numeric(length(ars))
   for(i in 1:length(ars)) {
@@
     for(j in 1:n_tests) {
-      data <- arima.sim(model = list(ar = ars[i]), rand.gen = rnorm, n = 500)
-      ar_results[j] <- round(ks.test(data, "pnorm")$p.value, 5)
+      data <- arima.sim(model = list(ar = ars[i]), rand.gen = rnorm, sd = sqrt(1-ars[i]^2), n = 500)
+      ar_results[j] <- ks.test(data, "pnorm")$p.value
     }
-    results[i] <- sum(ar_results < 0.05) / n_tests
+    hist_title <- paste("AR coefficient", ars[i])
+    hist(ar_results, main = hist_title, xlab = "P-value")
   }
-  return(results)
 }
-ars <- seq(-0.95, 0.95, by = 0.025)
-results <- suppressWarnings(test_correlation(1000, ars))
+
+ars <- seq(-0.5, 0.5, by = 0.1)
+suppressWarnings(test_correlation(1000, ars))
 ```
+```{r}
+check_var <- function(phi) {
+  data <- arima.sim(model = list(ar = phi), rand.gen = rnorm, sd = sqrt(1-phi^2), n = 10000)
+  cat("ar = ", phi, "\n")
+  cat("var = ", var(data), "\n")
+  cat("sd = ", sd(data), "\n")
+  cat("-----", "\n")
+}
 
-```{r}
-plot(x = ars, y = results, xlab = "ar", ylab = "Type I Error Rate", col = ifelse(results < 0.05,'red','black'))
-lines(x = ars, y = rep(c(0.05), times = length(ars)), lty = 2)
+for (ar in seq(-0.95, 0.95, by = 0.05)) {
+  check_var(ar)
+}
 ```

### 2021-12-21 Code/Simulation.Rmd
Changes to the Manuscript, adding a rough introduction. Added parametric bootstrap to the code file.

@@
 
-for (ar in seq(-0.95, 0.95, by = 0.05)) {
-  check_var(ar)
-}
+#for (ar in seq(-0.95, 0.95, by = 0.05)) {
+  #check_var(ar)
+#}
 ```
@@
 ```
+
+```{r}
+test_dgof <- function(n_tests, n_samples, rounded) {
+  results <- numeric(n_tests)
+  for(i in 1:n_tests) {
+    data <- round(rnorm(n_samples), rounded)
+    results[i] <- ks.test(data, "pnorm", exact = TRUE)$p.value
+  }
+  #power_level <- 1 - sum(results < 0.05) / n_tests
+  hist_title <- paste("P-values with", rounded, "rounded decimals")
+  hist(results, main = hist_title, xlab = "P-value")
+}
+
+par(mfrow=c(2,2))
+suppressWarnings(test_dgof(10000, 30, 4))
+suppressWarnings(test_dgof(10000, 30, 3))
+suppressWarnings(test_dgof(10000, 30, 2))
+suppressWarnings(test_dgof(10000, 30, 1))
+suppressWarnings(test_rounded(10000, 30, 4))
+suppressWarnings(test_rounded(10000, 30, 3))
+suppressWarnings(test_rounded(10000, 30, 2))
+suppressWarnings(test_rounded(10000, 30, 1))
+```
+
+```{r}
+test_parametric <- function(x, B = 200) {
+  mu <- mean(x)
+  sigma <- sd(x)
+  stat <- ks.test(x, "pnorm", mu, sigma)$statistic
+  n <- length(x)
+  stat.b <- double(B)
+  for (i in 1:B) {
+    x.b <- rnorm(n, mu, sigma)
+    mu.b <- mean(x.b)
+    sigma.b <- sd(x.b)
+    stat.b[i] <- ks.test(x.b, "pnorm", mu.b, sigma.b)$statistic
+  }
+  p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
+  list(statistics = stat, p.value = p.value, 
+       estimate = c(mean = mu, sd = sigma),
+       stat.sim = stat.b)
+}
+
+pvals_parametric <- replicate(1000, test_parametric(rnorm(100), B = 200)$p.value)
+
+test_ks <- function(x) {
+  p.value <- ks.test(x, "pnorm", mean = mean(x), sd = sd(x))$p.value
+  list(p.value = p.value)
+}
+
+pvals_regular <- replicate(1000, test_ks(rnorm(100))$p.value)
+
+hist(pvals_parametric)
+hist(pvals_regular)
+```
+
+```{r}
+ks.test(pvals, "punif")
+```

### 2021-12-21 Manuscript/manuscript.tex
Added p-value histograms for all tests. Correctly test correlated data.
Changes to the Manuscript, adding a rough introduction. Added parametric bootstrap to the code file.

@@
 It is not uncommon, however, to see in the literature that it was applied to dependent, discrete, or rounded data, with hypothesized distributions containing estimated parameters.
-For example, it has been “discovered” multiple times that the test is too conservative when the parameters are estimated [e.g., 39].
+For example, it has been “discovered” multiple times that the test is too conservative when the parameters are estimated [e.g.
+\citet{Steinskog}].
 This paper aims to survey the misuses of the KS test, demonstrate their consequences through simulation, and provide remedies as needed.
@@
 
-Introuction here.
+The Kolmogorov-Smirnov (K-S) statistic is one of the most popular goodness-of-fit tests for comparing a sample with a hypothesized parametric distribution.
+Given a sample of n observations, let $S_{n}(x)$ be the empirical cumulative distribution and $F(x)$ be the population cumulative distribution.
+The K-S statistic is defined by: \[d = max(\lvert F(x)-S_{n}(x) \rvert)\] If the value of $d$ exceeds the critical value given by the table, the null hypothesis that the observations are from a specified distribution is rejected.
+
+However, the test is often misused.
+The standard one-sample K-S test applies to independent, continuous data with a hypothesized distribution that is completely satisfied.
+Often in literature, the test is applied to dependent, discrete, or rounded data, with hypothesized distributions containing estimated parameters.
+As shown by \citet{Steinskog} and later in this paper, the test is too conservative when the parameters are estimated.
+Throughout this paper, the cumulative distribution $F(x)$ is standard normal.
+
+To begin, a simple demonstration is performed to show the impact of sample size and replicate tests.
+For $n$ in $[10, 100, 1000]$, a random standard normal distributions were generated and K-S tests were performed.
+With the hypothesized distribution of standard normal, the histograms in Figure 1 show that the sample size has little effect on the distribution of P-values.
+
+\begin{figure}[!ht]
+  \centering
+  \includegraphics[width=0.8\linewidth]{Fig1}
+  \caption{Histograms of impact of sample size and number of tests on P-value.}
+  \label{fig:Fig1}
+\end{figure}
+
+The standard K-S test also shows misuse when the data has been rounded.
+For this simulation, standard normal distributions are rounded up to 4 decimal places.
+The histograms in Figure 2 display the distribution of P-values for the tests.
+
+\begin{figure}[!ht]
+  \centering
+  \includegraphics[width=0.8\linewidth]{Fig2}
+  \caption{Histograms of P-values with rounded data}
+  \label{fig:Fig2}
+\end{figure}
+
+As the level of rounding increases, the resulting P-values stray from the expected uniform distribution.
 
@@
 
-Problem Under Serial Dependence here.
+The K-S test shows significant issues in the case of serial dependence.
 
@@
   \hline
- & Tests\_Samples & Power\_Level \\ 
+ & Tests, Samples & PowerLevel \\ 
   \hline
@@
 
-Here is an example citation: \citet{Steinskog}
+Adding these to see the full bibliography:
+
+\citet{Steinskog}
+\citet{Weiss}
+\citet{Massey}
+\citet{Lilliefors}
 

### 2022-01-04 Code/Simulation.Rmd
fixed test_dgof

--- 2021-12-06 Code/Simulation.Rmd
@@
 library(dgof)
+library(tidyverse)
 ```
@@
 test_normal <- function(n_tests, n_samples) {
-  results <- numeric(n_tests)
+  p_values <- c()
   for(i in 1:n_tests) {
     data <- rnorm(n_samples)
-    results[i] <- ks.test(data, "pnorm")$p.value
+    p_values[i] <- ks.test(data, "pnorm")$p.value
   }
-  #power_level <- 1 - sum(results < 0.05) / n_tests
-  hist_title <- paste("P-values for n =", n_samples, "and", n_tests, "replicate tests")
-  hist(results, main = hist_title, xlab = "P-value")
+  results <- data.frame(p_values)
+  bins <- 1 + 3.322 * log(n_tests)
+  hist <- ggplot(results, aes(x = p_values)) + geom_histogram(color="black", fill="grey", bins = bins)
+  return(hist)
 }
 
-par(mfrow=c(3,2))
 test_normal(10000, 10)
@@
 test_rounded <- function(n_tests, n_samples, rounded) {
-  results <- numeric(n_tests)
+  p_values <- c()
   for(i in 1:n_tests) {
     data <- round(rnorm(n_samples), rounded)
-    results[i] <- ks.test(data, "pnorm")$p.value
+    p_values[i] <- ks.test(data, "pnorm")$p.value
   }
-  #power_level <- 1 - sum(results < 0.05) / n_tests
-  hist_title <- paste("P-values with", rounded, "rounded decimals")
-  hist(results, main = hist_title, xlab = "P-value")
+  results <- data.frame(p_values)
+  h <- hist(p_values, breaks = "FD", plot = FALSE)
+  hist <- ggplot(results, aes(x = p_values)) + geom_histogram(color="black", fill="grey", breaks = h$breaks)
+  return(hist)
 }
 
-par(mfrow=c(2,2))
 suppressWarnings(test_rounded(1000, 10000, 4))
@@
 suppressWarnings(test_rounded(1000, 10000, 1))
+test_plot <- suppressWarnings(test_rounded(1000, 10000, 1))
+ggsave(filename="test_plot.pdf", plot=test_plot)
 ```
@@
 ```
+
 ```{r}
@@
   cat("-----", "\n")
-}
-
-for (ar in seq(-0.95, 0.95, by = 0.05)) {
-  check_var(ar)
 }
@@
 ```
+
+```{r}
+y <- pnorm(seq(-10.1, 10, by = .1))
+sfun  <- stepfun(seq(-10, 10, by = .1), y)
+plot(y)
+plot(sfun)
+```
+
+```{r}
+test_dgof <- function(n_tests, n_samples, rounded, B = 100) {
+  results1 <- c()
+  results2 <- c()
+  results3 <- c()
+  left <- -10-rounded*0.1
+  y <- pnorm(seq(left, 10, by = rounded*0.1))
+  sfun  <- stepfun(seq(-10, 10, by = rounded*0.1), y)
+  for (i in 1:n_tests) {
+    test <- round(rnorm(n_samples), rounded)
+    cat(i)
+    results1[i] <- ks.test(test, sfun)$p.value
+    results2[i] <- ks.test(test, sfun, simulate.p.value = TRUE, B = B)$p.value
+    results3[i] <- ks.test(test, "pnorm")$p.value
+  }
+  hist(results1, xlab = "P-value")
+  hist(results2, xlab = "P-value")
+  hist(results3, xlab = "P-value")
+}
+
+#suppressWarnings(test_dgof(1000, 30, 4))
+#suppressWarnings(test_dgof(1000, 30, 3))
+suppressWarnings(test_dgof(1000, 30, 2))
+suppressWarnings(test_dgof(1000, 30, 1))
+```
+
+```{r}
+test_dgofsimulate <- function(n_tests, n_samples, rounded, B = 100) {
+  results1 <- c()
+  results2 <- c()
+  left <- -10-rounded*0.1
+  y <- pnorm(seq(left, 10, by = rounded*0.1))
+  sfun  <- stepfun(seq(-10, 10, by = rounded*0.1), y)
+  for (i in 1:n_tests) {
+    test <- round(rnorm(n_samples), rounded)
+    cat(i)
+    results1[i] <- ks.test(test, sfun)$p.value
+    results2[i] <- ks.test(test, sfun, simulate.p.value = TRUE, B = B)$p.value
+  }
+  hist(results1, xlab = "P-value")
+  hist(results2, xlab = "P-value")
+}
+
+suppressWarnings(test_dgofsimulate(1000, 100, 1, 100))
+suppressWarnings(test_dgofsimulate(1000, 100, 2, 100))
+```
+
+```{r}
+test_parametric <- function(x, B = 200) {
+  mu <- mean(x)
+  sigma <- sd(x)
+  stat <- ks.test(x, "pnorm", mu, sigma)$statistic
+  n <- length(x)
+  stat.b <- double(B)
+  for (i in 1:B) {
+    x.b <- rnorm(n, mu, sigma)
+    mu.b <- mean(x.b)
+    sigma.b <- sd(x.b)
+    stat.b[i] <- ks.test(x.b, "pnorm", mu.b, sigma.b)$statistic
+  }
+  p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
+  list(statistics = stat, p.value = p.value, 
+       estimate = c(mean = mu, sd = sigma),
+       stat.sim = stat.b)
+}
+
+pvals_parametric <- replicate(1000, test_parametric(rnorm(100), B = 200)$p.value)
+
+test_ks <- function(x) {
+  p.value <- ks.test(x, "pnorm", mean = mean(x), sd = sd(x))$p.value
+  list(p.value = p.value)
+}
+
+pvals_regular <- replicate(1000, test_ks(rnorm(100))$p.value)
+
+hist(pvals_parametric)
+hist(pvals_regular)
+```
+
+```{r}
+ks.test(pvals_parametric, "punif")
+ks.test(pvals_regular, "punif")
+```

### 2022-01-24 Code/Simulation.Rmd
Replaced plots with ggplot styling

--- 2021-12-06 Code/Simulation.Rmd
@@
 test_normal <- function(n_tests, n_samples) {
-  results <- numeric(n_tests)
+  p_values <- c()
   for(i in 1:n_tests) {
     data <- rnorm(n_samples)
-    results[i] <- ks.test(data, "pnorm")$p.value
+    p_values[i] <- ks.test(data, "pnorm")$p.value
   }
-  #power_level <- 1 - sum(results < 0.05) / n_tests
-  hist_title <- paste("P-values for n =", n_samples, "and", n_tests, "replicate tests")
-  hist(results, main = hist_title, xlab = "P-value")
+  return(p_values)
 }
 
-par(mfrow=c(3,2))
-test_normal(10000, 10)
-test_normal(10000, 100)
-test_normal(10000, 1000)
-test_normal(10, 10000)
-test_normal(100, 10000)
-test_normal(1000, 10000)
+hist1 <- test_normal(10000, 10)
+hist2 <- test_normal(10000, 100)
+hist3 <- test_normal(10000, 1000)
+hist4 <- test_normal(10, 10000)
+hist5 <- test_normal(100, 10000)
+hist6 <- test_normal(1000, 10000)
+
+histogram <- c(rep("hist1", 10000), rep("hist2", 10000), rep("hist3", 10000), rep("hist4", 10), rep("hist5", 100), rep("hist6", 1000))
+p_values <- c(hist1, hist2, hist3, hist4, hist5, hist6)
+results <- data_frame(p_values, histogram)
+hist <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", bins = 20)
+hist + facet_wrap(.~histogram, scales = "free_y")
 ```
@@
 test_rounded <- function(n_tests, n_samples, rounded) {
-  results <- numeric(n_tests)
+  p_values <- c()
   for(i in 1:n_tests) {
     data <- round(rnorm(n_samples), rounded)
-    results[i] <- ks.test(data, "pnorm")$p.value
+    p_values[i] <- ks.test(data, "pnorm")$p.value
   }
-  #power_level <- 1 - sum(results < 0.05) / n_tests
-  hist_title <- paste("P-values with", rounded, "rounded decimals")
-  hist(results, main = hist_title, xlab = "P-value")
+  return(p_values)
 }
 
-par(mfrow=c(2,2))
-suppressWarnings(test_rounded(1000, 10000, 4))
-suppressWarnings(test_rounded(1000, 10000, 3))
-suppressWarnings(test_rounded(1000, 10000, 2))
-suppressWarnings(test_rounded(1000, 10000, 1))
+hist1 <- suppressWarnings(test_rounded(10000, 10000, 4))
+hist2 <- suppressWarnings(test_rounded(10000, 10000, 3))
+hist3 <- suppressWarnings(test_rounded(10000, 10000, 2))
+hist4 <- suppressWarnings(test_rounded(10000, 10000, 1))
+#ggsave(filename="test_plot.pdf", plot=test_plot)
+histogram <- c(rep("hist1", 10000), rep("hist2", 10000), rep("hist3", 10000), rep("hist4", 10000))
+p_values <- c(hist1, hist2, hist3, hist4)
+results <- data_frame(p_values, histogram)
+hist <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", bins = 20)
+hist + facet_wrap(.~histogram, scales = "free_y")
 ```
@@
 test_correlation <- function(n_tests, ars) {
+  columns <- c("p_value", "ar")
+  ar_results <- data.frame(matrix(ncol = 2, nrow = 0))
+  colnames(ar_results) <- columns
   for(i in 1:length(ars)) {
-    ar_results <- numeric(n_tests)
     for(j in 1:n_tests) {
       data <- arima.sim(model = list(ar = ars[i]), rand.gen = rnorm, sd = sqrt(1-ars[i]^2), n = 500)
-      ar_results[j] <- ks.test(data, "pnorm")$p.value
+      ar_results <- add_row(ar_results, p_value = ks.test(data, "pnorm")$p.value, ar = ars[i])
     }
-    hist_title <- paste("AR coefficient", ars[i])
-    hist(ar_results, main = hist_title, xlab = "P-value")
   }
+  return(ar_results)
 }
@@
 ars <- seq(-0.5, 0.5, by = 0.1)
-suppressWarnings(test_correlation(1000, ars))
-```
-```{r}
-check_var <- function(phi) {
-  data <- arima.sim(model = list(ar = phi), rand.gen = rnorm, sd = sqrt(1-phi^2), n = 10000)
-  cat("ar = ", phi, "\n")
-  cat("var = ", var(data), "\n")
-  cat("sd = ", sd(data), "\n")
-  cat("-----", "\n")
-}
-
-for (ar in seq(-0.95, 0.95, by = 0.05)) {
-  check_var(ar)
-}
+ar_results <- suppressWarnings(test_correlation(1000, ars))
 ```
 
+```{r}
+hist <- ggplot(ar_results, aes(x = p_value)) + geom_histogram(color="gray", fill="white", bins = 20)
+hist + facet_wrap(.~ar)
+```
 ```{r}
@@
 ```
+
+```{r}
+test_dgof <- function(n_tests, n_samples, rounded, B = 100) {
+  results1 <- c()
+  results2 <- c()
+  results3 <- c()
+  left <- -4-rounded*0.1
+  y <- pnorm(seq(left, 4, by = rounded*0.1))
+  sfun  <- stepfun(seq(-4, 4, by = rounded*0.1), y)
+  for (i in 1:n_tests) {
+    test <- round(rnorm(n_samples), rounded)
+    results1[i] <- ks.test(test, sfun)$p.value
+    results2[i] <- ks.test(test, sfun, simulate.p.value = TRUE, B = B)$p.value
+    results3[i] <- ks.test(test, "pnorm")$p.value
+  }
+  list(results1 = results1, results2 = results2, results3 = results3)
+}
+
+test1 <- suppressWarnings(test_dgof(1000, 30, 4))
+test2 <- suppressWarnings(test_dgof(1000, 30, 3))
+test3 <- suppressWarnings(test_dgof(1000, 30, 2))
+test4 <- suppressWarnings(test_dgof(1000, 30, 1))
+
+hist1 <- test1$results1
+hist2 <- test1$results2
+hsit3 <- test1$results3
+hist4 <- test2$results1
+hist5 <- test2$results2
+hist6 <- test2$results3
+hist7 <- test3$results1
+hist8 <- test3$results2
+hist9 <- test3$results3
+hist10 <- test4$results1
+hist11 <- test4$results2
+hist12 <- test4$results3
+
+histogram <- c(rep(1:12, each = 1000))
+p_values <- c(hist1, hist2, hist3, hist4, hist5, hist6, hist7, hist8, hist9, hist10, hist11, hist12)
+results <- data_frame(p_values, histogram)
+hist <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", bins = 20)
+hist + facet_wrap(.~histogram, scales = "free_y", ncol = 3)
+```
+
+```{r}
+test_dgofsimulate <- function(n_tests, n_samples, rounded, B = 100) {
+  results1 <- c()
+  results2 <- c()
+  left <- -4-rounded*0.1
+  y <- pnorm(seq(left, 4, by = rounded*0.1))
+  sfun  <- stepfun(seq(-4, 4, by = rounded*0.1), y)
+  for (i in 1:n_tests) {
+    test <- round(rnorm(n_samples), rounded)
+    results1[i] <- ks.test(test, sfun)$p.value
+    results2[i] <- ks.test(test, sfun, simulate.p.value = TRUE, B = B)$p.value
+  }
+  list(results1 = results1, results2 = results2)
+}
+
+test1 <- suppressWarnings(test_dgofsimulate(1000, 100, 1, 100))
+test2 <- suppressWarnings(test_dgofsimulate(1000, 100, 2, 100))
+
+hist1 <- test1$results1
+hist2 <- test1$results2
+hist3 <- test2$results1
+hist4 <- test2$results2
+histogram <- c(rep("hist1", 1000), rep("hist2", 1000), rep("hist3", 1000), rep("hist4", 1000))
+p_values <- c(hist1, hist2, hist3, hist4)
+results <- data_frame(p_values, histogram)
+hist <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", bins = 20)
+hist + facet_wrap(.~histogram, scales = "free_y")
+```
+
+```{r}
+test_parametric <- function(x, B = 200) {
+  mu <- mean(x)
+  sigma <- sd(x)
+  stat <- ks.test(x, "pnorm", mu, sigma)$statistic
+  n <- length(x)
+  stat.b <- double(B)
+  for (i in 1:B) {
+    x.b <- rnorm(n, mu, sigma)
+    mu.b <- mean(x.b)
+    sigma.b <- sd(x.b)
+    stat.b[i] <- ks.test(x.b, "pnorm", mu.b, sigma.b)$statistic
+  }
+  p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
+  list(statistics = stat, p.value = p.value, 
+       estimate = c(mean = mu, sd = sigma),
+       stat.sim = stat.b)
+}
+
+pvals_parametric <- replicate(1000, test_parametric(rnorm(100), B = 200)$p.value)
+
+test_ks <- function(x) {
+  p.value <- ks.test(x, "pnorm", mean = mean(x), sd = sd(x))$p.value
+  list(p.value = p.value)
+}
+
+pvals_regular <- replicate(1000, test_ks(rnorm(100))$p.value)
+
+histogram <- c(rep("parametric", 1000), rep("regular", 1000))
+p_values <- c(pvals_parametric, pvals_regular)
+results <- data_frame(p_values, histogram)
+hist <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", bins = 20)
+hist + facet_wrap(.~histogram, scales = "free_y")
+
+ks.test(pvals_parametric, "punif")
+ks.test(pvals_regular, "punif")
+```

### 2022-01-24 Code/Simulation.Rmd
Fixed typo in dgof tests, added more styling and a save commands for plots

--- 2021-12-21 Code/Simulation.Rmd
@@
 ```{r}
+# Load packages
 library(xtable)
 library(dgof)
+library(tidyverse)
 ```
@@
 test_normal <- function(n_tests, n_samples) {
-  results <- numeric(n_tests)
+
+  p_values <- c()
   for(i in 1:n_tests) {
+
+    # Generate random data, perform a KS-test, and store the p-value
     data <- rnorm(n_samples)
-    results[i] <- ks.test(data, "pnorm")$p.value
-  }
-  #power_level <- 1 - sum(results < 0.05) / n_tests
-  hist_title <- paste("P-values for n =", n_samples, "and", n_tests, "replicate tests")
-  hist(results, main = hist_title, xlab = "P-value")
+    p_values[i] <- ks.test(data, "pnorm")$p.value
   }
 
-par(mfrow=c(3,2))
-test_normal(10000, 10)
-test_normal(10000, 100)
-test_normal(10000, 1000)
-test_normal(10, 10000)
-test_normal(100, 10000)
-test_normal(1000, 10000)
+  samples_str <- paste("Samples:", n_samples)
+  tests_str <- paste("Replicate tests:", n_tests)
+
+  # Create a master data_frame for p-values
+  tests <- c(rep(tests_str, n_tests))
+  samples <- c(rep(samples_str, n_tests))
+  results <- data_frame(p_values, tests, samples)
+
+  return(results)
+}
+
+# Create the histograms displaying p-values from each test
+test1 <- test_normal(10000, 10)
+test2 <- test_normal(10000, 100)
+test3 <- test_normal(10000, 1000)
+test4 <- test_normal(10, 10000)
+test5 <- test_normal(100, 10000)
+test6 <- test_normal(1000, 10000)
+results <- rbind(test1, test2, test3, test4, test5, test6)
+
+# Generate histograms plot
+hist_normal <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", bins = 20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~tests+samples, scales = "free_y")
 ```
@@
 ```{r}
-test_rounded <- function(n_tests, n_samples, rounded) {
-  results <- numeric(n_tests)
+# Test to show that rounding changes the power of the test
+test_rounded <- function(n_tests, n_samples, digits) {
+
+  p_values <- c()
   for(i in 1:n_tests) {
-    data <- round(rnorm(n_samples), rounded)
-    results[i] <- ks.test(data, "pnorm")$p.value
-  }
-  #power_level <- 1 - sum(results < 0.05) / n_tests
-  hist_title <- paste("P-values with", rounded, "rounded decimals")
-  hist(results, main = hist_title, xlab = "P-value")
+
+    # Generate random rounded data, perform a KS-test, and store the p-value
+    data <- round(rnorm(n_samples), digits)
+    p_values[i] <- ks.test(data, "pnorm")$p.value
   }
 
-par(mfrow=c(2,2))
-suppressWarnings(test_rounded(1000, 10000, 4))
-suppressWarnings(test_rounded(1000, 10000, 3))
-suppressWarnings(test_rounded(1000, 10000, 2))
-suppressWarnings(test_rounded(1000, 10000, 1))
+  return(p_values)
+}
+
+# Create the histograms displaying p-values from each test
+hist1 <- suppressWarnings(test_rounded(10000, 10000, 4))
+hist2 <- suppressWarnings(test_rounded(10000, 10000, 3))
+hist3 <- suppressWarnings(test_rounded(10000, 10000, 2))
+hist4 <- suppressWarnings(test_rounded(10000, 10000, 1))
+
+# Create a master data_frame with all the results
+histogram <- c(rep(".0001", 10000), rep(".001", 10000), rep(".01", 10000), rep(".1", 10000))
+p_values <- c(hist1, hist2, hist3, hist4)
+results <- data_frame(p_values, histogram)
+
+# Generate histograms plot
+hist_rounded <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", bins = 20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~histogram, scales = "free_y")
 ```
@@
 ```{r}
+# Test to show that autocorrelation changes the power of the test
 test_correlation <- function(n_tests, ars) {
+
+  # Create a master data_frame for p-values
+  columns <- c("p_value", "ar")
+  ar_results <- data.frame(matrix(ncol = 2, nrow = 0))
+  colnames(ar_results) <- columns
+
+  # For AR coefficients from -0.5 to 0.5
   for(i in 1:length(ars)) {
-    ar_results <- numeric(n_tests)
+
     for(j in 1:n_tests) {
+
+      # Generate random correlated data, perform a KS-test, and store the p-value
       data <- arima.sim(model = list(ar = ars[i]), rand.gen = rnorm, sd = sqrt(1-ars[i]^2), n = 500)
-      ar_results[j] <- ks.test(data, "pnorm")$p.value
-    }
-    hist_title <- paste("AR coefficient", ars[i])
-    hist(ar_results, main = hist_title, xlab = "P-value")
+      ar_results <- add_row(ar_results, p_value = ks.test(data, "pnorm")$p.value, ar = ars[i])
     }
@@
 
-ars <- seq(-0.5, 0.5, by = 0.1)
-suppressWarnings(test_correlation(1000, ars))
-```
-```{r}
-check_var <- function(phi) {
-  data <- arima.sim(model = list(ar = phi), rand.gen = rnorm, sd = sqrt(1-phi^2), n = 10000)
-  cat("ar = ", phi, "\n")
-  cat("var = ", var(data), "\n")
-  cat("sd = ", sd(data), "\n")
-  cat("-----", "\n")
+  return(ar_results)
 }
 
-#for (ar in seq(-0.95, 0.95, by = 0.05)) {
-  #check_var(ar)
-#}
+ # Set AR coefficients and generate results
+ars <- seq(-0.5, 0.5, by = 0.1)
+ar_results <- suppressWarnings(test_correlation(1000, ars))
+
+# Generate histograms plot
+hist_correlation <- ggplot(ar_results, aes(x = p_value)) + geom_histogram(color="gray", fill="white", bins = 20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~ar, scales = "free_y", ncol = 3)
 ```
@@
 ```{r}
+# Test the xtable package
 test_table <- function(n_tests, n_samples) {
@@
 ```{r}
-test_dgof <- function(n_tests, n_samples, rounded) {
-  results <- numeric(n_tests)
-  for(i in 1:n_tests) {
-    data <- round(rnorm(n_samples), rounded)
-    results[i] <- ks.test(data, "pnorm", exact = TRUE)$p.value
-  }
-  #power_level <- 1 - sum(results < 0.05) / n_tests
-  hist_title <- paste("P-values with", rounded, "rounded decimals")
-  hist(results, main = hist_title, xlab = "P-value")
+# Test the dgof package as a solution to rounded data with 30 or under samples
+test_dgof <- function(n_tests, n_samples, digits, B = 100) {
+
+  results1 <- c()
+  results2 <- c()
+  results3 <- c()
+
+  # Create the rounded normal step function
+  left <- -4-0.1^digits
+  y <- pnorm(seq(left, 4, by = 0.1^digits))
+  sfun  <- stepfun(seq(-4, 4, by = 0.1^digits), y)
+
+  for (i in 1:n_tests) {
+
+    if (i%%100 == 0) {
+      cat(i)
     }
 
-par(mfrow=c(2,2))
-suppressWarnings(test_dgof(10000, 30, 4))
-suppressWarnings(test_dgof(10000, 30, 3))
-suppressWarnings(test_dgof(10000, 30, 2))
-suppressWarnings(test_dgof(10000, 30, 1))
-suppressWarnings(test_rounded(10000, 30, 4))
-suppressWarnings(test_rounded(10000, 30, 3))
-suppressWarnings(test_rounded(10000, 30, 2))
-suppressWarnings(test_rounded(10000, 30, 1))
+    # Generate random rounded data, perform 3 KS-tests, and store the p-values
+    # 1. Using the rounded normal step function
+    # 2. Using the naive continuous standard normal function
+    data <- round(rnorm(n_samples), digits)
+    results1[i] <- ks.test(data, sfun)$p.value
+    results2[i] <- ks.test(data, "pnorm")$p.value
+  }
+
+  # Create a master data_frame for p-values
+  test <- c(rep("dgof", n_tests), rep("naive", n_tests))
+  digits <- c(rep(.1^digits, 2*n_tests))
+  p_values <- c(results1, results2)
+  results <- data_frame(p_values, test, digits)
+
+  return(results)
+}
+
+# Create the histograms displaying p-values from each test
+test1 <- suppressWarnings(test_dgof(1000, 30, 3))
+test2 <- suppressWarnings(test_dgof(1000, 30, 2))
+test3 <- suppressWarnings(test_dgof(1000, 30, 1))
+results <- rbind(test1, test2, test3)
+
+# Generate histograms plot
+hist_dgof <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", bins = 20) + geom_histogram(color="gray", fill="white", bins = 20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, ncol = 3, scales = "free_y")
+hist_dgof
 ```
@@
 ```{r}
+# Test the dgof package's simulate p-values as a solution to rounded data with over 30 samples
+test_dgofsimulate <- function(n_tests, n_samples, digits, B = 100) {
+
+  # Results lists
+  results1 <- c()
+  results2 <- c()
+
+  # Create the rounded normal step function
+  left <- -4-0.1^digits
+  y <- pnorm(seq(left, 4, by = 0.1^digits))
+  sfun  <- stepfun(seq(-4, 4, by = 0.1^digits), y)
+
+  for (i in 1:n_tests) {
+
+    # Generate random rounded data, perform 2 KS-tests, and store the p-values
+    # 1. Using the rounded normal step function
+    # 2. Using the rounded normal step function with simulated p-values
+    test <- round(rnorm(n_samples), digits)
+    results1[i] <- ks.test(test, sfun)$p.value
+    results2[i] <- ks.test(test, sfun, simulate.p.value = TRUE, B = B)$p.value
+  }
+
+  # Create a master data_frame for p-values
+  test <- c(rep("dgof", n_tests), rep("simulated", n_tests))
+  digits <- c(rep(.1^digits, 2*n_tests))
+  p_values <- c(results1, results2)
+  results <- data_frame(p_values, test, digits)
+
+  return(results)
+}
+
+# Create the histograms displaying p-values from each test
+test1 <- suppressWarnings(test_dgofsimulate(1000, 100, 1, 100))
+test2 <- suppressWarnings(test_dgofsimulate(1000, 100, 2, 100))
+results <- rbind(test1, test2)
+
+# Generate histograms plot
+hist_dgofsim <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", bins = 20) + geom_histogram(color="gray", fill="white", bins = 20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, scales = "free_y")
+hist_dgofsim
+```
+
+```{r}
+# Test parametric bootstrap as a solution to fitting parameters
 test_parametric <- function(x, B = 200) {
+
+  # Summarize parameters
   mu <- mean(x)
   sigma <- sd(x)
+
+  # Store KS statistic from using fitted parameters
   stat <- ks.test(x, "pnorm", mu, sigma)$statistic
+
+  # Parametric bootstrap to approximate the null distribution
   n <- length(x)
@@
   p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
+
   list(statistics = stat, p.value = p.value, 
@@
 
-pvals_parametric <- replicate(1000, test_parametric(rnorm(100), B = 200)$p.value)
-
-test_ks <- function(x) {
+# Naive KS-test to show consequence of fitted parameters
+test_naive <- function(x) {
   p.value <- ks.test(x, "pnorm", mean = mean(x), sd = sd(x))$p.value
@@
 
-pvals_regular <- replicate(1000, test_ks(rnorm(100))$p.value)
+# Generate results
+pvals_parametric <- replicate(1000, test_parametric(rnorm(100), B = 200)$p.value)
+pvals_naive <- replicate(1000, test_naive(rnorm(100))$p.value)
 
-hist(pvals_parametric)
-hist(pvals_regular)
+# Create a master data_frame with all the results
+histogram <- c(rep("Parametric", 1000), rep("Naive", 1000))
+p_values <- c(pvals_parametric, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+# Generate histograms plot
+hist_parametric <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", bins = 20) + geom_histogram(color="gray", fill="white", bins = 20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~histogram, scales = "free_y")
+
+# Run KS-tests to check for uniform distribution
+ks.test(pvals_parametric, "punif")
+ks.test(pvals_naive, "punif")
 ```
@@
 ```{r}
-ks.test(pvals, "punif")
+ggsave(filename="hist_normal.pdf", plot=hist_normal, path = "/Users/anthony/Desktop/School Work/Honors Thesis/KS-Test-Thesis/Manuscript")
+ggsave(filename="hist_rounded.pdf", plot=hist_rounded, path = "/Users/anthony/Desktop/School Work/Honors Thesis/KS-Test-Thesis/Manuscript")
+ggsave(filename="hist_correlation.pdf", plot=hist_correlation, path = "/Users/anthony/Desktop/School Work/Honors Thesis/KS-Test-Thesis/Manuscript")
+ggsave(filename="hist_dgof.pdf", plot=hist_dgof, path = "/Users/anthony/Desktop/School Work/Honors Thesis/KS-Test-Thesis/Manuscript")
+ggsave(filename="hist_dgofsim.pdf", plot=hist_dgofsim, path = "/Users/anthony/Desktop/School Work/Honors Thesis/KS-Test-Thesis/Manuscript")
+ggsave(filename="hist_parametric.pdf", plot=hist_parametric, path = "/Users/anthony/Desktop/School Work/Honors Thesis/KS-Test-Thesis/Manuscript")
 ```

### 2022-01-24 Manuscript/manuscript.tex
Fixed typo in dgof tests, added more styling and a save commands for plots

@@
 
-\title{Survey of Misuses of the KS-Test}
+\title{Survey of Misuses of the Kolmogorov–Smirnov-Test}
 
@@
 Department of Statistics, University of Connecticut}
-\date{November 8, 2021}
+\date{January 23, 2021}
 
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{Fig1}
+  \includegraphics[width=0.8\linewidth]{hist_normal}
   \caption{Histograms of impact of sample size and number of tests on P-value.}
-  \label{fig:Fig1}
+  \label{fig:hist_normal}
 \end{figure}
 
-The standard K-S test also shows misuse when the data has been rounded.
-For this simulation, standard normal distributions are rounded up to 4 decimal places.
-The histograms in Figure 2 display the distribution of P-values for the tests.
+\hypertarget{sec:fitted}{%
+\section{Fitted Parameters}\label{sec:fitted}}
+
+The K-S test shows significant issues in the case of fitted parameters.
 
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{Fig2}
-  \caption{Histograms of P-values with rounded data}
-  \label{fig:Fig2}
+  \includegraphics[width=0.8\linewidth]{hist_parametric}
+  \caption{Histograms of P-values with parametric bootstrap.}
+  \label{fig:hist_parametric}
 \end{figure}
 
-As the level of rounding increases, the resulting P-values stray from the expected uniform distribution.
+\hypertarget{sec:rounded}{%
+\section{Rounded Data}\label{sec:rounded}}
 
-\hypertarget{sec:litrev}{%
-\section{Problem Under Serial Dependence}\label{sec:litrev}}
+The K-S test shows significant issues in the case of rounding data.
+
+\begin{figure}[!ht]
+  \centering
+  \includegraphics[width=0.8\linewidth]{hist_rounded}
+  \caption{Histograms of P-values with rounded data.}
+  \label{fig:hist_rounded}
+\end{figure}
+
+\begin{figure}[!ht]
+  \centering
+  \includegraphics[width=0.8\linewidth]{hist_dgof}
+  \caption{Histograms of P-values with dgof package.}
+  \label{fig:hist_dgof}
+\end{figure}
+
+\begin{figure}[!ht]
+  \centering
+  \includegraphics[width=0.8\linewidth]{hist_dgofsim}
+  \caption{Histograms of P-values when simulating p-value.}
+  \label{fig:hist_dgofsim}
+\end{figure}
+
+\hypertarget{sec:correlation}{%
+\section{Problem under Serial Dependence}\label{sec:correlation}}
 
@@
 
-\begin{table}[ht]
+\begin{figure}[!ht]
   \centering
-\begin{tabular}{rlr}
-  \hline
- & Tests, Samples & PowerLevel \\ 
-  \hline
-1 & 10000, 10 & 0.95 \\ 
-  2 & 10000, 100 & 0.96 \\ 
-  3 & 10000, 1000 & 0.95 \\ 
-  4 & 10, 10000 & 0.90 \\ 
-  5 & 100, 10000 & 0.92 \\ 
-  6 & 1000, 10000 & 0.94 \\ 
-   \hline
-\end{tabular}
-\end{table}
+  \includegraphics[width=0.8\linewidth]{hist_correlation}
+  \caption{Histograms of P-values with correlated data.}
+  \label{fig:hist_correlation}
+\end{figure}
 
-\hypertarget{sec:data}{%
-\section{Simulation}\label{sec:data}}
-
-Simulation here.
-
-\hypertarget{sec:methods}{%
-\section{Real Data Analysis}\label{sec:methods}}
-
-Real Data Analysis here.
-
-\hypertarget{sec:disc}{%
-\section{Conclusion}\label{sec:disc}}
+\hypertarget{sec:conclusion}{%
+\section{Conclusion}\label{sec:conclusion}}
 

### 2022-01-24 Code/Simulation.Rmd
Rough rounded section to manuscript, updates to .gitignore

@@
     if (i%%100 == 0) {
-      cat(i)
+      cat(i, " ")
     }
@@
   # Create a master data_frame for p-values
-  test <- c(rep("dgof", n_tests), rep("naive", n_tests))
+  test <- c(rep("dgof", n_tests), rep("Naive", n_tests))
   digits <- c(rep(.1^digits, 2*n_tests))
@@
 # Create the histograms displaying p-values from each test
-test1 <- suppressWarnings(test_dgof(1000, 30, 3))
-test2 <- suppressWarnings(test_dgof(1000, 30, 2))
-test3 <- suppressWarnings(test_dgof(1000, 30, 1))
+test1 <- suppressWarnings(test_dgof(10000, 30, 3))
+test2 <- suppressWarnings(test_dgof(10000, 30, 2))
+test3 <- suppressWarnings(test_dgof(10000, 30, 1))
 results <- rbind(test1, test2, test3)
@@
 hist_dgof <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", bins = 20) + geom_histogram(color="gray", fill="white", bins = 20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, ncol = 3, scales = "free_y")
-hist_dgof
 ```
@@
   # Create a master data_frame for p-values
-  test <- c(rep("dgof", n_tests), rep("simulated", n_tests))
+  test <- c(rep("dgof", n_tests), rep("Simulated", n_tests))
   digits <- c(rep(.1^digits, 2*n_tests))
@@
 hist_dgofsim <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", bins = 20) + geom_histogram(color="gray", fill="white", bins = 20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, scales = "free_y")
-hist_dgofsim
 ```

### 2022-01-24 Manuscript/manuscript.tex
Rough rounded section to manuscript, updates to .gitignore

@@
 
-The K-S test shows significant issues in the case of rounding data.
+Another assumption of the K-S test is that it applies to continuous data.
+Of course, in any case where the distribution is discrete, the test no longer applies and loses its power.
+To demonstrate this, simulations were conducted at varying levels of rounding.
+A random sample of size $10,000$ was collected from the standard normal distribution and subsequently rounded to the nearest degree, up to the ten thousandth.
+This simulation was replicated $10,000$ times for each rounding level and the results are shown in Figure~\ref{fig:hist_rounded}.
 
@@
 \end{figure}
+
+From the histograms it is clear that though it appears the distributions of p-values hold a uniform shape through rounding to the thousandth, it quickly deviates as the rounding becomes stronger.
+This simulation shows that rounding can have an impact on the power of the K-S test as early as the hundreths place and discrete data should not be used.
+
+There are some solutions in the case that a discrete distribution is in question.
+The chi-squared test [INSERT REFERENCE HERE] is another goodness-of-fit test that can be applied to discrete distributions.
+However, the standard K-S test holds various advantages over it.
+In small samples, \citet{Massey} explains that the chi-squared test loses information and validity due to the grouping performed, while the K-S test treats individual observations separately.
+\citet{Massey} additionally notes that the K-S test generally appears to be the more powerful test regardless of sample size.
 
@@
 \citet{Lilliefors}
+\citet{dgof}
+\citet{Conover}
+\citet{Gleser}
 

### 2022-01-31 Code/Simulation.Rmd
Fixed bins in histograms

@@
 # Create the histograms displaying p-values from each test
-hist1 <- suppressWarnings(test_rounded(10000, 10000, 4))
-hist2 <- suppressWarnings(test_rounded(10000, 10000, 3))
-hist3 <- suppressWarnings(test_rounded(10000, 10000, 2))
-hist4 <- suppressWarnings(test_rounded(10000, 10000, 1))
+hist1 <- suppressWarnings(test_rounded(10000, 100, 4))
+hist2 <- suppressWarnings(test_rounded(10000, 100, 3))
+hist3 <- suppressWarnings(test_rounded(10000, 100, 2))
+hist4 <- suppressWarnings(test_rounded(10000, 100, 1))
 
@@
 # Generate histograms plot
-hist_rounded <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", bins = 20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~histogram, scales = "free_y")
+hist_rounded <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value") + facet_wrap(.~histogram, scales = "free_y")
 ```
@@
       # Generate random correlated data, perform a KS-test, and store the p-value
-      data <- arima.sim(model = list(ar = ars[i]), rand.gen = rnorm, sd = sqrt(1-ars[i]^2), n = 500)
+      data <- arima.sim(model = list(ar = ars[i]), rand.gen = rnorm, sd = sqrt(1-ars[i]^2), n = 100)
       ar_results <- add_row(ar_results, p_value = ks.test(data, "pnorm")$p.value, ar = ars[i])
@@
 # Generate histograms plot
-hist_correlation <- ggplot(ar_results, aes(x = p_value)) + geom_histogram(color="gray", fill="white", bins = 20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~ar, scales = "free_y", ncol = 3)
+hist_correlation <- ggplot(ar_results, aes(x = p_value)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~ar, scales = "free_y", ncol = 3)
 ```
@@
 # Create the histograms displaying p-values from each test
-test1 <- suppressWarnings(test_dgof(10000, 30, 3))
-test2 <- suppressWarnings(test_dgof(10000, 30, 2))
-test3 <- suppressWarnings(test_dgof(10000, 30, 1))
+test1 <- suppressWarnings(test_dgof(10000, 100, 3))
+test2 <- suppressWarnings(test_dgof(10000, 100, 2))
+test3 <- suppressWarnings(test_dgof(10000, 100, 1))
 results <- rbind(test1, test2, test3)
@@
 # Generate histograms plot
-hist_dgof <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", bins = 20) + geom_histogram(color="gray", fill="white", bins = 20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, ncol = 3, scales = "free_y")
+hist_dgof <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, ncol = 3, scales = "free_y")
+hist_dgof
 ```
@@
 # Generate histograms plot
-hist_dgofsim <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", bins = 20) + geom_histogram(color="gray", fill="white", bins = 20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, scales = "free_y")
+hist_dgofsim <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, scales = "free_y")
 ```
@@
 ```{r}
+# Split sample size into blocks, apply bootstrap onto blocks. Use that as x.b. Fit, stat.b
 # Test parametric bootstrap as a solution to fitting parameters
-test_parametric <- function(x, B = 200) {
+test_parametric <- function(x, B = 1000) {
 
@@
 # Generate results
-pvals_parametric <- replicate(1000, test_parametric(rnorm(100), B = 200)$p.value)
+pvals_parametric <- replicate(1000, test_parametric(rnorm(100), B = 1000)$p.value)
 pvals_naive <- replicate(1000, test_naive(rnorm(100))$p.value)
@@
 # Generate histograms plot
-hist_parametric <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", bins = 20) + geom_histogram(color="gray", fill="white", bins = 20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~histogram, scales = "free_y")
+hist_parametric <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~histogram, scales = "free_y")
 
@@
 ```{r}
-ggsave(filename="hist_normal.pdf", plot=hist_normal, path = "/Users/anthony/Desktop/School Work/Honors Thesis/KS-Test-Thesis/Manuscript")
-ggsave(filename="hist_rounded.pdf", plot=hist_rounded, path = "/Users/anthony/Desktop/School Work/Honors Thesis/KS-Test-Thesis/Manuscript")
-ggsave(filename="hist_correlation.pdf", plot=hist_correlation, path = "/Users/anthony/Desktop/School Work/Honors Thesis/KS-Test-Thesis/Manuscript")
-ggsave(filename="hist_dgof.pdf", plot=hist_dgof, path = "/Users/anthony/Desktop/School Work/Honors Thesis/KS-Test-Thesis/Manuscript")
-ggsave(filename="hist_dgofsim.pdf", plot=hist_dgofsim, path = "/Users/anthony/Desktop/School Work/Honors Thesis/KS-Test-Thesis/Manuscript")
-ggsave(filename="hist_parametric.pdf", plot=hist_parametric, path = "/Users/anthony/Desktop/School Work/Honors Thesis/KS-Test-Thesis/Manuscript")
+ggsave(filename="hist_normal.pdf", plot=hist_normal, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
+ggsave(filename="hist_rounded.pdf", plot=hist_rounded, path = "/Users/anthony//KS-Test-Thesis/Manuscript")
+ggsave(filename="hist_correlation.pdf", plot=hist_correlation, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
+ggsave(filename="hist_dgof.pdf", plot=hist_dgof, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
+ggsave(filename="hist_dgofsim.pdf", plot=hist_dgofsim, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
+ggsave(filename="hist_parametric.pdf", plot=hist_parametric, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
 ```

### 2022-01-31 Code/Simulation.Rmd
Added block bootstrap, working incorrectly

@@
 ```{r}
+# Split sample size into blocks, apply bootstrap onto blocks. Use that as x.b. Fit, stat.b
+nmblk <- function(n, l) {
+    b <- n / l
+    idx <- sample(seq(1, n - l + 1, by = l), b, replace = TRUE)
+    c(outer(0:(l - 1), idx, "+"))
+}
+
+mvblk <- function(n, l) {
+    b <- n / l
+    idx <- sample(1:(n - l + 1), b, replace = TRUE)
+    c(outer(0:(l - 1), idx, "+"))
+}
+
+test_block <- function(ar, B = 1000, l, n) {
+
+  x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)
+  stat <- ks.test(x, "pnorm")$statistic
+  stat.b <- double(B)
+  for (i in 1:B) {
+    x.b <- x[nmblk(n, l)]
+    stat.b[i] <- ks.test(x.b, "pnorm")$statistic
+  }
+
+  p.value <- (sum(stat.b >= stat)) / (B + 1)
+  list(p.value = p.value)
+}
+
+# Naive KS-test to show consequence of fitted parameters
+test_naive_block <- function(ar, n) {
+  x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)
+  p.value <- ks.test(x, "pnorm")$p.value
+  list(p.value = p.value)
+}
+
+# Generate results
+pvals_block <- suppressWarnings(replicate(20, test_block(ar = 0.5, B = 1000, l = 5, n = 100)$p.value))
+pvals_block
+pvals_naive_block <- suppressWarnings(replicate(20, test_naive_block(ar = 0.5, n = 100)$p.value))
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Block", 20), rep("Naive", 20))
+p_values <- c(pvals_block, pvals_naive_block)
+results <- data_frame(p_values, histogram)
+
+# Generate histograms plot
+hist_boot <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~histogram, scales = "free_y")
+hist_boot
+```
+
+```{r}
+# Split sample size into blocks, apply bootstrap onto blocks. Use that as x.b. Fit, stat.b
+# Test parametric bootstrap as a solution to fitting parameters
+test_corr_block <- function(ar, B = 1000, l, n) {
+
+  x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)
+
+  # Store KS statistic from using fitted parameters
+  stat <- cor(x[-1], x[-length(x)])
+
+  # Parametric bootstrap to approximate the null distribution
+  stat.b <- double(B)
+  for (i in 1:B) {
+    x.b <- x[nmblk(n, l)]
+    stat.b[i] <- cor(x.b[-1], x.b[-length(x.b)])
+  }
+
+  list(stat = stat, stat.b = stat.b)
+}
+
+do1rep <- function(ar, B = 1000, l, n) {
+    bt <- test_corr_block(ar, B, l, n)
+    c(bt$stat, sd(bt$stat.b))
+}
+
+corr_block <- suppressWarnings(replicate(50, do1rep(0.5, B = 1000, 10, 100)))
+corr_block
+```
+
+```{r}
 ggsave(filename="hist_normal.pdf", plot=hist_normal, path = "/Users/anthony/KS-Test-Thesis/Manuscript")

### 2022-01-31 Code/Simulation.Rmd
Removed unnecessary functions

@@
 library(tidyverse)
-```
-
-```{r}
-# Testing a simple random normal distribution
-test_normal <- function(n_tests, n_samples) {
-
-  p_values <- c()
-  for(i in 1:n_tests) {
-
-    # Generate random data, perform a KS-test, and store the p-value
-    data <- rnorm(n_samples)
-    p_values[i] <- ks.test(data, "pnorm")$p.value
-  }
-
-  samples_str <- paste("Samples:", n_samples)
-  tests_str <- paste("Replicate tests:", n_tests)
-
-  # Create a master data_frame for p-values
-  tests <- c(rep(tests_str, n_tests))
-  samples <- c(rep(samples_str, n_tests))
-  results <- data_frame(p_values, tests, samples)
-
-  return(results)
-}
-
-# Create the histograms displaying p-values from each test
-test1 <- test_normal(10000, 10)
-test2 <- test_normal(10000, 100)
-test3 <- test_normal(10000, 1000)
-test4 <- test_normal(10, 10000)
-test5 <- test_normal(100, 10000)
-test6 <- test_normal(1000, 10000)
-results <- rbind(test1, test2, test3, test4, test5, test6)
-
-# Generate histograms plot
-hist_normal <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", bins = 20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~tests+samples, scales = "free_y")
 ```
@@
 hist_correlation <- ggplot(ar_results, aes(x = p_value)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~ar, scales = "free_y", ncol = 3)
-```
-
-```{r}
-# Test the xtable package
-test_table <- function(n_tests, n_samples) {
-  results <- numeric(n_tests)
-  for(i in 1:n_tests) {
-    data <- rnorm(n_samples)
-    results[i] <- ks.test(data, "pnorm")$p.value
-  }
-  power_level <- 1 - sum(results < 0.05) / n_tests
-  return(power_level)
-}
-Tests_Samples <- c("10000, 10", "10000, 100", "10000, 1000", "10, 10000", "100, 10000", "1000, 10000")
-Power_Level <- c(0, 0, 0, 0, 0, 0)
-tab <- data.frame(Tests_Samples, Power_Level)
-tab[1, "Power_Level"] <- test_table(10000, 10)
-tab[2, "Power_Level"] <- test_table(10000, 100)
-tab[3, "Power_Level"] <- test_table(10000, 1000)
-tab[4, "Power_Level"] <- test_table(10, 10000)
-tab[5, "Power_Level"] <- test_table(100, 10000)
-tab[6, "Power_Level"] <- test_table(1000, 10000)
-tab <- xtable(tab)
-tab
 ```

### 2022-02-11 Code/Simulation.Rmd
Add noisy function, test for KSgeneral

@@
 library(tidyverse)
-```
-
-```{r}
-# Test to show that rounding changes the power of the test
-test_rounded <- function(n_tests, n_samples, digits) {
-
-  p_values <- c()
-  for(i in 1:n_tests) {
-
-    # Generate random rounded data, perform a KS-test, and store the p-value
-    data <- round(rnorm(n_samples), digits)
-    p_values[i] <- ks.test(data, "pnorm")$p.value
-  }
-
-  return(p_values)
-}
-
-# Create the histograms displaying p-values from each test
-hist1 <- suppressWarnings(test_rounded(10000, 100, 4))
-hist2 <- suppressWarnings(test_rounded(10000, 100, 3))
-hist3 <- suppressWarnings(test_rounded(10000, 100, 2))
-hist4 <- suppressWarnings(test_rounded(10000, 100, 1))
-
-# Create a master data_frame with all the results
-histogram <- c(rep(".0001", 10000), rep(".001", 10000), rep(".01", 10000), rep(".1", 10000))
-p_values <- c(hist1, hist2, hist3, hist4)
-results <- data_frame(p_values, histogram)
-
-# Generate histograms plot
-hist_rounded <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value") + facet_wrap(.~histogram, scales = "free_y")
-```
-
-```{r}
-# Test to show that autocorrelation changes the power of the test
-test_correlation <- function(n_tests, ars) {
-
-  # Create a master data_frame for p-values
-  columns <- c("p_value", "ar")
-  ar_results <- data.frame(matrix(ncol = 2, nrow = 0))
-  colnames(ar_results) <- columns
-
-  # For AR coefficients from -0.5 to 0.5
-  for(i in 1:length(ars)) {
-
-    for(j in 1:n_tests) {
-
-      # Generate random correlated data, perform a KS-test, and store the p-value
-      data <- arima.sim(model = list(ar = ars[i]), rand.gen = rnorm, sd = sqrt(1-ars[i]^2), n = 100)
-      ar_results <- add_row(ar_results, p_value = ks.test(data, "pnorm")$p.value, ar = ars[i])
-    }
-  }
-
-  return(ar_results)
-}
-
- # Set AR coefficients and generate results
-ars <- seq(-0.5, 0.5, by = 0.1)
-ar_results <- suppressWarnings(test_correlation(1000, ars))
-
-# Generate histograms plot
-hist_correlation <- ggplot(ar_results, aes(x = p_value)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~ar, scales = "free_y", ncol = 3)
-```
-
-```{r}
-# Test the dgof package as a solution to rounded data with 30 or under samples
-test_dgof <- function(n_tests, n_samples, digits, B = 100) {
-
-  results1 <- c()
-  results2 <- c()
-  results3 <- c()
-
-  # Create the rounded normal step function
-  left <- -4-0.1^digits
-  y <- pnorm(seq(left, 4, by = 0.1^digits))
-  sfun  <- stepfun(seq(-4, 4, by = 0.1^digits), y)
-
-  for (i in 1:n_tests) {
-
-    if (i%%100 == 0) {
-      cat(i, " ")
-    }
-
-    # Generate random rounded data, perform 3 KS-tests, and store the p-values
-    # 1. Using the rounded normal step function
-    # 2. Using the naive continuous standard normal function
-    data <- round(rnorm(n_samples), digits)
-    results1[i] <- ks.test(data, sfun)$p.value
-    results2[i] <- ks.test(data, "pnorm")$p.value
-  }
-
-  # Create a master data_frame for p-values
-  test <- c(rep("dgof", n_tests), rep("Naive", n_tests))
-  digits <- c(rep(.1^digits, 2*n_tests))
-  p_values <- c(results1, results2)
-  results <- data_frame(p_values, test, digits)
-
-  return(results)
-}
-
-# Create the histograms displaying p-values from each test
-test1 <- suppressWarnings(test_dgof(10000, 100, 3))
-test2 <- suppressWarnings(test_dgof(10000, 100, 2))
-test3 <- suppressWarnings(test_dgof(10000, 100, 1))
-results <- rbind(test1, test2, test3)
-
-# Generate histograms plot
-hist_dgof <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, ncol = 3, scales = "free_y")
-hist_dgof
-```
-
-```{r}
-# Test the dgof package's simulate p-values as a solution to rounded data with over 30 samples
-test_dgofsimulate <- function(n_tests, n_samples, digits, B = 100) {
-
-  # Results lists
-  results1 <- c()
-  results2 <- c()
-
-  # Create the rounded normal step function
-  left <- -4-0.1^digits
-  y <- pnorm(seq(left, 4, by = 0.1^digits))
-  sfun  <- stepfun(seq(-4, 4, by = 0.1^digits), y)
-
-  for (i in 1:n_tests) {
-
-    # Generate random rounded data, perform 2 KS-tests, and store the p-values
-    # 1. Using the rounded normal step function
-    # 2. Using the rounded normal step function with simulated p-values
-    test <- round(rnorm(n_samples), digits)
-    results1[i] <- ks.test(test, sfun)$p.value
-    results2[i] <- ks.test(test, sfun, simulate.p.value = TRUE, B = B)$p.value
-  }
-
-  # Create a master data_frame for p-values
-  test <- c(rep("dgof", n_tests), rep("Simulated", n_tests))
-  digits <- c(rep(.1^digits, 2*n_tests))
-  p_values <- c(results1, results2)
-  results <- data_frame(p_values, test, digits)
-
-  return(results)
-}
-
-# Create the histograms displaying p-values from each test
-test1 <- suppressWarnings(test_dgofsimulate(1000, 100, 1, 100))
-test2 <- suppressWarnings(test_dgofsimulate(1000, 100, 2, 100))
-results <- rbind(test1, test2)
-
-# Generate histograms plot
-hist_dgofsim <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, scales = "free_y")
 ```
@@
 
-  list(statistics = stat, p.value = p.value, 
-       estimate = c(mean = mu, sd = sigma),
-       stat.sim = stat.b)
+  list(p.value = p.value)
 }
@@
 ```{r}
+noisy <- function(x) {
+  v <- var(x)
+  n <- length(x)
+  noise <- rnorm(n, mean = 0, sd = 1/100*v)
+  return(x + noise)
+}
+
+ar <- 0.5
+n <- 10
+x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)
+x
+noisy(x)
+```
+
+```{r}
 # Split sample size into blocks, apply bootstrap onto blocks. Use that as x.b. Fit, stat.b
@@
 
-test_block <- function(ar, B = 1000, l, n) {
+test_block <- function(x, B = 1000, l) {
 
-  x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)
   stat <- ks.test(x, "pnorm")$statistic
+
+  n <- length(x)
   stat.b <- double(B)
   for (i in 1:B) {
-    x.b <- x[nmblk(n, l)]
+    x.b <- noisy(x[mvblk(n, l)])
+    # add small noise compared to variance of x. sd of noise is 1%, or 1/10%, of sd of regular variance
     stat.b[i] <- ks.test(x.b, "pnorm")$statistic
   }
+  p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
+  list(p.value = p.value)
 
-  p.value <- (sum(stat.b >= stat)) / (B + 1)
-  list(p.value = p.value)
 }
 
-# Naive KS-test to show consequence of fitted parameters
 test_naive_block <- function(ar, n) {
@@
 
-# Generate results
-pvals_block <- suppressWarnings(replicate(20, test_block(ar = 0.5, B = 1000, l = 5, n = 100)$p.value))
-pvals_block
-pvals_naive_block <- suppressWarnings(replicate(20, test_naive_block(ar = 0.5, n = 100)$p.value))
+ptm <- proc.time()
+
+ar = 0.5
+n = 100
+n_tests = 1000
+l = 10
+pvals_boot <- replicate(n_tests, test_block(arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n), B = 1000, l = l)$p.value)
+pvals_naive_block <- replicate(n_tests, test_naive_block(ar = ar, n = n)$p.value)
 
 # Create a master data_frame with all the results
-histogram <- c(rep("Block", 20), rep("Naive", 20))
-p_values <- c(pvals_block, pvals_naive_block)
+histogram <- c(rep("Boot", n_tests), rep("Naive", n_tests))
+p_values <- c(pvals_boot, pvals_naive_block)
 results <- data_frame(p_values, histogram)
@@
 hist_boot
+
+proc.time() - ptm
 ```
 
+```{r}
+blkboot <- function(tseries, statistic, R, l) {
+  n <- length(tseries)
+
+  stat <- statistic(tseries)
+
+  nm.stat <- replicate(R, statistic(noisy(tseries[nmblk(n, l)])))
+  mv.stat <- replicate(R, statistic(noisy(tseries[mvblk(n, l)])))
+
+  nmp.value <- (sum(nm.stat >= stat) + 0.5) / (R + 1)
+  mvp.value <- (sum(mv.stat >= stat) + 0.5) / (R + 1)
+
+  list(stat = stat, nmp.value = nmp.value, mvp.value = mvp.value)
+}
+
+ar1 <- function(x) ks.test(x, "pnorm")$statistic
+
+do1rep <- function(n, ar, l) {
+  x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)
+  bt <- blkboot(x, ar1, R = 1000, l)
+  list(stat = bt$stat, nmp.value = bt$nmp.value, mvp.value = bt$mvp.value)
+}
+
+ptm <- proc.time()
+
+n <- 100
+ar <- 0.5
+l = 5
+n_tests <- 1000
+
+pvals_boot2 <- replicate(n_tests, do1rep(n, ar, l)$mvp.value)
+pvals_naive_block <- replicate(n_tests, test_naive_block(ar = ar, n = n)$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Boot", n_tests), rep("Naive", n_tests))
+p_values <- c(pvals_boot2, pvals_naive_block)
+results <- data_frame(p_values, histogram)
+
+# Generate histograms plot
+hist_boot2 <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~histogram, scales = "free_y")
+hist_boot2
+
+proc.time() - ptm
+```
 ```{r}
@@
 ```{r}
-ggsave(filename="hist_normal.pdf", plot=hist_normal, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
-ggsave(filename="hist_rounded.pdf", plot=hist_rounded, path = "/Users/anthony//KS-Test-Thesis/Manuscript")
-ggsave(filename="hist_correlation.pdf", plot=hist_correlation, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
-ggsave(filename="hist_dgof.pdf", plot=hist_dgof, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
-ggsave(filename="hist_dgofsim.pdf", plot=hist_dgofsim, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
-ggsave(filename="hist_parametric.pdf", plot=hist_parametric, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
+library(boot)
+
+fun <- function(x) {
+  x <- noisy(x)
+  p.value <- ks.test(x, "pnorm")$p.value
+  return(p.value)
+}
+
+test <- replicate(25, tsboot(arima.sim(list(ar = 0.5), rand.gen = rnorm, sd = sqrt(1-0.5^2), 100), fun, 1000, sim = "fixed", l = 5))
+hist(test[,1]$t)
 ```
+
+```{r}
+# Test to show that rounding changes the power of the test
+test_rounded <- function(n_tests, n_samples, digits) {
+
+  p_values <- c()
+  for(i in 1:n_tests) {
+
+    # Generate random rounded data, perform a KS-test, and store the p-value
+    data <- round(rnorm(n_samples), digits)
+    p_values[i] <- ks.test(data, "pnorm")$p.value
+  }
+
+  return(p_values)
+}
+
+# Create the histograms displaying p-values from each test
+hist1 <- suppressWarnings(test_rounded(1000, 100, 2))
+hist2 <- suppressWarnings(test_rounded(1000, 100, 1))
+
+# Create a master data_frame with all the results
+histogram <- c(rep(".01", 1000), rep(".1", 1000))
+p_values <- c(hist1, hist2)
+results <- data_frame(p_values, histogram)
+
+# Generate histograms plot
+hist_rounded <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~histogram, scales = "free_y")
+```
+
+```{r}
+# Test the KSgeneral package as a solution to rounded data
+test_general <- function(n_tests, n_samples, digits, B = 100) {
+
+  results1 <- c()
+  results2 <- c()
+
+  # Create the rounded normal step function
+  left <- -4-0.1^digits
+  y <- pnorm(seq(left, 4, by = 0.1^digits))
+  sfun  <- stepfun(seq(-4, 4, by = 0.1^digits), y)
+
+  for (i in 1:n_tests) {
+
+    # Generate random rounded data, perform 3 KS-tests, and store the p-values
+    # 1. Using the rounded normal step function
+    # 2. Using the naive continuous standard normal function
+    data <- round(rnorm(n_samples), digits)
+    results1[i] <- KSgeneral::disc_ks_test(data, sfun, exact = TRUE)$p.value
+    results2[i] <- dgof::ks.test(data, "pnorm")$p.value
+
+  }
+
+  # Create a master data_frame for p-values
+  test <- c(rep("KSgeneral", n_tests), rep("Naive", n_tests))
+  digits <- c(rep(.1^digits, 2*n_tests))
+  p_values <- c(results1, results2)
+  results <- data_frame(p_values, test, digits)
+
+  return(results)
+}
+
+# Create the histograms displaying p-values from each test
+test1 <- suppressWarnings(test_general(1000, 100, 2))
+test2 <- suppressWarnings(test_general(1000, 100, 1))
+results <- rbind(test1, test2)
+
+# Generate histograms plot
+hist_general <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, ncol = 2, scales = "free_y")
+hist_general
+```
+
+```{r}
+# Test the dgof package as a solution to rounded data with 30 or under samples
+test_dgof <- function(n_tests, n_samples, digits, B = 100) {
+
+  results1 <- c()
+  results2 <- c()
+
+  # Create the rounded normal step function
+  left <- -4-0.1^digits
+  y <- pnorm(seq(left, 4, by = 0.1^digits))
+  sfun  <- stepfun(seq(-4, 4, by = 0.1^digits), y)
+
+  for (i in 1:n_tests) {
+
+    # Generate random rounded data, perform 3 KS-tests, and store the p-values
+    # 1. Using the rounded normal step function
+    # 2. Using the naive continuous standard normal function
+    data <- round(rnorm(n_samples), digits)
+    results1[i] <- ks.test(data, sfun)$p.value
+    results2[i] <- ks.test(data, "pnorm")$p.value
+
+  }
+
+  # Create a master data_frame for p-values
+  test <- c(rep("dgof", n_tests), rep("Naive", n_tests))
+  digits <- c(rep(.1^digits, 2*n_tests))
+  p_values <- c(results1, results2)
+  results <- data_frame(p_values, test, digits)
+
+  return(results)
+}
+
+# Create the histograms displaying p-values from each test
+test1 <- suppressWarnings(test_dgof(1000, 100, 2))
+test2 <- suppressWarnings(test_dgof(1000, 100, 1))
+results <- rbind(test1, test2)
+
+# Generate histograms plot
+hist_dgof <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, ncol = 2, scales = "free_y")
+```
+
+```{r}
+# Test the dgof package's simulate p-values as a solution to rounded data with over 30 samples
+test_dgofsimulate <- function(n_tests, n_samples, digits, B = 100) {
+
+  # Results lists
+  results1 <- c()
+  results2 <- c()
+
+  # Create the rounded normal step function
+  left <- -4-0.1^digits
+  y <- pnorm(seq(left, 4, by = 0.1^digits))
+  sfun  <- stepfun(seq(-4, 4, by = 0.1^digits), y)
+
+  for (i in 1:n_tests) {
+    cat(i, "\n")
+    # Generate random rounded data, perform 2 KS-tests, and store the p-values
+    # 1. Using the rounded normal step function
+    # 2. Using the rounded normal step function with simulated p-values
+    test <- round(rnorm(n_samples), digits)
+    results1[i] <- ks.test(test, sfun)$p.value
+    results2[i] <- ks.test(test, sfun, simulate.p.value = TRUE, B = B)$p.value
+  }
+
+  # Create a master data_frame for p-values
+  test <- c(rep("dgof", n_tests), rep("Simulated", n_tests))
+  digits <- c(rep(.1^digits, 2*n_tests))
+  p_values <- c(results1, results2)
+  results <- data_frame(p_values, test, digits)
+
+  return(results)
+}
+
+# Create the histograms displaying p-values from each test
+test1 <- suppressWarnings(test_dgofsimulate(1000, 100, 1, 100))
+test2 <- suppressWarnings(test_dgofsimulate(1000, 100, 2, 100))
+results <- rbind(test1, test2)
+
+# Generate histograms plot
+hist_dgofsim <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, scales = "free_y")
+```
+
+```{r}
+# Test to show that autocorrelation changes the power of the test
+test_correlation <- function(n_tests, ars) {
+
+  # Create a master data_frame for p-values
+  columns <- c("p_value", "ar")
+  ar_results <- data.frame(matrix(ncol = 2, nrow = 0))
+  colnames(ar_results) <- columns
+
+  # For AR coefficients from -0.5 to 0.5
+  for(i in 1:length(ars)) {
+
+    for(j in 1:n_tests) {
+
+      # Generate random correlated data, perform a KS-test, and store the p-value
+      data <- arima.sim(model = list(ar = ars[i]), rand.gen = rnorm, sd = sqrt(1-ars[i]^2), n = 100)
+      ar_results <- add_row(ar_results, p_value = ks.test(data, "pnorm")$p.value, ar = round(ars[i], 1))
+    }
+  }
+
+  return(ar_results)
+}
+
+ # Set AR coefficients and generate results
+ars <- seq(-0.3, 0.3, by = 0.1)
+ar_results <- test_correlation(1000, ars)
+
+# Generate histograms plot
+hist_correlation <- ggplot(ar_results, aes(x = p_value)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~ar, scales = "free_y", ncol = 4)
+```
+
+```{r}
+ggsave(filename="hist_parametric.pdf", plot=hist_parametric, path = "../Manuscript", width = 4, height = 2, units = "in")
+ggsave(filename="hist_rounded.pdf", plot=hist_rounded, path = "../Manuscript", width = 4, height = 2, units = "in")
+ggsave(filename="hist_dgof.pdf", plot=hist_dgof, path = "../Manuscript", width = 4, height = 4, units = "in")
+ggsave(filename="hist_dgofsim.pdf", plot=hist_dgofsim, path = "../Manuscript", width = 4, height = 4, units = "in")
+ggsave(filename="hist_correlation.pdf", plot=hist_correlation, path = "../Manuscript", width = 8, height = 4, units = "in")
+```

### 2022-02-11 Manuscript/manuscript.tex
Updated manuscript in fitted parameters and rounded

--- 2022-01-24 Manuscript/manuscript.tex
@@
 
+\makeatletter
+\newcommand*{\Xbar}{}%
+\DeclareRobustCommand*{\Xbar}{%
+  \mathpalette\@Xbar{}%
+}
+\newcommand*{\@Xbar}[2]{%
+  % #1: math style
+  % #2: unused (empty)
+  \sbox0{$#1\mathrm{X}\m@th$}%
+  \sbox2{$#1X\m@th$}%
+  \rlap{%
+    \hbox to\wd2{%
+      \hfill
+      $\overline{%
+        \vrule width 0pt height\ht0 %
+        \kern\wd0 %
+      }$%
+    }%
+  }%
+  \copy2 %
+}
+\makeatother
+
 \title{Survey of Misuses of the Kolmogorov–Smirnov-Test}
@@
 \begin{abstract}
-The Kolmogorov–Smirnov (KS) test is one the most popular goodness-of-fit tests for comparing a sample with a hypothesized parametric distribution.
+The Kolmogorov-Smirnov (KS) test is one the most popular goodness-of-fit tests for comparing a sample with a hypothesized parametric distribution.
 Nevertheless, it has often been misused.
@@
 Given a sample of n observations, let $S_{n}(x)$ be the empirical cumulative distribution and $F(x)$ be the population cumulative distribution.
-The K-S statistic is defined by: \[d = max(\lvert F(x)-S_{n}(x) \rvert)\] If the value of $d$ exceeds the critical value given by the table, the null hypothesis that the observations are from a specified distribution is rejected.
+The K-S statistic is defined by: \[d = max(\lvert F(x)-S_{n}(x) \rvert)\] The null hypothesis is that the observations are from the specified distribution $F(x)$, and the alternate hypothesis is that the data is not from $F(x)$.
+If the value of $d$ exceeds the critical value given by a table, the null hypothesis is rejected.
 
 However, the test is often misused.
-The standard one-sample K-S test applies to independent, continuous data with a hypothesized distribution that is completely satisfied.
+The standard one-sample K-S test applies to independent, continuous data with a hypothesized distribution that is completely specified.
 Often in literature, the test is applied to dependent, discrete, or rounded data, with hypothesized distributions containing estimated parameters.
@@
 Throughout this paper, the cumulative distribution $F(x)$ is standard normal.
-
-To begin, a simple demonstration is performed to show the impact of sample size and replicate tests.
-For $n$ in $[10, 100, 1000]$, a random standard normal distributions were generated and K-S tests were performed.
-With the hypothesized distribution of standard normal, the histograms in Figure 1 show that the sample size has little effect on the distribution of P-values.
-
-\begin{figure}[!ht]
-  \centering
-  \includegraphics[width=0.8\linewidth]{hist_normal}
-  \caption{Histograms of impact of sample size and number of tests on P-value.}
-  \label{fig:hist_normal}
-\end{figure}
 
@@
 The K-S test shows significant issues in the case of fitted parameters.
+As previously mentioned, one assumption of the K-S test is that the hypothesized distribution is completely specified.
+However, the procedure is sometimes performed where the population cumulative distribution $F(x)$ has parameters $\mu=\Xbar$, the sample mean, and $\sigma^2=s^2$, the sample variance \citep{Lilliefors}.
+\citet{Lilliefors} also shows that using the standard table when values of the mean and standard deviation are estimated obtains extremely conservative results.
+
+To resolve this problem, parametric bootstrap can be performed.
+The parameters of the null distribution are approximated from the bootstrap.
+Figure~\ref{fig:hist_parametric} displays the results of $1000$ replicate tests using the standard normal distribution with sample size $n=100$.
+In each parametric test, $1000$ bootstrap samples are obtained and the corresponding p-value of the K-S test is calculated.
+In the naive case, K-S tests are performed with fitted parameters.
 
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{hist_parametric}
-  \caption{Histograms of P-values with parametric bootstrap.}
+  \includegraphics[scale=0.7]{hist_parametric}
+  \caption{Histograms demonstrating fitted parameters.}
   \label{fig:hist_parametric}
 \end{figure}
+
+Since the data is generated from a standard normal distributions with seemingly all assumptions met, a uniform distribution of $U(0,1)$ is expected for the p-values.
+The naive histogram shows that when the parameters are estimated there is notable deviation from the uniform distribution.
+However, through parametric bootstrap of the parameters the p-values appear to retain a uniform distribution.
 
@@
 
-The K-S test shows significant issues in the case of rounding data.
+Another assumption of the K-S test is that it applies to continuous data.
+This can be easily violated by performing a level of rounding on the data.
+Rounding causes the data to become discrete, and the K-S test can be shown to no longer apply.
+To demonstrate this, simulations were conducted at varying levels of rounding.
+A random sample of size $100$ was collected from the standard normal distribution and subsequently rounded to the degrees of $.01$ and  $.1$.
+This simulation was replicated $1000$ times for each rounding level and the results are shown in Figure~\ref{fig:hist_rounded}.
 
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{hist_rounded}
+  \includegraphics[scale=0.7]{hist_rounded}
   \caption{Histograms of P-values with rounded data.}
@@
 
+As mentioned before, the expected distribution of p-values is $U(0,1)$.
+For rounding to the hundreths, though the distribution appears uniform it is still not recommended to use the basic K-S test due to ties in the data.
+The issue is apparent when rounding to the tenths, as the distribution of p-values does not hold a standard uniform distribution and the test no longer applies.
+This simulation shows that rounding can have a serious impact on the power of the K-S test and should be avoided.
+
+There are some solutions in the case that a discrete distribution is in question.
+The chi-squared test is another goodness-of-fit test that can be applied to discrete distributions \citep{Massey}.
+However, the standard K-S test holds various advantages over it.
+In small samples, \citet{Massey} explains that the chi-squared test loses information and validity due to the grouping performed, while the K-S test treats individual observations separately.
+\citet{Massey} additionally notes that the K-S test generally appears to be the more powerful test regardless of sample size.
+
+In addition, a proposed revision of the K-S test can be found in \citet{dgof}.\citet{dgof} provides a revision to R's `ks-test()` function for the case that the null distribution is discrete.
+
 \begin{figure}[!ht]
   \centering
-  \includegraphics[width=0.8\linewidth]{hist_dgof}
+  \includegraphics[scale=0.7]{hist_dgof}
   \caption{Histograms of P-values with dgof package.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{hist_dgofsim}
+  \includegraphics[scale=0.7]{hist_dgofsim}
   \caption{Histograms of P-values when simulating p-value.}
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{hist_correlation}
+  \includegraphics[scale=0.7]{hist_correlation}
   \caption{Histograms of P-values with correlated data.}

### 2022-02-25 Manuscript/manuscript.tex
updated manuscript pdfs and citations

@@
 
-\begin{figure}[!ht]
+\begin{figure}[tbp]
   \centering
-  \includegraphics[scale=0.7]{hist_parametric}
+  \includegraphics{hist_parametric}
   \caption{Histograms demonstrating fitted parameters.}
@@
 
-\begin{figure}[!ht]
+\begin{figure}[tbp]
   \centering
-  \includegraphics[scale=0.7]{hist_rounded}
+  \includegraphics{hist_rounded}
   \caption{Histograms of P-values with rounded data.}
@@
 
-In addition, a proposed revision of the K-S test can be found in \citet{dgof}.\citet{dgof} provides a revision to R's `ks-test()` function for the case that the null distribution is discrete.
+In addition, a proposed revision of the K-S test can be found in \citet{dgof}.\citet{dgof} provides a revision to R's `ks.test()` function for the case that the null distribution is discrete.
 
-\begin{figure}[!ht]
+\begin{figure}[tbp]
   \centering
-  \includegraphics[scale=0.7]{hist_dgof}
-  \caption{Histograms of P-values with dgof package.}
-  \label{fig:hist_dgof}
-\end{figure}
-
-\begin{figure}[!ht]
-  \centering
-  \includegraphics[scale=0.7]{hist_dgofsim}
-  \caption{Histograms of P-values when simulating p-value.}
-  \label{fig:hist_dgofsim}
+  \includegraphics{hist_general}
+  \caption{Histograms of P-values with KSGeneral and dgof packages.}
+  \label{fig:hist_general}
 \end{figure}
@@
 
-\begin{figure}[!ht]
+\begin{figure}[tbp]
   \centering
-  \includegraphics[scale=0.7]{hist_correlation}
+  \includegraphics{hist_correlation}
   \caption{Histograms of P-values with correlated data.}
   \label{fig:hist_correlation}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics{hist_block}
+  \caption{Histograms of P-values when using block bootstrap.}
+  \label{fig:hist_block}
 \end{figure}
@@
 \citet{Lilliefors}
-\citet{dgof}
+\citet{Arnold}
 \citet{Conover}
 \citet{Gleser}
+\citet{Babu}
+\citet{Butorina}
+\citet{Racine}
+\citet{Wang}
+\citet{Capasso}
+\citet{Dimitrova}
 

### 2022-02-25 Code/Simulation.Rmd
updated code with discrete plots combined and other changes

--- 2022-01-31 Code/Simulation.Rmd
@@
 library(tidyverse)
+library(KSgeneral)
+library(snpar)
 ```
 
-```{r}
-# Test to show that rounding changes the power of the test
-test_rounded <- function(n_tests, n_samples, digits) {
-
-  p_values <- c()
-  for(i in 1:n_tests) {
-
-    # Generate random rounded data, perform a KS-test, and store the p-value
-    data <- round(rnorm(n_samples), digits)
-    p_values[i] <- ks.test(data, "pnorm")$p.value
-  }
-
-  return(p_values)
-}
-
-# Create the histograms displaying p-values from each test
-hist1 <- suppressWarnings(test_rounded(10000, 100, 4))
-hist2 <- suppressWarnings(test_rounded(10000, 100, 3))
-hist3 <- suppressWarnings(test_rounded(10000, 100, 2))
-hist4 <- suppressWarnings(test_rounded(10000, 100, 1))
-
-# Create a master data_frame with all the results
-histogram <- c(rep(".0001", 10000), rep(".001", 10000), rep(".01", 10000), rep(".1", 10000))
-p_values <- c(hist1, hist2, hist3, hist4)
-results <- data_frame(p_values, histogram)
-
-# Generate histograms plot
-hist_rounded <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value") + facet_wrap(.~histogram, scales = "free_y")
-```
-
-```{r}
-# Test to show that autocorrelation changes the power of the test
-test_correlation <- function(n_tests, ars) {
-
-  # Create a master data_frame for p-values
-  columns <- c("p_value", "ar")
-  ar_results <- data.frame(matrix(ncol = 2, nrow = 0))
-  colnames(ar_results) <- columns
-
-  # For AR coefficients from -0.5 to 0.5
-  for(i in 1:length(ars)) {
-
-    for(j in 1:n_tests) {
-
-      # Generate random correlated data, perform a KS-test, and store the p-value
-      data <- arima.sim(model = list(ar = ars[i]), rand.gen = rnorm, sd = sqrt(1-ars[i]^2), n = 100)
-      ar_results <- add_row(ar_results, p_value = ks.test(data, "pnorm")$p.value, ar = ars[i])
-    }
-  }
-
-  return(ar_results)
-}
-
- # Set AR coefficients and generate results
-ars <- seq(-0.5, 0.5, by = 0.1)
-ar_results <- suppressWarnings(test_correlation(1000, ars))
-
-# Generate histograms plot
-hist_correlation <- ggplot(ar_results, aes(x = p_value)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~ar, scales = "free_y", ncol = 3)
-```
-
-```{r}
-# Test the dgof package as a solution to rounded data with 30 or under samples
-test_dgof <- function(n_tests, n_samples, digits, B = 100) {
-
-  results1 <- c()
-  results2 <- c()
-  results3 <- c()
-
-  # Create the rounded normal step function
-  left <- -4-0.1^digits
-  y <- pnorm(seq(left, 4, by = 0.1^digits))
-  sfun  <- stepfun(seq(-4, 4, by = 0.1^digits), y)
-
-  for (i in 1:n_tests) {
-
-    if (i%%100 == 0) {
-      cat(i, " ")
-    }
-
-    # Generate random rounded data, perform 3 KS-tests, and store the p-values
-    # 1. Using the rounded normal step function
-    # 2. Using the naive continuous standard normal function
-    data <- round(rnorm(n_samples), digits)
-    results1[i] <- ks.test(data, sfun)$p.value
-    results2[i] <- ks.test(data, "pnorm")$p.value
-  }
-
-  # Create a master data_frame for p-values
-  test <- c(rep("dgof", n_tests), rep("Naive", n_tests))
-  digits <- c(rep(.1^digits, 2*n_tests))
-  p_values <- c(results1, results2)
-  results <- data_frame(p_values, test, digits)
-
-  return(results)
-}
-
-# Create the histograms displaying p-values from each test
-test1 <- suppressWarnings(test_dgof(10000, 100, 3))
-test2 <- suppressWarnings(test_dgof(10000, 100, 2))
-test3 <- suppressWarnings(test_dgof(10000, 100, 1))
-results <- rbind(test1, test2, test3)
-
-# Generate histograms plot
-hist_dgof <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, ncol = 3, scales = "free_y")
-hist_dgof
-```
-
-```{r}
-# Test the dgof package's simulate p-values as a solution to rounded data with over 30 samples
-test_dgofsimulate <- function(n_tests, n_samples, digits, B = 100) {
-
-  # Results lists
-  results1 <- c()
-  results2 <- c()
-
-  # Create the rounded normal step function
-  left <- -4-0.1^digits
-  y <- pnorm(seq(left, 4, by = 0.1^digits))
-  sfun  <- stepfun(seq(-4, 4, by = 0.1^digits), y)
-
-  for (i in 1:n_tests) {
-
-    # Generate random rounded data, perform 2 KS-tests, and store the p-values
-    # 1. Using the rounded normal step function
-    # 2. Using the rounded normal step function with simulated p-values
-    test <- round(rnorm(n_samples), digits)
-    results1[i] <- ks.test(test, sfun)$p.value
-    results2[i] <- ks.test(test, sfun, simulate.p.value = TRUE, B = B)$p.value
-  }
-
-  # Create a master data_frame for p-values
-  test <- c(rep("dgof", n_tests), rep("Simulated", n_tests))
-  digits <- c(rep(.1^digits, 2*n_tests))
-  p_values <- c(results1, results2)
-  results <- data_frame(p_values, test, digits)
-
-  return(results)
-}
-
-# Create the histograms displaying p-values from each test
-test1 <- suppressWarnings(test_dgofsimulate(1000, 100, 1, 100))
-test2 <- suppressWarnings(test_dgofsimulate(1000, 100, 2, 100))
-results <- rbind(test1, test2)
-
-# Generate histograms plot
-hist_dgofsim <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~test+digits, scales = "free_y")
-```
-
-```{r}
-# Split sample size into blocks, apply bootstrap onto blocks. Use that as x.b. Fit, stat.b
+```{r hist_parametric}
 # Test parametric bootstrap as a solution to fitting parameters
@@
     stat.b[i] <- ks.test(x.b, "pnorm", mu.b, sigma.b)$statistic
+    # write own ks test statistic formula here
+    # is.character(y)
   }
@@
 # Generate results
-pvals_parametric <- replicate(1000, test_parametric(rnorm(100), B = 1000)$p.value)
-pvals_naive <- replicate(1000, test_naive(rnorm(100))$p.value)
+pvals_parametric <- replicate(100, test_parametric(rnorm(100), B = 1000)$p.value)
+pvals_naive <- replicate(100, test_naive(rnorm(100))$p.value)
 
 # Create a master data_frame with all the results
-histogram <- c(rep("Parametric", 1000), rep("Naive", 1000))
+histogram <- c(rep("Parametric", 100), rep("Naive", 100))
 p_values <- c(pvals_parametric, pvals_naive)
@@
 # Generate histograms plot
-hist_parametric <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~histogram, scales = "free_y")
+hist_parametric <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
 
-# Run KS-tests to check for uniform distribution
-ks.test(pvals_parametric, "punif")
-ks.test(pvals_naive, "punif")
+# Save the histogram figure
+ggsave(filename = "hist_parametric.pdf", plot = hist_parametric, path = "../Manuscript", height = 2.1, width = 6)
 ```
 
-```{r}
-# Split sample size into blocks, apply bootstrap onto blocks. Use that as x.b. Fit, stat.b
+```{r block functions}
+# Functions supporting block bootstrap
+
+# Add small noise to data
+add_noise <- function(x) {
+
+  # Grab variance and length
+  v <- var(x)
+  n <- length(x)
+
+  # Generate noise where standard deviation is 1% of variance
+  noise <- rnorm(n, mean = 0, sd = 1/100*v)
+
+  # Return jittered data
+  return(x + noise)
+}
+
+# Non-moving block generation
 nmblk <- function(n, l) {
+
+  # Number of blocks
   b <- n / l
+
+  # Create non-moving block indices
   idx <- sample(seq(1, n - l + 1, by = l), b, replace = TRUE)
+
+  # Return indices
   c(outer(0:(l - 1), idx, "+"))
@@
 
+# Moving block generation
 mvblk <- function(n, l) {
+
+  # Number of blocks
   b <- n / l
+
+  # Create moving block indices
   idx <- sample(1:(n - l + 1), b, replace = TRUE)
+
+  # Return indices
   c(outer(0:(l - 1), idx, "+"))
 }
+```
 
-test_block <- function(ar, B = 1000, l, n) {
+```{r hist_block}
+# Block bootstrap function
+blkboot <- function(tseries, statistic, R, l) {
 
-  x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)
-  stat <- ks.test(x, "pnorm")$statistic
-  stat.b <- double(B)
-  for (i in 1:B) {
-    x.b <- x[nmblk(n, l)]
-    stat.b[i] <- ks.test(x.b, "pnorm")$statistic
+  n <- length(tseries)
+
+  # Gather observed statistic
+  stat <- statistic(tseries)
+
+  # Replicate block bootstrap samples with noise
+  nm.stat <- replicate(R, statistic(add_noise(tseries[nmblk(n, l)])))
+  mv.stat <- replicate(R, statistic(add_noise(tseries[mvblk(n, l)])))
+
+  # Calculate p-values
+  nmp.value <- (sum(nm.stat >= stat) + 0.5) / (R + 1)
+  mvp.value <- (sum(mv.stat >= stat) + 0.5) / (R + 1)
+
+  list(stat = stat, nmp.value = nmp.value, mvp.value = mvp.value)
 }
 
-  p.value <- (sum(stat.b >= stat)) / (B + 1)
+# Calculate ks-statistic
+ks_statistic <- function(x) ks.test(x, "pnorm")$statistic
+
+# 1 test
+do1rep <- function(n, ar, l) {
+
+  # Create correlated data
+  x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)
+
+  # Apply block bootstrap
+  bt <- blkboot(x, ks_statistic, R = 1000, l)
+
+  list(stat = bt$stat, nmp.value = bt$nmp.value, mvp.value = bt$mvp.value)
+}
+
+# Naive example
+test_naive_block <- function(ar, n) {
+
+  # Generate correlated data
+  x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)
+
+  # Gather p-value
+  p.value <- ks.test(x, "pnorm")$p.value
+
   list(p.value = p.value)
@@
 
-# Naive KS-test to show consequence of fitted parameters
-test_naive_block <- function(ar, n) {
-  x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)
-  p.value <- ks.test(x, "pnorm")$p.value
-  list(p.value = p.value)
-}
+ptm <- proc.time()
+
+n <- 100
+ar <- 0.5
+l = 5
+n_tests <- 100
 
 # Generate results
-pvals_block <- suppressWarnings(replicate(20, test_block(ar = 0.5, B = 1000, l = 5, n = 100)$p.value))
-pvals_block
-pvals_naive_block <- suppressWarnings(replicate(20, test_naive_block(ar = 0.5, n = 100)$p.value))
+pvals_block <- replicate(n_tests, do1rep(n, ar, l)$mvp.value)
+pvals_naive_block <- replicate(n_tests, test_naive_block(ar = ar, n = n)$p.value)
 
 # Create a master data_frame with all the results
-histogram <- c(rep("Block", 20), rep("Naive", 20))
+histogram <- c(rep("Block", n_tests), rep("Naive", n_tests))
 p_values <- c(pvals_block, pvals_naive_block)
@@
 # Generate histograms plot
-hist_boot <- ggplot(results, aes(x = p_values)) + geom_histogram(color="gray", fill="white", boundary = 0, binwidth = 1/20, size = 1) + theme(text=element_text(size=14)) + scale_x_continuous(name = "p-value", breaks=c(0, 1)) + facet_wrap(.~histogram, scales = "free_y")
-hist_boot
+hist_block <- ggplot(results) +
+             geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+             scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+             facet_grid(~histogram) +
+             theme(legend.position = "none")
+
+# Save the histogram figure
+ggsave(filename = "hist_block.pdf", plot = hist_block, path = "../Manuscript", height = 2.1, width = 6)
+
+proc.time() - ptm
 ```
@@
 ```{r}
-# Split sample size into blocks, apply bootstrap onto blocks. Use that as x.b. Fit, stat.b
-# Test parametric bootstrap as a solution to fitting parameters
-test_corr_block <- function(ar, B = 1000, l, n) {
+test_snpar <- function(ar, n) {
 
+  # Generate correlated data
   x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)
 
-  # Store KS statistic from using fitted parameters
-  stat <- cor(x[-1], x[-length(x)])
+  # Gather p-value
+  p.value <- snpar::KS.test(x, "pnorm")$p.value
 
-  # Parametric bootstrap to approximate the null distribution
-  stat.b <- double(B)
-  for (i in 1:B) {
-    x.b <- x[nmblk(n, l)]
-    stat.b[i] <- cor(x.b[-1], x.b[-length(x.b)])
+  list(p.value = p.value)
 }
 
-  list(stat = stat, stat.b = stat.b)
+n <- 100
+ar <- 0.5
+n_tests <- 1000
+
+# Generate results
+pvals_snpar <- replicate(n_tests, test_snpar(ar = ar, n = n)$p.value)
+pvals_naive_block <- replicate(n_tests, test_naive_block(ar = ar, n = n)$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("snpar", n_tests), rep("Naive", n_tests))
+p_values <- c(pvals_snpar, pvals_naive_block)
+results <- data_frame(p_values, histogram)
+
+# Generate histograms plot
+hist_snpar <- ggplot(results) +
+             geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+             scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+             facet_grid(~histogram) + 
+             theme(legend.position = "none")
+
+hist_snpar
+```
+
+```{r hist_rounded}
+# Test to show that rounding changes the power of the test
+test_rounded <- function(n_tests, n_samples, digits) {
+
+  p_values <- double(n_tests)
+
+  for(i in 1:n_tests) {
+
+    # Generate random rounded data, perform a KS-test, and store the p-value
+    data <- round(rnorm(n_samples), digits)
+    p_values[i] <- ks.test(data, "pnorm")$p.value
   }
 
-do1rep <- function(ar, B = 1000, l, n) {
-    bt <- test_corr_block(ar, B, l, n)
-    c(bt$stat, sd(bt$stat.b))
+  return(p_values)
 }
 
-corr_block <- suppressWarnings(replicate(50, do1rep(0.5, B = 1000, 10, 100)))
-corr_block
+# Create the histograms displaying p-values from each test
+hist1 <- suppressWarnings(test_rounded(1000, 100, 2))
+hist2 <- suppressWarnings(test_rounded(1000, 100, 1))
+
+# Create a master data_frame with all the results
+histogram <- c(rep(".01", 1000), rep(".1", 1000))
+p_values <- c(hist1, hist2)
+results <- data_frame(p_values, histogram)
+
+# Generate histograms plot
+hist_rounded <- ggplot(results) + 
+                geom_histogram(aes(x = p_values, fill = histogram), binwidth = 1/20, boundary = 0) + 
+                facet_grid(~histogram) +
+                theme(legend.position = "none") +
+                scale_x_continuous(name = "p-value", breaks = seq(0, 1))
+
+# Save the histogram figure
+ggsave(filename = "hist_rounded.pdf", plot = hist_rounded, path = "../Manuscript", height = 2.1, width = 6)
 ```
 
-```{r}
-ggsave(filename="hist_normal.pdf", plot=hist_normal, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
-ggsave(filename="hist_rounded.pdf", plot=hist_rounded, path = "/Users/anthony//KS-Test-Thesis/Manuscript")
-ggsave(filename="hist_correlation.pdf", plot=hist_correlation, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
-ggsave(filename="hist_dgof.pdf", plot=hist_dgof, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
-ggsave(filename="hist_dgofsim.pdf", plot=hist_dgofsim, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
-ggsave(filename="hist_parametric.pdf", plot=hist_parametric, path = "/Users/anthony/KS-Test-Thesis/Manuscript")
+```{r hist_general}
+# Test the KSgeneral package as a solution to rounded data
+test_general <- function(n_tests, n_samples, digits, B = 100) {
+
+  results1 <- double(n_tests)
+  results2 <- double(n_tests)
+  results3 <- double(n_tests)
+  results4 <- double(n_tests)
+
+  # Create the rounded normal step function
+  left <- -4-0.1^digits
+  y <- pnorm(seq(left, 4, by = 0.1^digits))
+  sfun  <- stepfun(seq(-4, 4, by = 0.1^digits), y)
+
+  for (i in 1:n_tests) {
+
+    # Generate random rounded data, perform 3 KS-tests, and store the p-values
+    # 1. Using the rounded normal step function
+    # 2. Using the naive continuous standard normal function
+    data <- round(rnorm(n_samples), digits)
+    results1[i] <- KSgeneral::disc_ks_test(data, sfun, exact = TRUE)$p.value
+    results2[i] <- dgof::ks.test(data, sfun)$p.value
+    results3[i] <- ks.test(data, sfun, simulate.p.value = TRUE, B = B)$p.value
+    results4[i] <- ks.test(data, "pnorm")$p.value
+
+  }
+
+  # Create a master data_frame for p-values
+  test <- c(rep("KSgeneral", n_tests), rep("dgof", n_tests), rep("dgofsim", n_tests), rep("Naive", n_tests))
+  digits <- c(rep(.1^digits, 4*n_tests))
+  p_values <- c(results1, results2, results3, results4)
+  results <- data_frame(p_values, test, digits)
+
+  return(results)
+}
+
+ptm <- proc.time()
+
+n_tests = 1000
+n = 50
+
+# Create the histograms displaying p-values from each test
+test1 <- suppressWarnings(test_general(n_tests, n, 2))
+test2 <- suppressWarnings(test_general(n_tests, n, 1))
+results <- rbind(test1, test2)
+
+# Generate histograms plot
+hist_general <- ggplot(results) + 
+                geom_histogram(aes(x = p_values, fill = test), boundary = 0, binwidth = 1/20) + 
+                scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                facet_grid(test~digits) +
+                theme(legend.position = "none")
+
+# Save the histogram figure
+ggsave(filename = "hist_general.pdf", plot = hist_general, path = "../Manuscript", height = 4.2, width = 6)
+
+proc.time() - ptm
+# could try qqplot for unit interval
+# is qqplot close to 45 degree line, otherwise no
 ```
+
+```{r hist_correlationn}
+# Test to show that autocorrelation changes the power of the test
+test_correlation <- function(n_tests, ars) {
+
+  # Create a master data_frame for p-values
+  columns <- c("p_value", "ar")
+  ar_results <- data.frame(matrix(ncol = 2, nrow = 0))
+  colnames(ar_results) <- columns
+
+  # For AR coefficients from -0.5 to 0.5
+  for(i in 1:length(ars)) {
+
+    for(j in 1:n_tests) {
+
+      # Generate random correlated data, perform a KS-test, and store the p-value
+      data <- arima.sim(model = list(ar = ars[i]), rand.gen = rnorm, sd = sqrt(1-ars[i]^2), n = 100)
+      ar_results <- add_row(ar_results, p_value = ks.test(data, "pnorm")$p.value, ar = round(ars[i], 1))
+    }
+  }
+
+  return(ar_results)
+}
+
+ # Set AR coefficients and generate results
+ars <- seq(-0.3, 0.3, by = 0.1)
+ar_results <- test_correlation(1000, ars)
+
+# Generate histograms plot
+hist_correlation <- ggplot(ar_results) + 
+                    geom_histogram(aes(x = p_value, fill = ar), boundary = 0, binwidth = 1/20) + 
+                    facet_grid(~ar) +
+                    theme(legend.position = "none") +
+                    scale_x_continuous(name = "p-value", breaks=c(0, 1))
+
+# Save the histogram figure
+ggsave(filename = "hist_correlation.pdf", plot = hist_correlation, path = "../Manuscript", height = 2.1, width = 6)
+```

### 2022-02-25 Code/Simulation.Rmd
added babu for time series, qqplot try

@@
 
-```{r}
+```{r snpar}
 test_snpar <- function(ar, n) {
@@
              theme(legend.position = "none")
-
-hist_snpar
 ```
@@
 ggsave(filename = "hist_rounded.pdf", plot = hist_rounded, path = "../Manuscript", height = 2.1, width = 6)
+
+qqplot(hist1, runif(100), xlab = "Rounded", ylab = "Uniform", main = "Testing qqplot")
+abline(0, 1)
+p <- ggplot(results, aes(sample = p_values))
+p + stat_qq(distribution = stats::qunif) + geom_abline(intercept = 0, slope = 1) + xlim(0, 1) + ylim(0, 1)
 ```
@@
 
-n_tests = 1000
+n_tests = 100
 n = 50
@@
 proc.time() - ptm
+
+qqplot(test1$p_values[1:100], runif(100), xlab = "KSGeneral", ylab = "Uniform", main = "Testing qqplot")
+abline(0, 1)
 # could try qqplot for unit interval
@@
 
-```{r hist_correlationn}
+```{r hist_correlation}
 # Test to show that autocorrelation changes the power of the test
@@
 ```
+
+```{r babu}
+ecdf.leftcont <- function (x) {
+    x <- sort(x)
+    n <- length(x)
+    if (n < 1) 
+        stop("'x' must have 1 or more non-missing values")
+    vals <- unique(x)
+    ## making it left continuous!
+    rval <- approxfun(vals, cumsum(tabulate(match(x, vals)))/n - 1/n, 
+        method = "constant", yleft = 0, yright = 1, f = 1, ties = "ordered")
+    class(rval) <- c("ecdf", "stepfun", class(rval))
+    assign("nobs", n, envir = environment(rval))
+    attr(rval, "call") <- sys.call()
+    rval
+}
+
+ks.np.babu <- function(x, B = 1000) {
+    ## for normal distribution only
+    n <- length(x)
+    Fn <- ecdf(x)
+    Gn <- ecdf.leftcont(x)
+    mu <- mean(x); ss <- sd(x)
+    Ftheta <- pnorm(x, mu, ss)
+    Bn1 <- Fn(x) - Ftheta
+    Bn2 <- Gn(x) - Ftheta
+    d1 <- abs(Bn1)
+    d2 <- abs(Bn2)
+    stat <- max(d1, d2)
+    stat.b <- double(B)
+    for (i in 1:B) {
+        x.b <- sample(x, size = n, replace = TRUE)
+        Fn.b <- ecdf(x.b)
+        Gn.b <- ecdf.leftcont(x.b)
+        mu.b <- mean(x.b); ss.b <- sd(x.b)
+        ## evaluate at x (not x.b)
+        Ftheta.b <- pnorm(x, mu.b, ss.b)
+        d1.b <- abs(Fn.b(x) - Ftheta.b - Bn1)
+        d2.b <- abs(Gn.b(x) - Ftheta.b - Bn2)
+        stat.b[i] <- max(d1.b, d2.b)
+    }
+    p.value <-  (sum(stat.b >= stat) + 0.5) / (B + 1)
+    list(p.value = p.value,
+         statistic = stat, stat.b = stat.b)
+}
+```
+
+```{r babu.ts}
+ks.np.babu.ts <- function(x, l, B = 1000) {
+  ## for normal distribution only
+  n <- length(x)
+  Fn <- ecdf(x)
+  Gn <- ecdf.leftcont(x)
+  mu <- mean(x); ss <- sd(x)
+  Ftheta <- pnorm(x, mu, ss)
+  Bn1 <- Fn(x) - Ftheta
+  Bn2 <- Gn(x) - Ftheta
+  d1 <- abs(Bn1)
+  d2 <- abs(Bn2)
+  stat <- max(d1, d2)
+  stat.b <- double(B)
+  for (i in 1:B) {
+    x.b <- x[nmblk(n, 5)]
+    Fn.b <- ecdf(x.b)
+    Gn.b <- ecdf.leftcont(x.b)
+    mu.b <- mean(x.b); ss.b <- sd(x.b)
+    ## evaluate at x (not x.b)
+    Ftheta.b <- pnorm(x, mu.b, ss.b)
+    d1.b <- abs(Fn.b(x) - Ftheta.b - Bn1)
+    d2.b <- abs(Gn.b(x) - Ftheta.b - Bn2)
+    stat.b[i] <- max(d1.b, d2.b)
+  }
+  p.value <-  (sum(stat.b >= stat) + 0.5) / (B + 1)
+  list(p.value = p.value,
+       statistic = stat, stat.b = stat.b)
+}
+```
+
+```{r hist_babu}
+test_babu <- function(n_tests, n, ar, l) {
+
+  results1 <- double(n_tests)
+  results2 <- double(n_tests)
+  results3 <- double(n_tests)
+
+  for (i in 1:n_tests) {
+
+    cat(i, " ")
+
+    x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n = n)
+
+    results1[i] <- ks.np.babu.ts(x, l, B = 1000)$p.value
+    results2[i] <- blkboot(x, ks_statistic, R = 1000, l)$nmp.value
+    results3[i] <- ks.test(x, "pnorm")$p.value
+
+  }
+
+  # Create a master data_frame for p-values
+  test <- c(rep("Babu", n_tests), rep("Block", n_tests), rep("Naive", n_tests))
+  p_values <- c(results1, results2, results3)
+  results <- data_frame(p_values, test)
+
+  return(results)
+}
+
+n_tests = 100
+n = 100
+l = 10
+ar = 0.5
+
+ptm <- proc.time()
+
+# Create the histograms displaying p-values from each test
+results <- suppressWarnings(test_babu(n_tests = n_tests, n = n, ar = ar, l = l))
+
+# Time per test
+(proc.time() - ptm)["elapsed"] / n_tests
+
+# Total time
+proc.time() - ptm
+
+# Generate histograms plot
+hist_babu <- ggplot(results) + 
+                geom_histogram(aes(x = p_values, fill = test), boundary = 0, binwidth = 1/20) + 
+                scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                facet_grid(~test) +
+                theme(legend.position = "none")
+hist_babu
+```
+
+```{r}
+#hist_babu1000
+#hist_babu_1000
+```

### 2022-02-25 Code/tspb.R
template for copula-based stationary pb

@@ -1,0 +1,31 @@
+n <- 100
+x <- arima.sim(list(ar = 0.4), n)
+
+ks.ts.pb <- function(x, dist, B = 1000) {
+    ## example assuming normal distribution; normal copula
+    ## get observed stat
+    n <- length(x)
+    theta <- fit(x) # theta = (mu, sigma)
+    stat  <- ks.test(x, dist, theta)
+    ## get lag-1 sample auto-spearman rho
+    rho  <-  cor(x[-1], x[-n], method = "spearman")
+    r <- iRho(normalCopula(), rho)
+    ## parametric bootstrap to get an empirical distribution of stat
+    ## set up containers
+    u <- double(n)
+    for (i in 1:B) {
+        ## get one bootstrap sample
+        ## 1. the marginal distribution is the fitted dist
+        ## 2. there is temporal dependence
+        u <- runif(1)
+        for (j in 2:n) {
+            ## could test other copulas later
+            u[j]  <- copula::cCopula(u[j - 1], normalCopula(r))
+        }
+        x.b <- qnorm(u, mean = theta[1], sd = theta[2])
+        ## fit it
+        theta.b <- fit(x.b)
+        stat.b <- ks.test(x.b, dist, theta.b)
+    }
+    # return empirical p-value    
+}

### 2022-03-03 Code/tspb.R
Copula-based error in time series bootstrap

@@ -1,16 +1,16 @@
-n <- 100
-x <- arima.sim(list(ar = 0.4), n)
+library(copula)
+library(dgof)
 
 ks.ts.pb <- function(x, dist, B = 1000) {
     ## example assuming normal distribution; normal copula
     ## get observed stat
     n <- length(x)
-    theta <- fit(x) # theta = (mu, sigma)
-    stat  <- ks.test(x, dist, theta)
+    stat  <- ks.test(x, dist)$statistic
     ## get lag-1 sample auto-spearman rho
     rho  <-  cor(x[-1], x[-n], method = "spearman")
     r <- iRho(normalCopula(), rho)
     ## parametric bootstrap to get an empirical distribution of stat
+    stat.b <- double(n)
     ## set up containers
     u <- double(n)
     for (i in 1:B) {
@@ -20,12 +20,22 @@ ks.ts.pb <- function(x, dist, B = 1000) {
         u <- runif(1)
         for (j in 2:n) {
             ## could test other copulas later
-            u[j]  <- copula::cCopula(u[j - 1], normalCopula(r))
+            u[j]  <- cCopula(u[j - 1], normalCopula(r))
         }
-        x.b <- qnorm(u, mean = theta[1], sd = theta[2])
+        x.b <- qnorm(u)
         ## fit it
-        theta.b <- fit(x.b)
-        stat.b <- ks.test(x.b, dist, theta.b)
+        mu.b <- mean(x.b)
+        sd.b <- sd(x.b)
+        stat.b[i] <- ks.test(x.b, dist, mu.b, sd.b)$statistic
     }
+    
+    p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
+    
+    return(p.value)
     # return empirical p-value    
 }
+
+n <- 100
+ar = 0.5
+x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n = n)
+ks.ts.pb(x, "pnorm")

### 2022-03-03 Code/tspb.R
added fitted parameters to copula pb

@@ -5,7 +5,9 @@ ks.ts.pb <- function(x, dist, B = 1000) {
     ## example assuming normal distribution; normal copula
     ## get observed stat
     n <- length(x)
-    stat  <- ks.test(x, dist)$statistic
+    mu <- mean(x)
+    sigma <- sd(x)
+    stat  <- ks.test(x, dist, mu, sigma)$statistic
     ## get lag-1 sample auto-spearman rho
     rho  <-  cor(x[-1], x[-n], method = "spearman")
     r <- iRho(normalCopula(), rho)
@@ -25,8 +27,8 @@ ks.ts.pb <- function(x, dist, B = 1000) {
         x.b <- qnorm(u)
         ## fit it
         mu.b <- mean(x.b)
-        sd.b <- sd(x.b)
-        stat.b[i] <- ks.test(x.b, dist, mu.b, sd.b)$statistic
+        sigma.b <- sd(x.b)
+        stat.b[i] <- ks.test(x.b, dist, mu.b, sigma.b)$statistic
     }
     
     p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)

### 2022-03-04 Code/tspb.R
fixed cCopula usage and bootstrap sampling

@@ -1,34 +1,35 @@
 library(copula)
 library(dgof)
 
-ks.ts.pb <- function(x, dist, B = 1000) {
+ks.ts.pb <- function(x, dist, B = 100) {
     ## example assuming normal distribution; normal copula
     ## get observed stat
     n <- length(x)
     mu <- mean(x)
     sigma <- sd(x)
-    stat  <- ks.test(x, dist, mu, sigma)$statistic
+    stat  <- ks.test(x, dist, mean = mu, sd = sigma)$statistic
     ## get lag-1 sample auto-spearman rho
     rho  <-  cor(x[-1], x[-n], method = "spearman")
     r <- iRho(normalCopula(), rho)
+    np <- normalCopula(r)
     ## parametric bootstrap to get an empirical distribution of stat
     stat.b <- double(n)
     ## set up containers
-    u <- double(n)
     for (i in 1:B) {
         ## get one bootstrap sample
         ## 1. the marginal distribution is the fitted dist
         ## 2. there is temporal dependence
-        u <- runif(1)
+        u <- runif(n)
         for (j in 2:n) {
             ## could test other copulas later
-            u[j]  <- cCopula(u[j - 1], normalCopula(r))
+            u[j]  <- cCopula(c(u[j-1], u[j]), np, indices = 2, inverse = TRUE)
         }
-        x.b <- qnorm(u)
+        ## get bootstrap sample
+        x.b <- qnorm(u, mean = mu, sd = sigma)
         ## fit it
         mu.b <- mean(x.b)
         sigma.b <- sd(x.b)
-        stat.b[i] <- ks.test(x.b, dist, mu.b, sigma.b)$statistic
+        stat.b[i] <- ks.test(x.b, dist, mean = mu.b, sd = sigma.b)$statistic
     }
     
     p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
@@ -41,3 +42,10 @@ n <- 100
 ar = 0.5
 x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n = n)
 ks.ts.pb(x, "pnorm")
+
+nrep <- 100
+pval <- replicate(nrep, ks.ts.pb(arima.sim(list(ar = ar),
+                                          rand.gen=rnorm,
+                                          sd = sqrt(1 - ar^2), n = n),
+                                "pnorm"))
+hist(pval)

### 2022-03-04 Code/Simulation.Rmd
Added copula ks-test histogram, added babu to fitted parameters, removed block bs sections

@@
 library(KSgeneral)
-library(snpar)
+library(copula)
 ```
@@
     stat.b[i] <- ks.test(x.b, "pnorm", mu.b, sigma.b)$statistic
-    # write own ks test statistic formula here
-    # is.character(y)
   }
@@
 
+  counter <<- counter + 1
+  cat(counter, "")
+  list(p.value = p.value)
+}
+
+test_babu <- function(x, B = 1000) {
+  p.value <- ks.np.babu(x, B = 1000)$p.value
+  counter <<- counter + 1
+  cat(counter, "")
   list(p.value = p.value)
@@
 # Generate results
-pvals_parametric <- replicate(100, test_parametric(rnorm(100), B = 1000)$p.value)
-pvals_naive <- replicate(100, test_naive(rnorm(100))$p.value)
+n_tests = 100
+n = 100
+counter <- 0
+pvals_parametric <- replicate(n_tests, test_parametric(rnorm(n), B = 1000)$p.value)
+counter <- 0
+pvals_babu <- replicate(n_tests, test_babu(rnorm(n), B = 1000)$p.value)
+pvals_naive <- replicate(n_tests, test_naive(rnorm(n))$p.value)
 
 # Create a master data_frame with all the results
-histogram <- c(rep("Parametric", 100), rep("Naive", 100))
-p_values <- c(pvals_parametric, pvals_naive)
+histogram <- c(rep("Parametric", n_tests), rep("Babu", n_tests), rep("Naive", n_tests))
+p_values <- c(pvals_parametric, pvals_babu, pvals_naive)
 results <- data_frame(p_values, histogram)
@@
 # Generate histograms plot
-hist_parametric <- ggplot(results) + 
+hist_fitted <- ggplot(results) + 
                    geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
@@
 # Save the histogram figure
-ggsave(filename = "hist_parametric.pdf", plot = hist_parametric, path = "../Manuscript", height = 2.1, width = 6)
-```
-
-```{r block functions}
-# Functions supporting block bootstrap
-
-# Add small noise to data
-add_noise <- function(x) {
-
-  # Grab variance and length
-  v <- var(x)
-  n <- length(x)
-
-  # Generate noise where standard deviation is 1% of variance
-  noise <- rnorm(n, mean = 0, sd = 1/100*v)
-
-  # Return jittered data
-  return(x + noise)
-}
-
-# Non-moving block generation
-nmblk <- function(n, l) {
-
-  # Number of blocks
-  b <- n / l
-
-  # Create non-moving block indices
-  idx <- sample(seq(1, n - l + 1, by = l), b, replace = TRUE)
-
-  # Return indices
-  c(outer(0:(l - 1), idx, "+"))
-}
-
-# Moving block generation
-mvblk <- function(n, l) {
-
-  # Number of blocks
-  b <- n / l
-
-  # Create moving block indices
-  idx <- sample(1:(n - l + 1), b, replace = TRUE)
-
-  # Return indices
-  c(outer(0:(l - 1), idx, "+"))
-}
-```
-
-```{r hist_block}
-# Block bootstrap function
-blkboot <- function(tseries, statistic, R, l) {
-
-  n <- length(tseries)
-
-  # Gather observed statistic
-  stat <- statistic(tseries)
-
-  # Replicate block bootstrap samples with noise
-  nm.stat <- replicate(R, statistic(add_noise(tseries[nmblk(n, l)])))
-  mv.stat <- replicate(R, statistic(add_noise(tseries[mvblk(n, l)])))
-
-  # Calculate p-values
-  nmp.value <- (sum(nm.stat >= stat) + 0.5) / (R + 1)
-  mvp.value <- (sum(mv.stat >= stat) + 0.5) / (R + 1)
-
-  list(stat = stat, nmp.value = nmp.value, mvp.value = mvp.value)
-}
-
-# Calculate ks-statistic
-ks_statistic <- function(x) ks.test(x, "pnorm")$statistic
-
-# 1 test
-do1rep <- function(n, ar, l) {
-
-  # Create correlated data
-  x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)
-
-  # Apply block bootstrap
-  bt <- blkboot(x, ks_statistic, R = 1000, l)
-
-  list(stat = bt$stat, nmp.value = bt$nmp.value, mvp.value = bt$mvp.value)
-}
-
-# Naive example
-test_naive_block <- function(ar, n) {
-
-  # Generate correlated data
-  x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)
-
-  # Gather p-value
-  p.value <- ks.test(x, "pnorm")$p.value
-
-  list(p.value = p.value)
-}
-
-ptm <- proc.time()
-
-n <- 100
-ar <- 0.5
-l = 5
-n_tests <- 100
-
-# Generate results
-pvals_block <- replicate(n_tests, do1rep(n, ar, l)$mvp.value)
-pvals_naive_block <- replicate(n_tests, test_naive_block(ar = ar, n = n)$p.value)
-
-# Create a master data_frame with all the results
-histogram <- c(rep("Block", n_tests), rep("Naive", n_tests))
-p_values <- c(pvals_block, pvals_naive_block)
-results <- data_frame(p_values, histogram)
-
-# Generate histograms plot
-hist_block <- ggplot(results) +
-             geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
-             scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
-             facet_grid(~histogram) +
-             theme(legend.position = "none")
-
-# Save the histogram figure
-ggsave(filename = "hist_block.pdf", plot = hist_block, path = "../Manuscript", height = 2.1, width = 6)
-
-proc.time() - ptm
-```
-
-```{r snpar}
-test_snpar <- function(ar, n) {
-
-  # Generate correlated data
-  x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n)
-
-  # Gather p-value
-  p.value <- snpar::KS.test(x, "pnorm")$p.value
-
-  list(p.value = p.value)
-}
-
-n <- 100
-ar <- 0.5
-n_tests <- 1000
-
-# Generate results
-pvals_snpar <- replicate(n_tests, test_snpar(ar = ar, n = n)$p.value)
-pvals_naive_block <- replicate(n_tests, test_naive_block(ar = ar, n = n)$p.value)
-
-# Create a master data_frame with all the results
-histogram <- c(rep("snpar", n_tests), rep("Naive", n_tests))
-p_values <- c(pvals_snpar, pvals_naive_block)
-results <- data_frame(p_values, histogram)
-
-# Generate histograms plot
-hist_snpar <- ggplot(results) +
-             geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
-             scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
-             facet_grid(~histogram) + 
-             theme(legend.position = "none")
+ggsave(filename = "hist_fitted.pdf", plot = hist_fitted, path = "../Manuscript", height = 2.1, width = 6)
 ```
@@
 # Create the histograms displaying p-values from each test
-hist1 <- suppressWarnings(test_rounded(1000, 100, 2))
-hist2 <- suppressWarnings(test_rounded(1000, 100, 1))
+n_tests <- 1000
+n <- 100
+hist1 <- suppressWarnings(test_rounded(n_tests, n, 2))
+hist2 <- suppressWarnings(test_rounded(n_tests, n, 1))
 
 # Create a master data_frame with all the results
-histogram <- c(rep(".01", 1000), rep(".1", 1000))
+histogram <- c(rep(".01", n_tests), rep(".1", n_tests))
 p_values <- c(hist1, hist2)
@@
 # Test the KSgeneral package as a solution to rounded data
-test_general <- function(n_tests, n_samples, digits, B = 100) {
+test_general <- function(n_tests, n_samples, digits, B) {
 
@@
   for (i in 1:n_tests) {
-
+    cat(i, "")
     # Generate random rounded data, perform 3 KS-tests, and store the p-values
@@
     results4[i] <- ks.test(data, "pnorm")$p.value
-
   }
@@
 n_tests = 100
-n = 50
+n = 100
+B = 1000
 
 # Create the histograms displaying p-values from each test
-test1 <- suppressWarnings(test_general(n_tests, n, 2))
-test2 <- suppressWarnings(test_general(n_tests, n, 1))
+test1 <- suppressWarnings(test_general(n_tests, n, digits = 2, B = B))
+test2 <- suppressWarnings(test_general(n_tests, n, digits = 1, B = B))
 results <- rbind(test1, test2)
@@
 
-```{r babu.ts}
-ks.np.babu.ts <- function(x, l, B = 1000) {
-  ## for normal distribution only
+```{r}
+test_copula <- function(x, dist, B = 100) {
+    ## example assuming normal distribution; normal copula
+    ## get observed stat
     n <- length(x)
-  Fn <- ecdf(x)
-  Gn <- ecdf.leftcont(x)
-  mu <- mean(x); ss <- sd(x)
-  Ftheta <- pnorm(x, mu, ss)
-  Bn1 <- Fn(x) - Ftheta
-  Bn2 <- Gn(x) - Ftheta
-  d1 <- abs(Bn1)
-  d2 <- abs(Bn2)
-  stat <- max(d1, d2)
-  stat.b <- double(B)
+    mu <- mean(x)
+    sigma <- sd(x)
+    stat  <- ks.test(x, dist, mean = mu, sd = sigma)$statistic
+    ## get lag-1 sample auto-spearman rho
+    rho  <-  cor(x[-1], x[-n], method = "spearman")
+    r <- iRho(normalCopula(), rho)
+    np <- normalCopula(r)
+    ## parametric bootstrap to get an empirical distribution of stat
+    stat.b <- double(n)
+    ## set up containers
     for (i in 1:B) {
-    x.b <- x[nmblk(n, 5)]
-    Fn.b <- ecdf(x.b)
-    Gn.b <- ecdf.leftcont(x.b)
-    mu.b <- mean(x.b); ss.b <- sd(x.b)
-    ## evaluate at x (not x.b)
-    Ftheta.b <- pnorm(x, mu.b, ss.b)
-    d1.b <- abs(Fn.b(x) - Ftheta.b - Bn1)
-    d2.b <- abs(Gn.b(x) - Ftheta.b - Bn2)
-    stat.b[i] <- max(d1.b, d2.b)
+        ## get one bootstrap sample
+        ## 1. the marginal distribution is the fitted dist
+        ## 2. there is temporal dependence
+        u <- runif(n)
+        for (j in 2:n) {
+            ## could test other copulas later
+            u[j]  <- cCopula(c(u[j-1], u[j]), np, indices = 2, inverse = TRUE)
         }
-  p.value <-  (sum(stat.b >= stat) + 0.5) / (B + 1)
-  list(p.value = p.value,
-       statistic = stat, stat.b = stat.b)
-}
-```
-
-```{r hist_babu}
-test_babu <- function(n_tests, n, ar, l) {
-
-  results1 <- double(n_tests)
-  results2 <- double(n_tests)
-  results3 <- double(n_tests)
-
-  for (i in 1:n_tests) {
-
-    cat(i, " ")
-
-    x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n = n)
-
-    results1[i] <- ks.np.babu.ts(x, l, B = 1000)$p.value
-    results2[i] <- blkboot(x, ks_statistic, R = 1000, l)$nmp.value
-    results3[i] <- ks.test(x, "pnorm")$p.value
-
+        ## get bootstrap sample
+        x.b <- qnorm(u, mean = mu, sd = sigma)
+        ## fit it
+        mu.b <- mean(x.b)
+        sigma.b <- sd(x.b)
+        stat.b[i] <- ks.test(x.b, dist, mean = mu.b, sd = sigma.b)$statistic
     }
 
-  # Create a master data_frame for p-values
-  test <- c(rep("Babu", n_tests), rep("Block", n_tests), rep("Naive", n_tests))
-  p_values <- c(results1, results2, results3)
-  results <- data_frame(p_values, test)
+    p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
 
-  return(results)
+    counter <<- counter + 1
+    cat(counter)
+
+    return(p.value)
+    # return empirical p-value    
 }
 
-n_tests = 100
-n = 100
-l = 10
+# Naive KS-test
+test_naive_copula <- function(x) {
+  p.value <- ks.test(x, "pnorm")$p.value
+  list(p.value = p.value)
+}
+
+# Generate results
+n <- 100
 ar = 0.5
+counter <- 0
+nrep <- 1000
+pvals_copula <- replicate(nrep, test_copula(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), "pnorm"))
+pvals_naive <- replicate(nrep, test_naive_copula(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)
 
-ptm <- proc.time()
-
-# Create the histograms displaying p-values from each test
-results <- suppressWarnings(test_babu(n_tests = n_tests, n = n, ar = ar, l = l))
-
-# Time per test
-(proc.time() - ptm)["elapsed"] / n_tests
-
-# Total time
-proc.time() - ptm
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
+p_values <- c(pvals_copula, pvals_naive)
+results <- data_frame(p_values, histogram)
 
 # Generate histograms plot
-hist_babu <- ggplot(results) + 
-                geom_histogram(aes(x = p_values, fill = test), boundary = 0, binwidth = 1/20) + 
+hist_copula <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                    scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
-                facet_grid(~test) +
-                theme(legend.position = "none")
-hist_babu
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+hist_copula
+
+# Save the histogram figure
+ggsave(filename = "hist_copula.pdf", plot = hist_copula, path = "../Manuscript", height = 2.1, width = 6)
 ```
-
-```{r}
-#hist_babu1000
-#hist_babu_1000
-```

### 2022-03-04 Manuscript/manuscript.tex
added copula histogram and babu into fitted parameters histogram, removed block bs

@@
 The parameters of the null distribution are approximated from the bootstrap.
-Figure~\ref{fig:hist_parametric} displays the results of $1000$ replicate tests using the standard normal distribution with sample size $n=100$.
+Figure~\ref{fig:hist_fitted} displays the results of $1000$ replicate tests using the standard normal distribution with sample size $n=100$.
 In each parametric test, $1000$ bootstrap samples are obtained and the corresponding p-value of the K-S test is calculated.
@@
   \centering
-  \includegraphics{hist_parametric}
+  \includegraphics{hist_fitted}
   \caption{Histograms demonstrating fitted parameters.}
-  \label{fig:hist_parametric}
+  \label{fig:hist_fitted}
 \end{figure}
@@
   \centering
-  \includegraphics{hist_block}
-  \caption{Histograms of P-values when using block bootstrap.}
-  \label{fig:hist_block}
+  \includegraphics{hist_copula}
+  \caption{Histograms demonstrating copula to correct correlation.}
+  \label{fig:hist_copula}
 \end{figure}

### 2022-03-05 Code/tspb.R
more general data generation and testing

@@ -1,17 +1,21 @@
 library(copula)
 library(dgof)
 
-ks.ts.pb <- function(x, dist, B = 100) {
+
+## wcopula: working copula assumed in constructing bootstrap sample
+ks.ts.pb <- function(x, dist, B = 100, wcopula = normalCopula) {
     ## example assuming normal distribution; normal copula
     ## get observed stat
     n <- length(x)
+    ## get fitted parameters; could check MASS::fitdistr for general solution
+    ## the next two lines only work when dist is normal
     mu <- mean(x)
     sigma <- sd(x)
     stat  <- ks.test(x, dist, mean = mu, sd = sigma)$statistic
     ## get lag-1 sample auto-spearman rho
     rho  <-  cor(x[-1], x[-n], method = "spearman")
-    r <- iRho(normalCopula(), rho)
-    np <- normalCopula(r)
+    r <- iRho(wcopula(), rho)
+    wcop <- wcopula(r)
     ## parametric bootstrap to get an empirical distribution of stat
     stat.b <- double(n)
     ## set up containers
@@ -22,30 +26,64 @@ ks.ts.pb <- function(x, dist, B = 100) {
         u <- runif(n)
         for (j in 2:n) {
             ## could test other copulas later
-            u[j]  <- cCopula(c(u[j-1], u[j]), np, indices = 2, inverse = TRUE)
+            u[j]  <- cCopula(c(u[j-1], u[j]), wcop, indices = 2, inverse = TRUE)
         }
         ## get bootstrap sample
+        ## get fitted parameters for the bootstrap sample
+        ## the next lines only work when dist is normal
         x.b <- qnorm(u, mean = mu, sd = sigma)
-        ## fit it
         mu.b <- mean(x.b)
         sigma.b <- sd(x.b)
         stat.b[i] <- ks.test(x.b, dist, mean = mu.b, sd = sigma.b)$statistic
     }
-    
+    ## return empirical p-value    
     p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
-    
     return(p.value)
-    # return empirical p-value    
 }
 
-n <- 100
-ar = 0.5
-x <- arima.sim(list(ar = ar), rand.gen = rnorm, sd = sqrt(1-ar^2), n = n)
-ks.ts.pb(x, "pnorm")
+## generating observations from a specified distribution with serial dependence
+genData <- function(n, qdist, ..., copula, rho) {
+    ## n: sample size
[…]

### 2022-03-25 Code/Simulation.Rmd
added MA(1) process, ARMA(1,1) process, test for gamma with copulas

@@
 library(copula)
+source('tspb.R')
 ```
@@
 
-qqplot(hist1, runif(100), xlab = "Rounded", ylab = "Uniform", main = "Testing qqplot")
+qqplot(hist2, runif(100), xlab = "Rounded", ylab = "Uniform", main = "Testing qqplot")
 abline(0, 1)
@@
     results1[i] <- KSgeneral::disc_ks_test(data, sfun, exact = TRUE)$p.value
-    results2[i] <- dgof::ks.test(data, sfun)$p.value
+    results2[i] <- dgof::ks.test(data, sfun, exact = TRUE)$p.value
     results3[i] <- ks.test(data, sfun, simulate.p.value = TRUE, B = B)$p.value
@@
 n_tests = 100
-n = 100
+n = 30
 B = 1000
@@
 ```{r}
-test_copula <- function(x, dist, B = 100) {
+test_copula <- function(x, dist, B) {
     ## example assuming normal distribution; normal copula
@@
     counter <<- counter + 1
-    cat(counter)
+    cat(counter, "")
 
@@
 
+ptm <- proc.time()
+
 # Generate results
 n <- 100
-ar = 0.5
+ar <- 0.5
 counter <- 0
 nrep <- 1000
-pvals_copula <- replicate(nrep, test_copula(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), "pnorm"))
+B <- 1000
+pvals_copula <- replicate(nrep, test_copula(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), "pnorm", B = B))
 pvals_naive <- replicate(nrep, test_naive_copula(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)
@@
 
+print(proc.time() - ptm)
+
 # Save the histogram figure
@@
 ```
+
+```{r}
+## Test AR(2) model
+ptm <- proc.time()
+
+# Generate results
+n <- 100
+counter <- 0
+nrep <- 1000
+B <- 100
+b1 <- 0.5
+b2 <- 0.3
+pvals_copula <- replicate(nrep, test_copula(arima.sim(list(order = c(2, 0, 0), 
+                                                           ar = c(b1, b2)), 
+                                                          rand.gen=rnorm, 
+                                                          sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)), 
+                                                          n = n), "pnorm", B = B))
+pvals_naive <- replicate(nrep, test_naive_copula(arima.sim(list(order = c(2, 0, 0), ar = c(b1, b2)), rand.gen=rnorm, sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)), n = n))$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
+p_values <- c(pvals_copula, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+# Generate histograms plot
+hist_copula_ar2 <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+
+print(proc.time() - ptm)
+
+hist_copula_ar2
+
+# Save the histogram figure
+#ggsave(filename = "hist_copula_ar2.pdf", plot = hist_copula_ar2, path = "../Manuscript", height = 2.1, width = 6)
+```
+
+```{r}
+b1 <- 0.5
+b2 <- 0.3
+n <- 100
+x <- arima.sim(list(order = c(2, 0, 0), ar = c(b1, b2)), rand.gen=rnorm, sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)), n = n)
+sd(x)
+var(x)
+
+ma <- 0.5
+x <- arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n)
+sd(x)
+var(x)
+
+ar <- 0.5
+x <- arima.sim(list(ar = ar, ma = ma), rand.gen = rnorm, sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), n = n)
+sd(x)
+var(x)
+```
+
+```{r}
+## Test MA(1) model
+ptm <- proc.time()
+
+# Generate results
+n <- 100
+counter <- 0
+nrep <- 1000
+B <- 100
+ma <- 0.5
+pvals_copula <- replicate(nrep, test_copula(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), "pnorm", B = B))
+pvals_naive <- replicate(nrep, test_naive_copula(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n))$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
+p_values <- c(pvals_copula, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+# Generate histograms plot
+hist_copula_ma1 <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+
+print(proc.time() - ptm)
+
+hist_copula_ma1
+
+# Save the histogram figure
+ggsave(filename = "hist_copula_ma1.pdf", plot = hist_copula_ma1, path = "../Manuscript", height = 2.1, width = 6)
+```
+
+```{r}
+## Test ARMA(1,1) model
+ptm <- proc.time()
+
+# Generate results
+n <- 100
+counter <- 0
+nrep <- 1000
+B <- 100
+ar <- 0.5
+ma <- 0.3
+pvals_copula <- replicate(nrep, test_copula(arima.sim(list(ar = ar, 
+                                                           ma = ma), 
+                                                      rand.gen=rnorm, 
+                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
+                                                      n = n),
+                                            "pnorm", B = B))
+pvals_naive <- replicate(nrep, test_naive_copula(arima.sim(list(ar = ar, 
+                                                                ma = ma), 
+                                                      rand.gen=rnorm, 
+                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
+                                                      n = n))$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
+p_values <- c(pvals_copula, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+# Generate histograms plot
+hist_copula_arma <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+
+print(proc.time() - ptm)
+
+hist_copula_arma
+
+# Save the histogram figure
+ggsave(filename = "hist_copula_arma.pdf", plot = hist_copula_arma, path = "../Manuscript", height = 2.1, width = 6)
+```
+
+```{r}
+## wcopula: working copula assumed in constructing bootstrap sample
+test_copula2 <- function(x, dist, B = 100, wcopula = normalCopula) {
+    ## example assuming normal distribution; normal copula
+    ## get observed stat
+    n <- length(x)
+    ## get fitted parameters; could check MASS::fitdistr for general solution
+    ## the next two lines only work when dist is normal
+    mu <- mean(x)
+    sigma <- sd(x)
+    stat  <- ks.test(x, dist, mean = mu, sd = sigma)$statistic
+    ## get lag-1 sample auto-spearman rho
+    rho  <-  cor(x[-1], x[-n], method = "spearman")
+    r <- iRho(wcopula(), rho)
+    wcop <- wcopula(r)
+    ## parametric bootstrap to get an empirical distribution of stat
+    stat.b <- double(n)
+    ## set up containers
+    for (i in 1:B) {
+        ## get one bootstrap sample
+        ## 1. the marginal distribution is the fitted dist
+        ## 2. there is temporal dependence
+        u <- runif(n)
+        for (j in 2:n) {
+            ## could test other copulas later
+            u[j]  <- cCopula(c(u[j-1], u[j]), wcop, indices = 2, inverse = TRUE)
+        }
+        ## get bootstrap sample
+        ## get fitted parameters for the bootstrap sample
+        ## the next lines only work when dist is normal
+        x.b <- qnorm(u, mean = mu, sd = sigma)
+        mu.b <- mean(x.b)
+        sigma.b <- sd(x.b)
+        stat.b[i] <- ks.test(x.b, dist, mean = mu.b, sd = sigma.b)$statistic
+    }
+    ## return empirical p-value    
+    p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
+
+    counter <<- counter + 1
+    cat(counter, "")
+
+    return(p.value)
+}
+
+## generating observations from a specified distribution with serial dependence
+genData <- function(n, qdist, ..., copula, rho) {
+    ## n: sample size
+    ## qdist: quantile function of the desired marginal distribution
+    ## copula: copula for serial distribution
+    ## rho: spearman's rho
+    theta <- iRho(copula(), rho)
+    cop <- copula(theta)
+    u <- runif(n)
+    for (j in 2:n) {
+        u[j] <- cCopula(c(u[j-1], u[j]), cop, indices = 2, inverse = TRUE)
+    }
+    qdist(u, ...)
+}
+
+# Naive KS-test
+test_naive_copula <- function(x) {
+  p.value <- ks.test(x, "pnorm")$p.value
+  list(p.value = p.value)
+}
+
+ptm <- proc.time()
+
+# Generate results
+n <- 100
+rho <- 0.5
+counter <- 0
+nrep <- 100
+B <- 100
+pvals_copula <- replicate(nrep, test_copula2(genData(n, qnorm, mean = 1, sd = 1, copula = claytonCopula, rho = rho), "pnorm", B = B))
+pvals_naive <- replicate(nrep, test_naive_copula(genData(n, qnorm, mean = 1, sd = 1, copula = claytonCopula, rho = rho))$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
+p_values <- c(pvals_copula, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+# Generate histograms plot
+hist_copula2 <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+
+print(proc.time() - ptm)
+
+hist_copula2
+
+# Save the histogram figure
+#ggsave(filename = "hist_copula_c2.pdf", plot = hist_copula_c, path = "../Manuscript", height = 2.1, width = 6)
+```
+
+```{r}
+library(fitdistrplus)
+test_gamma <- function(x, dist, B = 100, wcopula = normalCopula) {
+
+    #fit <- fitdist(x, "gamma", method = "mle", lower = c(0, 0), start = list(scale = 1, shape = 1))
+    #shape <- fit$estimate[1]
+    #scale <- fit$estimate[2]
+
+    m <- mean(x)
+    v <- var(x)
+    scale <- v/m
+    shape <- m*m/v
+
+    stat  <- ks.test(x, dist, shape = shape, scale = scale)$statistic
+
+    ## example assuming normal distribution; normal copula
+    ## get observed stat
+    n <- length(x)
+
+    ## get lag-1 sample auto-spearman rho
+    rho  <-  cor(x[-1], x[-n], method = "spearman")
+    r <- iRho(wcopula(), rho)
+    wcop <- wcopula(r)
+    ## parametric bootstrap to get an empirical distribution of stat
+    stat.b <- double(n)
+    ## set up containers
+    for (i in 1:B) {
+        ## get one bootstrap sample
+        ## 1. the marginal distribution is the fitted dist
+        ## 2. there is temporal dependence
+        u <- runif(n)
+        for (j in 2:n) {
+            ## could test other copulas later
+            u[j]  <- cCopula(c(u[j-1], u[j]), wcop, indices = 2, inverse = TRUE)
+        }
+        ## get bootstrap sample
+        ## get fitted parameters for the bootstrap sample
+
+        x.b <- qgamma(u, shape = shape, scale = scale)
+
+        m.b <- mean(x.b)
+        v.b <- var(x.b)
+
+        scale.b <- v.b/m.b
+        shape.b <- m.b*m.b/v.b
+
+        #fit.b <- fitdist(x.b, "gamma", method = "mle", lower = c(0, 0), start = list(scale = 1, shape = 1))
+        #shape.b <- fit.b$estimate[1]
+        #scale.b <- fit.b$estimate[2]
+
+        stat.b[i] <- ks.test(x.b, dist, shape = shape.b, scale = scale.b)$statistic
+    }
+    ## return empirical p-value    
+    p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
+
+    counter <<- counter + 1
+    cat(counter, "")
+
+    return(p.value)
+}
+
+# Naive KS-test
+test_naive_copula <- function(x) {
+  p.value <- ks.test(x, "pgamma", shape = 3, scale = 1)$p.value
+  list(p.value = p.value)
+}
+
+ptm <- proc.time()
+
+# Generate results
+n <- 100
+rho <- 0.5
+counter <- 0
+nrep <- 1000
+B <- 1000
+pvals_copula <- replicate(nrep, test_gamma(genData(n, qgamma, shape = 3, scale = 1, copula = normalCopula, rho = rho), "pgamma", B = B))
+pvals_naive <- replicate(nrep, test_naive_copula(genData(n, qgamma, shape = 3, scale = 1, copula = normalCopula, rho = rho))$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
+p_values <- c(pvals_copula, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+# Generate histograms plot
+hist_copula_gamma <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+
+print(proc.time() - ptm)
+
+hist_copula_gamma
+```
+
+```{r}
+rho <- 0.5
+x <- genData(100, qgamma, shape = 3, rate = 2, copula = normalCopula, rho = rho)
+ks.test(x, "pgamma", shape = 3, rate = 2)
+```
+}}

### 2022-03-25 Manuscript/manuscript.tex
changed order of sections
more rough detail in fitted parameters and intro

@@
 The Kolmogorov-Smirnov (K-S) statistic is one of the most popular goodness-of-fit tests for comparing a sample with a hypothesized parametric distribution.
+The test is performed as follows.
 Given a sample of n observations, let $S_{n}(x)$ be the empirical cumulative distribution and $F(x)$ be the population cumulative distribution.
 The K-S statistic is defined by: \[d = max(\lvert F(x)-S_{n}(x) \rvert)\] The null hypothesis is that the observations are from the specified distribution $F(x)$, and the alternate hypothesis is that the data is not from $F(x)$.
-If the value of $d$ exceeds the critical value given by a table, the null hypothesis is rejected.
+The table of critical values for $d$ are given by \citet{Massey} for various sample sizes $n$ and significance levels $a$.
+If the value of $d$ exceeds the test's corresponding critical value, the null hypothesis is rejected.
 
@@
 The standard one-sample K-S test applies to independent, continuous data with a hypothesized distribution that is completely specified.
-Often in literature, the test is applied to dependent, discrete, or rounded data, with hypothesized distributions containing estimated parameters.
-As shown by \citet{Steinskog} and later in this paper, the test is too conservative when the parameters are estimated.
-Throughout this paper, the cumulative distribution $F(x)$ is standard normal.
+Often in literature, it has been "discovered" that the test loses its power when applied to dependent, discrete, or rounded data, with hypothesized distributions containing estimated parameters.
+For instance in \citet{Steinskog}, the authors demonstrate the change in power when using estimated parameters and stress caution when using the K-S test in such ways.
+The purpose of this paper is to expand on the misuses of the K-S test and propose solutions in the case that the K-S test would still like to be used.
+
+In order to set up the demonstrations, simulated data is used throughout.
+Unless otherwise specified, the random data is generated from a standard normal distribution with sample size $100$.
+Therefore the cumulative distribution $F(x)$ of the K-S test is standard normal.
 
@@
 However, the procedure is sometimes performed where the population cumulative distribution $F(x)$ has parameters $\mu=\Xbar$, the sample mean, and $\sigma^2=s^2$, the sample variance \citep{Lilliefors}.
-\citet{Lilliefors} also shows that using the standard table when values of the mean and standard deviation are estimated obtains extremely conservative results.
+\citet{Lilliefors} shows that using the standard table when values of the mean and standard deviation are estimated obtains extremely conservative results.
+\citet{Capasso} concludes that failing to re-estimate the parameters may lead to wrong, overly-conservative approximations to the distributions of goodness-of-fit test statistics based on the empirical distribution function.
+\citet{Capasso} also notes that the impact of this possible mistake may turn out to be dramatic and does not vanish as the sample size increases.
+This case is demonstrated in Figure~\ref{fig:hist_fitted} under the Naive plot.
+The naive K-S test was performed by estimating the parameters of $F(x)$ using the fitted distribution of the sample data.
+Since the data is generated from a standard normal distribution with seemingly all assumptions met, a uniform distribution of $U(0,1)$ is expected for the p-values.
+However this is under the assumption that the K-S test holds its power, which it no longer does due to using fitted parameters.
+Therefore, there is notable deviation from the uniform distribution.
 
-To resolve this problem, parametric bootstrap can be performed.
-The parameters of the null distribution are approximated from the bootstrap.
+To resolve this problem, both parametric and non-parametric bootstrap can be performed.
+Performing bootstrap onto goodness-of-fit tests such as the K-S test is a well-researched topic.
+\citet{Genest} provides validity for using parametric bootstrap with various goodness-of-fit tests.
+\citet{Babu} details the bootstrap procedure for goodness-of-fit tests and notes that both parametric and non-parametric procedures lead to correct asymptotic levels, however there is a correction required for the non-parametric case.
+
+The bootstrap procedure is as follows.
+Let $X_1^*,...,X_n^*$ be i.i.d random variables from $\hat{F}_n$, an estimator of the distribution function $F$ based on the sample $X_1,...,X_n$.
+Let $\hat{\theta}_n^* = \theta_n(X_1^*,...,X_n^*)$.
+$\theta$ is the parameter vector, so $\hat{\theta}_n$ represents the sample mean and variance of the sample $X_1,...,X_n$.
+It follows that $\hat{\theta}_n^*$ represents the sample mean and variance of the bootstrap sample $X_1^*,...,X_n^*$.
+
+In the parametric case, the resampling is done where $\hat{F}_n = F(.;\hat{\theta}_n)$.
+Bootstrap samples are drawn from ${F}(.,\hat{\theta}_n)$ where the assumed distribution $F$ is normal and $\hat{\theta}_n = (\Xbar, s)$, the sample mean and sample standard deviation.
+For each bootstrap sample, a K-S test statistic is found using those fitted parameters
+
 Figure~\ref{fig:hist_fitted} displays the results of $1000$ replicate tests using the standard normal distribution with sample size $n=100$.
-In each parametric test, $1000$ bootstrap samples are obtained and the corresponding p-value of the K-S test is calculated.
-In the naive case, K-S tests are performed with fitted parameters.
+In both the parametric and non-parametric cases, $1000$ bootstrap samples are obtained and the corresponding p-value of the K-S test is calculated.
 
@@
   \label{fig:hist_fitted}
-\end{figure}
-
-Since the data is generated from a standard normal distributions with seemingly all assumptions met, a uniform distribution of $U(0,1)$ is expected for the p-values.
-The naive histogram shows that when the parameters are estimated there is notable deviation from the uniform distribution.
-However, through parametric bootstrap of the parameters the p-values appear to retain a uniform distribution.
-
-\hypertarget{sec:rounded}{%
-\section{Rounded Data}\label{sec:rounded}}
-
-Another assumption of the K-S test is that it applies to continuous data.
-This can be easily violated by performing a level of rounding on the data.
-Rounding causes the data to become discrete, and the K-S test can be shown to no longer apply.
-To demonstrate this, simulations were conducted at varying levels of rounding.
-A random sample of size $100$ was collected from the standard normal distribution and subsequently rounded to the degrees of $.01$ and  $.1$.
-This simulation was replicated $1000$ times for each rounding level and the results are shown in Figure~\ref{fig:hist_rounded}.
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics{hist_rounded}
-  \caption{Histograms of P-values with rounded data.}
-  \label{fig:hist_rounded}
-\end{figure}
-
-As mentioned before, the expected distribution of p-values is $U(0,1)$.
-For rounding to the hundreths, though the distribution appears uniform it is still not recommended to use the basic K-S test due to ties in the data.
-The issue is apparent when rounding to the tenths, as the distribution of p-values does not hold a standard uniform distribution and the test no longer applies.
-This simulation shows that rounding can have a serious impact on the power of the K-S test and should be avoided.
-
-There are some solutions in the case that a discrete distribution is in question.
-The chi-squared test is another goodness-of-fit test that can be applied to discrete distributions \citep{Massey}.
-However, the standard K-S test holds various advantages over it.
-In small samples, \citet{Massey} explains that the chi-squared test loses information and validity due to the grouping performed, while the K-S test treats individual observations separately.
-\citet{Massey} additionally notes that the K-S test generally appears to be the more powerful test regardless of sample size.
-
-In addition, a proposed revision of the K-S test can be found in \citet{dgof}.\citet{dgof} provides a revision to R's `ks.test()` function for the case that the null distribution is discrete.
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics{hist_general}
-  \caption{Histograms of P-values with KSGeneral and dgof packages.}
-  \label{fig:hist_general}
 \end{figure}
@@
 \citet{Dimitrova}
+\citet{Genest}
 

### 2022-03-31 Code/Simulation.Rmd
Added GEV testing function, comments in code, and correct naive functions

@@
 library(copula)
+library(evd)
 source('tspb.R')
@@
   }
+
+  # Return empirical p-value
   p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
@@
 
+# Test non-parametric bootstrap as a solution to fitted parameters
 test_babu <- function(x, B = 1000) {
@@
 test_copula <- function(x, dist, B) {
-    ## example assuming normal distribution; normal copula
-    ## get observed stat
+
+    # Get observed statistic
     n <- length(x)
@@
     stat  <- ks.test(x, dist, mean = mu, sd = sigma)$statistic
-    ## get lag-1 sample auto-spearman rho
+
+    # Get lag-1 sample auto-spearman rho
     rho  <-  cor(x[-1], x[-n], method = "spearman")
@@
     np <- normalCopula(r)
-    ## parametric bootstrap to get an empirical distribution of stat
+
+    # Perform parametric bootstrap to get an empirical distribution of stat
     stat.b <- double(n)
-    ## set up containers
+
     for (i in 1:B) {
-        ## get one bootstrap sample
-        ## 1. the marginal distribution is the fitted dist
-        ## 2. there is temporal dependence
+        # 1. The marginal distribution is the fitted dist
+        # 2. There is temporal dependence
         u <- runif(n) 
         for (j in 2:n) {
-            ## could test other copulas later
             u[j]  <- cCopula(c(u[j-1], u[j]), np, indices = 2, inverse = TRUE)
         }
-        ## get bootstrap sample
+
+        # Transform bootstrap sample and fit the parameters
         x.b <- qnorm(u, mean = mu, sd = sigma)
-        ## fit it
         mu.b <- mean(x.b)
         sigma.b <- sd(x.b)
+
+        # Gather bootstrap sample's test statistic
         stat.b[i] <- ks.test(x.b, dist, mean = mu.b, sd = sigma.b)$statistic
@@
 
+    # Return empirical p-value
     p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
@@
     return(p.value)
-    # return empirical p-value    
 }
 
-# Naive KS-test
-test_naive_copula <- function(x) {
-  p.value <- ks.test(x, "pnorm")$p.value
+# Super naive KS-test with fitted parameters
+test_super_naive <- function(x) {
+  p.value <- ks.test(x, "pnorm", mean = mean(x), sd = sd(x))$p.value
   list(p.value = p.value)
@@
 nrep <- 1000
-B <- 1000
+B <- 100
 pvals_copula <- replicate(nrep, test_copula(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), "pnorm", B = B))
-pvals_naive <- replicate(nrep, test_naive_copula(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)
+counter <- 0
+pvals_parametric <- replicate(nrep, test_parametric(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)
+pvals_naive <- replicate(nrep, test_super_naive(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)
 
 # Create a master data_frame with all the results
-histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
-p_values <- c(pvals_copula, pvals_naive)
+histogram <- c(rep("Copula", nrep), rep("Naive Parametric", nrep), rep("Super Naive", nrep))
+p_values <- c(pvals_copula, pvals_parametric, pvals_naive)
 results <- data_frame(p_values, histogram)
@@
 
-# Generate results
+# Set variables
 n <- 100
@@
 b2 <- 0.3
+
+# P-vals from using bootstrap with copulas
 pvals_copula <- replicate(nrep, test_copula(arima.sim(list(order = c(2, 0, 0), 
@@
                                                       sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
-                                                          n = n), "pnorm", B = B))
-pvals_naive <- replicate(nrep, test_naive_copula(arima.sim(list(order = c(2, 0, 0), ar = c(b1, b2)), rand.gen=rnorm, sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)), n = n))$p.value)
+                                                      n = n), 
+                                            "pnorm", 
+                                            B = B))
+counter <- 0
+
+# P-vals from using parametric bootstrap
+pvals_parametric <- replicate(nrep, test_parametric(arima.sim(list(order = c(2, 0, 0), 
+                                                                   ar = c(b1, b2)), 
+                                                              rand.gen=rnorm, 
+                                                              sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)), 
+                                                              n = n))$p.value)
+
+# P-vals from naively using fitted parameters
+pvals_naive <- replicate(nrep, test_super_naive(arima.sim(list(order = c(2, 0, 0), 
+                                                               ar = c(b1, b2)), 
+                                                          rand.gen=rnorm, 
+                                                          sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)), 
+                                                          n = n))$p.value)
 
 # Create a master data_frame with all the results
-histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
-p_values <- c(pvals_copula, pvals_naive)
+histogram <- c(rep("Copula", nrep), rep("Naive Parametric", nrep), rep("Super Naive", nrep))
+p_values <- c(pvals_copula, pvals_parametric, pvals_naive)
 results <- data_frame(p_values, histogram)
@@
 # Save the histogram figure
-#ggsave(filename = "hist_copula_ar2.pdf", plot = hist_copula_ar2, path = "../Manuscript", height = 2.1, width = 6)
-```
-
-```{r}
-b1 <- 0.5
-b2 <- 0.3
-n <- 100
-x <- arima.sim(list(order = c(2, 0, 0), ar = c(b1, b2)), rand.gen=rnorm, sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)), n = n)
-sd(x)
-var(x)
-
-ma <- 0.5
-x <- arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n)
-sd(x)
-var(x)
-
-ar <- 0.5
-x <- arima.sim(list(ar = ar, ma = ma), rand.gen = rnorm, sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), n = n)
-sd(x)
-var(x)
+ggsave(filename = "hist_copula_ar2.pdf", plot = hist_copula_ar2, path = "../Manuscript", height = 2.1, width = 6)
 ```
@@
 ma <- 0.5
+
+# P-vals from using bootstrap with copulas
 pvals_copula <- replicate(nrep, test_copula(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), "pnorm", B = B))
-pvals_naive <- replicate(nrep, test_naive_copula(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n))$p.value)
+counter <- 0
+
+# P-vals from using parametric bootstrap
+pvals_parametric <- replicate(nrep, test_parametric(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n))$p.value)
+
+# P-vals from naively using fitted parameters
+pvals_naive <- replicate(nrep, test_super_naive(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n))$p.value)
 
 # Create a master data_frame with all the results
-histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
-p_values <- c(pvals_copula, pvals_naive)
+histogram <- c(rep("Copula", nrep), rep("Naive Parametric", nrep), rep("Super Naive", nrep))
+p_values <- c(pvals_copula, pvals_parametric, pvals_naive)
 results <- data_frame(p_values, histogram)
@@
 ma <- 0.3
+
+# P-vals from using bootstrap with copulas
 pvals_copula <- replicate(nrep, test_copula(arima.sim(list(ar = ar, 
@@
                                             "pnorm", B = B))
-pvals_naive <- replicate(nrep, test_naive_copula(arima.sim(list(ar = ar, 
+counter <- 0
+
+# P-vals from using parametric bootstrap
+pvals_parametric <- replicate(nrep, test_parametric(arima.sim(list(ar = ar, 
+                                                              ma = ma), 
+                                                      rand.gen=rnorm, 
+                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
+                                                      n = n))$p.value)
+
+# P-vals from naively using fitted parameters
+pvals_naive <- replicate(nrep, test_super_naive(arima.sim(list(ar = ar, 
                                                               ma = ma), 
@@
 # Create a master data_frame with all the results
-histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
-p_values <- c(pvals_copula, pvals_naive)
+histogram <- c(rep("Copula", nrep), rep("Naive Parametric", nrep), rep("Super Naive", nrep))
+p_values <- c(pvals_copula, pvals_parametric, pvals_naive)
 results <- data_frame(p_values, histogram)
@@
 ```{r}
-library(fitdistrplus)
+# Testing bootstrap with copulas for gamma distribution
 test_gamma <- function(x, dist, B = 100, wcopula = normalCopula) {
 
-    #fit <- fitdist(x, "gamma", method = "mle", lower = c(0, 0), start = list(scale = 1, shape = 1))
-    #shape <- fit$estimate[1]
-    #scale <- fit$estimate[2]
-
+    # Get observed stat
+    n <- length(x)
     m <- mean(x)
@@
 
-    ## example assuming normal distribution; normal copula
-    ## get observed stat
-    n <- length(x)
-
-    ## get lag-1 sample auto-spearman rho
+    # Get lag-1 sample auto-spearman rho
     rho  <-  cor(x[-1], x[-n], method = "spearman")
@@
     wcop <- wcopula(r)
-    ## parametric bootstrap to get an empirical distribution of stat
+
+    # Parametric bootstrap to get an empirical distribution of stat
     stat.b <- double(n)
-    ## set up containers
+
     for (i in 1:B) {
-        ## get one bootstrap sample
-        ## 1. the marginal distribution is the fitted dist
-        ## 2. there is temporal dependence
+        # 1. The marginal distribution is the fitted dist
+        # 2. There is temporal dependence
         u <- runif(n)
         for (j in 2:n) {
-            ## could test other copulas later
             u[j]  <- cCopula(c(u[j-1], u[j]), wcop, indices = 2, inverse = TRUE)
         }
-        ## get bootstrap sample
-        ## get fitted parameters for the bootstrap sample
 
+        # Transform the bootstrap sample and fit the parameters
         x.b <- qgamma(u, shape = shape, scale = scale)
@@
         v.b <- var(x.b)
-
         scale.b <- v.b/m.b
@@
 
-        #fit.b <- fitdist(x.b, "gamma", method = "mle", lower = c(0, 0), start = list(scale = 1, shape = 1))
-        #shape.b <- fit.b$estimate[1]
-        #scale.b <- fit.b$estimate[2]
-
+        # Calculate new test statistic
         stat.b[i] <- ks.test(x.b, dist, shape = shape.b, scale = scale.b)$statistic
     }
-    ## return empirical p-value    
+
+    # Return empirical p-value    
     p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
@@
 
-# Naive KS-test
-test_naive_copula <- function(x) {
-  p.value <- ks.test(x, "pgamma", shape = 3, scale = 1)$p.value
+# Parametric bootstrap to solve fitted parameters for gamma distribution
+test_parametric_gamma <- function(x, B = 1000) {
+
+  # Summarize parameters
+  m <- mean(x)
+  v <- var(x)
+  scale <- v/m
+  shape <- m*m/v
+
+  # Store KS statistic from using fitted parameters
+  stat <- ks.test(x, "pgamma", shape = shape, scale = scale)$statistic
+
+  # Parametric bootstrap to approximate the null distribution
+  n <- length(x)
+  stat.b <- double(B)
+  for (i in 1:B) {
+    x.b <- rgamma(n, shape = shape, scale = scale)
+
+    m.b <- mean(x.b)
+    v.b <- var(x.b)
+
+    scale.b <- v.b/m.b
+    shape.b <- m.b*m.b/v.b
+
+    stat.b[i] <- ks.test(x.b, "pgamma", shape = shape.b, scale = scale.b)$statistic
+  }
+
+  # Return empirical p-value
+  p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
+
+  counter <<- counter + 1
+  cat(counter, "")
+  list(p.value = p.value)
+}
+
+# Naive function that incorrectly uses fitted parameters for gamma distribution
+test_super_naive_gamma <- function(x) {
+
+  m <- mean(x)
+  v <- var(x)
+  scale <- v/m
+  shape <- m*m/v
+
+  p.value <- ks.test(x, "pgamma", shape = shape, scale = scale)$p.value
   list(p.value = p.value)
@@
 
-# Generate results
+# Set variables
 n <- 100
-rho <- 0.5
+rho <- 0.7
 counter <- 0
 nrep <- 1000
-B <- 1000
+B <- 100
+
+# P-vals from using bootstrap with copulas
 pvals_copula <- replicate(nrep, test_gamma(genData(n, qgamma, shape = 3, scale = 1, copula = normalCopula, rho = rho), "pgamma", B = B))
-pvals_naive <- replicate(nrep, test_naive_copula(genData(n, qgamma, shape = 3, scale = 1, copula = normalCopula, rho = rho))$p.value)
+counter <- 0
+
+# P-vals from using parametric bootstrap
+pvals_parametric <- replicate(nrep, test_parametric_gamma(genData(n, qgamma, shape = 3, scale = 1, copula = normalCopula, rho = rho))$p.value)
+
+# P-vals from naively using fitted parameters
+pvals_naive <- replicate(nrep, test_super_naive_gamma(genData(n, qgamma, shape = 3, scale = 1, copula = normalCopula, rho = rho))$p.value)
 
 # Create a master data_frame with all the results
-histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
-p_values <- c(pvals_copula, pvals_naive)
+histogram <- c(rep("Copula", nrep), rep("Naive Parametric", nrep), rep("Super Naive", nrep))
+p_values <- c(pvals_copula, pvals_parametric, pvals_naive)
 results <- data_frame(p_values, histogram)
@@
 ```{r}
+# Testing bootstrap with copulas for GEV distribution
+test_gev <- function(x, B = 100, wcopula = normalCopula) {
+
+    n <- length(x)
+
+    # Get observed stat
+    fit <- fgev(x, std.err = FALSE)
+    loc <- fit$estimate[1]
+    scale <- fit$estimate[2]
+    shape <- fit$estimate[3]
+
+    stat  <- ks.test(x, 'pgev', loc = loc, scale = scale, shape = shape)$statistic
+
+    # Get lag-1 sample auto-spearman rho
+    rho  <-  cor(x[-1], x[-n], method = "spearman")
+    r <- iRho(wcopula(), rho)
+    wcop <- wcopula(r)
+
+    # Parametric bootstrap to get an empirical distribution of stat
+    stat.b <- double(n)
+
+    for (i in 1:B) {
+        # 1. The marginal distribution is the fitted dist
+        # 2. There is temporal dependence
+        u <- runif(n)
+        for (j in 2:n) {
+            u[j]  <- cCopula(c(u[j-1], u[j]), wcop, indices = 2, inverse = TRUE)
+        }
+
+        # Transform the bootstrap sample and fit the parameters
+        x.b <- qgev(u, loc = loc, scale = scale, shape = shape)
+
+        fit.b <- fgev(x.b, std.err = FALSE)
+        loc.b <- fit.b$estimate[1]
+        scale.b <- fit.b$estimate[2]
+        shape.b <- fit.b$estimate[3]
+
+        # Calculate bootstrap test statistic
+        stat.b[i] <- ks.test(x.b, 'pgev', loc = loc.b, scale = scale.b, shape = shape.b)$statistic
+    }
+
+    # Return empirical p-value    
+    p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
+
+    counter <<- counter + 1
+    cat(counter, "")
+
+    return(p.value)
+}
+
+# Parametric bootstrap to solve fitted parameters for GEV distribution
+test_parametric_gev <- function(x, B = 1000) {
+
+  # Summarize parameters
+  fit <- fgev(x)
+  loc <- fit$estimate[1]
+  scale <- fit$estimate[2]
+  shape <- fit$estimate[3]
+
+  # Store KS statistic from using fitted parameters
+  stat <- ks.test(x, "pgev", loc = loc, scale = scale, shape = shape)$statistic
+
+  # Parametric bootstrap to approximate the null distribution
+  n <- length(x)
+  stat.b <- double(B)
+  for (i in 1:B) {
+    x.b <- rgev(n, loc = loc, scale = scale, shape = shape)
+
+    fit.b <- fgev(x.b)
+    loc.b <- fit.b$estimate[1]
+    scale.b <- fit.b$estimate[2]
+    shape.b <- fit.b$estimate[3]
+
+    stat.b[i] <- ks.test(x.b, "pgev", shape = shape.b, scale = scale.b)$statistic
+  }
+
+  # Return empirical p-value
+  p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
+
+  counter <<- counter + 1
+  cat(counter, "")
+  list(p.value = p.value)
+}
+
+# Naive function that incorrectly uses fitted parameters for GEV distribution
+test_super_naive_gev <- function(x) {
+
+  fit <- fgev(x)
+  loc <- fit$estimate[1]
+  scale <- fit$estimate[2]
+  shape <- fit$estimate[3]
+
+  p.value <- ks.test(x, "pgev", loc = loc, scale = scale, shape = shape)$p.value
+  list(p.value = p.value)
+}
+
+ptm <- proc.time()
+
+# Set variables
+n <- 100
 rho <- 0.5
-x <- genData(100, qgamma, shape = 3, rate = 2, copula = normalCopula, rho = rho)
-ks.test(x, "pgamma", shape = 3, rate = 2)
+counter <- 0
+nrep <- 1000
+B <- 100
+
+# P-vals from using bootstrap with copulas
+pvals_copula <- suppressWarnings(replicate(nrep, test_gev(genData(n, qgev, loc = 0, shape = 1, scale = 1, copula = normalCopula, rho = rho), B = B)))
+counter <- 0
+
+# P-vals from using parametric bootstrap
+pvals_parametric <- suppressWarnings(replicate(nrep, test_parametric_gamma(genData(n, qgev, shape = 1, scale = 1, copula = normalCopula, rho = rho))$p.value))
+
+# P-vals from naively using fitted parameters
+pvals_naive <- suppressWarnings(replicate(nrep, test_super_naive_gamma(genData(n, qgev, shape = 1, scale = 1, copula = normalCopula, rho = rho))$p.value))
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive Parametric", nrep), rep("Super Naive", nrep))
+p_values <- c(pvals_copula, pvals_parametric, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+# Generate histograms plot
+hist_copula_gev <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+
+print(proc.time() - ptm)
+
+hist_copula_gev
+
+# Save the histogram figure
+ggsave(filename = "hist_copula_gev.pdf", plot = hist_copula_gev, path = "../Manuscript", height = 2.1, width = 6)
 ```
-}}

### 2022-03-31 Code/Simulation.Rmd
Added temporary captions to figures for parameters

@@
 B <- 100
+shape <- 3
+scale <- 1
 
@@
                    theme(legend.position = "none") +
-                   facet_wrap(~histogram, scales = "free_y")
+                   facet_wrap(~histogram, scales = "free_y") +
+                   labs(caption = sprintf("Rho = %s, Shape = %s, Scale = %s", rho, shape, scale))
 
@@
 hist_copula_gamma
+
+# Save the histogram figure
+ggsave(filename = "hist_copula_gamma.pdf", plot = hist_copula_gamma, path = "../Manuscript", height = 2.1, width = 6)
 ```
@@
 B <- 100
+loc <- 0
+shape <- 1
+scale <- 1
 
@@
                    theme(legend.position = "none") +
-                   facet_wrap(~histogram, scales = "free_y")
+                   facet_wrap(~histogram, scales = "free_y") +
+                   labs(caption = sprintf("Rho = %s, Loc = %s, Shape = %s, Scale = %s", rho, loc, shape, scale))
 

### 2022-04-01 Manuscript/manuscript.tex
incomplete literature review in the introduction, added sources

@@
 \begin{abstract}
-The Kolmogorov-Smirnov (KS) test is one the most popular goodness-of-fit tests for comparing a sample with a hypothesized parametric distribution.
-Nevertheless, it has often been misused.
-The standard one-sample KS test applies to independent, continuous data with a hypothesized distribution that is completely specified.
-It is not uncommon, however, to see in the literature that it was applied to dependent, discrete, or rounded data, with hypothesized distributions containing estimated parameters.
-For example, it has been “discovered” multiple times that the test is too conservative when the parameters are estimated [e.g.
-\citet{Steinskog}].
-This paper aims to survey the misuses of the KS test, demonstrate their consequences through simulation, and provide remedies as needed.
+The Kolmogorov-Smirnov (KS) test is one the most popular goodness-of-fit tests for 
+comparing a sample with a hypothesized parametric distribution. Nevertheless, it has 
+often been misused. The standard one-sample KS test applies to independent, continuous 
+data with a hypothesized distribution that is completely specified. It is not uncommon, 
+however, to see in the literature that it was applied to dependent, discrete, or 
+rounded data, with hypothesized distributions containing estimated parameters. 
+For example, it has been “discovered” multiple times that the test is too conservative 
+when the parameters are estimated [e.g. \citet{Steinskog}]. This paper aims to survey 
+the misuses of the KS test, demonstrate their consequences through simulation, and 
+provide remedies as needed.
 \end{abstract}
@@
 
-The Kolmogorov-Smirnov (K-S) statistic is one of the most popular goodness-of-fit tests for comparing a sample with a hypothesized parametric distribution.
-The test is performed as follows.
-Given a sample of n observations, let $S_{n}(x)$ be the empirical cumulative distribution and $F(x)$ be the population cumulative distribution.
-The K-S statistic is defined by: \[d = max(\lvert F(x)-S_{n}(x) \rvert)\] The null hypothesis is that the observations are from the specified distribution $F(x)$, and the alternate hypothesis is that the data is not from $F(x)$.
-The table of critical values for $d$ are given by \citet{Massey} for various sample sizes $n$ and significance levels $a$.
-If the value of $d$ exceeds the test's corresponding critical value, the null hypothesis is rejected.
+The Kolmogorov-Smirnov (K-S) statistic is one of the most popular goodness-of-fit 
+tests for comparing a sample with a hypothesized parametric distribution. The test is 
+performed as follows. Given a sample of n observations, let $S_{n}(x)$ be the empirical 
+cumulative distribution and $F(x)$ be the population cumulative distribution. The K-S 
+statistic is defined by: \[d = max(\lvert F(x)-S_{n}(x) \rvert)\] The null hypothesis 
+is that the observations are from the specified distribution $F(x)$, and the 
+alternate hypothesis is that the data is not from $F(x)$. The table of critical 
+values for $d$ are given by \citet{Massey} for various sample sizes $n$ and significance 
+levels $a$. If the value of $d$ exceeds the test's corresponding critical value, 
+the null hypothesis is rejected.
 
-However, the test is often misused.
-The standard one-sample K-S test applies to independent, continuous data with a hypothesized distribution that is completely specified.
-Often in literature, it has been "discovered" that the test loses its power when applied to dependent, discrete, or rounded data, with hypothesized distributions containing estimated parameters.
-For instance in \citet{Steinskog}, the authors demonstrate the change in power when using estimated parameters and stress caution when using the K-S test in such ways.
-The purpose of this paper is to expand on the misuses of the K-S test and propose solutions in the case that the K-S test would still like to be used.
+However, the test is often misused. The standard one-sample K-S test applies to 
+independent, continuous data with a hypothesized distribution that is completely specified. 
+Often in literature, it has been "discovered" that the test loses its power when 
+applied to dependent or discrete data with hypothesized distributions containing 
+estimated parameters. In the case of estimated parameters, \citet{Steinskog} 
+demonstrates the change in power when using estimated parameters and stress caution in 
+using the K-S test in such ways. \citet{Lilliefors} shows 
+that using the standard table when values of the mean and standard deviation are 
+estimated obtains extremely conservative results. This is supported by \citet{Capasso}, which 
+concludes that failing to re-estimate the parameters may lead to wrong, overly-conservative 
+approximations to the distributions of goodness-of-fit test statistics based on the empirical 
+distribution function. \citet{Capasso} also notes that the impact of this possible mistake 
+may turn out to be dramatic and does not vanish as the sample size increases. Remedies are provided 
+by \citet{Genest} and \citet{Babu} in the form of bootstrap. \citet{Genest} provides validity 
+for using parametric bootstrap with various goodness-of-fit tests. \citet{Babu} details 
+the bootstrap procedure for goodness-of-fit tests and notes that both parametric and 
+non-parametric procedures lead to correct asymptotic levels, however there is a correction 
+required for the non-parametric case. In the case of dependent data, \citet{Durilleul} demonstrates 
+that the K-S statistic is too liberal for medium-to-high positive autocorrelation values. 
+\citet{Durilleul} also shows that for negative autocorrelation values, the behavior is 
+asymmettrical with respect to positive values. For remedies, \citet{Weiss} provides a 
+procedure that is applicable specifically for data modeled by the second-order auto-regressive (AR) process 
+where the parameters are known. \citet{Lanzante} tests various strategies for dealing with temporal dependence
+and concludes that a test based on Monte-Carlo simulations performed the best.
 
-In order to set up the demonstrations, simulated data is used throughout.
-Unless otherwise specified, the random data is generated from a standard normal distribution with sample size $100$.
-Therefore the cumulative distribution $F(x)$ of the K-S test is standard normal.
+The purpose of this paper is to expand on the misuses of the K-S test and propose 
+solutions in the case that the K-S test would still like to be used. In order to set 
+up the demonstrations, simulated data is used throughout. Unless otherwise specified, 
+the random data is generated from a standard normal distribution with sample size $n = 100$. 
+Therefore the cumulative distribution $F(x)$ of the K-S test for much of this paper is standard normal.
 
@@
 
-The K-S test shows significant issues in the case of fitted parameters.
-As previously mentioned, one assumption of the K-S test is that the hypothesized distribution is completely specified.
-However, the procedure is sometimes performed where the population cumulative distribution $F(x)$ has parameters $\mu=\Xbar$, the sample mean, and $\sigma^2=s^2$, the sample variance \citep{Lilliefors}.
-\citet{Lilliefors} shows that using the standard table when values of the mean and standard deviation are estimated obtains extremely conservative results.
-\citet{Capasso} concludes that failing to re-estimate the parameters may lead to wrong, overly-conservative approximations to the distributions of goodness-of-fit test statistics based on the empirical distribution function.
-\citet{Capasso} also notes that the impact of this possible mistake may turn out to be dramatic and does not vanish as the sample size increases.
-This case is demonstrated in Figure~\ref{fig:hist_fitted} under the Naive plot.
-The naive K-S test was performed by estimating the parameters of $F(x)$ using the fitted distribution of the sample data.
-Since the data is generated from a standard normal distribution with seemingly all assumptions met, a uniform distribution of $U(0,1)$ is expected for the p-values.
-However this is under the assumption that the K-S test holds its power, which it no longer does due to using fitted parameters.
-Therefore, there is notable deviation from the uniform distribution.
+The K-S test shows significant issues in the case of fitted parameters. One assumption 
+of the K-S test is that the hypothesized distribution is completely specified. 
+However, the procedure is sometimes performed where the population cumulative 
+distribution $F(x)$ has parameters $\mu=\Xbar$, the sample mean, and $\sigma^2=s^2$, 
+the sample variance \citep{Lilliefors}. This case is demonstrated in Figure~\ref{fig:hist_fitted} 
+under the Naive plot. The naive K-S test was performed by estimating the parameters 
+of $F(x)$ using the fitted distribution of the sample data. Since the data is generated 
+from a standard normal distribution with seemingly all assumptions met, a uniform 
+distribution of $U(0,1)$ is expected for the p-values. However this is under the 
+assumption that the K-S test holds its power, which it no longer does due to using 
+fitted parameters. Therefore, there is notable deviation from the uniform distribution.
 
 To resolve this problem, both parametric and non-parametric bootstrap can be performed. 
-Performing bootstrap onto goodness-of-fit tests such as the K-S test is a well-researched topic.
-\citet{Genest} provides validity for using parametric bootstrap with various goodness-of-fit tests.
-\citet{Babu} details the bootstrap procedure for goodness-of-fit tests and notes that both parametric and non-parametric procedures lead to correct asymptotic levels, however there is a correction required for the non-parametric case.
+Performing bootstrap onto goodness-of-fit tests such as the K-S test is a well-researched 
+topic.
 
@@
 
-\citet{Steinskog}
 \citet{Weiss}
-\citet{Massey}
-\citet{Lilliefors}
 \citet{Arnold}
@@
 \citet{Gleser}
-\citet{Babu}
 \citet{Butorina}
@@
 \citet{Wang}
-\citet{Capasso}
 \citet{Dimitrova}
-\citet{Genest}
 

### 2022-04-10 Poster/poster.Rmd
poster for frontiers presentation

---
title: "Survey of Misuses of the Kolmogorov-Smirnov Test"
author:
  - name: Anthony Zeimbekakis
    affil: 1
  - name: Jun Yan
    affil: 1
affiliation:
  - num: 1
    address: Department of Statistics, University of Connecticut
column_numbers: 4
poster_height: "30in"
poster_width: "48in"
logoleft_name: "uconn-wordmark-single-white.png"
logoright_name: "uconn-wordmark-single-white.png"
primary_colour: "#000E2F"
secondary_colour: "#FFFFFF"
sectitle2_textcol: "#000E2F"
body_textsize: "30pt"
sectitle_textsize: "50pt"
column_margins: "0.2in"
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: ../Manuscript/citations.bib
---

```{css, echo=FALSE}
#title {
  padding-top: 1.5cm;
  padding-bottom: 1.5cm;
}

.title_container {
  height: calc(38in * 0.13);
}

img {
  margin-top: 0cm;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# 1. Introduction

The Kolmogorov-Smirnov (K-S) test is one the most popular goodness-of-fit tests for 
comparing a sample with a hypothesized parametric distribution:

- Given a sample of n observations, let $S_{n}(x)$ be the empirical 
cumulative distribution and $F(x)$ be the population cumulative distribution
- The K-S statistic is defined by: \[d = max(\lvert F(x)-S_{n}(x) \rvert)\] 
- $H_0=$ The data follows a specified distribution $F(x)$
- $H_A=$ The data does not follow a specified distribution $F(x)$
- If the value of $d$ exceeds the test's corresponding critical value, 
the null hypothesis is rejected

The standard one-sample KS test applies to **independent, continuous data with a hypothesized distribution that 
is completely specified**, though it's often used incorrectly. We aim to survey misuses of the K-S test, 
demonstrate their consequences through simulation, and 
provide remedies as needed.

- All simulations unless specified are performed with the standard normal distribution $N(0,1)$

# 2. Fitted Parameters

## 2.1. Assumption:

- Hypothesized distribution $F(x)$ is completely specified

## 2.2. Misuse:

- Hypothesized distribution $F(x)$ is fitted with parameters from the sample

Ex: For the normal distribution, the test is performed where $F(x)$ ~ $N(\bar{X}, s^2)$ [@Lilliefors].

## 2.3. Remedy:

A remedy for this issue is to use bootstrap, detailed by [@Genest] and [@Babu]:

- $d_0$ is the observed K-S statistic
- Let $X_1^*,...,X_n^*$ be i.i.d random variables from $\hat{S}_n$, an estimator of the empirical distribution function $S$ based on the sample $X_1,...,X_n$
- Let $\hat{\theta}_n^* = \theta_n(X_1^*,...,X_n^*)$. $\theta$ represent the sample mean and variance of the bootstrap sample $X_1^*,...,X_n^*$
- New K-S statistic: $d = max(\lvert F(x)-S_{n}(x;\hat{\theta}_n^*) \rvert)$
- Count the number of bootstrap K-S statistics greater than or equal to $d_0$, and divide by the number of 
bootstrap samples to calculate p-value

## 2.4. Results:

<image width="100%" src="../Manuscript/hist_fitted.pdf"/>

- Naive plot was performed with $F(x)$ ~ $N(\bar{X}, s^2)$

- Parametric plot was performed with $\hat{S}_n = F(.;\hat{\theta}_n)$

- Babu plot was performed with $\hat{S}_n = S_n$ and a correction for bias from [@Babu]

With replicate tests, the distribution of p-values is $U(0,1)$. 
However since the assumption of a specified distribution is violated, the naive plot too 
often does not reject the null hypothesis. Bootstrap restores the power of the test.

# 3. Temporal Dependence

## 3.1 Assumption:

- The empirical distribution $S_{n}(x)$ contains independent data

## 3.2 Misues:

- The empirical distribution $S_{n}(x)$ contains dependent data

To demonstrate this, data is simulated from an $AR(1)$ process with $AR = (-3, 3)$.
There is an inverse relationship between negative and positive $AR$ values [@Durilleul], and the 
distributions are not uniform when temporal dependence is present.

<image width="100%" src="../Manuscript/hist_correlation.pdf"/>

## 3.3 Remedy:

- Use copulas combined with bootstrap, for two reasons
1. Ensure that the marginal distribution of our bootstrap data is the same as the fitted distribution
2. Introduce temporal dependence at the same level as the fitted distribution
The procedure used is the same as bootstrap, except the re-sampling comes from correlated data generated by
copulas

## 3.4 Results:

<image width="100%" src="../Manuscript/hist_copula_only.pdf"/>

- The copula remedy restores the $U(0,1)$ nature of the p-values

# 4. Fitted Parameters + Temporal Dependence

If both assumptions are violated, the copula fix works as well.

<image width="100%" src="../Manuscript/hist_copula.pdf"/>

- First plot shows the distribution of p-values when performing the copula remedy
- Second plot shows the distribution of p-values when performing basic parametric bootstrap,
which naively ignores dependence
- Third plot shows the violation of both assumptions,
where fitted parameters are used and dependence is not considered

# 5. Conclusion

- When the K-S test is used with violated assumptions, it no longer holds it's power
and corrections must be made

- In the case of fitted parameters, parametric and non-parametric bootstrap are recommended solutions

- When there is dependence in the data, performing bootstrap with copulas is recommended.

- When both assumptions are violated, meaning there is dependent data and parameters must be estimated,
perform bootstrap with copulas

- If the guess isn't far from the true distribution it may still be reasonably accurate for other distributions.

# 6. References

### 2022-04-10 Code/tspb.R
minor typo fix

@@ -59,7 +59,7 @@ genData <- function(n, qdist, ..., copula, rho) {
 n <- 10000
 rho  <- 0.5
 ## gamma distribution with clayton copula for serial dependence
-x <- genData(n, qamma, shape = 2, scale = 4, copula = claytonCopula, rho = rho)
+x <- genData(n, qgamma, shape = 2, scale = 4, copula = claytonCopula, rho = rho)
 cor(x[-1], x[-n], method = "spearman")
 ## normal distribution with gumbel copula for searial dependence
 x <- genData(n, qnorm, mean = 2, sd = 2, copula = claytonCopula, rho = rho)

### 2022-04-10 Code/Simulation.Rmd
changed gev fit function, captions for hists

@@
 library(evd)
+library(ismev)
 source('tspb.R')
@@
 B <- 100
+
+# P-vals from using bootstrap with copulas
 pvals_copula <- replicate(nrep, test_copula(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), "pnorm", B = B))
 counter <- 0
+
+# P-vals from using parametric bootstrap
 pvals_parametric <- replicate(nrep, test_parametric(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)
+
+# P-vals from naively using fitted parameters
 pvals_naive <- replicate(nrep, test_super_naive(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)
@@
                    theme(legend.position = "none") +
-                   facet_wrap(~histogram, scales = "free_y")
+                   facet_wrap(~histogram, scales = "free_y") +
+                   labs(caption = sprintf("AR = %s", ar))
 hist_copula
@@
 nrep <- 1000
-B <- 100
+B <- 1000
 b1 <- 0.5
@@
                    theme(legend.position = "none") +
-                   facet_wrap(~histogram, scales = "free_y")
+                   facet_wrap(~histogram, scales = "free_y") +
+                   labs(caption = sprintf("AR = (%s, %s)", b1, b2))
 
@@
 nrep <- 1000
-B <- 100
+B <- 1000
 ma <- 0.5
@@
                    theme(legend.position = "none") +
-                   facet_wrap(~histogram, scales = "free_y")
+                   facet_wrap(~histogram, scales = "free_y") +
+                   labs(caption = sprintf("MA = %s", ma))
 
@@
 nrep <- 1000
-B <- 100
+B <- 1000
 ar <- 0.5
@@
                    theme(legend.position = "none") +
-                   facet_wrap(~histogram, scales = "free_y")
+                   facet_wrap(~histogram, scales = "free_y") +
+                   labs(caption = sprintf("AR = %s, MA = %s", ar, ma))
 
@@
 nrep <- 1000
-B <- 100
+B <- 1000
 shape <- 3
@@
     # Get observed stat
-    fit <- fgev(x, std.err = FALSE)
-    loc <- fit$estimate[1]
-    scale <- fit$estimate[2]
-    shape <- fit$estimate[3]
+    fit <- gev.fit(x, show = FALSE)
+    loc <- fit$mle[1]
+    scale <- fit$mle[2]
+    shape <- fit$mle[3]
 
@@
 
-        fit.b <- fgev(x.b, std.err = FALSE)
-        loc.b <- fit.b$estimate[1]
-        scale.b <- fit.b$estimate[2]
-        shape.b <- fit.b$estimate[3]
+        fit.b <- gev.fit(x.b, show = FALSE)
+        loc.b <- fit.b$mle[1]
+        scale.b <- fit.b$mle[2]
+        shape.b <- fit.b$mle[3]
 
@@
   # Summarize parameters
-  fit <- fgev(x)
-  loc <- fit$estimate[1]
-  scale <- fit$estimate[2]
-  shape <- fit$estimate[3]
+  fit <- gev.fit(x, show = FALSE)
+  loc <- fit$mle[1]
+  scale <- fit$mle[2]
+  shape <- fit$mle[3]
 
@@
 
-    fit.b <- fgev(x.b)
-    loc.b <- fit.b$estimate[1]
-    scale.b <- fit.b$estimate[2]
-    shape.b <- fit.b$estimate[3]
+    fit.b <- gev.fit(x.b, show = FALSE)
+    loc.b <- fit.b$mle[1]
+    scale.b <- fit.b$mle[2]
+    shape.b <- fit.b$mle[3]
 
@@
 
-  fit <- fgev(x)
-  loc <- fit$estimate[1]
-  scale <- fit$estimate[2]
-  shape <- fit$estimate[3]
+  fit <- gev.fit(x, show = FALSE)
+  loc <- fit$mle[1]
+  scale <- fit$mle[2]
+  shape <- fit$mle[3]
 
@@
 loc <- 0
-shape <- 1
+shape <- 0.2
 scale <- 1
@@
 # P-vals from using bootstrap with copulas
-pvals_copula <- suppressWarnings(replicate(nrep, test_gev(genData(n, qgev, loc = 0, shape = 1, scale = 1, copula = normalCopula, rho = rho), B = B)))
+pvals_copula <- replicate(nrep, test_gev(genData(n, qgev, loc = 0, shape = shape, scale = 1, copula = normalCopula, rho = rho), B = B))
 counter <- 0
@@
 # P-vals from using parametric bootstrap
-pvals_parametric <- suppressWarnings(replicate(nrep, test_parametric_gamma(genData(n, qgev, shape = 1, scale = 1, copula = normalCopula, rho = rho))$p.value))
+pvals_parametric <- suppressWarnings(replicate(nrep, test_parametric_gamma(genData(n, qgev, loc = 0, shape = shape, scale = 1, copula = normalCopula, rho = rho))$p.value))
 
 # P-vals from naively using fitted parameters
-pvals_naive <- suppressWarnings(replicate(nrep, test_super_naive_gamma(genData(n, qgev, shape = 1, scale = 1, copula = normalCopula, rho = rho))$p.value))
+pvals_naive <- replicate(nrep, test_super_naive_gamma(genData(n, qgev, loc = 0, shape = shape, scale = 1, copula = normalCopula, rho = rho))$p.value)
 
@@
 ```
+
+```{r}
+ptm <- proc.time()
+
+# Set variables
+n <- 100
+ar <- 0.5
+counter <- 0
+nrep <- 1
+B <- 100
+
+# P-vals from using bootstrap with copulas
+pvals_copula <- replicate(nrep, test_copula(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), "pnorm", B = B))
+counter <- 0
+
+# P-vals from naively using fitted parameters
+pvals_naive <- replicate(nrep, test_super_naive(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
+p_values <- c(pvals_copula, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+# Generate histograms plot
+hist_copula_only <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y") +
+                   labs(caption = sprintf("AR = %s", ar))
+hist_copula_only
+
+print(proc.time() - ptm)
+
+# Save the histogram figure
+ggsave(filename = "hist_copula_only.pdf", plot = hist_copula_only, path = "../Manuscript", height = 2.1, width = 6)
+```

### 2022-04-10 Manuscript/manuscript.tex
slightly more detail in fitted, beginning of dependence

@@
 To resolve this problem, both parametric and non-parametric bootstrap can be performed. 
-Performing bootstrap onto goodness-of-fit tests such as the K-S test is a well-researched 
-topic.
-
 The bootstrap procedure is as follows.
-Let $X_1^*,...,X_n^*$ be i.i.d random variables from $\hat{F}_n$, an estimator of the distribution function $F$ based on the sample $X_1,...,X_n$.
+Let $X_1^*,...,X_n^*$ be i.i.d random variables from $\hat{S}_n$, an estimator of the distribution function $S_n$ based on the sample $X_1,...,X_n$.
 Let $\hat{\theta}_n^* = \theta_n(X_1^*,...,X_n^*)$.
@@
 It follows that $\hat{\theta}_n^*$ represents the sample mean and variance of the bootstrap sample $X_1^*,...,X_n^*$.
+Thus, the K-S statistic for each bootstrap case is \[max(\lvert F(x)-S^*_n(x) \rvert)\]
 
-In the parametric case, the resampling is done where $\hat{F}_n = F(.;\hat{\theta}_n)$.
+In parametric bootstrap, the resampling is done where $\hat{S}_n = F(.;\hat{\theta}_n)$.
 Bootstrap samples are drawn from ${F}(.,\hat{\theta}_n)$ where the assumed distribution $F$ is normal and $\hat{\theta}_n = (\Xbar, s)$, the sample mean and sample standard deviation.
@@
 
-Figure~\ref{fig:hist_fitted} displays the results of $1000$ replicate tests using the standard normal distribution with sample size $n=100$.
-In both the parametric and non-parametric cases, $1000$ bootstrap samples are obtained and the corresponding p-value of the K-S test is calculated.
+In non-parametric bootstrap, the resampling is done where $\hat{S}_n = S_n$.
+
+Figure~\ref{fig:hist_fitted} displays the results of from our simulations. The procedure 
+is replicated $1000$ times using the standard normal distribution with sample size $n=100$. 
+In each replicate test, $1000$ bootstrap samples are obtained. The p-value can be calculated
+by counting the number of bootstrap K-S statistics greater than or equal to the observed K-S statistic, 
+and then dividing by the number of bootstrap samples. It is clear from the figure that both
+bootstrap processes correct for the problem of fitted parameters. The plots appear to be
+$U(0,1)$, which is expected of a full power test.
 
@@
 
-The K-S test shows significant issues in the case of serial dependence.
+The K-S test also displays issues in the case of dependence. An assumption of the 
+test is that the data is independent. Unfortunately, real data is often temporally
+or spatially dependent and the results of a goodness-of-fit test would be valuable. 
+When the K-S test is performed on dependent data, it performs poorly. This is demonstrated
+with a simulation in Figure~\ref{fig:hist_correlation}. Data is generated from a
+first-order autoregressive model.
 

### 2022-04-11 Code/Simulation.Rmd
deleted unnecessary code, fixed copula_only section

@@
 # Load packages
-library(xtable)
 library(dgof)
 library(tidyverse)
-library(KSgeneral)
 library(copula)
@@
 ggsave(filename = "hist_fitted.pdf", plot = hist_fitted, path = "../Manuscript", height = 2.1, width = 6)
-```
-
-```{r hist_rounded}
-# Test to show that rounding changes the power of the test
-test_rounded <- function(n_tests, n_samples, digits) {
-
-  p_values <- double(n_tests)
-
-  for(i in 1:n_tests) {
-
-    # Generate random rounded data, perform a KS-test, and store the p-value
-    data <- round(rnorm(n_samples), digits)
-    p_values[i] <- ks.test(data, "pnorm")$p.value
-  }
-
-  return(p_values)
-}
-
-# Create the histograms displaying p-values from each test
-n_tests <- 1000
-n <- 100
-hist1 <- suppressWarnings(test_rounded(n_tests, n, 2))
-hist2 <- suppressWarnings(test_rounded(n_tests, n, 1))
-
-# Create a master data_frame with all the results
-histogram <- c(rep(".01", n_tests), rep(".1", n_tests))
-p_values <- c(hist1, hist2)
-results <- data_frame(p_values, histogram)
-
-# Generate histograms plot
-hist_rounded <- ggplot(results) + 
-                geom_histogram(aes(x = p_values, fill = histogram), binwidth = 1/20, boundary = 0) + 
-                facet_grid(~histogram) +
-                theme(legend.position = "none") +
-                scale_x_continuous(name = "p-value", breaks = seq(0, 1))
-
-# Save the histogram figure
-ggsave(filename = "hist_rounded.pdf", plot = hist_rounded, path = "../Manuscript", height = 2.1, width = 6)
-
-qqplot(hist2, runif(100), xlab = "Rounded", ylab = "Uniform", main = "Testing qqplot")
-abline(0, 1)
-p <- ggplot(results, aes(sample = p_values))
-p + stat_qq(distribution = stats::qunif) + geom_abline(intercept = 0, slope = 1) + xlim(0, 1) + ylim(0, 1)
-```
-
-```{r hist_general}
-# Test the KSgeneral package as a solution to rounded data
-test_general <- function(n_tests, n_samples, digits, B) {
-
-  results1 <- double(n_tests)
-  results2 <- double(n_tests)
-  results3 <- double(n_tests)
-  results4 <- double(n_tests)
-
-  # Create the rounded normal step function
-  left <- -4-0.1^digits
-  y <- pnorm(seq(left, 4, by = 0.1^digits))
-  sfun  <- stepfun(seq(-4, 4, by = 0.1^digits), y)
-
-  for (i in 1:n_tests) {
-    cat(i, "")
-    # Generate random rounded data, perform 3 KS-tests, and store the p-values
-    # 1. Using the rounded normal step function
-    # 2. Using the naive continuous standard normal function
-    data <- round(rnorm(n_samples), digits)
-    results1[i] <- KSgeneral::disc_ks_test(data, sfun, exact = TRUE)$p.value
-    results2[i] <- dgof::ks.test(data, sfun, exact = TRUE)$p.value
-    results3[i] <- ks.test(data, sfun, simulate.p.value = TRUE, B = B)$p.value
-    results4[i] <- ks.test(data, "pnorm")$p.value
-  }
-
-  # Create a master data_frame for p-values
-  test <- c(rep("KSgeneral", n_tests), rep("dgof", n_tests), rep("dgofsim", n_tests), rep("Naive", n_tests))
-  digits <- c(rep(.1^digits, 4*n_tests))
-  p_values <- c(results1, results2, results3, results4)
-  results <- data_frame(p_values, test, digits)
-
-  return(results)
-}
-
-ptm <- proc.time()
-
-n_tests = 100
-n = 30
-B = 1000
-
-# Create the histograms displaying p-values from each test
-test1 <- suppressWarnings(test_general(n_tests, n, digits = 2, B = B))
-test2 <- suppressWarnings(test_general(n_tests, n, digits = 1, B = B))
-results <- rbind(test1, test2)
-
-# Generate histograms plot
-hist_general <- ggplot(results) + 
-                geom_histogram(aes(x = p_values, fill = test), boundary = 0, binwidth = 1/20) + 
-                scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
-                facet_grid(test~digits) +
-                theme(legend.position = "none")
-
-# Save the histogram figure
-ggsave(filename = "hist_general.pdf", plot = hist_general, path = "../Manuscript", height = 4.2, width = 6)
-
-proc.time() - ptm
-
-qqplot(test1$p_values[1:100], runif(100), xlab = "KSGeneral", ylab = "Uniform", main = "Testing qqplot")
-abline(0, 1)
-# could try qqplot for unit interval
-# is qqplot close to 45 degree line, otherwise no
 ```
@@
 
+# Super naive KS-test with fitted parameters
+test_super_duper_naive <- function(x) {
+  p.value <- ks.test(x, "pnorm", mean = 0, sd = 1)$p.value
+  list(p.value = p.value)
+}
+
 # Set variables
@@
 counter <- 0
-nrep <- 1
+nrep <- 1000
 B <- 100
@@
 # P-vals from naively using fitted parameters
-pvals_naive <- replicate(nrep, test_super_naive(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)
+pvals_naive <- replicate(nrep, test_super_duper_naive(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)
 

### 2022-04-11 Manuscript/manuscript.tex
additions to dependence, more figures

@@
 \begin{abstract}
-The Kolmogorov-Smirnov (KS) test is one the most popular goodness-of-fit tests for 
+The Kolmogorov-Smirnov (K-S) test is one the most popular goodness-of-fit tests for 
 comparing a sample with a hypothesized parametric distribution. Nevertheless, it has 
@@
 For example, it has been “discovered” multiple times that the test is too conservative 
-when the parameters are estimated [e.g. \citet{Steinskog}]. This paper aims to survey 
-the misuses of the KS test, demonstrate their consequences through simulation, and 
-provide remedies as needed.
+when the parameters are estimated. This paper aims to survey the misuses of the KS test, 
+demonstrate their consequences through simulation, and provide remedies as needed.
 \end{abstract}
@@
 and concludes that a test based on Monte-Carlo simulations performed the best.
+We propose a procedure involving copulas to account for dependence.
 
@@
 The bootstrap procedure is as follows.
-Let $X_1^*,...,X_n^*$ be i.i.d random variables from $\hat{S}_n$, an estimator of the distribution function $S_n$ based on the sample $X_1,...,X_n$.
-Let $\hat{\theta}_n^* = \theta_n(X_1^*,...,X_n^*)$.
-$\theta$ is the parameter vector, so $\hat{\theta}_n$ represents the sample mean and variance of the sample $X_1,...,X_n$.
-It follows that $\hat{\theta}_n^*$ represents the sample mean and variance of the bootstrap sample $X_1^*,...,X_n^*$.
-Thus, the K-S statistic for each bootstrap case is \[max(\lvert F(x)-S^*_n(x) \rvert)\]
+
+\begin{itemize}
+  \item 
+    Let $X_1^*,...,X_n^*$ be i.i.d random variables from $\hat{S}_n$, an estimator 
+    of the distribution function $S_n$ based on the sample $X_1,...,X_n$
+  \item 
+    Let $\hat{\theta}_n^* = \theta_n(X_1^*,...,X_n^*)$, where $\theta$ is the 
+    parameter vector and $\hat{\theta}_n$ represents the sample mean and variance 
+    of the sample $X_1,...,X_n$
+  \item 
+    $\hat{\theta}_n^*$ represents the sample mean and variance of the bootstrap 
+    sample $X_1^*,...,X_n^*$
+  \item Thus, the K-S statistic for each bootstrap case is $max(\lvert F(x)-S^*_n(x) \rvert)$
+\end{itemize}
 
 In parametric bootstrap, the resampling is done where $\hat{S}_n = F(.;\hat{\theta}_n)$. 
-Bootstrap samples are drawn from ${F}(.,\hat{\theta}_n)$ where the assumed distribution $F$ is normal and $\hat{\theta}_n = (\Xbar, s)$, the sample mean and sample standard deviation.
-For each bootstrap sample, a K-S test statistic is found using those fitted parameters
+Bootstrap samples are drawn from ${F}(.,\hat{\theta}_n)$ where the assumed distribution 
+$F$ is normal and $\hat{\theta}_n = (\Xbar, s)$, the sample mean and sample standard 
+deviation. For each bootstrap sample, a K-S test statistic is found using those 
+fitted parameters.
 
@@
 
-\hypertarget{sec:correlation}{%
-\section{Problem under Serial Dependence}\label{sec:correlation}}
+\hypertarget{sec:dependence}{%
+\section{Problem under Serial Dependence}\label{sec:dependence}}
 
-The K-S test also displays issues in the case of dependence. An assumption of the 
+The K-S test also displays issues in the case of dependence. As mentioned, an assumption of the 
 test is that the data is independent. Unfortunately, real data is often temporally
 or spatially dependent and the results of a goodness-of-fit test would be valuable. 
-When the K-S test is performed on dependent data, it performs poorly. This is demonstrated
+When the K-S test is performed on dependent data it performs poorly. This is demonstrated
 with a simulation in Figure~\ref{fig:hist_correlation}. Data is generated from a
-first-order autoregressive model.
+first-order autoregressive model (AR(1)) with a standard normal distribution. The simulation
+is done with the levels of $\psi$ varying from $(-3,3)$. The results support \citet{Durilleul}'s 
+assertion that the K-S statistic is too liberal for positive autocorrelation values, and 
+that the behavior is asymmettrical for negative values.
 
@@
 
+In order to correct this, we can employ copulas. A copula is a mechanism to form 
+joined distributions. It allows us to incorporate temporal dependence while ensuring that our
+marginal distribution is the same as the fitted distribution. The procedure is as follows:
+
+\begin{enumerate}
+  \item Calculate the observed K-S statistic
+  \item Get the lag-1 sample auto-spearman rho
+  \item Perform parametric bootstrap to get an empirical distribution of the K-S statistic
+\end{enumerate}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics{hist_copula_only}
+  \caption{Histograms demonstrating copula use to correct dependence.}
+  \label{fig:hist_copula_only}
+\end{figure}
+
+Figure~\ref{fig:hist_copula_only} displays the results of the copula remedy for dependent data.
+The data is generated from an AR(1) model with $\psi = .5$. The copula used is to model
+dependence is the normal copula. $1000$ replicate tests were performed with $1000$ bootstrap samples per test.
+The naive test is performed by simply using the K-S test without correcting for any 
+potential dependence.
+
+\hypertarget{sec:fittedwithdependence}{%
+\section{Fitted with Dependence}\label{sec:fittedwithdependence}}
+
+The remedy using copulas is effective in the case where both assumptions are violated.
+This is shown in Figure~\ref{fig:hist_copula}. The "super naive" plot is the resulting 
+p-values when you naively use fitted parameters while ignoring dependence in the data.
+The "naive parametric" plot is the result of applying parametric bootstrap to correct
+for fitted parameters, as done in section \ref{fitted}. Of course, the "copula" plot 
+applies the fix for both assumptions.
+
 \begin{figure}[tbp]
@@
   \includegraphics{hist_copula}
-  \caption{Histograms demonstrating copula to correct correlation.}
+  \caption{Histograms demonstrating copula use to correct fitted parameters and dependence.}
   \label{fig:hist_copula}
+\end{figure}
+
+We would also like to show that copulas work for more than a simple AR(1) model. 
+Figure~\ref{fig:hist_copula_ma1} is the procedure performed on data generated from 
+an MA(1) model with $\theta = 0.5$. Figure~\ref{fig:hist_copula_arma} is the procedure 
+performed on data generated from an ARMA(1,1) model with $\psi = 0.5$ and $\theta = 0.3$. 
+It is also possible to apply our procedure to other distributions. The data in Figure~\ref{fig:hist_copula_gamma} is generated from $Gamma ~ (3,1)$ with $\rho = 0.5$.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics{hist_copula_ma1}
+  \caption{Histograms demonstrating remedy use with MA(1) model.}
+  \label{fig:hist_copula_ma1}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics{hist_copula_arma}
+  \caption{Histograms demonstrating remedy use with ARMA(1,1) model.}
+  \label{fig:hist_copula_arma}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics{hist_copula_gamma}
+  \caption{Histograms demonstrating remedy with Gamma(3,1).}
+  \label{fig:hist_copula_gamma}
 \end{figure}
@@
 
-Adding these to see the full bibliography:
-
-\citet{Weiss}
-\citet{Arnold}
-\citet{Conover}
-\citet{Gleser}
 \citet{Butorina}
@@
 \citet{Wang}
-\citet{Dimitrova}
 

### 2022-04-11 Manuscript/manuscript.tex
minor comments

@@
 
-\title{Survey of Misuses of the Kolmogorov–Smirnov-Test}
+\newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
+
+\title{On Misuses of the Kolmogorov–Smirnov-Test}
 
@@
 For example, it has been “discovered” multiple times that the test is too conservative 
-when the parameters are estimated. This paper aims to survey the misuses of the KS test, 
-demonstrate their consequences through simulation, and provide remedies as needed.
+when the parameters are estimated \citep[e.g.,][]{Steinskog}. This paper aims to survey 
+the misuses of the KS test, demonstrate their consequences through simulation, and 
+provide remedies as needed.
 \end{abstract}
@@
 cumulative distribution and $F(x)$ be the population cumulative distribution. The K-S 
-statistic is defined by: \[d = max(\lvert F(x)-S_{n}(x) \rvert)\] The null hypothesis 
+statistic is defined by:
+\[
+  d = \max(\lvert F(x)-S_{n}(x) \rvert).
+\]
+\jy{equations are part of sentences and should be punctuated.}
+The null hypothesis 
 is that the observations are from the specified distribution $F(x)$, and the 
@@
     sample $X_1^*,...,X_n^*$
-  \item Thus, the K-S statistic for each bootstrap case is $max(\lvert F(x)-S^*_n(x) \rvert)$
+  \item Thus, the K-S statistic for each bootstrap case is $\max(\lvert F(x)-S^*_n(x) \rvert)$
 \end{itemize}

### 2022-04-22 Manuscript/manuscript.tex
updated introduction and non-parametric sections

--- 2022-04-11 Manuscript/manuscript.tex
@@
 
-\title{Survey of Misuses of the Kolmogorov–Smirnov-Test}
+\title{On Misuses of the Kolmogorov–Smirnov-Test}
 
@@
 Department of Statistics, University of Connecticut}
-\date{January 23, 2021}
+\date{April 21, 2022}
 
@@
 For example, it has been “discovered” multiple times that the test is too conservative 
-when the parameters are estimated. This paper aims to survey the misuses of the KS test, 
+when the parameters are estimated. This paper aims to discuss misuses of the KS test, 
 demonstrate their consequences through simulation, and provide remedies as needed.
@@
 tests for comparing a sample with a hypothesized parametric distribution. The test is 
-performed as follows. Given a sample of n observations, let $S_{n}(x)$ be the empirical 
-cumulative distribution and $F(x)$ be the population cumulative distribution. The K-S 
-statistic is defined by: \[d = max(\lvert F(x)-S_{n}(x) \rvert)\] The null hypothesis 
-is that the observations are from the specified distribution $F(x)$, and the 
+performed as follows. Let $X_1, ..., X_n$ be i.i.d. random variables from $F_{n}(x)$,
+the empirical cumulative distribution.
+Let $F(x)$ be the population cumulative distribution. The K-S 
+statistic is \[d = \max\lvert F_{n}(x) - F(x) \rvert\]. The null hypothesis 
+is that the observations $X_1, ..., X_n$ are from the specified distribution $F(x)$, and the 
 alternate hypothesis is that the data is not from $F(x)$. The table of critical 
@@
 asymmettrical with respect to positive values. For remedies, \citet{Weiss} provides a 
-procedure that is applicable specifically for data modeled by the second-order auto-regressive (AR) process 
-where the parameters are known. \citet{Lanzante} tests various strategies for dealing with temporal dependence
-and concludes that a test based on Monte-Carlo simulations performed the best.
-We propose a procedure involving copulas to account for dependence.
+procedure that is applicable specifically for data modeled by the second-order auto-regressive (AR) process where the parameters are known.
+\citet{Lanzante} tests various strategies for dealing with temporal dependenceand concludes that a test based on Monte-Carlo simulations performed the best.
+We propose a bootstrap procedure involving copulas to account for dependence.
 
@@
   \item 
-    Let $X_1^*,...,X_n^*$ be i.i.d random variables from $\hat{S}_n$, an estimator 
-    of the distribution function $S_n$ based on the sample $X_1,...,X_n$
+    Let $X_1^*,...,X_n^*$ be i.i.d random variables from $\hat{F}_n$, an estimator 
+    of the distribution function $F_n$ based on the sample $X_1,...,X_n$
   \item 
@@
     sample $X_1^*,...,X_n^*$
-  \item Thus, the K-S statistic for each bootstrap case is $max(\lvert F(x)-S^*_n(x) \rvert)$
+  \item Thus, the K-S statistic for each bootstrap case is $max(\lvert F(x)-F^*_n(x) \rvert)$
 \end{itemize}
 
-In parametric bootstrap, the resampling is done where $\hat{S}_n = F(.;\hat{\theta}_n)$. 
+In parametric bootstrap, the resampling is done where $\hat{F}_n = F(.;\hat{\theta}_n)$. 
 Bootstrap samples are drawn from ${F}(.,\hat{\theta}_n)$ where the assumed distribution 
@@
 
-In non-parametric bootstrap, the resampling is done where $\hat{S}_n = S_n$.
+In non-parametric bootstrap, the resampling is done where $\hat{F}_n = F_n$. The non-parametric
+case requires a correction for bias detailed by \citet{Babu}. There is a known bias
+term $B_{n}(x) = \sqrt{n}(F_{n}(x) - F(x;\hat{\theta}_n)$. Including this term in the
+calculation of the K-S statistic corrects the bias \citet{Babu}:
+$d = \max\lvert F_{n}(x) - F(x) - B_{n}(x) \rvert$.
 
@@
 
+\begin{figure}[tbp]
+  \centering
+  \includegraphics{hist_copula_ar2}
+  \caption{Histograms demonstrating copula use to correct dependence.}
+  \label{fig:hist_copula_ar2}
+\end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics{hist_copula_gev}
+  \caption{Histograms demonstrating copula use to correct dependence.}
+  \label{fig:hist_copula_gev}
+\end{figure}
+
 \hypertarget{sec:conclusion}{%

### 2022-04-22 Manuscript/manuscript.tex

@@
 
+\newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
+
 \title{On Misuses of the Kolmogorov–Smirnov-Test}
@@
 For example, it has been “discovered” multiple times that the test is too conservative 
-when the parameters are estimated. This paper aims to discuss misuses of the KS test, 
-demonstrate their consequences through simulation, and provide remedies as needed.
+when the parameters are estimated \citep[e.g.,][]{Steinskog}. This paper aims to survey 
+the misuses of the KS test, demonstrate their consequences through simulation, and 
+provide remedies as needed.
 \end{abstract}
@@
 Let $F(x)$ be the population cumulative distribution. The K-S 
-statistic is \[d = \max\lvert F_{n}(x) - F(x) \rvert\]. The null hypothesis 
-is that the observations $X_1, ..., X_n$ are from the specified distribution $F(x)$, and the 
+statistic is 
+\[
+  d = \max{\lvert F_{n}(x) - F(x) \rvert}.
+\].
+The null hypothesis is that the observations $X_1, ..., X_n$ are from the specified distribution $F(x)$, and the 
 alternate hypothesis is that the data is not from $F(x)$. The table of critical 
@@
 asymmettrical with respect to positive values. For remedies, \citet{Weiss} provides a 
-procedure that is applicable specifically for data modeled by the second-order auto-regressive (AR) process where the parameters are known.
-\citet{Lanzante} tests various strategies for dealing with temporal dependenceand concludes that a test based on Monte-Carlo simulations performed the best.
+procedure that is applicable specifically for data modeled by the second-order auto-regressive (AR) 
+process where the parameters are known. \citet{Lanzante} tests various strategies for dealing with 
+temporal dependenceand concludes that a test based on Monte-Carlo simulations performed the best.
 We propose a bootstrap procedure involving copulas to account for dependence.
@@
     sample $X_1^*,...,X_n^*$
-  \item Thus, the K-S statistic for each bootstrap case is $max(\lvert F(x)-F^*_n(x) \rvert)$
+  \item Thus, the K-S statistic for each bootstrap case is $\max(\lvert F(x)-F^*_n(x) \rvert)$
 \end{itemize}

### 2022-04-22 Manuscript/manuscript.tex
updated conclusion

@@
 
-Conclusion here.
-
-\citet{Butorina}
-\citet{Racine}
-\citet{Wang}
+The K-S test has base assumptions that the hypothesized distribution is completely specified
+and the data is independent. When these assumptions are violated, the test is no
+longer accurate and remedies must be performed. In the case of fitted parameters, 
+parametric and non-parametric bootstrap can restore the power of the test. A bias 
+correction is required if the non-parametric form is used \citep{Babu}. In the case of dependent
+data, a procedure using bootstrap with copulas to model dependency shows positive results.
+When both assumptions are violated, that is the case where the data has dependence and 
+parameters must be fitted, the copula remedy also shows positive results. The tests were 
+performed on simulated data from a standard normal distribution, though also appear effective
+against other distributions such as gamma and gev. The copula remedy
+is not a complete solution. Regardless of the true depedence, we use an AR(1) model.
+Therefore, if the AR(1) model is a close approximation of the truth, the fix can work.
+However, in cases such as AR(2), the approximation is incorrect and the fix does not 
+completely restore power.
 

### 2022-04-22 Manuscript/manuscript.tex
more detail in fitted+dependence section

@@
 The "naive parametric" plot is the result of applying parametric bootstrap to correct
-for fitted parameters, as done in section \ref{fitted}. Of course, the "copula" plot 
-applies the fix for both assumptions.
+for fitted parameters while ignoring potential dependence. Of course, the "copula" 
+plot applies the fix for both assumptions. The results show that copula remedy generates 
+uniform p-values and restores the power of the K-S test.
 
@@
 
-We would also like to show that copulas work for more than a simple AR(1) model. 
+The copula fix is not a complete solution, because regardless of the true dependence in the data
+we assume an AR(1) model by taking the lag-1 sample auto-spearman rho. However, we can 
+show that as long as the AR(1) assumption is a close approximation, the correction still restores power to the test.
 Figure~\ref{fig:hist_copula_ma1} is the procedure performed on data generated from 
-an MA(1) model with $\theta = 0.5$. Figure~\ref{fig:hist_copula_arma} is the procedure 
-performed on data generated from an ARMA(1,1) model with $\psi = 0.5$ and $\theta = 0.3$. 
-It is also possible to apply our procedure to other distributions. The data in Figure~\ref{fig:hist_copula_gamma} is generated from $Gamma ~ (3,1)$ with $\rho = 0.5$.
+an MA(1) model with $\theta = 0.5$. Figure~\ref{fig:hist_copula_arma} displays results with 
+data generated from an ARMA(1,1) model with $\psi = 0.5$ and $\theta = 0.3$.
 
@@
 
+It is also possible to apply our procedure to other distributions. All of the simulations
+to this point have been done with standard normal data. The data in Figure~\ref{fig:hist_copula_gamma} 
+is generated from $Gamma ~ (3,1)$ with a correlation coefficient of $\rho = 0.5$. Figure~\ref{fig:hist_copula_gev}
+shows the procedure applied to data from $GEV ~ (0, 0.2, 1)$ with a correlation coefficient of $\rho = 0.5$.
+
 \begin{figure}[tbp]
@@
   \centering
+  \includegraphics{hist_copula_gev}
+  \caption{Histograms demonstrating copula use to correct dependence.}
+  \label{fig:hist_copula_gev}
+\end{figure}
+
+Where this remedy falls short is when the approximation of an AR(1) model is too inaccurate.
+An AR(2) model can be used to demonstrate this. For an AR(2) model with $\phi = (0.5, 0.3)$,
+Figure~\ref{fig:hist_copula_ar2} displays the results of applying the various remedies. 
+While the remedies improve the plot of the p-values in comparison to the naive case,
+because the approximation is not close enough the correction does not work completely.
+
+\begin{figure}[tbp]
+  \centering
   \includegraphics{hist_copula_ar2}
@@
   \label{fig:hist_copula_ar2}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics{hist_copula_gev}
-  \caption{Histograms demonstrating copula use to correct dependence.}
-  \label{fig:hist_copula_gev}
 \end{figure}

### 2022-04-23 Manuscript/manuscript.tex
comments and edits

@@
 
-\makeatletter
-\newcommand*{\Xbar}{}%
-\DeclareRobustCommand*{\Xbar}{%
-  \mathpalette\@Xbar{}%
-}
-\newcommand*{\@Xbar}[2]{%
-  % #1: math style
-  % #2: unused (empty)
-  \sbox0{$#1\mathrm{X}\m@th$}%
-  \sbox2{$#1X\m@th$}%
-  \rlap{%
-    \hbox to\wd2{%
-      \hfill
-      $\overline{%
-        \vrule width 0pt height\ht0 %
-        \kern\wd0 %
-      }$%
-    }%
-  }%
-  \copy2 %
-}
-\makeatother
-
 \newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
 
-\title{On Misuses of the Kolmogorov–Smirnov-Test}
+\title{On Misuses of the Kolmogorov–-Smirnov Test for One Sample Goodness-of-Fit}
 
@@
 \begin{abstract}
-The Kolmogorov-Smirnov (K-S) test is one the most popular goodness-of-fit tests for 
+The Kolmogorov--Smirnov (KS) test is one the most popular goodness-of-fit tests for 
 comparing a sample with a hypothesized parametric distribution. Nevertheless, it has 
@@
 rounded data, with hypothesized distributions containing estimated parameters. 
-For example, it has been “discovered” multiple times that the test is too conservative 
-when the parameters are estimated \citep[e.g.,][]{Steinskog}. This paper aims to survey 
-the misuses of the KS test, demonstrate their consequences through simulation, and 
-provide remedies as needed.
+For example, it has been ``discovered'' multiple times that the test is too conservative 
+when the parameters are estimated. We demonstrate
+misuses of the one-sample KS test in three scenarios through simulation studies:
+1) the hypothesized distribution has unspecified parameters;
+2) the data are serially dependent; and
+3) a combination of the first two scenarios.
+For each scenario, we provide remedies for practical applications.
 \end{abstract}
 
-\hypertarget{sec:intro}{%
-\section{Introduction}\label{sec:intro}}
+\jy{keep line width under 80 characters in tex source}
 
-The Kolmogorov-Smirnov (K-S) statistic is one of the most popular goodness-of-fit 
-tests for comparing a sample with a hypothesized parametric distribution. The test is 
-performed as follows. Let $X_1, ..., X_n$ be i.i.d. random variables from $F_{n}(x)$,
-the empirical cumulative distribution.
-Let $F(x)$ be the population cumulative distribution. The K-S 
-statistic is 
+\section{Introduction}\label{sec:intro}
+
+The Kolmogorov-Smirnov (KS) statistic is one of the most popular goodness-of-fit 
+tests for comparing a sample with a hypothesized parametric distribution.
+Let $X_1, ..., X_n$ be a random sample from some continuous
+distribution. The null hypothesis $H_0$ is that the population distribution is $F$.
+Let $F_n(\cdot)$ be the empirical cumulative distribution. The KS statistic is
 \[
-  d = \max{\lvert F_{n}(x) - F(x) \rvert}.
-\].
-The null hypothesis is that the observations $X_1, ..., X_n$ are from the specified distribution $F(x)$, and the 
-alternate hypothesis is that the data is not from $F(x)$. The table of critical 
-values for $d$ are given by \citet{Massey} for various sample sizes $n$ and significance 
-levels $a$. If the value of $d$ exceeds the test's corresponding critical value, 
-the null hypothesis is rejected.
+  D = \sup_x {\lvert F_{n}(x) - F(x) \rvert}.
+\]
+\jy{use upper case for random variables}
+The distribution of $D$ under $H_0$ turned out to be independent of the
+distribution $F$ and  table of critical values for $D$ has been constructed
+\citet{Massey} for various sample sizes $n$ and significance 
+levels $\alpha$. If the value of $d$ exceeds the test's corresponding critical value, 
+the null hypothesis is rejected. The KS test is available in popular statistical
+software packages, such as function \texttt{ks.test} in R \citep{R}.
+\jy{cite R and also some of the references on the help page of the function}
 
-However, the test is often misused. The standard one-sample K-S test applies to 
-independent, continuous data with a hypothesized distribution that is completely specified. 
+The standard one-sample KS test applies to independent data with a continuous
+hypothesized distribution that is completely specified.
+\jy{this paragraph needs some reorganization.
+  Flow: not applicable to discrete or rounded data (give references; which is
+  not the focus of this paper);
+  not applicable to fitted distributions;
+  not applicable to serially dependent data}
+\jy{break the big paragraph into smaller ones}
 Often in literature, it has been "discovered" that the test loses its power when 
@@
 demonstrates the change in power when using estimated parameters and stress caution in 
-using the K-S test in such ways. \citet{Lilliefors} shows 
+using the KS test in such ways. \citet{Lilliefors} shows 
 that using the standard table when values of the mean and standard deviation are 
@@
 required for the non-parametric case. In the case of dependent data, \citet{Durilleul} demonstrates
-that the K-S statistic is too liberal for medium-to-high positive autocorrelation values. 
+that the KS statistic is too liberal for medium-to-high positive autocorrelation values. 
 \citet{Durilleul} also shows that for negative autocorrelation values, the behavior is 
-asymmettrical with respect to positive values. For remedies, \citet{Weiss} provides a 
+asymmetrical with respect to positive values. For remedies, \citet{Weiss} provides a 
 procedure that is applicable specifically for data modeled by the second-order auto-regressive (AR) 
 process where the parameters are known. \citet{Lanzante} tests various strategies for dealing with 
-temporal dependenceand concludes that a test based on Monte-Carlo simulations performed the best.
+temporal dependence and concludes that a test based on Monte-Carlo simulations performed the best.
 We propose a bootstrap procedure involving copulas to account for dependence.
 
-The purpose of this paper is to expand on the misuses of the K-S test and propose 
-solutions in the case that the K-S test would still like to be used. In order to set 
+The contribution of this paper is a demonstration of misuses of the one-sample
+KS test in three scenarios and their remedies in practice. In order to set 
 up the demonstrations, simulated data is used throughout. Unless otherwise specified, 
 the random data is generated from a standard normal distribution with sample size $n = 100$. 
-Therefore the cumulative distribution $F(x)$ of the K-S test for much of this paper is standard normal.
+Therefore the cumulative distribution $F(x)$ of the KS test for much of this paper is standard normal.
+\jy{Let's not restrict to normal distributions.}
 
-\hypertarget{sec:fitted}{%
-\section{Fitted Parameters}\label{sec:fitted}}
+The rest of the paper is organized as follows. Section~\ref{sec:fitted}
+investigates the scenario where the hypothesized distribution has an unspecified
+parameters. Both parametric and nonparametric bootstrap are available to fix the
+issue. Section~\ref{sec:dependence} ... ... \jy{fill this}
+Section~\ref{sec:conclusion} concludes with a discussion.
 
-The K-S test shows significant issues in the case of fitted parameters. One assumption 
-of the K-S test is that the hypothesized distribution is completely specified. 
+\section{Fitted Parameters}\label{sec:fitted}
+
+The null distribution of the KS statistic changes when the hypothesized
+distribution contains fitted parameters. In this scenario, the null hypothesis
+is $H_0$: the random sample $X_1, \ldots, X_n$ come from a continuous
+distribution $F_{\theta}$ with unspecified parameter $\theta$.
+Let $\hat\theta_n$ be an estimator of $\theta$, which could be, for example,
+maximum likelihood estimator of moment estimator. The test statistic is
+\[
+  D = \sup_x | F_n(x) - F_{\hat\theta_n}(x) |.
+\]
+Because $F_{\hat\theta_n}$ is not the same as the true data generating
+$F_\theta$, the null distribution of $D$ obtained in existing implementations in
+software packages which assumes completely known $F_\theta$ no long applies.
+\jy{cite the paper that ``rediscovered'' the fact}
+
+For illustration, \jy{give the details of the setting}
 However, the procedure is sometimes performed where the population cumulative 
-distribution $F(x)$ has parameters $\mu=\Xbar$, the sample mean, and $\sigma^2=s^2$, 
+distribution $F(x)$ has parameters $\mu=\bar X$, the sample mean, and $\sigma^2=s^2$, 
 the sample variance \citep{Lilliefors}. This case is demonstrated in Figure~\ref{fig:hist_fitted} 
-under the Naive plot. The naive K-S test was performed by estimating the parameters 
+under the Naive plot. The naive KS test was performed by estimating the parameters 
 of $F(x)$ using the fitted distribution of the sample data. Since the data is generated 
@@
 distribution of $U(0,1)$ is expected for the p-values. However this is under the 
-assumption that the K-S test holds its power, which it no longer does due to using 
+assumption that the KS test holds its power, which it no longer does due to using 
 fitted parameters. Therefore, there is notable deviation from the uniform distribution.
 
-To resolve this problem, both parametric and non-parametric bootstrap can be performed. 
-The bootstrap procedure is as follows.
+To fix the problem, parametric bootstrap can be used to approximate the null
+distribution of the testing statistic. 
+\begin{enumerate}
+  \item 
+    Draw a random sample $X_1^*,...,X_n^*$ from the fitted distribution $F_{\hat\theta_n}$
+  \item 
+    Fit $F_\theta$ to the sample and obtain estimated $\hat\theta_n^*$
+  \item
+    Obtain the empirical distribution function of the random sample $F_n^*$
+  \item 
+    Calculate bootstrap KS statistic
+    \[
+      D^* = \sup_x \lvert F_n^* (x)- F_{\hat\theta_n}^*(x) \rvert.
+    \]
+  \item
+    Repeat the previous steps a large number $B$ times and use the empirical
+    distribution of the $B$ test statistics as an approximate distribution of
+    the null distribution of the observed statistic.      
+\end{enumerate}
 
-\begin{itemize}
-  \item 
-    Let $X_1^*,...,X_n^*$ be i.i.d random variables from $\hat{F}_n$, an estimator 
-    of the distribution function $F_n$ based on the sample $X_1,...,X_n$
-  \item 
-    Let $\hat{\theta}_n^* = \theta_n(X_1^*,...,X_n^*)$, where $\theta$ is the 
-    parameter vector and $\hat{\theta}_n$ represents the sample mean and variance 
-    of the sample $X_1,...,X_n$
-  \item 
-    $\hat{\theta}_n^*$ represents the sample mean and variance of the bootstrap 
-    sample $X_1^*,...,X_n^*$
-  \item Thus, the K-S statistic for each bootstrap case is $\max(\lvert F(x)-F^*_n(x) \rvert)$
-\end{itemize}
+% In parametric bootstrap, the resampling is done where $\hat{F}_n = F(.;\hat{\theta}_n)$. 
+% Bootstrap samples are drawn from ${F}(.,\hat{\theta}_n)$ where the assumed distribution 
+% $F$ is normal and $\hat{\theta}_n = (\bar X, s)$, the sample mean and sample standard 
+% deviation. For each bootstrap sample, a KS test statistic is found using those 
+% fitted parameters.
 
-In parametric bootstrap, the resampling is done where $\hat{F}_n = F(.;\hat{\theta}_n)$. 
-Bootstrap samples are drawn from ${F}(.,\hat{\theta}_n)$ where the assumed distribution 
-$F$ is normal and $\hat{\theta}_n = (\Xbar, s)$, the sample mean and sample standard 
-deviation. For each bootstrap sample, a K-S test statistic is found using those 
-fitted parameters.
+\jy{for clarity, give the steps of the nonparametric bootstrap procedure and
+  make clear the bias correction step.}
 
@@
 term $B_{n}(x) = \sqrt{n}(F_{n}(x) - F(x;\hat{\theta}_n)$. Including this term in the
-calculation of the K-S statistic corrects the bias \citet{Babu}:
+calculation of the KS statistic corrects the bias \citet{Babu}:
 $d = \max\lvert F_{n}(x) - F(x) - B_{n}(x) \rvert$.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=\textwidth]{hist_fitted}
+  \caption{Histograms demonstrating fitted parameters. \jy{make the caption self-contained.}}
+  \label{fig:hist_fitted}
+\end{figure}
 
@@
 In each replicate test, $1000$ bootstrap samples are obtained. The p-value can be calculated
-by counting the number of bootstrap K-S statistics greater than or equal to the observed K-S statistic, 
+by counting the number of bootstrap KS statistics greater than or equal to the observed KS statistic, 
 and then dividing by the number of bootstrap samples. It is clear from the figure that both
@@
 
-\begin{figure}[tbp]
-  \centering
-  \includegraphics{hist_fitted}
-  \caption{Histograms demonstrating fitted parameters.}
-  \label{fig:hist_fitted}
-\end{figure}
+\section{Serially Dependent Data}\label{sec:dependence}
 
-\hypertarget{sec:dependence}{%
-\section{Problem under Serial Dependence}\label{sec:dependence}}
-
-The K-S test also displays issues in the case of dependence. As mentioned, an assumption of the 
+The KS test also displays issues in the case of dependence. As mentioned, an assumption of the 
 test is that the data is independent. Unfortunately, real data is often temporally
 or spatially dependent and the results of a goodness-of-fit test would be valuable. 
-When the K-S test is performed on dependent data it performs poorly. This is demonstrated
+When the KS test is performed on dependent data it performs poorly. This is demonstrated
 with a simulation in Figure~\ref{fig:hist_correlation}. Data is generated from a
+\jy{give more details about the simulation setting: what ar1 coefficients were
+  considered? What was the null hypothesis? How was the test statistic calculated?}
 first-order autoregressive model (AR(1)) with a standard normal distribution. The simulation
-is done with the levels of $\psi$ varying from $(-3,3)$. The results support \citet{Durilleul}'s 
-assertion that the K-S statistic is too liberal for positive autocorrelation values, and 
-that the behavior is asymmettrical for negative values.
+is done with the levels of $\psi$ varying from $(-3,3)$. The results echo those of \citet{Durilleul}
+that the KS statistic is too liberal for positive autocorrelation values, and 
+that the behavior is asymmetrical for negative values.
 
@@
 
-In order to correct this, we can employ copulas. A copula is a mechanism to form 
-joined distributions. It allows us to incorporate temporal dependence while ensuring that our
-marginal distribution is the same as the fitted distribution. The procedure is as follows:
+In order to correct this, we can employ a parametric bootstrap procedure which
+assumes a working serial dependence structure through copulas. A copula is a
+multivariate distribution with standard uniform marginal distributions, which
+completely characterizes the dependence structure of a multivariate
+distribution \cite{copula, book}. For simplicity, we assume a normal copula with
+an AR-1 structure to characterize the serial dependence of the observations. The
+AR-1 parameter of the normal copula is set to match the be the sample serial
+Spearman's rho of the observed sample. The procedure is as follows.
 
 \begin{enumerate}
-  \item Calculate the observed K-S statistic
+  \item Calculate the observed KS statistic \jy{the observed statistic is
+      calculated the same way still, so it is not needed in the algorithm here}
   \item Get the lag-1 sample auto-spearman rho
-  \item Perform parametric bootstrap to get an empirical distribution of the K-S statistic
+  \item Perform parametric bootstrap to get an empirical distribution of the KS
+    statistic
+    \jy{need to spell out the details; how to generate $X_t$ given $X_{t-1}$?}
 \end{enumerate}
+
+\jy{add a discussion about the method. The method is exact if the true
+  dependence is indeed a normal copula with an ar1 structure. When it is not, it
+  may still give a reasonable approximation that can be useful for practical purpose}
 
@@
 The data is generated from an AR(1) model with $\psi = .5$. The copula used is to model
-dependence is the normal copula. $1000$ replicate tests were performed with $1000$ bootstrap samples per test.
-The naive test is performed by simply using the K-S test without correcting for any 
+dependence is the normal copula. $1000$ replicate tests were performed with
+$1000$ bootstrap samples per test.
+\jy{present other scenarios too}
+The naive test is performed by simply using the KS test without correcting for any 
 potential dependence.
 
-\hypertarget{sec:fittedwithdependence}{%
-\section{Fitted with Dependence}\label{sec:fittedwithdependence}}
+\section{Fitted Parameters and Serially Dependent Data}\label{sec:fittedwithdependence}
 
+\jy{give a stronger motivation; last section is not practical at all because we
+  often don't know the parameters; this section combines the last two}
 The remedy using copulas is effective in the case where both assumptions are violated.
-This is shown in Figure~\ref{fig:hist_copula}. The "super naive" plot is the resulting 
+This is shown in Figure~\ref{fig:hist_copula}. The ``super naive" method is the resulting 
 p-values when you naively use fitted parameters while ignoring dependence in the data.
-The "naive parametric" plot is the result of applying parametric bootstrap to correct
+The ``naive parametric" plot is the result of applying parametric bootstrap to correct
 for fitted parameters while ignoring potential dependence. Of course, the "copula" 
 plot applies the fix for both assumptions. The results show that copula remedy generates 
-uniform p-values and restores the power of the K-S test.
+uniform p-values and restores the power of the KS test.
 
@@
 
-\hypertarget{sec:conclusion}{%
-\section{Conclusion}\label{sec:conclusion}}
+\section{Conclusion}\label{sec:conclusion}
 
-The K-S test has base assumptions that the hypothesized distribution is completely specified
+The KS test has base assumptions that the hypothesized distribution is completely specified
 and the data is independent. When these assumptions are violated, the test is no
@@
 against other distributions such as gamma and gev. The copula remedy
-is not a complete solution. Regardless of the true depedence, we use an AR(1) model.
+is not a complete solution. Regardless of the true dependence, we use an AR(1) model.
 Therefore, if the AR(1) model is a close approximation of the truth, the fix can work.

### 2022-04-27 Manuscript/manuscript.tex
edits to introduction

@@
 \begin{abstract}
-The Kolmogorov--Smirnov (KS) test is one the most popular goodness-of-fit tests for 
-comparing a sample with a hypothesized parametric distribution. Nevertheless, it has 
-often been misused. The standard one-sample KS test applies to independent, continuous 
-data with a hypothesized distribution that is completely specified. It is not uncommon, 
-however, to see in the literature that it was applied to dependent, discrete, or 
-rounded data, with hypothesized distributions containing estimated parameters. 
-For example, it has been ``discovered'' multiple times that the test is too conservative 
-when the parameters are estimated. We demonstrate
-misuses of the one-sample KS test in three scenarios through simulation studies:
+The Kolmogorov--Smirnov (KS) test is one the most popular goodness-of-fit tests 
+for comparing a sample with a hypothesized parametric distribution. Nevertheless, 
+it has often been misused. The standard one-sample KS test applies to independent, 
+continuous data with a hypothesized distribution that is completely specified. 
+It is not uncommon, however, to see in the literature that it was applied to 
+dependent, discrete, or rounded data, with hypothesized distributions containing 
+estimated parameters. For example, it has been ``discovered'' multiple times 
+that the test is too conservative when the parameters are estimated. We 
+demonstrate misuses of the one-sample KS test in three scenarios through 
+simulation studies:
 1) the hypothesized distribution has unspecified parameters;
@@
 
-\jy{keep line width under 80 characters in tex source}
-
 \section{Introduction}\label{sec:intro}
@@
 tests for comparing a sample with a hypothesized parametric distribution.
-Let $X_1, ..., X_n$ be a random sample from some continuous
-distribution. The null hypothesis $H_0$ is that the population distribution is $F$.
+Let $X_1, ..., X_n$ be a random sample from some continuous distribution. 
+The null hypothesis $H_0$ is that the population distribution is $F$.
 Let $F_n(\cdot)$ be the empirical cumulative distribution. The KS statistic is
@@
 \]
-\jy{use upper case for random variables}
 The distribution of $D$ under $H_0$ turned out to be independent of the
-distribution $F$ and  table of critical values for $D$ has been constructed
+distribution $F$ and a table of critical values for $D$ has been constructed
 \citet{Massey} for various sample sizes $n$ and significance 
-levels $\alpha$. If the value of $d$ exceeds the test's corresponding critical value, 
-the null hypothesis is rejected. The KS test is available in popular statistical
-software packages, such as function \texttt{ks.test} in R \citep{R}.
-\jy{cite R and also some of the references on the help page of the function}
+levels $\alpha$. If the value of $d$ exceeds the test's corresponding critical 
+value, the null hypothesis is rejected. The KS test is available in popular 
+statistical software packages, such as function \texttt{ks.test} in R 
+\citep{R, Marsaglia}.
 
@@
 applied to dependent or discrete data with hypothesized distributions containing 
-estimated parameters. In the case of estimated parameters, \citet{Steinskog} 
-demonstrates the change in power when using estimated parameters and stress caution in 
-using the KS test in such ways. \citet{Lilliefors} shows 
-that using the standard table when values of the mean and standard deviation are 
-estimated obtains extremely conservative results. This is supported by \citet{Capasso}, which 
-concludes that failing to re-estimate the parameters may lead to wrong, overly-conservative 
-approximations to the distributions of goodness-of-fit test statistics based on the empirical 
-distribution function. \citet{Capasso} also notes that the impact of this possible mistake 
-may turn out to be dramatic and does not vanish as the sample size increases. Remedies are provided 
-by \citet{Genest} and \citet{Babu} in the form of bootstrap. \citet{Genest} provides validity 
-for using parametric bootstrap with various goodness-of-fit tests. \citet{Babu} details 
-the bootstrap procedure for goodness-of-fit tests and notes that both parametric and 
-non-parametric procedures lead to correct asymptotic levels, however there is a correction 
-required for the non-parametric case. In the case of dependent data, \citet{Durilleul} demonstrates
-that the KS statistic is too liberal for medium-to-high positive autocorrelation values. 
-\citet{Durilleul} also shows that for negative autocorrelation values, the behavior is 
-asymmetrical with respect to positive values. For remedies, \citet{Weiss} provides a 
-procedure that is applicable specifically for data modeled by the second-order auto-regressive (AR) 
-process where the parameters are known. \citet{Lanzante} tests various strategies for dealing with 
-temporal dependence and concludes that a test based on Monte-Carlo simulations performed the best.
-We propose a bootstrap procedure involving copulas to account for dependence.
+estimated parameters. DISCRETE SECTION HERE. This issue with discrete or rounded
+is not the focus of this paper, though is a common misuse that should be 
+noted.
+
+The KS test is not applicable when the hypothesized distribution contains fitted
+parameters. \citet{Steinskog} demonstrates the change in power when using 
+estimated parameters and stress caution in using the KS test in such ways. 
+\citet{Lilliefors} shows that using the standard table when values of the mean 
+and standard deviation are estimated obtains extremely conservative results. 
+This is supported by \citet{Capasso}, which concludes that failing to 
+re-estimate the parameters may lead to wrong, overly-conservative approximations 
+to the distributions of goodness-of-fit test statistics based on the empirical 
+distribution function. \citet{Capasso} also notes that the impact of this 
+possible mistake may turn out to be dramatic and does not vanish as the sample 
+size increases. Remedies are provided by \citet{Genest} and \citet{Babu} in the 
+form of bootstrap. \citet{Genest} provides validity for using parametric 
+bootstrap with various goodness-of-fit tests. \citet{Babu} details the bootstrap
+procedure for goodness-of-fit tests and notes that both parametric and 
+non-parametric procedures lead to correct asymptotic levels, however there 
+is a correction required for the non-parametric case.
+
+In the case of serially dependent data, \citet{Durilleul} demonstrates that the 
+KS statistic is too liberal for medium-to-high positive autocorrelation values. 
+\citet{Durilleul} also shows that for negative autocorrelation values, the 
+behavior is asymmetrical with respect to positive values. For remedies, 
+\citet{Weiss} provides a procedure that is applicable specifically for data 
+modeled by the second-order auto-regressive (AR) process where the parameters 
+are known. \citet{Lanzante} tests various strategies for dealing with temporal 
+dependence and concludes that a test based on Monte-Carlo simulations performed 
+the best. We propose a parametric bootstrap procedure involving copulas to 
+account for dependence.
 
@@
 KS test in three scenarios and their remedies in practice. In order to set 
-up the demonstrations, simulated data is used throughout. Unless otherwise specified, 
-the random data is generated from a standard normal distribution with sample size $n = 100$. 
-Therefore the cumulative distribution $F(x)$ of the KS test for much of this paper is standard normal.
-\jy{Let's not restrict to normal distributions.}
+up the demonstrations, simulated data is used throughout. The random data is 
+generated with sample size $n = 100$ and the remedies are performed on various
+families of distributions.
 
 The rest of the paper is organized as follows. Section~\ref{sec:fitted}
-investigates the scenario where the hypothesized distribution has an unspecified
+investigates the scenario where the hypothesized distribution has unspecified
 parameters. Both parametric and nonparametric bootstrap are available to fix the
-issue. Section~\ref{sec:dependence} ... ... \jy{fill this}
+issue. Section~\ref{sec:dependence} investigates the scenario where the data of 
+the empirical distribution is serially dependent. Our bootstrap procedure 
+employing copulas is a working solution. Section~\ref{sec:fittedwithdependence}
+explores the case where a combination of the first two scenarios occurs. The 
+copula procedure is available as a fix here as well. 
 Section~\ref{sec:conclusion} concludes with a discussion.

### 2022-04-28 Manuscript/manuscript.tex
generate data under copula
typo fixed
fitted/serial bootstrap

@@
 maximum likelihood estimator of moment estimator. The test statistic is
-\[
+\begin{equation}
+  \label{eq:ks_fitted}
   D = \sup_x | F_n(x) - F_{\hat\theta_n}(x) |.
-\]
+\end{equation}
 Because $F_{\hat\theta_n}$ is not the same as the true data generating
@@
     \[
-      D^* = \sup_x \lvert F_n^* (x)- F_{\hat\theta_n}^*(x) \rvert.
+      D^* = \sup_x \lvert F_n^* (x)- F_{\hat\theta_n^*}^*(x) \rvert.
     \]
@@
 
+\jy{simulate $X_t | X_{t-1}$, assuming $F$:
+  $Z_{t-1} = \Phi^{-1}[ F(X_{t-1})]$;
+  $Z_{t} = \rho Z_{t -1} +  \epsilon_t$;
+  $X_t = F^{-1} [ \Phi(Z_t) ]$
+  }
+
 \begin{enumerate}
@@
 \end{figure}
+
+Let $\hat\theta_n$ be the fitted parameter value of $F_{\theta}$. The observed
+KS statistic is calculated as in Equation~\eqref{eq:ks_fitted}. The bootstrap
+procedure in Section~\ref{sec:fitted} is no longer valid because the serial
+dependence is not accounted for. Let $r$ be the
+AR-1 coefficient of the normal copula that matches the sample first-order
+Spearman's rho of the observed data as obtained by the \texttt{iRho} function in
+the \textsf{copula} package. We propose the following bootstrap procedure to
+assess the significance of the observed KS statistic.
+\begin{enumerate}
+\item
+  Generate $Z_1, \ldots, Z_n$ from an AR(1) process with autocorrelation
+  coefficient $r$ such that the $Z_i$'s are $N(0, 1)$ variables.
+\item
+  Form a bootstrap sample $X_i^* = F^{-1}_{\hat\theta_n} [\Phi(Z_i)]$,
+  $i = 1, \ldots, n$, whose first-order sample Spearman's rho matches that of
+  the observed data.
+\item
+  Fit $F_\theta$ to the sample $X_1^*, \ldots, X_n^*$ and obtain estimator $\hat\theta_n^*$
+\item
+  Obtain the empirical distribution function $F_n^*$ of the bootstrap sample
+  $X_1^*, \ldots, X_n^*$.
+\item 
+  Calculate bootstrap KS statistic
+  \[
+    D^* = \sup_x \lvert F_n^* (x)- F_{\hat\theta_n^*}^*(x) \rvert.
+  \]
+\item
+  Repeat the previous steps a large number $B$ times and use the empirical
+    distribution of the $B$ test statistics to approximate
+    the null distribution of the observed statistic.      
+\end{enumerate}
 

### 2022-04-28 Manuscript/manuscript.tex
small fix
various edits

--- 2022-04-27 Manuscript/manuscript.tex
@@
 \usepackage[pagewise]{lineno}
-\linenumbers*[1]
+%\linenumbers*[1]
 % %% patches to make lineno work better with amsmath
@@
 
-\title{On Misuses of the Kolmogorov–-Smirnov Test for One Sample Goodness-of-Fit}
+\title{On Misuses of the Kolmogorov--Smirnov Test for One Sample Goodness-of-Fit}
 
-\author{Anthony Zeimbekakis and Jun Yan\\
+\author{Anthony Zeimbekakis\\
 \href{mailto:anthony.zeimbekakis@uconn.edu}{\nolinkurl{anthony.zeimbekakis@uconn.edu}}\\
-Department of Statistics, University of Connecticut}
-\date{April 21, 2022}
+Department of Statistics, University of Connecticut\\\\
+Thesis Advisor: Jun Yan\\
+Honors Advisor: Elizabeth Schifano}
+\date{}
 
@@
 \[
-  D = \sup_x {\lvert F_{n}(x) - F(x) \rvert}.
+  D = \sup_x | F_{n}(x) - F(x) |.
 \]
@@
 distribution $F$ and a table of critical values for $D$ has been constructed
-\citet{Massey} for various sample sizes $n$ and significance 
+\citep{Massey} for various sample sizes $n$ and significance 
 levels $\alpha$. If the value of $d$ exceeds the test's corresponding critical 
@@
 
-The KS test is not applicable when the hypothesized distribution contains fitted
-parameters. \citet{Steinskog} demonstrates the change in power when using 
-estimated parameters and stress caution in using the KS test in such ways. 
-\citet{Lilliefors} shows that using the standard table when values of the mean 
-and standard deviation are estimated obtains extremely conservative results. 
-This is supported by \citet{Capasso}, which concludes that failing to 
+The standard KS test is not applicable when the hypothesized distribution 
+contains fitted parameters. \citet{Steinskog} demonstrates the change in power 
+when using estimated parameters and stress caution in using the KS test in such 
+ways. \citet{Lilliefors} shows that using the standard table when values of the 
+mean and standard deviation are estimated obtains extremely conservative 
+results. This is supported by \citet{Capasso}, which concludes that failing to 
 re-estimate the parameters may lead to wrong, overly-conservative approximations 
@@
 The contribution of this paper is a demonstration of misuses of the one-sample
-KS test in three scenarios and their remedies in practice. In order to set 
-up the demonstrations, simulated data is used throughout. The random data is 
-generated with sample size $n = 100$ and the remedies are performed on various
-families of distributions.
+KS test in three scenarios and their remedies in practice. The scenarios are 
+where:
+1) the hypothesized distribution has unspecified parameters;
+2) the data are serially dependent; and
+3) a combination of the first two scenarios. 
+In each scenario, the misuse is performed and the impacts are shown. Then, a
+remedy is detailed and performed alongside the misuse to show its positive 
+effects. In order to set up the demonstrations, simulated data is used 
+throughout. The remedies are also performed on a various families of 
+distributions.
 
@@
 \]
-Because $F_{\hat\theta_n}$ is not the same as the true data generating
+Since $F_{\hat\theta_n}$ is not the same as the true data generating
 $F_\theta$, the null distribution of $D$ obtained in existing implementations in
-software packages which assumes completely known $F_\theta$ no long applies.
-\jy{cite the paper that ``rediscovered'' the fact}
+software packages which assumes completely known $F_\theta$ no long applies
+\citep{Steinskog}.
 
@@
     \[
-      D^* = \sup_x \lvert F_n^* (x)- F_{\hat\theta_n}^*(x) \rvert.
+      D^* = \sup_x | F_n^* (x)- F_{\hat\theta_n}^*(x) |.
     \]
@@
     Repeat the previous steps a large number $B$ times and use the empirical 
-    distribution of the $B$ test statistics as an approximate distribution of
-    the null distribution of the observed statistic.      
+    distribution of $D^*$ to approximate the null distribution of the observed 
+    statistic.    
 \end{enumerate}
 
-% In parametric bootstrap, the resampling is done where $\hat{F}_n = F(.;\hat{\theta}_n)$. 
-% Bootstrap samples are drawn from ${F}(.,\hat{\theta}_n)$ where the assumed distribution 
-% $F$ is normal and $\hat{\theta}_n = (\bar X, s)$, the sample mean and sample standard 
-% deviation. For each bootstrap sample, a KS test statistic is found using those 
-% fitted parameters.
-
-\jy{for clarity, give the steps of the nonparametric bootstrap procedure and
-  make clear the bias correction step.}
-
-In non-parametric bootstrap, the resampling is done where $\hat{F}_n = F_n$. The non-parametric
-case requires a correction for bias detailed by \citet{Babu}. There is a known bias
-term $B_{n}(x) = \sqrt{n}(F_{n}(x) - F(x;\hat{\theta}_n)$. Including this term in the
-calculation of the KS statistic corrects the bias \citet{Babu}:
-$d = \max\lvert F_{n}(x) - F(x) - B_{n}(x) \rvert$.
+Nonparametric bootstrap can also be used to approximate the null distribution 
+of the testing statistic. The procedure is similar, however there is a 
+correction for bias that is required \citep{Babu}.
+\begin{enumerate}
+  \item 
+    Draw a random sample $X_1^*,...,X_n^*$ from the empirical distribution $F_n$
+    with replacement
+  \item 
+    Fit $F_\theta$ to the sample and obtain estimated $\hat\theta_n^*$
+  \item
+    Obtain the empirical distribution function of the random sample $F_n^*$
+  \item 
+    Calculate bootstrap KS statistic
+    \[
+      D^* = \sup_x | F_n^* (x)- F_{\hat\theta_n}^*(x) - B_n(x) |.
+    \]
+    where $B_{n}(x) = \sqrt{n}(F_{n}(x) - F_{\hat\theta_n}(x))$ is the known bias
+    term \citep{Babu}
+  \item
+    Repeat the previous steps a large number $B$ times and use the empirical 
+    distribution of $D^*$ to approximate the null distribution of the observed 
+    statistic.
+\end{enumerate}
 
@@
   \includegraphics[width=\textwidth]{hist_fitted}
-  \caption{Histograms demonstrating fitted parameters. \jy{make the caption self-contained.}}
+  \caption{Implementing bootstrap remedies for fitted parameters misuse. \jy{make the caption self-contained.}}
   \label{fig:hist_fitted}
@@
 
-Figure~\ref{fig:hist_fitted} displays the results of from our simulations. The procedure 
-is replicated $1000$ times using the standard normal distribution with sample size $n=100$. 
-In each replicate test, $1000$ bootstrap samples are obtained. The p-value can be calculated
-by counting the number of bootstrap KS statistics greater than or equal to the observed KS statistic, 
-and then dividing by the number of bootstrap samples. It is clear from the figure that both
-bootstrap processes correct for the problem of fitted parameters. The plots appear to be
-$U(0,1)$, which is expected of a full power test.
+Figure~\ref{fig:hist_fitted} displays the results of from our simulations. The 
+procedure is replicated $1000$ times using the standard normal distribution with
+sample size $n=100$. In each replicate test, $B = 1000$ bootstrap samples are 
+obtained. The p-value can be calculated by counting the number of bootstrap KS 
+statistics greater than or equal to the observed KS statistic, and then dividing 
+by the number of bootstrap samples. It is clear from the figure that both
+bootstrap processes correct for the problem of fitted parameters. The plots 
+appear to be $U(0,1)$, which is expected of a full power test.
 
@@
 
-The KS test also displays issues in the case of dependence. As mentioned, an assumption of the 
-test is that the data is independent. Unfortunately, real data is often temporally
-or spatially dependent and the results of a goodness-of-fit test would be valuable. 
-When the KS test is performed on dependent data it performs poorly. This is demonstrated
-with a simulation in Figure~\ref{fig:hist_correlation}. Data is generated from a
-\jy{give more details about the simulation setting: what ar1 coefficients were
-  considered? What was the null hypothesis? How was the test statistic calculated?}
-first-order autoregressive model (AR(1)) with a standard normal distribution. The simulation
-is done with the levels of $\psi$ varying from $(-3,3)$. The results echo those of \citet{Durilleul}
-that the KS statistic is too liberal for positive autocorrelation values, and 
-that the behavior is asymmetrical for negative values.
+The KS test also displays issues in the case of dependence. As mentioned, an 
+assumption of the test is that the data is independent. Unfortunately, real data
+is often temporally or spatially dependent and the results of a goodness-of-fit 
+test would be valuable. When the KS test is performed on dependent data it 
+performs poorly. In this situation, the null hypothesis is $H_0$: the random 
+sample $X_1, \ldots, X_n$ come from a continuous distribution $F_{\theta}$ with 
+specified parameter $\theta$.
+Let $\hat\theta_n$ be an estimator of $\theta$, which could be, for example,
+maximum likelihood estimator of moment estimator. The test statistic is
+\[
+  D = \sup_x | F_n(x) - F_{\hat\theta_n}(x) |.
+\]
+However, since the data is dependent, the null hypothesis is wrong and must be 
+corrected. This is demonstrated with a simulation in 
+Figure~\ref{fig:hist_correlation}. Data is generated from a first-order 
+autoregressive model (AR-1) with a standard normal distribution. The simulation
+is done with the levels of the AR coefficient $\psi$, varying from $(-3,3)$. 
+The results echo those of \citet{Durilleul} that the KS statistic is too liberal 
+for positive autocorrelation values, and that the behavior is asymmetrical for 
+negative values.
 
@@
   \includegraphics{hist_correlation}
-  \caption{Histograms of P-values with correlated data.}
+  \caption{Results of varying AR levels of AR-1 simulated data.}
   \label{fig:hist_correlation}
@@
 completely characterizes the dependence structure of a multivariate
-distribution \cite{copula, book}. For simplicity, we assume a normal copula with
-an AR-1 structure to characterize the serial dependence of the observations. The
-AR-1 parameter of the normal copula is set to match the be the sample serial
+distribution \citep{Copula, Hofert}. For simplicity, we assume a normal copula 
+with an AR-1 structure to characterize the serial dependence of the observations. 
+The AR-1 parameter of the normal copula is set to match the be the sample serial
 Spearman's rho of the observed sample. The procedure is as follows.
@@
 \begin{enumerate}
-  \item Calculate the observed KS statistic \jy{the observed statistic is
-      calculated the same way still, so it is not needed in the algorithm here}
-  \item Get the lag-1 sample auto-spearman rho
-  \item Perform parametric bootstrap to get an empirical distribution of the KS
-    statistic
+  \item 
+    Black box
     \jy{need to spell out the details; how to generate $X_t$ given $X_{t-1}$?}
+  \item 
+    Transform bootstrap sample to 
+  \item
+    Repeat the previous steps a large number $B$ times and use the empirical
+    distribution of the $B$ test statistics as an approximate distribution of
+    the null distribution of the observed statistic. 
 \end{enumerate}
@@
 Figure~\ref{fig:hist_copula_only} displays the results of the copula remedy for dependent data.
-The data is generated from an AR(1) model with $\psi = .5$. The copula used is to model
+The data is generated from an AR-1 model with $\psi = .5$. The copula used is to model
 dependence is the normal copula. $1000$ replicate tests were performed with
-$1000$ bootstrap samples per test.
+$B = 1000$ bootstrap samples per test.
 \jy{present other scenarios too}
@@
   \includegraphics{hist_copula_ma1}
-  \caption{Histograms demonstrating remedy use with MA(1) model.}
+  \includegraphics{hist_copula_arma}
+  \caption{MA-1 and ARMA(1,1)}
   \label{fig:hist_copula_ma1}
-\end{figure}
-
-\begin{figure}[tbp]
-  \centering
-  \includegraphics{hist_copula_arma}
-  \caption{Histograms demonstrating remedy use with ARMA(1,1) model.}
-  \label{fig:hist_copula_arma}
 \end{figure}
@@
   \includegraphics{hist_copula_gamma}
-  \caption{Histograms demonstrating remedy with Gamma(3,1).}
+  \includegraphics{hist_copula_gev}
+  \caption{Gamma(3,1)}
   \label{fig:hist_copula_gamma}
@@
 
-\begin{figure}[tbp]
-  \centering
-  \includegraphics{hist_copula_gev}
-  \caption{Histograms demonstrating copula use to correct dependence.}
-  \label{fig:hist_copula_gev}
-\end{figure}
-
-Where this remedy falls short is when the approximation of an AR(1) model is too inaccurate.
-An AR(2) model can be used to demonstrate this. For an AR(2) model with $\phi = (0.5, 0.3)$,
-Figure~\ref{fig:hist_copula_ar2} displays the results of applying the various remedies. 
-While the remedies improve the plot of the p-values in comparison to the naive case,
-because the approximation is not close enough the correction does not work completely.
+Where this remedy falls short is when the approximation of an AR-1 dependence 
+structure is too inaccurate. An AR-2 model can be used to demonstrate this. For 
+an AR-2 model with $\phi = (0.5, 0.3)$, Figure~\ref{fig:hist_copula_ar2} 
+displays the results of applying the various remedies. While the remedies 
+improve the plot of the p-values in comparison to the naive case, because the 
+approximation is not close enough the correction does not work completely.
 
@@
   \includegraphics{hist_copula_ar2}
-  \caption{Histograms demonstrating copula use to correct dependence.}
+  \caption{AR-2}
   \label{fig:hist_copula_ar2}
@@
 
-The KS test has base assumptions that the hypothesized distribution is completely specified
-and the data is independent. When these assumptions are violated, the test is no
-longer accurate and remedies must be performed. In the case of fitted parameters, 
-parametric and non-parametric bootstrap can restore the power of the test. A bias 
-correction is required if the non-parametric form is used \citep{Babu}. In the case of dependent
-data, a procedure using bootstrap with copulas to model dependency shows positive results.
-When both assumptions are violated, that is the case where the data has dependence and 
-parameters must be fitted, the copula remedy also shows positive results. The tests were 
-performed on simulated data from a standard normal distribution, though also appear effective
-against other distributions such as gamma and gev. The copula remedy
-is not a complete solution. Regardless of the true dependence, we use an AR(1) model.
-Therefore, if the AR(1) model is a close approximation of the truth, the fix can work.
-However, in cases such as AR(2), the approximation is incorrect and the fix does not 
-completely restore power.
+The KS test has base assumptions that the hypothesized distribution is 
+completely specified and the data is independent. When these assumptions are 
+violated, the test is no longer accurate and remedies must be performed. In the 
+case of fitted parameters, parametric and non-parametric bootstrap can restore 
+the power of the test. A bias correction is required if the non-parametric form 
+is used \citep{Babu}. In the case of dependent data, a procedure using bootstrap 
+with copulas to model dependency shows positive results. When both assumptions 
+are violated, that is the case where the data has dependence and parameters must 
+be fitted, the copula remedy also shows positive results. The tests were 
+performed on simulated data from a standard normal distribution, though also 
+appear effective against other distributions such as gamma and gev. The copula 
+remedy is not a complete solution. Regardless of the true dependence, we use an 
+AR-1 model. Therefore, if the AR-1 model is a close approximation of the truth, 
+the fix can work. However, in cases such as AR-2, the approximation too far and 
+the fix does not completely restore power.
 

### 2022-04-28 Manuscript/manuscript.tex

@@
 Let $F_n(\cdot)$ be the empirical cumulative distribution. The KS statistic is
-\[
+\begin{equation}
+  \label{eq:ks_standard}
   D = \sup_x | F_{n}(x) - F(x) |.
-\]
+\end{equation}
 The distribution of $D$ under $H_0$ turned out to be independent of the
@@
 maximum likelihood estimator of moment estimator. The test statistic is
-\[
+\begin{equation}
+  \label{eq:ks_fitted}
   D = \sup_x | F_n(x) - F_{\hat\theta_n}(x) |.
-\]
+\end{equation}
 Since $F_{\hat\theta_n}$ is not the same as the true data generating
@@
   \item
-    Obtain the empirical distribution function of the random sample $F_n^*$
+    Obtain the empirical distribution function $F_n^*$ of $X_1^*, \ldots, X_n^*$.
   \item 
@@
     Repeat the previous steps a large number $B$ times and use the empirical
-    distribution of the $B$ test statistics as an approximate distribution of
+    distribution of the $B$ test statistics to approximate
     the null distribution of the observed statistic. 
@@
 \end{figure}
+
+Let $\hat\theta_n$ be the fitted parameter value of $F_{\theta}$. The observed
+KS statistic is calculated as in Equation~\eqref{eq:ks_fitted}. The bootstrap
+procedure in Section~\ref{sec:fitted} is no longer valid because the serial
+dependence is not accounted for. Let $r$ be the
+AR-1 coefficient of the normal copula that matches the sample first-order
+Spearman's rho of the observed data as obtained by the \texttt{iRho} function in
+the \textsf{copula} package. We propose the following bootstrap procedure to
+assess the significance of the observed KS statistic.
+\begin{enumerate}
+\item
+  Generate $Z_1, \ldots, Z_n$ from an AR(1) process with autocorrelation
+  coefficient $r$ such that the $Z_i$'s are $N(0, 1)$ variables.
+\item
+  Form a bootstrap sample $X_i^* = F^{-1}_{\hat\theta_n} [\Phi(Z_i)]$,
+  $i = 1, \ldots, n$, whose first-order sample Spearman's rho matches that of
+  the observed data.
+\item
+  Fit $F_\theta$ to the sample $X_1^*, \ldots, X_n^*$ and obtain estimator $\hat\theta_n^*$
+\item
+  Obtain the empirical distribution function $F_n^*$ of the bootstrap sample
+  $X_1^*, \ldots, X_n^*$.
+\item 
+  Calculate bootstrap KS statistic
+  \[
+    D^* = \sup_x \lvert F_n^* (x)- F_{\hat\theta_n^*}(x) \rvert.
+  \]
+\item
+  Repeat the previous steps a large number $B$ times and use the empirical
+    distribution of the $B$ test statistics to approximate
+    the null distribution of the observed statistic.      
+\end{enumerate}
 

### 2022-04-28 Code/Simulation.Rmd
code for section 3 (only dependence) plus refactoring

@@
 # Load packages
-library(dgof)
 library(tidyverse)
@@
 
-```{r hist_parametric}
+```{r hist_correlation}
+# Test to show that autocorrelation changes the power of the test
+test_correlation <- function(n_tests, ars) {
+
+  # Create a master data_frame for p-values
+  columns <- c("p_value", "ar")
+  ar_results <- data.frame(matrix(ncol = 2, nrow = 0))
+  colnames(ar_results) <- columns
+
+  # For AR coefficients from -0.5 to 0.5
+  for(i in 1:length(ars)) {
+
+    for(j in 1:n_tests) {
+
+      # Generate random correlated data, perform a KS-test, and store the p-value
+      data <- arima.sim(model = list(ar = ars[i]), rand.gen = rnorm, sd = sqrt(1-ars[i]^2), n = 100)
+      ar_results <- add_row(ar_results, p_value = ks.test(data, "pnorm")$p.value, ar = round(ars[i], 1))
+    }
+  }
+
+  return(ar_results)
+}
+
+ # Set AR coefficients and generate results
+ars <- seq(-0.3, 0.3, by = 0.1)
+ar_results <- test_correlation(1000, ars)
+
+# Generate histograms plot
+hist_correlation <- ggplot(ar_results) + 
+                    geom_histogram(aes(x = p_value, fill = ar), boundary = 0, binwidth = 1/20) + 
+                    facet_grid(~ar) +
+                    theme(legend.position = "none") +
+                    scale_x_continuous(name = "p-value", breaks=c(0, 1))
+
+# Save the histogram figure
+ggsave(filename = "hist_correlation.pdf", plot = hist_correlation, path = "../Manuscript", height = 2.1, width = 6)
+```
+
+```{r Parametric}
 # Test parametric bootstrap as a solution to fitting parameters
@@
 # Generate results
-n_tests = 100
+n_tests = 1000
 n = 100
@@
 ggsave(filename = "hist_fitted.pdf", plot = hist_fitted, path = "../Manuscript", height = 2.1, width = 6)
-```
 
-```{r hist_correlation}
-# Test to show that autocorrelation changes the power of the test
-test_correlation <- function(n_tests, ars) {
-
-  # Create a master data_frame for p-values
-  columns <- c("p_value", "ar")
-  ar_results <- data.frame(matrix(ncol = 2, nrow = 0))
-  colnames(ar_results) <- columns
-
-  # For AR coefficients from -0.5 to 0.5
-  for(i in 1:length(ars)) {
-
-    for(j in 1:n_tests) {
-
-      # Generate random correlated data, perform a KS-test, and store the p-value
-      data <- arima.sim(model = list(ar = ars[i]), rand.gen = rnorm, sd = sqrt(1-ars[i]^2), n = 100)
-      ar_results <- add_row(ar_results, p_value = ks.test(data, "pnorm")$p.value, ar = round(ars[i], 1))
-    }
-  }
-
-  return(ar_results)
-}
-
- # Set AR coefficients and generate results
-ars <- seq(-0.3, 0.3, by = 0.1)
-ar_results <- test_correlation(1000, ars)
+data_new <- results                              # Replicate data
+data_new$histogram <- factor(data_new$histogram,      # Reordering group factor levels
+                         levels = c("Naive", "Parametric", "Babu"))
 
 # Generate histograms plot
-hist_correlation <- ggplot(ar_results) + 
-                    geom_histogram(aes(x = p_value, fill = ar), boundary = 0, binwidth = 1/20) + 
-                    facet_grid(~ar) +
+hist_fitted <- ggplot(data_new) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                    theme(legend.position = "none") +
-                    scale_x_continuous(name = "p-value", breaks=c(0, 1))
-
-# Save the histogram figure
-ggsave(filename = "hist_correlation.pdf", plot = hist_correlation, path = "../Manuscript", height = 2.1, width = 6)
+                   facet_wrap(~histogram, scales = "free_y")
+hist_fitted
 ```
@@
 
-```{r}
-test_copula <- function(x, dist, B) {
+```{r gen_data}
+## generating observations from a specified distribution with serial dependence
+genData <- function(n, qdist, ..., copula, rho) {
+    ## n: sample size
+    ## qdist: quantile function of the desired marginal distribution
+    ## copula: copula for serial distribution
+    ## rho: spearman's rho
+    theta <- iRho(copula(), rho)
+    cop <- copula(theta)
+    u <- runif(n)
+    for (j in 2:n) {
+        u[j] <- cCopula(c(u[j-1], u[j]), cop, indices = 2, inverse = TRUE)
+    }
+    qdist(u, ...)
+}
+```
+
+```{r AR(1) D}
+test_copula_D <- function(x, dist, B, mean, sd) {
+
+    # Get observed statistic
+    n <- length(x)
+
+    stat  <- ks.test(x, dist, mean = mean, sd = sd)$statistic
+
+    # Get lag-1 sample auto-spearman rho
+    rho  <-  cor(x[-1], x[-n], method = "spearman")
+    r <- iRho(normalCopula(), rho)
+    np <- normalCopula(r)
+
+    # Perform parametric bootstrap to get an empirical distribution of stat
+    stat.b <- double(n)
+
+    for (i in 1:B) {
+        # 1. The marginal distribution is the fitted dist
+        # 2. There is temporal dependence
+        u <- runif(n) 
+        for (j in 2:n) {
+            u[j]  <- cCopula(c(u[j-1], u[j]), np, indices = 2, inverse = TRUE)
+        }
+
+        # Transform bootstrap sample and fit the parameters
+        x.b <- qnorm(u, mean = mean, sd = sd)
+
+        # Gather bootstrap sample's test statistic
+        stat.b[i] <- ks.test(x.b, dist, mean = mean, sd = sd)$statistic
+    }
+
+    # Return empirical p-value
+    p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
+
+    counter <<- counter + 1
+    cat(counter, "")
+
+    return(p.value)
+}
+
+# Standard KS test
+test_standard_ks <- function(x, mean, sd) {
+  p.value <- ks.test(x, "pnorm", mean = mean, sd = sd)$p.value
+  list(p.value = p.value)
+}
+
+ptm <- proc.time()
+
+# Set variables
+n <- 100
+ar <- 0.5
+counter <- 0
+nrep <- 500
+B <- 100
+mean <- 0
+sd <- 1
+
+# P-vals from using bootstrap with copulas
+pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), 
+                                              "pnorm", 
+                                              B = B, 
+                                              mean = mean, 
+                                              sd = sd))
+counter <- 0
+
+# P-vals from standard KS test
+pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), 
+                                                mean = mean, 
+                                                sd = sd)$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
+p_values <- c(pvals_copula, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+# Generate histograms plot
+hist_ar1_D <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+hist_ar1_D
+
+print(proc.time() - ptm)
+
+# Save the histogram figure
+ggsave(filename = "hist_ar1_D.pdf", plot = hist_ar1_D, path = "../Manuscript", height = 2.1, width = 6)
+```
+
+```{r MA(1) D}
+ptm <- proc.time()
+
+# Set variables
+n <- 100
+counter <- 0
+nrep <- 100
+B <- 100
+ma <- 0.5
+mean <- 0
+sd <- 1
+
+# P-vals from using bootstrap with copulas
+pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), 
+                                              "pnorm", 
+                                              B = B,
+                                              mean = mean,
+                                              sd = sd))
+counter <- 0
+
+# P-vals from standard KS test
+pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n),
+                                                mean = mean,
+                                                sd = sd)$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
+p_values <- c(pvals_copula, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+# Generate histograms plot
+hist_ma1_D <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+hist_ma1_D
+
+print(proc.time() - ptm)
+
+# Save the histogram figure
+ggsave(filename = "hist_ma1_D.pdf", plot = hist_ma1_D, path = "../Manuscript", height = 2.1, width = 6)
+```
+
+```{r ARMA(1,1) D}
+ptm <- proc.time()
+
+# Set variables
+n <- 100
+counter <- 0
+nrep <- 100
+B <- 100
+ar <- 0.5
+ma <- 0.3
+mean <- 0
+sd <- 1
+
+# P-vals from using bootstrap with copulas
+pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ar = ar, 
+                                                           ma = ma), 
+                                                      rand.gen=rnorm, 
+                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
+                                                      n = n), 
+                                            "pnorm", 
+                                            B = B,
+                                            mean = mean,
+                                            sd = sd))
+counter <- 0
+
+# P-vals from standard KS test
+pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(order = c(2, 0, 0), 
+                                                           ar = c(b1, b2)),
+                                                      rand.gen=rnorm,
+                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
+                                                      n = n))$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
+p_values <- c(pvals_copula, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+# Generate histograms plot
+hist_arma_D <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+hist_arma_D
+
+print(proc.time() - ptm)
+
+# Save the histogram figure
+ggsave(filename = "hist_arma_D.pdf", plot = hist_arma_D, path = "../Manuscript", height = 2.1, width = 6)
+```
+
+```{r AR(2) D}
+ptm <- proc.time()
+
+# Set variables
+n <- 100
+counter <- 0
+nrep <- 100
+B <- 100
+b1 <- 0.5
+b2 <- 0.3
+mean <- 0
+sd <- 1
+
+# P-vals from using bootstrap with copulas
+pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(order = c(2, 0, 0), 
+                                                           ar = c(b1, b2)),
+                                                      rand.gen=rnorm,
+                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
+                                                      n = n), 
+                                            "pnorm", 
+                                            B = B,
+                                            mean = mean,
+                                            sd = sd))
+counter <- 0
+
+# P-vals from standard KS test
+pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(order = c(2, 0, 0), 
+                                                           ar = c(b1, b2)),
+                                                      rand.gen=rnorm,
+                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
+                                                      n = n),
+                                                mean = mean,
+                                                sd = sd)$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
+p_values <- c(pvals_copula, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+# Generate histograms plot
+hist_ar2_D <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+hist_ar2_D
+
+print(proc.time() - ptm)
+
+# Save the histogram figure
+ggsave(filename = "hist_ar2_D.pdf", plot = hist_ar2_D, path = "../Manuscript", height = 2.1, width = 6)
+```
+
+```{r Gamma D}
+# Testing bootstrap with copulas for gamma distribution
+test_gamma_D <- function(x, dist, B = 100, wcopula = normalCopula, shape, scale) {
+
+    # Get observed stat
+    n <- length(x)
+
+    stat  <- ks.test(x, dist, shape = shape, scale = scale)$statistic
+
+    # Get lag-1 sample auto-spearman rho
+    rho  <-  cor(x[-1], x[-n], method = "spearman")
+    r <- iRho(wcopula(), rho)
+    wcop <- wcopula(r)
+
+    # Parametric bootstrap to get an empirical distribution of stat
+    stat.b <- double(n)
+
+    for (i in 1:B) {
+        # 1. The marginal distribution is the fitted dist
+        # 2. There is temporal dependence
+        u <- runif(n)
+        for (j in 2:n) {
+            u[j]  <- cCopula(c(u[j-1], u[j]), wcop, indices = 2, inverse = TRUE)
+        }
+
+        # Transform the bootstrap sample and fit the parameters
+        x.b <- qgamma(u, shape = shape, scale = scale)
+
+        # Calculate new test statistic
+        stat.b[i] <- ks.test(x.b, dist, shape = shape, scale = scale)$statistic
+    }
+
+    # Return empirical p-value    
+    p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
+
+    counter <<- counter + 1
+    cat(counter, "")
+
+    return(p.value)
+}
+
+# Naive function that incorrectly uses fitted parameters for gamma distribution
+test_standard_gamma <- function(x, shape, scale) {
+  p.value <- ks.test(x, "pgamma", shape = shape, scale = scale)$p.value
+  list(p.value = p.value)
+}
+
+ptm <- proc.time()
+
+# Set variables
+n <- 100
+rho <- 0.5
+counter <- 0
+nrep <- 100
+B <- 100
+shape <- 3
+scale <- 1
+
+# P-vals from using bootstrap with copulas
+pvals_copula <- replicate(nrep, test_gamma_D(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
+                                             "pgamma", 
+                                             B = B,
+                                             shape = shape,
+                                             scale = scale))
+counter <- 0
+
+# P-vals from naively using fitted parameters
+pvals_naive <- replicate(nrep, test_standard_gamma(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
+                                                   shape = shape, 
+                                                   scale = scale)$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
+p_values <- c(pvals_copula, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+# Generate histograms plot
+hist_gamma_D <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+hist_gamma_D
+
+print(proc.time() - ptm)
+
+# Save the histogram figure
+ggsave(filename = "hist_gamma_D.pdf", plot = hist_gamma_D, path = "../Manuscript", height = 2.1, width = 6)
+```
+
+```{r GEV D}
+# Testing bootstrap with copulas for GEV distribution
+test_gev_D <- function(x, B = 100, wcopula = normalCopula, loc, scale, shape) {
+
+    n <- length(x)
+
+    # Get observed stat
+    stat  <- ks.test(x, 'pgev', loc = loc, scale = scale, shape = shape)$statistic
+
+    # Get lag-1 sample auto-spearman rho
+    rho  <-  cor(x[-1], x[-n], method = "spearman")
+    r <- iRho(wcopula(), rho)
+    wcop <- wcopula(r)
+
+    # Parametric bootstrap to get an empirical distribution of stat
+    stat.b <- double(n)
+
+    for (i in 1:B) {
+        # 1. The marginal distribution is the fitted dist
+        # 2. There is temporal dependence
+        u <- runif(n)
+        for (j in 2:n) {
+            u[j]  <- cCopula(c(u[j-1], u[j]), wcop, indices = 2, inverse = TRUE)
+        }
+
+        # Transform the bootstrap sample
+        x.b <- qgev(u, loc = loc, scale = scale, shape = shape)
+
+        # Calculate bootstrap test statistic
+        stat.b[i] <- ks.test(x.b, 'pgev', loc = loc, scale = scale, shape = shape)$statistic
+    }
+
+    # Return empirical p-value    
+    p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
+
+    counter <<- counter + 1
+    cat(counter, "")
+
+    return(p.value)
+}
+
+# Standard KS test for GEV distribution
+test_standard_gev <- function(x, loc, scale, shape) {
+  p.value <- ks.test(x, "pgev", loc = loc, scale = scale, shape = shape)$p.value
+  list(p.value = p.value)
+}
+
+ptm <- proc.time()
+
+# Set variables
+n <- 100
+rho <- 0.5
+counter <- 0
+nrep <- 100
+B <- 100
+loc <- 0
+shape <- 0.2
+scale <- 1
+
+# P-vals from using bootstrap with copulas
+pvals_copula <- replicate(nrep, test_gev_D(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho),
+                                           loc = loc, 
+                                           shape = shape,
+                                           scale = scale,
+                                           B = B))
+counter <- 0
+
+# P-vals from standard KS test
+pvals_naive <- replicate(nrep, test_standard_gev(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
+                                                 loc = loc, 
+                                                 shape = shape,
+                                                 scale = scale)$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
+p_values <- c(pvals_copula, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+# Generate histograms plot
+hist_gev_D <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+hist_gev_D
+
+print(proc.time() - ptm)
+
+# Save the histogram figure
+ggsave(filename = "hist_gev_D.pdf", plot = hist_gev_D, path = "../Manuscript", height = 2.1, width = 6)
+```
+
+```{r Copula FD}
+test_copula_D <- function(x, dist, B) {
 
@@
 # Super naive KS-test with fitted parameters
-test_super_naive <- function(x) {
+test_standard_ks_F <- function(x) {
   p.value <- ks.test(x, "pnorm", mean = mean(x), sd = sd(x))$p.value
@@
 nrep <- 1000
-B <- 100
+B <- 1000
 
 # P-vals from using bootstrap with copulas
-pvals_copula <- replicate(nrep, test_copula(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), "pnorm", B = B))
+pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), "pnorm", B = B))
 counter <- 0
@@
 # P-vals from naively using fitted parameters
-pvals_naive <- replicate(nrep, test_super_naive(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)
+pvals_naive <- replicate(nrep, test_standard_ks_F(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive Parametric", nrep), rep("Super Naive", nrep))
+p_values <- c(pvals_copula, pvals_parametric, pvals_naive)
+results <- data_frame(p_values, histogram)
+save(results, file = "results_copula.RData")
+
+# Generate histograms plot
+hist_ar1_D <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+hist_ar1_D
+
+print(proc.time() - ptm)
+
+# Save the histogram figure
+ggsave(filename = "hist_ar1_D", plot = hist_ar1_D, path = "../Manuscript", height = 2.1, width = 6)
+```
+
+```{r MA(1) FD}
+## Test MA(1) model
+ptm <- proc.time()
+
+# Set variables
+n <- 100
+counter <- 0
+nrep <- 1000
+B <- 1000
+ma <- 0.5
+
+# P-vals from using bootstrap with copulas
+pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ma = ma), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), "pnorm", B = B))
+counter <- 0
+
+# P-vals from using parametric bootstrap
+pvals_parametric <- replicate(nrep, test_parametric(arima.sim(list(ma = ma), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n))$p.value)
+
+# P-vals from naively using fitted parameters
+pvals_naive <- replicate(nrep, test_standard_ks_F(arima.sim(list(ma = ma), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n))$p.value)
 
@@
 # Generate histograms plot
-hist_copula <- ggplot(results) + 
+hist_ma1_D <- ggplot(results) + 
                    geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
@@
                    theme(legend.position = "none") +
-                   facet_wrap(~histogram, scales = "free_y") +
-                   labs(caption = sprintf("AR = %s", ar))
-hist_copula
+                   facet_wrap(~histogram, scales = "free_y")
 
@@
 
+hist_ma1_D
+
 # Save the histogram figure
-ggsave(filename = "hist_copula.pdf", plot = hist_copula, path = "../Manuscript", height = 2.1, width = 6)
+ggsave(filename = "hist_ma1_D.pdf", plot = hist_ma1_D, path = "../Manuscript", height = 2.1, width = 6)
 ```
 
-```{r}
+```{r ARMA(1,1) FD}
+## Test ARMA(1,1) model
+ptm <- proc.time()
+
+# Set variables
+n <- 100
+counter <- 0
+nrep <- 1000
+B <- 1000
+ar <- 0.5
+ma <- 0.3
+
+# P-vals from using bootstrap with copulas
+pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ar = ar, 
+                                                           ma = ma), 
+                                                      rand.gen=rnorm, 
+                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
+                                                      n = n),
+                                            "pnorm", B = B))
+counter <- 0
+
+# P-vals from using parametric bootstrap
+pvals_parametric <- replicate(nrep, test_parametric(arima.sim(list(ar = ar, 
+                                                              ma = ma), 
+                                                      rand.gen=rnorm, 
+                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
+                                                      n = n))$p.value)
+
+# P-vals from naively using fitted parameters
+pvals_naive <- replicate(nrep, test_standard_ks_F(arima.sim(list(ar = ar, 
+                                                              ma = ma), 
+                                                      rand.gen=rnorm, 
+                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
+                                                      n = n))$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive Parametric", nrep), rep("Super Naive", nrep))
+p_values <- c(pvals_copula, pvals_parametric, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+# Generate histograms plot
+hist_arma_D <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+
+print(proc.time() - ptm)
+
+hist_arma_D
+
+# Save the histogram figure
+ggsave(filename = "hist_arma_D.pdf", plot = hist_arma_D, path = "../Manuscript", height = 2.1, width = 6)
+```
+
+```{r AR(2) FD}
 ## Test AR(2) model
@@
 # P-vals from using bootstrap with copulas
-pvals_copula <- replicate(nrep, test_copula(arima.sim(list(order = c(2, 0, 0), 
+pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(order = c(2, 0, 0), 
                                                            ar = c(b1, b2)),
@@
 # Generate histograms plot
-hist_copula_ar2 <- ggplot(results) + 
-                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
-                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
-                   theme(legend.position = "none") +
-                   facet_wrap(~histogram, scales = "free_y") +
-                   labs(caption = sprintf("AR = (%s, %s)", b1, b2))
-
-print(proc.time() - ptm)
-
-hist_copula_ar2
-
-# Save the histogram figure
-ggsave(filename = "hist_copula_ar2.pdf", plot = hist_copula_ar2, path = "../Manuscript", height = 2.1, width = 6)
-```
-
-```{r}
-## Test MA(1) model
-ptm <- proc.time()
-
-# Set variables
-n <- 100
-counter <- 0
-nrep <- 1000
-B <- 1000
-ma <- 0.5
-
-# P-vals from using bootstrap with copulas
-pvals_copula <- replicate(nrep, test_copula(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), "pnorm", B = B))
-counter <- 0
-
-# P-vals from using parametric bootstrap
-pvals_parametric <- replicate(nrep, test_parametric(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n))$p.value)
-
-# P-vals from naively using fitted parameters
-pvals_naive <- replicate(nrep, test_super_naive(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n))$p.value)
-
-# Create a master data_frame with all the results
-histogram <- c(rep("Copula", nrep), rep("Naive Parametric", nrep), rep("Super Naive", nrep))
-p_values <- c(pvals_copula, pvals_parametric, pvals_naive)
-results <- data_frame(p_values, histogram)
-
-# Generate histograms plot
-hist_copula_ma1 <- ggplot(results) + 
-                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
-                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
-                   theme(legend.position = "none") +
-                   facet_wrap(~histogram, scales = "free_y") +
-                   labs(caption = sprintf("MA = %s", ma))
-
-print(proc.time() - ptm)
-
-hist_copula_ma1
-
-# Save the histogram figure
-ggsave(filename = "hist_copula_ma1.pdf", plot = hist_copula_ma1, path = "../Manuscript", height = 2.1, width = 6)
-```
-
-```{r}
-## Test ARMA(1,1) model
-ptm <- proc.time()
-
-# Set variables
-n <- 100
-counter <- 0
-nrep <- 1000
-B <- 1000
-ar <- 0.5
-ma <- 0.3
-
-# P-vals from using bootstrap with copulas
-pvals_copula <- replicate(nrep, test_copula(arima.sim(list(ar = ar, 
-                                                           ma = ma), 
-                                                      rand.gen=rnorm, 
-                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
-                                                      n = n),
-                                            "pnorm", B = B))
-counter <- 0
-
-# P-vals from using parametric bootstrap
-pvals_parametric <- replicate(nrep, test_parametric(arima.sim(list(ar = ar, 
-                                                              ma = ma), 
-                                                      rand.gen=rnorm, 
-                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
-                                                      n = n))$p.value)
-
-# P-vals from naively using fitted parameters
-pvals_naive <- replicate(nrep, test_super_naive(arima.sim(list(ar = ar, 
-                                                              ma = ma), 
-                                                      rand.gen=rnorm, 
-                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
-                                                      n = n))$p.value)
-
-# Create a master data_frame with all the results
-histogram <- c(rep("Copula", nrep), rep("Naive Parametric", nrep), rep("Super Naive", nrep))
-p_values <- c(pvals_copula, pvals_parametric, pvals_naive)
-results <- data_frame(p_values, histogram)
-
-# Generate histograms plot
-hist_copula_arma <- ggplot(results) + 
-                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
-                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
-                   theme(legend.position = "none") +
-                   facet_wrap(~histogram, scales = "free_y") +
-                   labs(caption = sprintf("AR = %s, MA = %s", ar, ma))
-
-print(proc.time() - ptm)
-
-hist_copula_arma
-
-# Save the histogram figure
-ggsave(filename = "hist_copula_arma.pdf", plot = hist_copula_arma, path = "../Manuscript", height = 2.1, width = 6)
-```
-
-```{r}
-## wcopula: working copula assumed in constructing bootstrap sample
-test_copula2 <- function(x, dist, B = 100, wcopula = normalCopula) {
-    ## example assuming normal distribution; normal copula
-    ## get observed stat
-    n <- length(x)
-    ## get fitted parameters; could check MASS::fitdistr for general solution
-    ## the next two lines only work when dist is normal
-    mu <- mean(x)
-    sigma <- sd(x)
-    stat  <- ks.test(x, dist, mean = mu, sd = sigma)$statistic
-    ## get lag-1 sample auto-spearman rho
-    rho  <-  cor(x[-1], x[-n], method = "spearman")
-    r <- iRho(wcopula(), rho)
-    wcop <- wcopula(r)
-    ## parametric bootstrap to get an empirical distribution of stat
-    stat.b <- double(n)
-    ## set up containers
-    for (i in 1:B) {
-        ## get one bootstrap sample
-        ## 1. the marginal distribution is the fitted dist
-        ## 2. there is temporal dependence
-        u <- runif(n)
-        for (j in 2:n) {
-            ## could test other copulas later
-            u[j]  <- cCopula(c(u[j-1], u[j]), wcop, indices = 2, inverse = TRUE)
-        }
-        ## get bootstrap sample
-        ## get fitted parameters for the bootstrap sample
-        ## the next lines only work when dist is normal
-        x.b <- qnorm(u, mean = mu, sd = sigma)
-        mu.b <- mean(x.b)
-        sigma.b <- sd(x.b)
-        stat.b[i] <- ks.test(x.b, dist, mean = mu.b, sd = sigma.b)$statistic
-    }
-    ## return empirical p-value    
-    p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
-
-    counter <<- counter + 1
-    cat(counter, "")
-
-    return(p.value)
-}
-
-## generating observations from a specified distribution with serial dependence
-genData <- function(n, qdist, ..., copula, rho) {
-    ## n: sample size
-    ## qdist: quantile function of the desired marginal distribution
-    ## copula: copula for serial distribution
-    ## rho: spearman's rho
-    theta <- iRho(copula(), rho)
-    cop <- copula(theta)
-    u <- runif(n)
-    for (j in 2:n) {
-        u[j] <- cCopula(c(u[j-1], u[j]), cop, indices = 2, inverse = TRUE)
-    }
-    qdist(u, ...)
-}
-
-# Naive KS-test
-test_naive_copula <- function(x) {
-  p.value <- ks.test(x, "pnorm")$p.value
-  list(p.value = p.value)
-}
-
-ptm <- proc.time()
-
-# Generate results
-n <- 100
-rho <- 0.5
-counter <- 0
-nrep <- 100
-B <- 100
-pvals_copula <- replicate(nrep, test_copula2(genData(n, qnorm, mean = 1, sd = 1, copula = claytonCopula, rho = rho), "pnorm", B = B))
-pvals_naive <- replicate(nrep, test_naive_copula(genData(n, qnorm, mean = 1, sd = 1, copula = claytonCopula, rho = rho))$p.value)
-
-# Create a master data_frame with all the results
-histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
-p_values <- c(pvals_copula, pvals_naive)
-results <- data_frame(p_values, histogram)
-
-# Generate histograms plot
-hist_copula2 <- ggplot(results) + 
+hist_ar2_D <- ggplot(results) + 
                    geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
@@
 
-hist_copula2
+hist_ar2_D
 
 # Save the histogram figure
-#ggsave(filename = "hist_copula_c2.pdf", plot = hist_copula_c, path = "../Manuscript", height = 2.1, width = 6)
+ggsave(filename = "hist_ar2_D.pdf", plot = hist_ar2_D, path = "../Manuscript", height = 2.1, width = 6)
 ```
 
-```{r}
+```{r Gamma FD}
 # Testing bootstrap with copulas for gamma distribution
-test_gamma <- function(x, dist, B = 100, wcopula = normalCopula) {
+test_gamma_FD <- function(x, dist, B = 100, wcopula = normalCopula) {
 
@@
 n <- 100
-rho <- 0.7
+rho <- 0.5
 counter <- 0
@@
 # P-vals from using bootstrap with copulas
-pvals_copula <- replicate(nrep, test_gamma(genData(n, qgamma, shape = 3, scale = 1, copula = normalCopula, rho = rho), "pgamma", B = B))
+pvals_copula <- replicate(nrep, test_gamma_FD(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), "pgamma", B = B))
 counter <- 0
@@
 # P-vals from using parametric bootstrap
-pvals_parametric <- replicate(nrep, test_parametric_gamma(genData(n, qgamma, shape = 3, scale = 1, copula = normalCopula, rho = rho))$p.value)
+pvals_parametric <- replicate(nrep, test_parametric_gamma(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho))$p.value)
 
 # P-vals from naively using fitted parameters
-pvals_naive <- replicate(nrep, test_super_naive_gamma(genData(n, qgamma, shape = 3, scale = 1, copula = normalCopula, rho = rho))$p.value)
+pvals_naive <- replicate(nrep, test_super_naive_gamma(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho))$p.value)
 
@@
 # Generate histograms plot
-hist_copula_gamma <- ggplot(results) + 
+hist_gamma_FD <- ggplot(results) + 
                    geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
@@
                    theme(legend.position = "none") +
-                   facet_wrap(~histogram, scales = "free_y") +
-                   labs(caption = sprintf("Rho = %s, Shape = %s, Scale = %s", rho, shape, scale))
+                   facet_wrap(~histogram, scales = "free_y")
 
@@
 
-hist_copula_gamma
+hist_gamma_FD
 
 # Save the histogram figure
-ggsave(filename = "hist_copula_gamma.pdf", plot = hist_copula_gamma, path = "../Manuscript", height = 2.1, width = 6)
+ggsave(filename = "hist_gamma_FD.pdf", plot = hist_gamma_FD, path = "../Manuscript", height = 2.1, width = 6)
 ```
 
-```{r}
+```{r GEV FD}
 # Testing bootstrap with copulas for GEV distribution
-test_gev <- function(x, B = 100, wcopula = normalCopula) {
+test_gev_FD <- function(x, B = 100, wcopula = normalCopula) {
 
@@
 nrep <- 1000
-B <- 100
+B <- 1000
 loc <- 0
@@
 # P-vals from using bootstrap with copulas
-pvals_copula <- replicate(nrep, test_gev(genData(n, qgev, loc = 0, shape = shape, scale = 1, copula = normalCopula, rho = rho), B = B))
+pvals_copula <- replicate(nrep, test_gev_FD(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho), B = B))
 counter <- 0
@@
 # P-vals from using parametric bootstrap
-pvals_parametric <- suppressWarnings(replicate(nrep, test_parametric_gamma(genData(n, qgev, loc = 0, shape = shape, scale = 1, copula = normalCopula, rho = rho))$p.value))
+pvals_parametric <- suppressWarnings(replicate(nrep, test_parametric_gamma(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho))$p.value))
 
 # P-vals from naively using fitted parameters
-pvals_naive <- replicate(nrep, test_super_naive_gamma(genData(n, qgev, loc = 0, shape = shape, scale = 1, copula = normalCopula, rho = rho))$p.value)
+pvals_naive <- replicate(nrep, test_super_naive_gamma(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho))$p.value)
 
@@
 # Generate histograms plot
-hist_copula_gev <- ggplot(results) + 
+hist_gev_FD <- ggplot(results) + 
                    geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
@@
                    theme(legend.position = "none") +
-                   facet_wrap(~histogram, scales = "free_y") +
-                   labs(caption = sprintf("Rho = %s, Loc = %s, Shape = %s, Scale = %s", rho, loc, shape, scale))
+                   facet_wrap(~histogram, scales = "free_y")
 
@@
 
-hist_copula_gev
+hist_gev_FD
 
 # Save the histogram figure
-ggsave(filename = "hist_copula_gev.pdf", plot = hist_copula_gev, path = "../Manuscript", height = 2.1, width = 6)
+ggsave(filename = "hist_gev_FD.pdf", plot = hist_gev_FD, path = "../Manuscript", height = 2.1, width = 6)
 ```
-
-```{r}
-ptm <- proc.time()
-
-# Super naive KS-test with fitted parameters
-test_super_duper_naive <- function(x) {
-  p.value <- ks.test(x, "pnorm", mean = 0, sd = 1)$p.value
-  list(p.value = p.value)
-}
-
-# Set variables
-n <- 100
-ar <- 0.5
-counter <- 0
-nrep <- 1000
-B <- 100
-
-# P-vals from using bootstrap with copulas
-pvals_copula <- replicate(nrep, test_copula(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), "pnorm", B = B))
-counter <- 0
-
-# P-vals from naively using fitted parameters
-pvals_naive <- replicate(nrep, test_super_duper_naive(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)
-
-# Create a master data_frame with all the results
-histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
-p_values <- c(pvals_copula, pvals_naive)
-results <- data_frame(p_values, histogram)
-
-# Generate histograms plot
-hist_copula_only <- ggplot(results) + 
-                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
-                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
-                   theme(legend.position = "none") +
-                   facet_wrap(~histogram, scales = "free_y") +
-                   labs(caption = sprintf("AR = %s", ar))
-hist_copula_only
-
-print(proc.time() - ptm)
-
-# Save the histogram figure
-ggsave(filename = "hist_copula_only.pdf", plot = hist_copula_only, path = "../Manuscript", height = 2.1, width = 6)
-```

### 2022-04-28 Manuscript/manuscript.tex
renamed and reordered plots

@@
   \centering
-  \includegraphics{hist_copula_only}
+  \includegraphics{hist_ar1_FD}
   \caption{Histograms demonstrating copula use to correct dependence.}
-  \label{fig:hist_copula_only}
+  \label{fig:hist_ar1_FD}
 \end{figure}
 
-Figure~\ref{fig:hist_copula_only} displays the results of the copula remedy for dependent data.
+Figure~\ref{fig:hist_ar1_FD} displays the results of the copula remedy for dependent data.
 The data is generated from an AR-1 model with $\psi = .5$. The copula used is to model
@@
 The remedy using copulas is effective in the case where both assumptions are violated.
-This is shown in Figure~\ref{fig:hist_copula}. The ``super naive" method is the resulting 
+This is shown in Figure~\ref{fig:hist_ar1_FD}. The ``super naive" method is the resulting 
 p-values when you naively use fitted parameters while ignoring dependence in the data.
@@
   \centering
-  \includegraphics{hist_copula}
+  \includegraphics{hist_ar1_FD}
   \caption{Histograms demonstrating copula use to correct fitted parameters and dependence.}
-  \label{fig:hist_copula}
+  \label{fig:hist_ar1_FD}
 \end{figure}
@@
 show that as long as the AR(1) assumption is a close approximation, the correction still restores power to the test.
-Figure~\ref{fig:hist_copula_ma1} is the procedure performed on data generated from 
-an MA(1) model with $\theta = 0.5$. Figure~\ref{fig:hist_copula_arma} displays results with 
+Figure~\ref{fig:hist_ma1_FD} is the procedure performed on data generated from 
+an MA(1) model with $\theta = 0.5$. Figure~\ref{fig:hist_arma_FD} displays results with 
 data generated from an ARMA(1,1) model with $\psi = 0.5$ and $\theta = 0.3$.
@@
   \centering
-  \includegraphics{hist_copula_ma1}
-  \includegraphics{hist_copula_arma}
+  \includegraphics{hist_ma1_FD}
+  \includegraphics{hist_arma_FD}
   \caption{MA-1 and ARMA(1,1)}
@@
 It is also possible to apply our procedure to other distributions. All of the simulations
-to this point have been done with standard normal data. The data in Figure~\ref{fig:hist_copula_gamma} 
-is generated from $Gamma ~ (3,1)$ with a correlation coefficient of $\rho = 0.5$. Figure~\ref{fig:hist_copula_gev}
+to this point have been done with standard normal data. The data in Figure~\ref{fig:hist_gamma_FD} 
+is generated from $Gamma ~ (3,1)$ with a correlation coefficient of $\rho = 0.5$. Figure~\ref{fig:hist_gev_FD}
 shows the procedure applied to data from $GEV ~ (0, 0.2, 1)$ with a correlation coefficient of $\rho = 0.5$.
@@
   \centering
-  \includegraphics{hist_copula_gamma}
-  \includegraphics{hist_copula_gev}
+  \includegraphics{hist_gamma_FD}
+  \includegraphics{hist_gev_FD}
   \caption{Gamma(3,1)}
-  \label{fig:hist_copula_gamma}
+  \label{fig:hist_gamma_FD}
 \end{figure}
@@
 structure is too inaccurate. An AR-2 model can be used to demonstrate this. For 
-an AR-2 model with $\phi = (0.5, 0.3)$, Figure~\ref{fig:hist_copula_ar2} 
+an AR-2 model with $\phi = (0.5, 0.3)$, Figure~\ref{fig:hist_ar2_FD} 
 displays the results of applying the various remedies. While the remedies 
@@
   \centering
-  \includegraphics{hist_copula_ar2}
+  \includegraphics{hist_ar2_FD}
   \caption{AR-2}
-  \label{fig:hist_copula_ar2}
+  \label{fig:hist_ar2_FD}
 \end{figure}

### 2022-04-28 Manuscript/manuscript.tex
introduction discrete discussion

@@
 The standard one-sample KS test applies to independent data with a continuous
-hypothesized distribution that is completely specified.
-\jy{this paragraph needs some reorganization.
-  Flow: not applicable to discrete or rounded data (give references; which is
-  not the focus of this paper);
-  not applicable to fitted distributions;
-  not applicable to serially dependent data}
-\jy{break the big paragraph into smaller ones}
-Often in literature, it has been "discovered" that the test loses its power when 
-applied to dependent or discrete data with hypothesized distributions containing 
-estimated parameters. DISCRETE SECTION HERE. This issue with discrete or rounded
-is not the focus of this paper, though is a common misuse that should be 
-noted.
+hypothesized distribution that is completely specified. Often in literature, it 
+has been "discovered" that the test loses its power when applied to dependent or 
+discrete data with hypothesized distributions containing estimated parameters 
+\citep{Steinskog}.
+
+It is well known that the standard test does not apply for
+discrete data. \citet{Noether} provides a brief demonstration of the 
+conservative character of the KS test when using discrete functions. 
+There are remedies that allow the KS test to be used in discrete cases. 
+\citet{Conover} describes a method for finding the exact critical level for 
+discrete cases and derives its power. \citet{Gleser} provides methods for 
+adapting existing algorithms to provide results when F(x) is discontinuous.
+The discrete KS test is available in various statistical software packages.
+The package \textsf{dgof} implements the methods from \citet{Conover} for 
+one-sided tests and the methods from \citet{Gleser} for exact two-sided 
+p-values \citep{Arnold}. The \textsf{KSgeneral} package provides a fast and 
+accurate method for when F(x) is arbitrary, discontinuous, or continuous that 
+uses an alternative fast Fourier transform based method \citep{Dimitrova}.
+This issue with discrete or rounded is not the focus of this paper, though is a
+common misuse that should be noted.
 
 The standard KS test is not applicable when the hypothesized distribution 
-contains fitted parameters. \citet{Steinskog} demonstrates the change in power 
+contains fitted parameters. \citet{Steinskog} "discovers" the change in power 
 when using estimated parameters and stress caution in using the KS test in such 

### 2022-04-29 Manuscript/manuscript.tex
combined plots, figure captions, other edits

@@
 dependent, discrete, or rounded data, with hypothesized distributions containing 
-estimated parameters. For example, it has been ``discovered'' multiple times 
+estimated parameters. For example, it has been ``discovered" multiple times 
 that the test is too conservative when the parameters are estimated. We 
@@
 
-\section{Introduction}\label{sec:intro}
+\section{Introduction}
+\label{sec:intro}
 
@@
 hypothesized distribution that is completely specified. Often in literature, it 
-has been "discovered" that the test loses its power when applied to dependent or 
-discrete data with hypothesized distributions containing estimated parameters 
+has been ``discovered" that the test loses its power when applied to dependent 
+or discrete data with hypothesized distributions containing estimated parameters 
 \citep{Steinskog}.
 
-It is well known that the standard test does not apply for
-discrete data. \citet{Noether} provides a brief demonstration of the 
+\citet{Noether} provides a brief demonstration of the 
 conservative character of the KS test when using discrete functions. 
@@
 effects. In order to set up the demonstrations, simulated data is used 
-throughout. The remedies are also performed on a various families of 
+throughout. The remedies are also performed on various families of 
 distributions.
@@
 
-\section{Fitted Parameters}\label{sec:fitted}
+\section{Fitted Parameters}
+\label{sec:fitted}
 
@@
     \]
-    where $B_{n}(x) = \sqrt{n}(F_{n}(x) - F_{\hat\theta_n}(x))$ is the known bias
-    term \citep{Babu}
+    where $B_{n}(x) = \sqrt{n}(F_{n}(x) - F_{\hat\theta_n}(x))$ is the known 
+    bias term \citep{Babu}
   \item
@@
 \end{enumerate}
+The p-value can be calculated by counting the number of bootstrap KS 
+statistics greater than or equal to the observed KS statistic, and then dividing 
+by the number of bootstrap samples. Figure~\ref{fig:hist_fitted} displays the 
+results of from our simulations. We would expect the distribution of p-values 
+to be normal in the case where the KStest holds its power. It is clear from the 
+figure that both bootstrap processes correct for the problem of fitted 
+parameters. The plots for the bootstrapped p-values appear to be $U(0,1)$, 
+unlike the naive p-values.
 
@@
   \includegraphics[width=\textwidth]{hist_fitted}
-  \caption{Implementing bootstrap remedies for fitted parameters misuse. \jy{make the caption self-contained.}}
+  \caption{The Naive plot (left) is the histogram of p-values from the standard 
+  KS test with fitted parameters. The Parametric plot (middle) is the histogram
+  of p-values from implementing parametric bootstrap. The Babu plot (right) is 
+  the histogram of p-values from implementing the nonparametric bootstrap with a 
+  correction for bias. In each case, $1000$ replicate tests were performed on 
+  the standard normal distribution with sample size $n = 100$. $B = 1000$ 
+  bootstrap samples are obtained for each test.}
   \label{fig:hist_fitted}
@@
 
-Figure~\ref{fig:hist_fitted} displays the results of from our simulations. The 
-procedure is replicated $1000$ times using the standard normal distribution with
-sample size $n=100$. In each replicate test, $B = 1000$ bootstrap samples are 
-obtained. The p-value can be calculated by counting the number of bootstrap KS 
-statistics greater than or equal to the observed KS statistic, and then dividing 
-by the number of bootstrap samples. It is clear from the figure that both
-bootstrap processes correct for the problem of fitted parameters. The plots 
-appear to be $U(0,1)$, which is expected of a full power test.
-
-\section{Serially Dependent Data}\label{sec:dependence}
+\section{Serially Dependent Data}
+\label{sec:dependence}
 
@@
 performs poorly. In this situation, the null hypothesis is $H_0$: the random 
-sample $X_1, \ldots, X_n$ come from a continuous distribution $F_{\theta}$ with 
-specified parameter $\theta$.
-Let $\hat\theta_n$ be an estimator of $\theta$, which could be, for example,
-maximum likelihood estimator of moment estimator. The test statistic is
-\[
-  D = \sup_x | F_n(x) - F_{\hat\theta_n}(x) |.
-\]
-However, since the data is dependent, the null hypothesis is wrong and must be 
-corrected. This is demonstrated with a simulation in 
-Figure~\ref{fig:hist_correlation}. Data is generated from a first-order 
-autoregressive model (AR-1) with a standard normal distribution. The simulation
-is done with the levels of the AR coefficient $\psi$, varying from $(-3,3)$. 
-The results echo those of \citet{Durilleul} that the KS statistic is too liberal 
-for positive autocorrelation values, and that the behavior is asymmetrical for 
-negative values.
+sample $X_1, \ldots, X_n$ come from a continuous distribution $F$ where $F$ has 
+completely specified parameters. The test statistic is the same as 
+Equation~\ref{eq:ks_standard}. However, since the data is dependent, the null 
+hypothesis is wrong and must be corrected. This is demonstrated with a 
+simulation in Figure~\ref{fig:hist_correlation}. Data is generated from a 
+first-order autoregressive model (AR(1)) with a standard normal distribution. 
+The simulationis done with the levels of the AR coefficient $\psi$, varying 
+from $(-3,3)$. The results echo those of \citet{Durilleul} that the KS statistic
+is too liberal for positive autocorrelation values, and that the behavior is 
+asymmetrical for negative values.
 
@@
   \includegraphics{hist_correlation}
-  \caption{Results of varying AR levels of AR-1 simulated data.}
+  \caption{Each histogram is a plot of the p-values of standard KS tests
+  performed on dependent data simulated from an AR(1) process of the standard 
+  normal distribution. The titles represent the various levels of the AR 
+  coefficient $\psi$ tested. The sample size is $n = 100$ and $1000$ replicate 
+  tests were performed for each AR coefficient.}
   \label{fig:hist_correlation}
@@
 distribution \citep{Copula, Hofert}. For simplicity, we assume a normal copula 
-with an AR-1 structure to characterize the serial dependence of the observations. 
-The AR-1 parameter of the normal copula is set to match the be the sample serial
-Spearman's rho of the observed sample. The procedure is as follows.
-
-\jy{simulate $X_t | X_{t-1}$, assuming $F$:
-  $Z_{t-1} = \Phi^{-1}[ F(X_{t-1})]$;
-  $Z_{t} = \rho Z_{t -1} +  \epsilon_t$;
-  $X_t = F^{-1} [ \Phi(Z_t) ]$
-  }
+with an AR(1) structure to characterize the serial dependence of the 
+observations. The AR(1) parameter of the normal copula is set to match the be 
+the sample serial Spearman's rho of the observed sample. The procedure is as 
+follows.
 
@@
 \item
-    Black box
-    \jy{need to spell out the details; how to generate $X_t$ given $X_{t-1}$?}
+  Generate $Z_1, \ldots, Z_n$ from an AR(1) process with autocorrelation
+  coefficient $r$ such that the $Z_i$'s are $N(0, 1)$ variables.
 \item
-    Transform bootstrap sample to 
+  Form a bootstrap sample $X_i^* = F^{-1} [\Phi(Z_i)]$,
+  $i = 1, \ldots, n$, whose first-order sample Spearman's rho matches that of
+  the observed data.
+\item
+  Obtain the empirical distribution function $F_n^*$ of the bootstrap sample
+  $X_1^*, \ldots, X_n^*$.
+\item 
+  Calculate bootstrap KS statistic
+  \[
+    D^* = \sup_x \lvert F_n^* (x)- F(x) \rvert.
+  \]
 \item
@@
 
-\jy{add a discussion about the method. The method is exact if the true
-  dependence is indeed a normal copula with an ar1 structure. When it is not, it
-  may still give a reasonable approximation that can be useful for practical purpose}
+As mentioned, throughout the procedure we assume an AR(1) structure regardless 
+of the true dependence. If the true dependence is indeed a normal copula with 
+an AR(1) structure, this method is exact. When the true dependence is not AR(1),
+it may still give a reasonable approximation that can be useful for practical 
+purposes. This is demonstrated with different dependence structures in 
+Figure~\ref{fig:hist_ma1_FD}.
 
@@
   \centering
-  \includegraphics{hist_ar1_FD}
-  \caption{Histograms demonstrating copula use to correct dependence.}
-  \label{fig:hist_ar1_FD}
+  \includegraphics{hist_ar1_D}
+  \caption{The Naive plot is the histogram of p-values from the standard KS 
+  test. The Copula plot is the histogram of p-values from implementing 
+  parametric bootstrap with copulas for dependence. In each case, $1000$ 
+  replicate tests were performed with the data generated from an AR(1) process 
+  of the standard normal distribution with $\psi = .5$. The sample size is $n = 
+  100$ and $B = 1000$ bootstrap samples are obtained for each test.}
+  \label{fig:hist_ar1_D}
 \end{figure}
 
-Figure~\ref{fig:hist_ar1_FD} displays the results of the copula remedy for dependent data.
-The data is generated from an AR-1 model with $\psi = .5$. The copula used is to model
-dependence is the normal copula. $1000$ replicate tests were performed with
-$B = 1000$ bootstrap samples per test.
+Figure~\ref{fig:hist_ar1_D} displays the results of the copula remedy for 
+dependent data. The data is generated from an AR(1) model with $\psi = .5$. The 
+copula used is to model dependence is the normal copula. $1000$ replicate tests 
+were performed with $B = 1000$ bootstrap samples per test.
 \jy{present other scenarios too}
-The naive test is performed by simply using the KS test without correcting for any 
-potential dependence.
-
-\section{Fitted Parameters and Serially Dependent Data}\label{sec:fittedwithdependence}
-
-\jy{give a stronger motivation; last section is not practical at all because we
-  often don't know the parameters; this section combines the last two}
-The remedy using copulas is effective in the case where both assumptions are violated.
-This is shown in Figure~\ref{fig:hist_ar1_FD}. The ``super naive" method is the resulting 
-p-values when you naively use fitted parameters while ignoring dependence in the data.
-The ``naive parametric" plot is the result of applying parametric bootstrap to correct
-for fitted parameters while ignoring potential dependence. Of course, the "copula" 
-plot applies the fix for both assumptions. The results show that copula remedy generates 
-uniform p-values and restores the power of the KS test.
+The naive test is performed by simply using the KS test without correcting for 
+any potential dependence.
 
@@
   \centering
-  \includegraphics{hist_ar1_FD}
-  \caption{Histograms demonstrating copula use to correct fitted parameters and dependence.}
-  \label{fig:hist_ar1_FD}
+  \includegraphics{hist_ma1_arma_ar2_D}
+  \caption{The Naive plots are the histograms of p-values from the standard KS 
+  test. The Copula plots are the histograms of p-values from parametric 
+  bootstrap with copulas for dependence. The data is generated from an MA(1) 
+  process (left) with $\theta = .5$, ARMA(1, 1) process (middle) with $\psi = 
+  .5$ and $\theta = .3$, and AR(2) process (right) with $\psi = (.5, .3)$ of the 
+  standard normal distribution. In each case, $1000$ replicate tests were 
+  performed with sample size $n = 100$ and $B = 1000$ bootstrap samples.}
+  \label{fig:hist_ma1_arma_ar2_D}
 \end{figure}
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics{hist_gamma_gev_D}
+  \caption{The Naive plots are the histograms of p-values from the standard KS 
+  test. The Copula plots are the histograms of p-values from parametric 
+  bootstrap with copulas for dependence. The data is generated from $Gamma(3, 
+  1)$ (left) and $GEV(0, .2, 1)$ (right) with a correlation coefficient of $r = 
+  0.5$. In each case, $1000$ replicate tests were performed with sample size $n 
+  = 100$ and $B = 1000$ bootstrap samples.}
+  \label{fig:hist_gamma_gev_D}
+\end{figure}
+
+\section{Fitted Parameters and Serially Dependent Data}
+\label{sec:fittedwithdependence}
+
+The procedure demonstrated in Section~\ref{sec:dependence} works when the data 
+is dependent and the hypothesized distribution is completely specified. However,
+this is not practical. In practice we do not know the parameters of the 
+hypothesized distribution. Therefore, it is valuable to have a procedure that
+corrects for both fitted parameters and serially dependent data. The remedy 
+using copulas can be modified to be effective in the case where both assumptions
+must be violated. The null hypothesis is equivalent to Section~\ref{sec:fitted} 
+and the test statistic is equal to Equation~\ref{eq:ks_fitted}.
 
@@
 procedure in Section~\ref{sec:fitted} is no longer valid because the serial
-dependence is not accounted for. Let $r$ be the
-AR-1 coefficient of the normal copula that matches the sample first-order
-Spearman's rho of the observed data as obtained by the \texttt{iRho} function in
-the \textsf{copula} package. We propose the following bootstrap procedure to
-assess the significance of the observed KS statistic.
+dependence is not accounted for. Let $r$ be the AR(1) coefficient of the normal 
+copula that matches the sample first-order Spearman's rho of the observed data 
+as obtained by the \texttt{iRho} function in the \textsf{copula} package. We 
+propose the following bootstrap procedure to assess the significance of the 
+observed KS statistic.
 \begin{enumerate}
@@
 \item
-  Fit $F_\theta$ to the sample $X_1^*, \ldots, X_n^*$ and obtain estimator $\hat\theta_n^*$
+  Fit $F_\theta$ to the sample $X_1^*, \ldots, X_n^*$ and obtain estimator 
+  $\hat\theta_n^*$
 \item
@@
 
+Figure~\ref{fig:hist_ar1_FD} shows the results of our simulation on data 
+simulated from an AR(1) process. The ``super naive" method is the resulting 
+p-values when you naively use fitted parameters while ignoring dependence in the
+data. The ``naive parametric" plot is the result of applying parametric 
+bootstrap to correct for fitted parameters while ignoring potential dependence. 
+Of course, the "copula" plot applies the fix for both assumptions. The results 
+show that copula remedy generates uniform p-values and restores the power of the
+KS test.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics{hist_ar1_FD}
+  \caption{The Super Naive plot (left) is the histogram of p-values from the 
+  standard KS test with fitted parameters. The Naive Parametric plot (middle) is
+  the histogram of p-values from implementing parametric bootstrap. The Copula 
+  plot is the histogram of p-values from implementing parametric bootstrap with 
+  copulas for dependence and correcting for fitted parameters. In each case, 
+  $1000$ replicate tests were performed with the data generated from an AR(1) 
+  process of the standard normal distribution with $\psi = .5$. The sample size 
+  is $n = 100$ and $B = 1000$ bootstrap samples are obtained for each test.}
+  \label{fig:hist_ar1_FD}
+\end{figure}
+
 The copula fix is not a complete solution, because regardless of the true dependence in the data
@@
   \centering
-  \includegraphics{hist_ma1_FD}
-  \includegraphics{hist_arma_FD}
-  \caption{MA-1 and ARMA(1,1)}
-  \label{fig:hist_copula_ma1}
+  \includegraphics{hist_ma1_arma_ar2_FD}
+  \caption{The Super Naive plots (left) are the histograms of p-values from the 
+  standard KS test with fitted parameters. The Naive Parametric plots (middle) 
+  are the histograms of p-values from implementing parametric bootstrap. The 
+  Copula plots are the histograms of p-values from implementing parametric 
+  bootstrap with copulas for dependence and correcting for fitted parameters. 
+  The data is generated from an MA(1) process (left) with $\theta = .5$, ARMA(1,
+  1) process (middle) with $\psi = .5$ and $\theta = .3$, and AR(2) process 
+  (right) with $\psi = (.5, .3)$ of the standard normal distribution. In each 
+  case, $1000$ replicate tests were performed with sample size $n = 100$ and 
+  $B = 1000$ bootstrap samples.}
+  \label{fig:hist_ma1_arma_ar2_FD}
 \end{figure}
@@
   \centering
-  \includegraphics{hist_gamma_FD}
-  \includegraphics{hist_gev_FD}
-  \caption{Gamma(3,1)}
-  \label{fig:hist_gamma_FD}
+  \includegraphics{hist_gamma_gev_FD}
+  \caption{The Super Naive plots (left) are the histograms of p-values from the 
+  standard KS test with fitted parameters. The Naive Parametric plots (middle) 
+  are the histograms of p-values from implementing parametric bootstrap. The 
+  Copula plots are the histograms of p-values from implementing parametric 
+  bootstrap with copulas for dependence and correcting for fitted parameters. 
+  The data is generated from $Gamma(3, 1)$ (left) and $GEV(0, .2, 1)$ (right) 
+  with a correlation coefficient of $r = 0.5$. In each case, $1000$ replicate 
+  tests were performed with sample size $n = 100$ and $B = 1000$ bootstrap 
+  samples.}
+  \label{fig:hist_gamma__gev_FD}
 \end{figure}
 
-Where this remedy falls short is when the approximation of an AR-1 dependence 
-structure is too inaccurate. An AR-2 model can be used to demonstrate this. For 
-an AR-2 model with $\phi = (0.5, 0.3)$, Figure~\ref{fig:hist_ar2_FD} 
+Where this remedy falls short is when the approximation of an AR(1) dependence 
+structure is too inaccurate. An AR(2) model can be used to demonstrate this. For 
+an AR(2) model with $\phi = (0.5, 0.3)$, Figure~\ref{fig:hist_ar2_FD} 
 displays the results of applying the various remedies. While the remedies 
@@
 
-\begin{figure}[tbp]
-  \centering
-  \includegraphics{hist_ar2_FD}
-  \caption{AR-2}
-  \label{fig:hist_ar2_FD}
-\end{figure}
-
-\section{Conclusion}\label{sec:conclusion}
+\section{Conclusion}
+\label{sec:conclusion}
 
@@
 remedy is not a complete solution. Regardless of the true dependence, we use an 
-AR-1 model. Therefore, if the AR-1 model is a close approximation of the truth, 
+AR(1) model. Therefore, if the AR(1) model is a close approximation of the truth, 
 the fix can work. However, in cases such as AR-2, the approximation too far and 

### 2022-04-29 Code/Simulation.Rmd
code to create combined plots

@@
 
+results$histogram <- factor(results$histogram, levels = c("Naive", "Parametric", "Babu"))
+
 # Generate histograms plot
@@
 ggsave(filename = "hist_fitted.pdf", plot = hist_fitted, path = "../Manuscript", height = 2.1, width = 6)
-
-data_new <- results                              # Replicate data
-data_new$histogram <- factor(data_new$histogram,      # Reordering group factor levels
-                         levels = c("Naive", "Parametric", "Babu"))
-
-# Generate histograms plot
-hist_fitted <- ggplot(data_new) + 
-                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
-                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
-                   theme(legend.position = "none") +
-                   facet_wrap(~histogram, scales = "free_y")
-hist_fitted
 ```
@@
 counter <- 0
-nrep <- 500
-B <- 100
+nrep <- 1000
+B <- 1000
 mean <- 0
@@
 
+results$histogram <- factor(results$histogram, levels = c("Naive", "Copula"))
+
 # Generate histograms plot
@@
 counter <- 0
-nrep <- 100
-B <- 100
+nrep <- 1000
+B <- 1000
 ma <- 0.5
@@
 counter <- 0
-nrep <- 100
-B <- 100
+nrep <- 1000
+B <- 1000
 ar <- 0.5
@@
 # P-vals from standard KS test
-pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(order = c(2, 0, 0), 
-                                                           ar = c(b1, b2)),
+pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ar = ar, 
+                                                           ma = ma), 
                                                       rand.gen=rnorm, 
-                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
-                                                      n = n))$p.value)
+                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
+                                                      n = n),
+                                                mean = mean,
+                                                sd = sd)$p.value)
 
@@
 counter <- 0
-nrep <- 100
-B <- 100
+nrep <- 1000
+B <- 1000
 b1 <- 0.5
@@
 counter <- 0
-nrep <- 100
-B <- 100
+nrep <- 1000
+B <- 1000
 shape <- 3
@@
 counter <- 0
-nrep <- 100
-B <- 100
+nrep <- 1000
+B <- 1000
 loc <- 0
@@
 
-```{r Copula FD}
-test_copula_D <- function(x, dist, B) {
+```{r AR(1) FD}
+test_copula_FD <- function(x, dist, B) {
 
@@
 # P-vals from using bootstrap with copulas
-pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), "pnorm", B = B))
+pvals_copula <- replicate(nrep, test_copula_FD(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), "pnorm", B = B))
 counter <- 0
@@
 results <- data_frame(p_values, histogram)
-save(results, file = "results_copula.RData")
-
-# Generate histograms plot
-hist_ar1_D <- ggplot(results) + 
+
+results$histogram <- factor(results$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))
+
+# Generate histograms plot
+hist_ar1_FD <- ggplot(results) + 
                    geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
@@
                    facet_wrap(~histogram, scales = "free_y")
-hist_ar1_D
+hist_ar1_FD
 
@@
 # Save the histogram figure
-ggsave(filename = "hist_ar1_D", plot = hist_ar1_D, path = "../Manuscript", height = 2.1, width = 6)
+ggsave(filename = "hist_ar1_FD.pdf", plot = hist_ar1_FD, path = "../Manuscript", height = 2.1, width = 6)
 ```
@@
 
-# Generate histograms plot
-hist_ma1_D <- ggplot(results) + 
+results$histogram <- factor(results$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))
+
+# Generate histograms plot
+hist_ma1_FD <- ggplot(results) + 
                    geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
@@
 
-hist_ma1_D
-
-# Save the histogram figure
-ggsave(filename = "hist_ma1_D.pdf", plot = hist_ma1_D, path = "../Manuscript", height = 2.1, width = 6)
+hist_ma1_FD
+
+# Save the histogram figure
+ggsave(filename = "hist_ma1_FD.pdf", plot = hist_ma1_FD, path = "../Manuscript", height = 2.1, width = 6)
 ```
@@
 
-# Generate histograms plot
-hist_arma_D <- ggplot(results) + 
+results$histogram <- factor(results$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))
+
+# Generate histograms plot
+hist_arma_FD <- ggplot(results) + 
                    geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
@@
 
-hist_arma_D
-
-# Save the histogram figure
-ggsave(filename = "hist_arma_D.pdf", plot = hist_arma_D, path = "../Manuscript", height = 2.1, width = 6)
+hist_arma_FD
+
+# Save the histogram figure
+ggsave(filename = "hist_arma_FD.pdf", plot = hist_arma_FD, path = "../Manuscript", height = 2.1, width = 6)
 ```
@@
 
-# Generate histograms plot
-hist_ar2_D <- ggplot(results) + 
+results$histogram <- factor(results$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))
+
+# Generate histograms plot
+hist_ar2_FD <- ggplot(results) + 
                    geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
@@
 
-hist_ar2_D
-
-# Save the histogram figure
-ggsave(filename = "hist_ar2_D.pdf", plot = hist_ar2_D, path = "../Manuscript", height = 2.1, width = 6)
+hist_ar2_FD
+
+# Save the histogram figure
+ggsave(filename = "hist_ar2_FD.pdf", plot = hist_ar2_FD, path = "../Manuscript", height = 2.1, width = 6)
 ```
@@
 
+results$histogram <- factor(results$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))
+
 # Generate histograms plot
@@
 
-    stat.b[i] <- ks.test(x.b, "pgev", shape = shape.b, scale = scale.b)$statistic
+    stat.b[i] <- ks.test(x.b, "pgev", loc.b, shape = shape.b, scale = scale.b)$statistic
   }
@@
 ```
+
+```{r hist_ma1_arma_ar2_D}
+load('results_ma1_D.RData')
+model <- rep("MA(1)", 2000)
+ma1 <- data_frame(results, new_col)
+
+load('results_arma_D.RData')
+model <- rep("ARMA(1, 1)", 2000)
+arma <- data_frame(results, new_col)
+
+load('results_ar2_D.RData')
+model <- rep("AR(2)", 2000)
+ar2 <- data_frame(results, new_col)
+
+data <- rbind(ma1, arma, ar2)
+
+data$model <- factor(data$model, levels = c("MA(1)", "ARMA(1, 1)", "AR(2)"))
+data$histogram <- factor(data$histogram, levels = c("Naive", "Copula"))
+
+# Generate histograms plot
+hist_ma1_arma_ar2_D <- ggplot(data) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(histogram~model, scales = "free_y")
+hist_ma1_arma_ar2_D
+
+ggsave(filename = "hist_ma1_arma_ar2_D.pdf", plot = hist_ma1_arma_ar2_D, path = "../Manuscript", height = 4.2, width = 6)
+```
+
+```{r hist_gamma_gev_D}
+load('results_gamma_D.RData')
+model <- rep("Gamma", 2000)
+gamma <- data_frame(results, model)
+
+load('results_gev_D.RData')
+model <- rep("GEV", 2000)
+gev <- data_frame(results, model)
+
+data <- rbind(gamma, gev)
+
+data$model <- factor(data$model, levels = c("Gamma", "GEV"))
+data$histogram <- factor(data$histogram, levels = c("Naive", "Copula"))
+
+# Generate histograms plot
+hist_gamma_gev_D <- ggplot(data) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(histogram~model, scales = "free_y")
+hist_gamma_gev_D
+
+ggsave(filename = "hist_gamma_gev_D.pdf", plot = hist_gamma_gev_D, path = "../Manuscript", height = 4.2, width = 6)
+```
+
+```{r hist_ma1_arma_ar2_FD}
+load('results_ma1_FD.RData')
+model <- rep("MA(1)", 3000)
+ma1 <- data_frame(results, model)
+
+load('results_arma_FD.RData')
+model <- rep("ARMA(1, 1)", 3000)
+arma <- data_frame(results, model)
+
+load('results_ar2_FD.RData')
+model <- rep("AR(2)", 3000)
+ar2 <- data_frame(results, model)
+
+data <- rbind(ma1, arma, ar2)
+
+data$model <- factor(data$model, levels = c("MA(1)", "ARMA(1, 1)", "AR(2)"))
+data$histogram <- factor(data$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))
+
+# Generate histograms plot
+hist_ma1_arma_ar2_FD <- ggplot(data) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(histogram~model, scales = "free_y")
+hist_ma1_arma_ar2_FD
+
+ggsave(filename = "hist_ma1_arma_ar2_FD.pdf", plot = hist_ma1_arma_ar2_FD, path = "../Manuscript", height = 4.2, width = 6)
+```
+
+```{r hist_gamma_gev_FD}
+load('results_gamma_FD.RData')
+model <- rep("Gamma", 3000)
+gamma <- data_frame(results, model)
+
+load('results_gev_FD.RData')
+model <- rep("GEV", 3000)
+gev <- data_frame(results, model)
+
+data <- rbind(gamma, gev)
+
+data$model <- factor(data$model, levels = c("Gamma", "GEV"))
+data$histogram <- factor(data$histogram, levels = c("Super Naive", "Naive Parametric", "Copula"))
+
+# Generate histograms plot
+hist_gamma_gev_FD <- ggplot(data) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(histogram~model, scales = "free_y", ncol = 2)
+hist_gamma_gev_FD
+
+ggsave(filename = "hist_gamma_gev_FD.pdf", plot = hist_gamma_gev_FD, path = "../Manuscript", height = 4.2, width = 6)
+```

### 2022-04-29 Manuscript/manuscript.tex
other scenarios in dependence section and other edits

@@
 \author{Anthony Zeimbekakis\\
-\href{mailto:anthony.zeimbekakis@uconn.edu}{\nolinkurl{anthony.zeimbekakis@uconn.edu}}\\
+\href{mailto:anthony.zeimbekakis@uconn.edu}
+{\nolinkurl{anthony.zeimbekakis@uconn.edu}}\\
 Department of Statistics, University of Connecticut\\\\
@@
 The Kolmogorov--Smirnov (KS) test is one the most popular goodness-of-fit tests 
-for comparing a sample with a hypothesized parametric distribution. Nevertheless, 
-it has often been misused. The standard one-sample KS test applies to independent, 
-continuous data with a hypothesized distribution that is completely specified. 
-It is not uncommon, however, to see in the literature that it was applied to 
-dependent, discrete, or rounded data, with hypothesized distributions containing 
-estimated parameters. For example, it has been ``discovered" multiple times 
-that the test is too conservative when the parameters are estimated. We 
-demonstrate misuses of the one-sample KS test in three scenarios through 
-simulation studies:
+for comparing a sample with a hypothesized parametric distribution. 
+Nevertheless, it has often been misused. The standard one-sample KS test applies
+to independent, continuous data with a hypothesized distribution that is 
+completely specified. It is not uncommon, however, to see in the literature that
+it was applied to dependent, discrete, or rounded data, with hypothesized 
+distributions containing estimated parameters. For example, it has been 
+``discovered" multiple times that the test is too conservative when the 
+parameters are estimated. We demonstrate misuses of the one-sample KS test in 
+three scenarios through simulation studies:
 1) the hypothesized distribution has unspecified parameters;
@@
 discrete cases and derives its power. \citet{Gleser} provides methods for 
-adapting existing algorithms to provide results when F(x) is discontinuous.
+adapting existing algorithms to provide results when $F(x)$ is discontinuous.
 The discrete KS test is available in various statistical software packages.
@@
 p-values \citep{Arnold}. The \textsf{KSgeneral} package provides a fast and 
-accurate method for when F(x) is arbitrary, discontinuous, or continuous that 
+accurate method for when $F(x)$ is arbitrary, discontinuous, or continuous that 
 uses an alternative fast Fourier transform based method \citep{Dimitrova}.
@@
 distribution contains fitted parameters. In this scenario, the null hypothesis
-is $H_0$: the random sample $X_1, \ldots, X_n$ come from a continuous
+is $H_0$: the random sample $X_1, \ldots, X_n$ comes from a continuous
 distribution $F_{\theta}$ with unspecified parameter $\theta$.
@@
 
-For illustration, \jy{give the details of the setting}
-However, the procedure is sometimes performed where the population cumulative 
-distribution $F(x)$ has parameters $\mu=\bar X$, the sample mean, and $\sigma^2=s^2$, 
-the sample variance \citep{Lilliefors}. This case is demonstrated in Figure~\ref{fig:hist_fitted} 
-under the Naive plot. The naive KS test was performed by estimating the parameters 
-of $F(x)$ using the fitted distribution of the sample data. Since the data is generated 
-from a standard normal distribution with seemingly all assumptions met, a uniform 
-distribution of $U(0,1)$ is expected for the p-values. However this is under the 
-assumption that the KS test holds its power, which it no longer does due to using 
-fitted parameters. Therefore, there is notable deviation from the uniform distribution.
+To demonstrate the consequences of this problem, a simulation is performed. A 
+random sample $X_1, \ldots, X_n$ is generated from the standard normal 
+distribution with sample size $n = 100$. The p-values of $1000$ replicate tests 
+are displayed in the Naive plot of Figure~\ref{fig:hist_fitted}. Each KS test 
+was performed using fitted parameters, i.e. the hypothesized distribution is 
+$N(\bar X, s^2)$ where $\bar X$ is the sample mean and $s^2$ is the sample 
+variance. Since the data is generated from a standard normal distribution with 
+seemingly all assumptions met, a uniform distribution of $U(0, 1)$ is expected 
+for the p-values. However this is under the assumption that the KS test holds 
+its power, which it no longer does due to using fitted parameters. Therefore, 
+there is notable deviation from the uniform distribution.
 
@@
   \item 
-    Draw a random sample $X_1^*,...,X_n^*$ from the fitted distribution $F_{\hat\theta_n}$
+    Draw a random sample $X_1^*,...,X_n^*$ from the fitted distribution 
+    $F_{\hat\theta_n}$
   \item 
@@
   \item
-    Obtain the empirical distribution function $F_n^*$ of $X_1^*, \ldots, X_n^*$.
+    Obtain the empirical distribution function $F_n^*$ of $X_1^*, \ldots, 
+    X_n^*$.
   \item 
@@
 Nonparametric bootstrap can also be used to approximate the null distribution 
-of the testing statistic. The procedure is similar, however there is a 
-correction for bias that is required \citep{Babu}.
+of the testing statistic. The procedure is similar, however the resampling is 
+performed differently and there is a correction for bias that is required 
+\citep{Babu}.
 \begin{enumerate}
@@
 results of from our simulations. We would expect the distribution of p-values 
-to be normal in the case where the KStest holds its power. It is clear from the 
-figure that both bootstrap processes correct for the problem of fitted 
-parameters. The plots for the bootstrapped p-values appear to be $U(0,1)$, 
-unlike the naive p-values.
+to be normal in the case where the KS test holds its power. It is clear from the 
+figure that both parametric and nonparametric bootstrap processes correct for 
+the problem of fitted parameters. The plots for the bootstrapped p-values appear
+to be $U(0,1)$, unlike the naive p-values.
 
@@
 first-order autoregressive model (AR(1)) with a standard normal distribution. 
-The simulationis done with the levels of the AR coefficient $\psi$, varying 
-from $(-3,3)$. The results echo those of \citet{Durilleul} that the KS statistic
-is too liberal for positive autocorrelation values, and that the behavior is 
-asymmetrical for negative values.
+P-values are gathered from $1000$ replicate tests for different levels of the 
+AR coefficient $\psi$, varying from $(-3,3)$. In the presence of serially 
+dependent data, the distribution of p-values no longer follows $U(0, 1)$ as 
+would be expected of a valid test. The results echo those of \citet{Durilleul} 
+that the KS statistic is too liberal for positive autocorrelation values, and 
+that the behavior is asymmetrical for negative values.
 
@@
 
-As mentioned, throughout the procedure we assume an AR(1) structure regardless 
-of the true dependence. If the true dependence is indeed a normal copula with 
-an AR(1) structure, this method is exact. When the true dependence is not AR(1),
-it may still give a reasonable approximation that can be useful for practical 
-purposes. This is demonstrated with different dependence structures in 
-Figure~\ref{fig:hist_ma1_FD}.
+As mentioned, throughout the procedure we assume an AR(1) dependence structure 
+regardless of the true dependence. If the true dependence is indeed a normal 
+copula with an AR(1) structure, this method is exact. When the true dependence 
+is not AR(1), it may still give a reasonable approximation that can be useful 
+for practical purposes. This is demonstrated with different dependence 
+structures in Figure~\ref{fig:hist_ma1_arma_ar2_D}.
 
@@
   \includegraphics{hist_ar1_D}
-  \caption{The Naive plot is the histogram of p-values from the standard KS 
-  test. The Copula plot is the histogram of p-values from implementing 
-  parametric bootstrap with copulas for dependence. In each case, $1000$ 
-  replicate tests were performed with the data generated from an AR(1) process 
-  of the standard normal distribution with $\psi = .5$. The sample size is $n = 
-  100$ and $B = 1000$ bootstrap samples are obtained for each test.}
+  \caption{The Naive plot (left) is the histogram of p-values from the 
+  standard KS test. The Copula plot (right) is the histogram of p-values from 
+  implementing parametric bootstrap with copulas for dependence. In each case, 
+  $1000$ replicate tests were performed with the data generated from an AR(1) 
+  process of the standard normal distribution with $\psi = .5$. The sample size 
+  is $n = 100$ and $B = 1000$ bootstrap samples are obtained for each test.}
   \label{fig:hist_ar1_D}
@@
 Figure~\ref{fig:hist_ar1_D} displays the results of the copula remedy for 
-dependent data. The data is generated from an AR(1) model with $\psi = .5$. The 
-copula used is to model dependence is the normal copula. $1000$ replicate tests 
-were performed with $B = 1000$ bootstrap samples per test.
-\jy{present other scenarios too}
-The naive test is performed by simply using the KS test without correcting for 
-any potential dependence.
+dependent data. The data is generated from the standard normal distribution with
+an AR(1) dependence structure where $\psi = .5$. The copula used is to model 
+dependence is the normal copula. The distribution of p-values is again expected
+to be $U(0, 1)$ for a valid test. The Naive plot is clearly not uniform and 
+reinforces the results shown in Figure~\ref{fig:hist_correlation}. The Copula 
+plot, which implements the aforementioned procedure to correct for dependence
+in the data, appears to be uniform and restores the power of the KS test.
+
+The procedure detailed in this section can also provide a reasonable 
+approximation in cases where the true dependence structure is not far from 
+AR(1). Figure~\ref{fig:hist_ma1_arma_ar2_D} shows the distribution of p-values 
+for dependence structures MA(1), ARMA(1, 1), and AR(2). As expected, 
+naively performing the KS test without correcting for dependence provides plots 
+of p-values that deviate from the uniform distribution. In the case of MA(1) 
+and ARMA(1, 1), the true dependence structure is close enough to our 
+assumption of AR(1) that the bootstrap procedure provides a reasonable 
+approximation. However, the AR(2) copula plot shows the limitation of this 
+technique when the true dependence is too far from our assumption.
 
@@
 \end{figure}
+
+To further demonstrate the effectiveness of the procedure, we perform similar 
+simulations on other families of distributions. 
+Figure~\ref{fig:hist_gamma_gev_D} displays the results of tests using dependent 
+data generated from the gamma and the generalized extreme value distributions.
+The procedure corrects the distribution of p-values for both distributions and 
+is shown to be applicable irregardless of the family of distribution tested.
 
@@
 copula that matches the sample first-order Spearman's rho of the observed data 
-as obtained by the \texttt{iRho} function in the \textsf{copula} package. We 
-propose the following bootstrap procedure to assess the significance of the 
-observed KS statistic.
+as obtained by the \texttt{iRho} function in the \textsf{copula} package 
+\citep{Copula}. We propose the following bootstrap procedure to assess the 
+significance of the observed KS statistic.
 \begin{enumerate}

### 2022-04-29 Code/Simulation.Rmd
minor changes to figures

@@
 
-```{r}
+```{r packages}
 # Load packages
@@
 
-```{r ARMA(1,1) D}
+```{r ARMA(1, 1) D}
 ptm <- proc.time()
@@
 model <- rep("MA(1)", 2000)
-ma1 <- data_frame(results, new_col)
+ma1 <- data_frame(results, model)
 
@@
 model <- rep("ARMA(1, 1)", 2000)
-arma <- data_frame(results, new_col)
+arma <- data_frame(results, model)
 
@@
 model <- rep("AR(2)", 2000)
-ar2 <- data_frame(results, new_col)
+ar2 <- data_frame(results, model)
 

### 2022-04-29 Manuscript/manuscript.tex
updates to fitted+dependence section and conclustion

@@
 Figure~\ref{fig:hist_ar1_FD} shows the results of our simulation on data 
-simulated from an AR(1) process. The ``super naive" method is the resulting 
-p-values when you naively use fitted parameters while ignoring dependence in the
-data. The ``naive parametric" plot is the result of applying parametric 
-bootstrap to correct for fitted parameters while ignoring potential dependence. 
-Of course, the "copula" plot applies the fix for both assumptions. The results 
-show that copula remedy generates uniform p-values and restores the power of the
-KS test.
+simulated from an AR(1) process. As should be expected, naively fitting 
+parameters while providing no adjustment for dependent data invalidates the KS 
+test. As well, only using the parametric bootstrap remedy for fitted parameters 
+from Section~\ref{sec:fitted} seems to provide weaker results than the 
+copula remedy presented above. The results show that copula remedy generates 
+uniform p-values and restores the power of the KS test.
 
@@
 
-The copula fix is not a complete solution, because regardless of the true dependence in the data
-we assume an AR(1) model by taking the lag-1 sample auto-spearman rho. However, we can 
-show that as long as the AR(1) assumption is a close approximation, the correction still restores power to the test.
-Figure~\ref{fig:hist_ma1_FD} is the procedure performed on data generated from 
-an MA(1) model with $\theta = 0.5$. Figure~\ref{fig:hist_arma_FD} displays results with 
-data generated from an ARMA(1,1) model with $\psi = 0.5$ and $\theta = 0.3$.
+Similar to Section~\ref{sec:dependence}, the copula fix is not a complete 
+solution. Regardless of the true dependence in the data we assume an AR(1) 
+dependence structure by taking the lag-1 sample auto-spearman rho. However, we 
+can show that as long as the AR(1) assumption is a close approximation, the 
+correction still provides a reasonable approximation that can be useful for 
+practical purposes. Figure~\ref{fig:hist_ma1_arma_ar2_FD} shows the results of the 
+procedure performed on data generated with dependence structures of  MA(1), 
+ARMA(1, 1), and AR(2). Naively fitting parameters and not adjusting for 
+dependence clearly deviates from a uniform distribution of p-values. Parametric 
+bootstrap provides some correction but does not account for depedence, so 
+therefore the results of the copula remedy are more accurate and favorable.
+In the case of MA(1) and ARMA(1, 1), the true dependence appears close enough 
+to our assumption of AR(1) that the results are reasonable. AR(2) however
+appears to be just far enough from our assumption, showing a limitation of the 
+procedure.
 
@@
 
-It is also possible to apply our procedure to other distributions. All of the simulations
-to this point have been done with standard normal data. The data in Figure~\ref{fig:hist_gamma_FD} 
-is generated from $Gamma ~ (3,1)$ with a correlation coefficient of $\rho = 0.5$. Figure~\ref{fig:hist_gev_FD}
-shows the procedure applied to data from $GEV ~ (0, 0.2, 1)$ with a correlation coefficient of $\rho = 0.5$.
+It is also possible to apply our procedure to other families of distributions. 
+The data in Figure~\ref{fig:hist_gamma_gev_FD} is generated from the gamma and 
+generalized extreme value distributions. The results are favorable and show that 
+the procedure outlined as a fix for fitted parameters and spatially dependent 
+can be adapted for various families of distributions.
 
@@
 
-Where this remedy falls short is when the approximation of an AR(1) dependence 
-structure is too inaccurate. An AR(2) model can be used to demonstrate this. For 
-an AR(2) model with $\phi = (0.5, 0.3)$, Figure~\ref{fig:hist_ar2_FD} 
-displays the results of applying the various remedies. While the remedies 
-improve the plot of the p-values in comparison to the naive case, because the 
-approximation is not close enough the correction does not work completely.
-
 \section{Conclusion}
@@
 are violated, that is the case where the data has dependence and parameters must 
-be fitted, the copula remedy also shows positive results. The tests were 
-performed on simulated data from a standard normal distribution, though also 
-appear effective against other distributions such as gamma and gev. The copula 
-remedy is not a complete solution. Regardless of the true dependence, we use an 
-AR(1) model. Therefore, if the AR(1) model is a close approximation of the truth, 
-the fix can work. However, in cases such as AR-2, the approximation too far and 
-the fix does not completely restore power.
+be fitted, an adjusted copula procedure also shows positive results. The tests 
+appear effective for a variety of families of distributions. The copula remedy 
+is not a complete solution and has limitations. Regardless of the true 
+dependence, we assume an AR(1) depedennce structure. Therefore, if the AR(1) 
+dependence structure is a close approximation of the truth, the fix can work. 
+However, in cases such as AR(2), if the approximation is too far from the true 
+depedence structure the fix does not completely restore power As well, tests 
+were only performed with the normal copula. It is possible that other copulas
+could provide stronger results based on the true dependence of the data.
 

### 2022-04-29 Manuscript/manuscript.tex
comments and edits

@@
 
+% control floats
+\renewcommand\floatpagefraction{.9}
+\renewcommand\topfraction{.9}
+\renewcommand\bottomfraction{.9}
+\renewcommand\textfraction{.1}
+\setcounter{totalnumber}{50}
+\setcounter{topnumber}{50}
+\setcounter{bottomnumber}{50}
+
 \newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
 
-\title{On Misuses of the Kolmogorov--Smirnov Test for One Sample Goodness-of-Fit}
+\title{On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit}
 
@@
 \begin{abstract}
-The Kolmogorov--Smirnov (KS) test is one the most popular goodness-of-fit tests 
+The Kolmogorov--Smirnov (KS) test is one of the most popular goodness-of-fit tests 
 for comparing a sample with a hypothesized parametric distribution. 
@@
 
-The Kolmogorov-Smirnov (KS) statistic is one of the most popular goodness-of-fit 
+The Kolmogorov-Smirnov (KS) test is one of the most popular goodness-of-fit 
 tests for comparing a sample with a hypothesized parametric distribution.
@@
 \citep{R, Marsaglia}.
-
 The standard one-sample KS test applies to independent data with a continuous
-hypothesized distribution that is completely specified. Often in literature, it 
-has been ``discovered" that the test loses its power when applied to dependent 
-or discrete data with hypothesized distributions containing estimated parameters 
-\citep{Steinskog}.
+hypothesized distribution that is completely specified. In practice, however, it
+has often been applied without realizing that one or more of these assumptions
+do not hold.
 
@@
 The standard KS test is not applicable when the hypothesized distribution 
-contains fitted parameters. \citet{Steinskog} "discovers" the change in power 
+contains fitted parameters. \citet{Steinskog} ``discovers'' the change in power 
 when using estimated parameters and stress caution in using the KS test in such 
@@
 mean and standard deviation are estimated obtains extremely conservative 
-results. This is supported by \citet{Capasso}, which concludes that failing to 
+results. This is supported by \citet{Capasso}, who concludes that failing to 
 re-estimate the parameters may lead to wrong, overly-conservative approximations 
@@
 possible mistake may turn out to be dramatic and does not vanish as the sample 
-size increases. Remedies are provided by \citet{Genest} and \citet{Babu} in the 
-form of bootstrap. \citet{Genest} provides validity for using parametric 
-bootstrap with various goodness-of-fit tests. \citet{Babu} details the bootstrap
+size increases. Remedies are provided by \citet{Babu} and \citet{Genest} in the
+form of bootstrap.  \citet{Babu} details the bootstrap
 procedure for goodness-of-fit tests and notes that both parametric and 
@@
 is a correction required for the non-parametric case.
+\citet{Genest} provides validity for using parametric 
+bootstrap with various goodness-of-fit tests.
 
@@
 
-\section{Fitted Parameters}
+\section{Unspecified Parameters}
 \label{sec:fitted}
@@
 is $H_0$: the random sample $X_1, \ldots, X_n$ comes from a continuous
-distribution $F_{\theta}$ with unspecified parameter $\theta$.
+distribution $F_{\theta}$ with unspecified parameter vector $\theta$.
 Let $\hat\theta_n$ be an estimator of $\theta$, which could be, for example,
@@
 $F_\theta$, the null distribution of $D$ obtained in existing implementations in
-software packages which assumes completely known $F_\theta$ no long applies
+software packages which assumes completely known $F_\theta$ no longer applies
 \citep{Steinskog}.
@@
 seemingly all assumptions met, a uniform distribution of $U(0, 1)$ is expected 
-for the p-values. However this is under the assumption that the KS test holds 
-its power, which it no longer does due to using fitted parameters. Therefore, 
+for the p-values. However this is under the assumption that the KS test
+assumptions hold, which no longer do due to using fitted parameters. Therefore, 
 there is notable deviation from the uniform distribution.
@@
 of the testing statistic. The procedure is similar, however the resampling is 
-performed differently and there is a correction for bias that is required 
+performed with the empirical distribution instead of the fitted parametric
+distribution and there is a correction for bias that is required
 \citep{Babu}.
@@
 results of from our simulations. We would expect the distribution of p-values 
-to be normal in the case where the KS test holds its power. It is clear from the 
+to be normal in the case where the KS test holds its size. It is clear from the 
 figure that both parametric and nonparametric bootstrap processes correct for 
@@
 
-The KS test also displays issues in the case of dependence. As mentioned, an 
+The KS test also displays issues in the case of dependent data. As mentioned, an 
 assumption of the test is that the data is independent. Unfortunately, real data
@@
 with an AR(1) structure to characterize the serial dependence of the 
-observations. The AR(1) parameter of the normal copula is set to match the be 
+observations. The AR(1) parameter $r$ of the normal copula is set to match the be 
 the sample serial Spearman's rho of the observed sample. The procedure is as 
@@
 \item
-  Form a bootstrap sample $X_i^* = F^{-1} [\Phi(Z_i)]$,
+  Form a bootstrap sample $X_i^* = F^{-1} [\Phi(Z_i)]$, where $\Phi$ is the
+  distribution function of $N(0, 1)$, 
   $i = 1, \ldots, n$, whose first-order sample Spearman's rho matches that of
@@
 
-As mentioned, throughout the procedure we assume an AR(1) dependence structure 
+Throughout the simulation we assume a working AR(1) dependence structure 
 regardless of the true dependence. If the true dependence is indeed a normal 
@@
 plot, which implements the aforementioned procedure to correct for dependence
-in the data, appears to be uniform and restores the power of the KS test.
-
-The procedure detailed in this section can also provide a reasonable 
-approximation in cases where the true dependence structure is not far from 
-AR(1). Figure~\ref{fig:hist_ma1_arma_ar2_D} shows the distribution of p-values 
-for dependence structures MA(1), ARMA(1, 1), and AR(2). As expected, 
-naively performing the KS test without correcting for dependence provides plots 
-of p-values that deviate from the uniform distribution. In the case of MA(1) 
-and ARMA(1, 1), the true dependence structure is close enough to our 
-assumption of AR(1) that the bootstrap procedure provides a reasonable 
-approximation. However, the AR(2) copula plot shows the limitation of this 
-technique when the true dependence is too far from our assumption.
+in the data, appears to be uniform and restores the size of the KS test.
+\jy{we didn't study the power here (probability to reject the null when the null
+  is false). Can do it for the paper.}
 
@@
 
-To further demonstrate the effectiveness of the procedure, we perform similar 
-simulations on other families of distributions. 
-Figure~\ref{fig:hist_gamma_gev_D} displays the results of tests using dependent 
-data generated from the gamma and the generalized extreme value distributions.
-The procedure corrects the distribution of p-values for both distributions and 
-is shown to be applicable irregardless of the family of distribution tested.
+The procedure detailed in this section can also provide a reasonable 
+approximation in cases where the true dependence structure is not far from 
+AR(1). Figure~\ref{fig:hist_ma1_arma_ar2_D} shows the distribution of p-values 
+for dependence structures MA(1), ARMA(1, 1), and AR(2). As expected, 
+naively performing the KS test without correcting for dependence provides plots 
+of p-values that deviate from the uniform distribution. In the case of MA(1) 
+and ARMA(1, 1), the true dependence structure is close enough to our 
+assumption of AR(1) that the bootstrap procedure provides a reasonable 
+approximation. However, the AR(2) copula plot shows the limitation of this 
+technique as no AR(1) process can approximate an AR(2) process unless the
+second-order coefficient is close to zero.
+
+\jy{I like the facet grid version better}
 
@@
 
-\section{Fitted Parameters and Serially Dependent Data}
+To further demonstrate the effectiveness of the procedure, we perform similar 
+simulations on other families of distributions. 
+Figure~\ref{fig:hist_gamma_gev_D} displays the results of tests using dependent 
+data generated from the gamma and the generalized extreme value distributions.
+The procedure corrects the distribution of p-values for both distributions and 
+is shown to be applicable irregardless of the family of distribution tested.
+
+\section{Unspecified Parameters and Serially Dependent Data}
 \label{sec:fittedwithdependence}
@@
 must be violated. The null hypothesis is equivalent to Section~\ref{sec:fitted} 
-and the test statistic is equal to Equation~\ref{eq:ks_fitted}.
-
-Let $\hat\theta_n$ be the fitted parameter value of $F_{\theta}$. The observed
-KS statistic is calculated as in Equation~\eqref{eq:ks_fitted}. The bootstrap
+and the test statistic is equal to Equation~\eqref{eq:ks_fitted}. The bootstrap
 procedure in Section~\ref{sec:fitted} is no longer valid because the serial
@@
 significance of the observed KS statistic.
+
 \begin{enumerate}
@@
 
-Figure~\ref{fig:hist_ar1_FD} shows the results of our simulation on data 
-simulated from an AR(1) process. As should be expected, naively fitting 
-parameters while providing no adjustment for dependent data invalidates the KS 
-test. As well, only using the parametric bootstrap remedy for fitted parameters 
-from Section~\ref{sec:fitted} seems to provide weaker results than the 
-copula remedy presented above. The results show that copula remedy generates 
-uniform p-values and restores the power of the KS test.
-
 \begin{figure}[tbp]
@@
 
-Similar to Section~\ref{sec:dependence}, the copula fix is not a complete 
-solution. Regardless of the true dependence in the data we assume an AR(1) 
-dependence structure by taking the lag-1 sample auto-spearman rho. However, we 
-can show that as long as the AR(1) assumption is a close approximation, the 
-correction still provides a reasonable approximation that can be useful for 
-practical purposes. Figure~\ref{fig:hist_ma1_arma_ar2_FD} shows the results of the 
-procedure performed on data generated with dependence structures of  MA(1), 
-ARMA(1, 1), and AR(2). Naively fitting parameters and not adjusting for 
-dependence clearly deviates from a uniform distribution of p-values. Parametric 
-bootstrap provides some correction but does not account for depedence, so 
-therefore the results of the copula remedy are more accurate and favorable.
-In the case of MA(1) and ARMA(1, 1), the true dependence appears close enough 
-to our assumption of AR(1) that the results are reasonable. AR(2) however
-appears to be just far enough from our assumption, showing a limitation of the 
-procedure.
+Figure~\ref{fig:hist_ar1_FD} shows the results of our simulation on data 
+simulated from an AR(1) process. As should be expected, naively fitting 
+parameters while providing no adjustment for dependent data invalidates the KS 
+test. As well, only using the parametric bootstrap remedy for fitted parameters 
+from Section~\ref{sec:fitted} seems to provide weaker results than the 
+copula remedy presented above. The results show that copula remedy generates 
+uniform p-values and restores the size of the KS test.
 
@@
 
-It is also possible to apply our procedure to other families of distributions. 
-The data in Figure~\ref{fig:hist_gamma_gev_FD} is generated from the gamma and 
-generalized extreme value distributions. The results are favorable and show that 
-the procedure outlined as a fix for fitted parameters and spatially dependent 
-can be adapted for various families of distributions.
+Similar to Section~\ref{sec:dependence}, the copula fix is not a complete 
+solution. Regardless of the true dependence in the data we assume an AR(1) 
+dependence structure by taking the lag-1 sample auto-spearman rho. However, we 
+can show that as long as the AR(1) assumption is a close approximation, the 
+correction still provides a reasonable approximation that can be useful for 
+practical purposes. Figure~\ref{fig:hist_ma1_arma_ar2_FD} shows the results of the 
+procedure performed on data generated with dependence structures of  MA(1), 
+ARMA(1, 1), and AR(2). Naively fitting parameters and not adjusting for 
+dependence clearly deviates from a uniform distribution of p-values. Parametric 
+bootstrap provides some correction but does not account for dependence, so 
+therefore the results of the copula remedy are more accurate and favorable.
+In the case of MA(1) and ARMA(1, 1), the true dependence appears close enough 
+to our assumption of AR(1) that the results are reasonable. AR(2) however
+appears to be just far enough from our assumption, showing a limitation of the 
+procedure.
 
@@
   samples.}
-  \label{fig:hist_gamma__gev_FD}
+  \label{fig:hist_gamma_gev_FD}
 \end{figure}
+
+It is also possible to apply our procedure to other families of distributions. 
+The data in Figure~\ref{fig:hist_gamma_gev_FD} is generated from the gamma and 
+generalized extreme value distributions. The results are favorable and show that 
+the procedure outlined as a fix for fitted parameters and spatially dependent 
+can be adapted for various families of distributions.
 
@@
 case of fitted parameters, parametric and non-parametric bootstrap can restore 
-the power of the test. A bias correction is required if the non-parametric form 
+the size of the test. A bias correction is required if the non-parametric form 
 is used \citep{Babu}. In the case of dependent data, a procedure using bootstrap 
@@
 is not a complete solution and has limitations. Regardless of the true 
-dependence, we assume an AR(1) depedennce structure. Therefore, if the AR(1) 
+dependence, we assume an AR(1) dependence structure. Therefore, if the AR(1) 
 dependence structure is a close approximation of the truth, the fix can work. 
 However, in cases such as AR(2), if the approximation is too far from the true 
-depedence structure the fix does not completely restore power As well, tests 
+dependence structure the fix does not completely solve the issue. As well, tests 
 were only performed with the normal copula. It is possible that other copulas

### 2022-04-29 Manuscript/manuscript.tex
textwidth graphs
facet_grid plot, final typos check

--- 2022-04-29 Manuscript/manuscript.tex
@@
 \end{equation}
-The distribution of $D$ under $H_0$ turned out to be independent of the
+The distribution of $D$ under $H_0$ turns out to be independent of the
 distribution $F$ and a table of critical values for $D$ has been constructed
 \citep{Massey} for various sample sizes $n$ and significance 
-levels $\alpha$. If the value of $d$ exceeds the test's corresponding critical 
-value, the null hypothesis is rejected. The KS test is available in popular 
+levels $\alpha$. If the value of $D$ exceeds the test's corresponding critical 
+value the null hypothesis is rejected. The KS test is available in popular 
 statistical software packages, such as function \texttt{ks.test} in R 
@@
 hypothesized distribution that is completely specified. Often in literature, it 
-has been ``discovered" that the test loses its power when applied to dependent 
+has been ``discovered" that the test loses its size when applied to dependent 
 or discrete data with hypothesized distributions containing estimated parameters 
@@
 The standard KS test is not applicable when the hypothesized distribution 
-contains fitted parameters. \citet{Steinskog} "discovers" the change in power 
+contains fitted parameters. \citet{Steinskog} ``discovers" the change in power 
 when using estimated parameters and stress caution in using the KS test in such 
-ways. \citet{Lilliefors} shows that using the standard table when values of the 
-mean and standard deviation are estimated obtains extremely conservative 
-results. This is supported by \citet{Capasso}, which concludes that failing to 
-re-estimate the parameters may lead to wrong, overly-conservative approximations 
-to the distributions of goodness-of-fit test statistics based on the empirical 
-distribution function. \citet{Capasso} also notes that the impact of this 
-possible mistake may turn out to be dramatic and does not vanish as the sample 
-size increases. Remedies are provided by \citet{Genest} and \citet{Babu} in the 
-form of bootstrap. \citet{Genest} provides validity for using parametric 
-bootstrap with various goodness-of-fit tests. \citet{Babu} details the bootstrap
-procedure for goodness-of-fit tests and notes that both parametric and 
-non-parametric procedures lead to correct asymptotic levels, however there 
-is a correction required for the non-parametric case.
+ways. \citet{Lilliefors} shows for the normal distribution that using the 
+standard table when values of the mean and standard deviation are estimated 
+obtains extremely conservative results. This is supported by \citet{Capasso}, 
+which concludes that failing to re-estimate the parameters may lead to wrong, 
+overly-conservative approximations to the distributions of goodness-of-fit test 
+statistics based on the empirical distribution function. \citet{Capasso} also 
+notes that the impact of this mistake may turn out to be dramatic and does not 
+vanish as the sample size increases. Remedies are provided by \citet{Genest} and
+\citet{Babu} in the form of bootstrap. \citet{Genest} provides validity for 
+using parametric bootstrap with various goodness-of-fit tests. \citet{Babu} 
+details the bootstrap procedure for goodness-of-fit tests and notes that both 
+parametric and non-parametric procedures lead to correct asymptotic levels, 
+however there is a correction required for the non-parametric case.
 
@@
 issue. Section~\ref{sec:dependence} investigates the scenario where the data of 
-the empirical distribution is serially dependent. Our bootstrap procedure 
+the empirical distribution is serially dependent. A bootstrap procedure 
 employing copulas is a working solution. Section~\ref{sec:fittedwithdependence}
 explores the case where a combination of the first two scenarios occurs. The 
-copula procedure is available as a fix here as well. 
+copula procedure can be adjusted for fitted parameters to be available as a fix. 
 Section~\ref{sec:conclusion} concludes with a discussion.
@@
 for the p-values. However this is under the assumption that the KS test holds 
-its power, which it no longer does due to using fitted parameters. Therefore, 
+its size, which it no longer does due to using fitted parameters. Therefore, 
 there is notable deviation from the uniform distribution.
@@
 results of from our simulations. We would expect the distribution of p-values 
-to be normal in the case where the KS test holds its power. It is clear from the 
+to be uniform in the case where the KS test holds its size. It is clear from the 
 figure that both parametric and nonparametric bootstrap processes correct for 
@@
   of p-values from implementing parametric bootstrap. The Babu plot (right) is 
-  the histogram of p-values from implementing the nonparametric bootstrap with a 
+  the histogram of p-values from implementing nonparametric bootstrap with a 
   correction for bias. In each case, $1000$ replicate tests were performed on 
@@
 completely specified parameters. The test statistic is the same as 
-Equation~\ref{eq:ks_standard}. However, since the data is dependent, the null 
+Equation~\eqref{eq:ks_standard}. However, since the data is dependent, the null 
 hypothesis is wrong and must be corrected. This is demonstrated with a 
@@
 plot, which implements the aforementioned procedure to correct for dependence
-in the data, appears to be uniform and restores the power of the KS test.
+in the data, appears to be uniform and restores the size of the KS test.
 
@@
 must be violated. The null hypothesis is equivalent to Section~\ref{sec:fitted} 
-and the test statistic is equal to Equation~\ref{eq:ks_fitted}.
+and the test statistic is equal to Equation~\eqref{eq:ks_fitted}.
 
@@
 copula remedy presented above. The results show that copula remedy generates 
-uniform p-values and restores the power of the KS test.
+uniform p-values and restores the size of the KS test.
 
@@
 solution. Regardless of the true dependence in the data we assume an AR(1) 
-dependence structure by taking the lag-1 sample auto-spearman rho. However, we 
-can show that as long as the AR(1) assumption is a close approximation, the 
-correction still provides a reasonable approximation that can be useful for 
-practical purposes. Figure~\ref{fig:hist_ma1_arma_ar2_FD} shows the results of the 
-procedure performed on data generated with dependence structures of  MA(1), 
+dependence structure by taking the sample first-order Spearman's rho. However, 
+we can show that as long as the AR(1) assumption is a close approximation, the 
+correction still provides a reasonable results that can be useful for 
+practical purposes. Figure~\ref{fig:hist_ma1_arma_ar2_FD} shows the results of 
+the procedure performed on data generated with dependence structures MA(1), 
 ARMA(1, 1), and AR(2). Naively fitting parameters and not adjusting for 
@@
   \includegraphics{hist_ma1_arma_ar2_FD}
-  \caption{The Super Naive plots (left) are the histograms of p-values from the 
+  \caption{The Super Naive plots (top) are the histograms of p-values from the 
   standard KS test with fitted parameters. The Naive Parametric plots (middle) 
   are the histograms of p-values from implementing parametric bootstrap. The 
-  Copula plots are the histograms of p-values from implementing parametric 
-  bootstrap with copulas for dependence and correcting for fitted parameters. 
-  The data is generated from an MA(1) process (left) with $\theta = .5$, ARMA(1,
-  1) process (middle) with $\psi = .5$ and $\theta = .3$, and AR(2) process 
-  (right) with $\psi = (.5, .3)$ of the standard normal distribution. In each 
-  case, $1000$ replicate tests were performed with sample size $n = 100$ and 
-  $B = 1000$ bootstrap samples.}
+  Copula plots (bottom) are the histograms of p-values from implementing 
+  parametric bootstrap with copulas for dependence and correcting for fitted 
+  parameters. The data is generated from an MA(1) process (left) with 
+  $\theta = .5$, ARMA(1, 1) process (middle) with $\psi = .5$ and $\theta = .3$,
+  and AR(2) process (right) with $\psi = (.5, .3)$ of the standard normal 
+  distribution. In each case, $1000$ replicate tests were performed with sample 
+  size $n = 100$ and $B = 1000$ bootstrap samples.}
   \label{fig:hist_ma1_arma_ar2_FD}
@@
   samples.}
-  \label{fig:hist_gamma__gev_FD}
+  \label{fig:hist_gamma_gev_FD}
 \end{figure}
@@
 is not a complete solution and has limitations. Regardless of the true 
-dependence, we assume an AR(1) depedennce structure. Therefore, if the AR(1) 
+dependence, we assume an AR(1) depedence structure. Therefore, if the AR(1) 
 dependence structure is a close approximation of the truth, the fix can work. 
 However, in cases such as AR(2), if the approximation is too far from the true 
-depedence structure the fix does not completely restore power As well, tests 
+depedence structure the fix does not completely restore size As well, tests 
 were only performed with the normal copula. It is possible that other copulas

### 2022-04-29 Manuscript/manuscript.tex

--- 2022-04-29 Manuscript/manuscript.tex
@@
 distributions containing estimated parameters. For example, it has been 
-``discovered" multiple times that the test is too conservative when the 
+``discovered'' multiple times that the test is too conservative when the 
 parameters are estimated. We demonstrate misuses of the one-sample KS test in 
@@
 \end{equation}
-The distribution of $D$ under $H_0$ turned out to be independent of the
+The distribution of $D$ under $H_0$ turns out to be independent of the
 distribution $F$ and a table of critical values for $D$ has been constructed
 \citep{Massey} for various sample sizes $n$ and significance 
-levels $\alpha$. If the value of $d$ exceeds the test's corresponding critical 
-value, the null hypothesis is rejected. The KS test is available in popular 
+levels $\alpha$. If the value of $D$ exceeds the test's corresponding critical 
+value the null hypothesis is rejected. The KS test is available in popular 
 statistical software packages, such as function \texttt{ks.test} in R 
 \citep{R, Marsaglia}.
+
 The standard one-sample KS test applies to independent data with a continuous
@@
 contains fitted parameters. \citet{Steinskog} ``discovers'' the change in power 
-when using estimated parameters and stress caution in using the KS test in such 
-ways. \citet{Lilliefors} shows that using the standard table when values of the 
-mean and standard deviation are estimated obtains extremely conservative 
-results. This is supported by \citet{Capasso}, who concludes that failing to 
-re-estimate the parameters may lead to wrong, overly-conservative approximations 
-to the distributions of goodness-of-fit test statistics based on the empirical 
-distribution function. \citet{Capasso} also notes that the impact of this 
-possible mistake may turn out to be dramatic and does not vanish as the sample 
-size increases. Remedies are provided by \citet{Babu} and \citet{Genest} in the
-form of bootstrap.  \citet{Babu} details the bootstrap
+when using estimated parameters and stresses caution in using the KS test in 
+such ways. \citet{Lilliefors} shows for the normal distribution that using the 
+standard table when values of the mean and standard deviation are estimated 
+obtains extremely conservative results. This is supported by \citet{Capasso}, 
+who concludes that failing to re-estimate the parameters may lead to wrong, 
+overly-conservative approximations to the distributions of goodness-of-fit test 
+statistics based on the empirical distribution function. \citet{Capasso} also 
+notes that the impact of this mistake may turn out to be dramatic and does not 
+vanish as the sample size increases. Remedies are provided by \citet{Babu} and 
+\citet{Genest} in the form of bootstrap. \citet{Babu} details the bootstrap
 procedure for goodness-of-fit tests and notes that both parametric and 
-non-parametric procedures lead to correct asymptotic levels, however there 
-is a correction required for the non-parametric case.
-\citet{Genest} provides validity for using parametric 
-bootstrap with various goodness-of-fit tests.
+non-parametric procedures lead to correct asymptotic levels, however there is a 
+correction required for the non-parametric case. \citet{Genest} provides 
+validity for using parametric bootstrap with various goodness-of-fit tests.
 
@@
 results of from our simulations. We would expect the distribution of p-values 
-to be normal in the case where the KS test holds its size. It is clear from the 
+to be uniform in the case where the KS test holds its size. It is clear from the 
 figure that both parametric and nonparametric bootstrap processes correct for 
@@
   \centering
-  \includegraphics{hist_correlation}
+  \includegraphics[width=\textwidth]{hist_correlation}
   \caption{Each histogram is a plot of the p-values of standard KS tests
@@
 with an AR(1) structure to characterize the serial dependence of the 
-observations. The AR(1) parameter $r$ of the normal copula is set to match the be 
-the sample serial Spearman's rho of the observed sample. The procedure is as 
+observations. The AR(1) parameter $r$ of the normal copula is set to match the 
+be the sample serial Spearman's rho of the observed sample. The procedure is as 
 follows.
@@
   Form a bootstrap sample $X_i^* = F^{-1} [\Phi(Z_i)]$, where $\Phi$ is the
-  distribution function of $N(0, 1)$, 
-  $i = 1, \ldots, n$, whose first-order sample Spearman's rho matches that of
-  the observed data.
+  distribution function of $N(0, 1)$, $i = 1, \ldots, n$, whose first-order 
+  sample Spearman's rho matches that of the observed data.
 \item
@@
   \centering
-  \includegraphics{hist_ar1_D}
+  \includegraphics[width=\textwidth]{hist_ar1_D}
   \caption{The Naive plot (left) is the histogram of p-values from the 
@@
 in the data, appears to be uniform and restores the size of the KS test.
-\jy{we didn't study the power here (probability to reject the null when the null
-  is false). Can do it for the paper.}
 
@@
   \centering
-  \includegraphics{hist_ma1_arma_ar2_D}
+  \includegraphics[width=\textwidth]{hist_ma1_arma_ar2_D}
   \caption{The Naive plots are the histograms of p-values from the standard KS 
@@
 
-\jy{I like the facet grid version better}
-
 \begin{figure}[tbp]
   \centering
-  \includegraphics{hist_gamma_gev_D}
+  \includegraphics[width=\textwidth]{hist_gamma_gev_D}
   \caption{The Naive plots are the histograms of p-values from the standard KS 
@@
   \centering
-  \includegraphics{hist_ar1_FD}
+  \includegraphics[width=\textwidth]{hist_ar1_FD}
   \caption{The Super Naive plot (left) is the histogram of p-values from the 
@@
   \centering
-  \includegraphics{hist_ma1_arma_ar2_FD}
+  \includegraphics[width=\textwidth]{hist_ma1_arma_ar2_FD}
   \caption{The Super Naive plots (left) are the histograms of p-values from the 
@@
   are the histograms of p-values from implementing parametric bootstrap. The 
-  Copula plots are the histograms of p-values from implementing parametric 
-  bootstrap with copulas for dependence and correcting for fitted parameters. 
-  The data is generated from an MA(1) process (left) with $\theta = .5$, ARMA(1,
-  1) process (middle) with $\psi = .5$ and $\theta = .3$, and AR(2) process 
-  (right) with $\psi = (.5, .3)$ of the standard normal distribution. In each 
-  case, $1000$ replicate tests were performed with sample size $n = 100$ and 
-  $B = 1000$ bootstrap samples.}
+  Copula plots (bottom) are the histograms of p-values from implementing 
+  parametric bootstrap with copulas for dependence and correcting for fitted 
+  parameters. The data is generated from an MA(1) process (left) with 
+  $\theta = .5$, ARMA(1, 1) process (middle) with $\psi = .5$ and $\theta = .3$,
+  and AR(2) process (right) with $\psi = (.5, .3)$ of the standard normal 
+  distribution. In each case, $1000$ replicate tests were performed with sample 
+  size $n = 100$ and $B = 1000$ bootstrap samples.}
   \label{fig:hist_ma1_arma_ar2_FD}
@@
   \centering
-  \includegraphics{hist_gamma_gev_FD}
+  \includegraphics[width=\textwidth]{hist_gamma_gev_FD}
   \caption{The Super Naive plots (left) are the histograms of p-values from the 

### 2022-04-29 Code/Simulation.Rmd
facet_grid for section 4

@@
                    theme(legend.position = "none") +
-                   facet_wrap(histogram~model, scales = "free_y")
+                   facet_grid(histogram~model, scales = "free_y")
 hist_ma1_arma_ar2_FD

### 2022-06-02 Code/Simulation.Rmd
sketch for arma(1,1) working copula

@@
 ```
+
+```{r ARMA(1,1) D}
+test_copula_D <- function(x, pdist, qdist, B, ...) {
+
+    ## Get observed statistic
+    n <- length(x) 
+    stat  <- ks.test(x, dist, mean = mean, sd = sd)$statistic
+
+    ## transform the data to standard normal scale and fit arma(1,1)
+    zx <- qnorm(rank(x) / (n + 1))
+    fit <- tseries::arma(zx, include.intercept = FALSE)
+
+    ## Perform parametric bootstrap to get an empirical distribution of stat
+    stat.b <- double(n)
+
+    for (i in 1:B) {
+        ## 1. The marginal distribution is the fitted dist
+        ## 2. There is arma(1,1) dependence on the normal scale
+        zx.b <- arima.sim(n, ...) # simulate from fit
+        u <- pnorm(zx.b)
+        # Transform bootstrap sample and fit the parameters
+        x.b <- qdist(u, ...) # mean = mean, sd = sd)
+
+        # Gather bootstrap sample's test statistic
+        stat.b[i] <- ks.test(x.b, pdist, mean = mean, sd = sd)$statistic # fix
+    }
+
+    # Return empirical p-value
+    p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
+
+    counter <<- counter + 1
+    cat(counter, "")
+
+    return(p.value)
+}
+```

### 2022-06-02 Code/Simulation.Rmd
added code for alternative method using arma(1,1) structure

--- 2022-04-29 Code/Simulation.Rmd
@@
 library(ismev)
+library(tseries)
 source('tspb.R')
@@
 
-```{r ARMA(1, 1) D}
+```{r ARMA(1,1) D}
 ptm <- proc.time()
@@
 ```
+
+```{r AR(1) D2}
+test_copula_D2 <- function(x, pdist, qdist, ..., B) {
+
+    ## Get observed statistic
+    n <- length(x) 
+    stat  <- ks.test(x, pdist, ...)$statistic
+
+    ## transform the data to standard normal scale and fit arma(1,1)
+    zx <- qnorm(rank(x) / (n + 1))
+    fit <- tseries::arma(zx, include.intercept = FALSE)
+
+    ar <- fit$coef[1]
+    ma <- fit$coef[2]
+
+    ## Perform parametric bootstrap to get an empirical distribution of stat
+    stat.b <- double(n)
+
+    for (i in 1:B) {
+        ## 1. The marginal distribution is the fitted dist
+        ## 2. There is arma(1,1) dependence on the normal scale
+        zx.b <- arima.sim(list(ar = ar, ma = ma), 
+                          rand.gen=rnorm, 
+                          sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
+                          n = n) # simulate from fit
+        u <- pnorm(zx.b)
+        # Transform bootstrap sample and fit the parameters
+        x.b <- qdist(u, ...)
+
+        # Gather bootstrap sample's test statistic
+        stat.b[i] <- ks.test(x.b, pdist, ...)$statistic
+    }
+
+    # Return empirical p-value
+    p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
+
+    counter <<- counter + 1
+    cat(counter, "")
+
+    return(p.value)
+}
+
+test_standard_ks <- function(x, pdist, ...) {
+  p.value <- ks.test(x, pdist, ...)$p.value
+  list(p.value = p.value)
+}
+
+# Set variables
+n <- 100
+ar <- 0.5
+ma <- 0.5
+counter <- 0
+nrep <- 1000
+B <- 1000
+mean <- 0
+sd <- 1
+
+# P-vals from using bootstrap with copulas
+pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), 
+                                              pnorm, 
+                                              qnorm,
+                                              mean = mean, 
+                                              sd = sd,
+                                              B = B))
+counter <- 0
+
+# P-vals from standard KS test
+pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), 
+                                                pnorm,
+                                                mean = mean, 
+                                                sd = sd)$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
+p_values <- c(pvals_copula, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+results$histogram <- factor(results$histogram, levels = c("Naive", "Copula"))
+
+save(results, file = "results_ar1_D2.RData")
+
+# Generate histograms plot
+hist_ar1_D2 <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+hist_ar1_D2
+```
+
+```{r MA(1) D2}
+# Set variables
+n <- 100
+ar <- 0.5
+ma <- 0.5
+counter <- 0
+nrep <- 1000
+B <- 1000
+mean <- 0
+sd <- 1
+
+# P-vals from using bootstrap with copulas
+pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(ma = ma), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), 
+                                              pnorm, 
+                                              qnorm,
+                                              mean = mean, 
+                                              sd = sd,
+                                              B = B))
+counter <- 0
+
+# P-vals from standard KS test
+pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ma = ma), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), 
+                                                pnorm,
+                                                mean = mean, 
+                                                sd = sd)$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
+p_values <- c(pvals_copula, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+results$histogram <- factor(results$histogram, levels = c("Naive", "Copula"))
+
+save(results, file = "results_ma1_D2.RData")
+
+# Generate histograms plot
+hist_ma1_D2 <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+hist_ma1_D2
+```
+
+```{r ARMA(1,1) D2}
+# Set variables
+n <- 100
+ar <- 0.5
+ma <- 0.5
+counter <- 0
+nrep <- 1000
+B <- 1000
+mean <- 0
+sd <- 1
+
+# P-vals from using bootstrap with copulas
+pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(ar = ar, 
+                                                           ma = ma), 
+                                                      rand.gen=rnorm, 
+                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
+                                                      n = n), 
+                                              pnorm, 
+                                              qnorm,
+                                              mean = mean, 
+                                              sd = sd,
+                                              B = B))
+counter <- 0
+
+# P-vals from standard KS test
+pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ar = ar, 
+                                                           ma = ma), 
+                                                      rand.gen=rnorm, 
+                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
+                                                      n = n), 
+                                                pnorm,
+                                                mean = mean, 
+                                                sd = sd)$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
+p_values <- c(pvals_copula, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+results$histogram <- factor(results$histogram, levels = c("Naive", "Copula"))
+
+save(results, file = "results_arma_D2.RData")
+
+# Generate histograms plot
+hist_arma_D2 <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+hist_arma_D2
+```
+
+```{r AR(2) D2}
+# Set variables
+n <- 100
+b1 <- 0.5
+b2 <- 0.3
+counter <- 0
+nrep <- 1000
+B <- 1000
+mean <- 0
+sd <- 1
+
+# P-vals from using bootstrap with copulas
+pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(order = c(2, 0, 0), 
+                                                           ar = c(b1, b2)),
+                                                      rand.gen=rnorm,
+                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
+                                                      n = n), 
+                                              pnorm, 
+                                              qnorm,
+                                              mean = mean, 
+                                              sd = sd,
+                                              B = B))
+counter <- 0
+
+# P-vals from standard KS test
+pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(order = c(2, 0, 0), 
+                                                           ar = c(b1, b2)),
+                                                      rand.gen=rnorm,
+                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
+                                                      n = n), 
+                                                pnorm,
+                                                mean = mean, 
+                                                sd = sd)$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
+p_values <- c(pvals_copula, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+results$histogram <- factor(results$histogram, levels = c("Naive", "Copula"))
+
+save(results, file = "results_ar2_D2.RData")
+
+# Generate histograms plot
+hist_ar2_D2 <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+hist_ar2_D2
+```
+
+```{r hist_ar1_ma1_arma_ar2_D2}
+load('results_ar1_D2.RData')
+model <- rep("AR(1)", 2000)
+ar1 <- data_frame(results, model)
+
+load('results_ma1_D2.RData')
+model <- rep("MA(1)", 2000)
+ma1 <- data_frame(results, model)
+
+load('results_arma_D2.RData')
+model <- rep("ARMA(1, 1)", 2000)
+arma <- data_frame(results, model)
+
+load('results_ar2_D2.RData')
+model <- rep("AR(2)", 2000)
+ar2 <- data_frame(results, model)
+
+data <- rbind(ar1, ma1, arma, ar2)
+
+data$model <- factor(data$model, levels = c("AR(1)", "MA(1)", "ARMA(1, 1)", "AR(2)"))
+data$histogram <- factor(data$histogram, levels = c("Naive", "Copula"))
+
+# Generate histograms plot
+hist_ar1_ma1_arma_ar2_D2 <- ggplot(data) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(histogram~model, scales = "free_y", ncol = 4)
+hist_ar1_ma1_arma_ar2_D2
+
+ggsave(filename = "hist_ar1_ma1_arma_ar2_D2.pdf", plot = hist_ar1_ma1_arma_ar2_D2, path = "../Manuscript", height = 4.2, width = 6)
+```
+
+```{r Gamma D2}
+# Set variables
+n <- 100
+rho <- 0.5
+counter <- 0
+nrep <- 1000
+B <- 1000
+shape <- 3
+scale <- 1
+
+# P-vals from using bootstrap with copulas
+pvals_copula <- replicate(nrep, test_copula_D2(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
+                                             pgamma, 
+                                             qgamma,
+                                             shape = shape,
+                                             scale = scale,
+                                             B = B))
+counter <- 0
+
+# P-vals from naively using fitted parameters
+pvals_naive <- replicate(nrep, test_standard_ks(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
+                                                pgamma,
+                                                shape = shape,
+                                                scale = scale)$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
+p_values <- c(pvals_copula, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+results$histogram <- factor(results$histogram, levels = c("Naive", "Copula"))
+
+save(results, file = "results_gamma_D2.RData")
+
+# Generate histograms plot
+hist_gamma_D2 <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+hist_gamma_D2
+```
+
+```{r GEV D2}
+# Set variables
+n <- 100
+rho <- 0.5
+counter <- 0
+nrep <- 1000
+B <- 1000
+loc <- 0
+shape <- 0.2
+scale <- 1
+
+# P-vals from using bootstrap with copulas
+pvals_copula <- replicate(nrep, test_copula_D2(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho),
+                                               pgev,
+                                               qgev,
+                                               loc = loc, 
+                                               shape = shape,
+                                               scale = scale,
+                                               B = B))
+counter <- 0
+
+# P-vals from standard KS test
+pvals_naive <- replicate(nrep, test_standard_ks(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
+                                                 pgev,
+                                                 loc = loc, 
+                                                 shape = shape,
+                                                 scale = scale)$p.value)
+
+# Create a master data_frame with all the results
+histogram <- c(rep("Copula", nrep), rep("Naive", nrep))
+p_values <- c(pvals_copula, pvals_naive)
+results <- data_frame(p_values, histogram)
+
+results$histogram <- factor(results$histogram, levels = c("Naive", "Copula"))
+
+save(results, file = "results_gev_D2.RData")
+
+# Generate histograms plot
+hist_gev_D <- ggplot(results) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(~histogram, scales = "free_y")
+hist_gev_D
+```
+
+```{r hist_gamma_gev_D2}
+load('results_gamma_D2.RData')
+model <- rep("Gamma", 2000)
+gamma <- data_frame(results, model)
+
+load('results_gev_D2.RData')
+model <- rep("GEV", 2000)
+gev <- data_frame(results, model)
+
+data <- rbind(gamma, gev)
+
+data$model <- factor(data$model, levels = c("Gamma", "GEV"))
+data$histogram <- factor(data$histogram, levels = c("Naive", "Copula"))
+
+# Generate histograms plot
+hist_gamma_gev_D2 <- ggplot(data) + 
+                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
+                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
+                   theme(legend.position = "none") +
+                   facet_wrap(histogram~model, scales = "free_y")
+hist_gamma_gev_D2
+
+ggsave(filename = "hist_gamma_gev_D2.pdf", plot = hist_gamma_gev_D2, path = "../Manuscript", height = 4.2, width = 6)
+```

### 2022-07-22 Code/Simulation.Rmd
ARMA(1,1) dependence model with updated figures

@@
 library(tseries)
+library(forecast)
 source('tspb.R')
@@
 ```{r AR(1) D}
-test_copula_D <- function(x, dist, B, mean, sd) {
+test_copula_D <- function(x, pdist, qdist, ..., B, wcopula = normalCopula) {
 
@@
 
-    stat  <- ks.test(x, dist, mean = mean, sd = sd)$statistic
+    stat  <- ks.test(x, pdist, ...)$statistic
 
@@
     rho  <-  cor(x[-1], x[-n], method = "spearman")
-    r <- iRho(normalCopula(), rho)
-    np <- normalCopula(r)
+    r <- iRho(wcopula(), rho)
+    wcop <- wcopula(r)
 
@@
         for (j in 2:n) {
-            u[j]  <- cCopula(c(u[j-1], u[j]), np, indices = 2, inverse = TRUE)
+            u[j]  <- cCopula(c(u[j-1], u[j]), wcop, indices = 2, inverse = TRUE)
         }
@@
         # Transform bootstrap sample and fit the parameters
-        x.b <- qnorm(u, mean = mean, sd = sd)
+        x.b <- qdist(u, ...)
 
         # Gather bootstrap sample's test statistic
-        stat.b[i] <- ks.test(x.b, dist, mean = mean, sd = sd)$statistic
+        stat.b[i] <- ks.test(x.b, pdist, ...)$statistic
     }
@@
 # Standard KS test
-test_standard_ks <- function(x, mean, sd) {
-  p.value <- ks.test(x, "pnorm", mean = mean, sd = sd)$p.value
+test_standard_ks <- function(x, pdist, ...) {
+  p.value <- ks.test(x, pdist, ...)$p.value
   list(p.value = p.value)
@@
 nrep <- 1000
-B <- 1000
+B <- 100
 mean <- 0
@@
 # P-vals from using bootstrap with copulas
-pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), 
-                                              "pnorm", 
+pvals_copula <- replicate(nrep, test_copula_D(genData(n = 100, qdist = qnorm, mean = 0, sd = 1, copula = claytonCopula, rho = 0.5), 
+                                              pdist = pnorm, 
+                                              qdist = qnorm,
+                                              mean = mean,
+                                              sd = sd,
                                               B = B, 
-                                              mean = mean, 
-                                              sd = sd))
+                                              wcopula = normalCopula))
 counter <- 0
@@
 # P-vals from standard KS test
-pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), 
+pvals_naive <- replicate(nrep, test_standard_ks(genData(n = 100, qdist = qnorm, mean = 0, sd = 1, copula = claytonCopula, rho = 0.5), 
+                                                pdist = pnorm,
                                                 mean = mean, 
@@
 pvals_copula <- replicate(nrep, test_copula_D(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), 
-                                              "pnorm", 
+                                              pdist = pnorm, 
+                                              qdist = qnorm,
+                                              mean = mean,
+                                              sd = sd,
                                               B = B,
-                                              mean = mean,
-                                              sd = sd))
+                                              wcopula = normalCopula))
 counter <- 0
@@
 pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ma = 0.5), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n),
+                                                pdist = pnorm,
                                                 mean = mean,
@@
                                                       n = n), 
-                                            "pnorm", 
+                                            pdist = pnorm, 
+                                            qdist = qnorm,
+                                            mean = mean,
+                                            sd = sd,
                                             B = B,
-                                            mean = mean,
-                                            sd = sd))
+                                            wcopula = normalCopula))
 counter <- 0
@@
                                                       n = n),
+                                                pdist = pnorm,
                                                 mean = mean,
@@
 ```{r Gamma D}
-# Testing bootstrap with copulas for gamma distribution
-test_gamma_D <- function(x, dist, B = 100, wcopula = normalCopula, shape, scale) {
-
-    # Get observed stat
-    n <- length(x)
-
-    stat  <- ks.test(x, dist, shape = shape, scale = scale)$statistic
-
-    # Get lag-1 sample auto-spearman rho
-    rho  <-  cor(x[-1], x[-n], method = "spearman")
-    r <- iRho(wcopula(), rho)
-    wcop <- wcopula(r)
-
-    # Parametric bootstrap to get an empirical distribution of stat
-    stat.b <- double(n)
-
-    for (i in 1:B) {
-        # 1. The marginal distribution is the fitted dist
-        # 2. There is temporal dependence
-        u <- runif(n)
-        for (j in 2:n) {
-            u[j]  <- cCopula(c(u[j-1], u[j]), wcop, indices = 2, inverse = TRUE)
-        }
-
-        # Transform the bootstrap sample and fit the parameters
-        x.b <- qgamma(u, shape = shape, scale = scale)
-
-        # Calculate new test statistic
-        stat.b[i] <- ks.test(x.b, dist, shape = shape, scale = scale)$statistic
-    }
-
-    # Return empirical p-value    
-    p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
-
-    counter <<- counter + 1
-    cat(counter, "")
-
-    return(p.value)
-}
-
-# Naive function that incorrectly uses fitted parameters for gamma distribution
-test_standard_gamma <- function(x, shape, scale) {
-  p.value <- ks.test(x, "pgamma", shape = shape, scale = scale)$p.value
-  list(p.value = p.value)
-}
-
 ptm <- proc.time()
@@
 # P-vals from using bootstrap with copulas
-pvals_copula <- replicate(nrep, test_gamma_D(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
-                                             "pgamma", 
+pvals_copula <- replicate(nrep, test_copula_D(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
+                                             pdist = pgamma,
+                                             qdist = qgamma,
+                                             shape = shape,
+                                             scale = scale,
                                              B = B,
-                                             shape = shape,
-                                             scale = scale))
+                                             wcopula = normalCopula))
 counter <- 0
@@
 # P-vals from naively using fitted parameters
-pvals_naive <- replicate(nrep, test_standard_gamma(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
+pvals_naive <- replicate(nrep, test_standard_ks(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
+                                                   pdist = pgamma,
                                                    shape = shape, 
@@
 ```{r GEV D}
-# Testing bootstrap with copulas for GEV distribution
-test_gev_D <- function(x, B = 100, wcopula = normalCopula, loc, scale, shape) {
-
-    n <- length(x)
-
-    # Get observed stat
-    stat  <- ks.test(x, 'pgev', loc = loc, scale = scale, shape = shape)$statistic
-
-    # Get lag-1 sample auto-spearman rho
-    rho  <-  cor(x[-1], x[-n], method = "spearman")
-    r <- iRho(wcopula(), rho)
-    wcop <- wcopula(r)
-
-    # Parametric bootstrap to get an empirical distribution of stat
-    stat.b <- double(n)
-
-    for (i in 1:B) {
-        # 1. The marginal distribution is the fitted dist
-        # 2. There is temporal dependence
-        u <- runif(n)
-        for (j in 2:n) {
-            u[j]  <- cCopula(c(u[j-1], u[j]), wcop, indices = 2, inverse = TRUE)
-        }
-
-        # Transform the bootstrap sample
-        x.b <- qgev(u, loc = loc, scale = scale, shape = shape)
-
-        # Calculate bootstrap test statistic
-        stat.b[i] <- ks.test(x.b, 'pgev', loc = loc, scale = scale, shape = shape)$statistic
-    }
-
-    # Return empirical p-value    
-    p.value <- (sum(stat.b >= stat) + 0.5) / (B + 1)
-
-    counter <<- counter + 1
-    cat(counter, "")
-
-    return(p.value)
-}
-
-# Standard KS test for GEV distribution
-test_standard_gev <- function(x, loc, scale, shape) {
-  p.value <- ks.test(x, "pgev", loc = loc, scale = scale, shape = shape)$p.value
-  list(p.value = p.value)
-}
-
 ptm <- proc.time()
@@
 # P-vals from using bootstrap with copulas
-pvals_copula <- replicate(nrep, test_gev_D(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho),
+pvals_copula <- replicate(nrep, test_copula_D(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho),
+                                           pdist = pgev,
+                                           qdist = qgev,
                                            loc = loc, 
@@
                                            scale = scale,
-                                           B = B))
+                                           B = B,
+                                           wcopula = normalCopula))
 counter <- 0
@@
 # P-vals from standard KS test
-pvals_naive <- replicate(nrep, test_standard_gev(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
+pvals_naive <- replicate(nrep, test_standard_ks(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
+                                                 pdist = pgev,
                                                  loc = loc, 
@@
     zx <- qnorm(rank(x) / (n + 1))
+
     fit <- tseries::arma(zx, include.intercept = FALSE)
-
     ar <- fit$coef[1]
@@
 
-test_standard_ks <- function(x, pdist, ...) {
-  p.value <- ks.test(x, pdist, ...)$p.value
-  list(p.value = p.value)
-}
-
 # Set variables
@@
 pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), 
-                                              pnorm, 
-                                              qnorm,
+                                              pdist = pnorm, 
+                                              qdist = qnorm,
                                               mean = mean, 
@@
 pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), 
-                                                pnorm,
+                                                pdist = pnorm,
                                                 mean = mean, 
@@
 
-save(results, file = "results_ar1_D2.RData")
+#save(results, file = "results_ar1_D2.RData")
 
@@
 pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(ma = ma), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), 
-                                              pnorm, 
-                                              qnorm,
+                                              pdist = pnorm, 
+                                              qdist = qnorm,
                                               mean = mean, 
@@
 pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ma = ma), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), 
-                                                pnorm,
+                                                pdist = pnorm,
                                                 mean = mean, 
@@
 
-save(results, file = "results_ma1_D2.RData")
+#save(results, file = "results_ma1_D2.RData")
 
@@
                                                       n = n), 
-                                              pnorm, 
-                                              qnorm,
+                                              pdist = pnorm, 
+                                              qdist = qnorm,
                                               mean = mean, 
@@
                                                       n = n), 
-                                                pnorm,
+                                                pdist = pnorm,
                                                 mean = mean, 
@@
 
-save(results, file = "results_arma_D2.RData")
+#save(results, file = "results_arma_D2.RData")
 
@@
 
-save(results, file = "results_ar2_D2.RData")
+#save(results, file = "results_ar2_D2.RData")
 
@@
 pvals_copula <- replicate(nrep, test_copula_D2(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
-                                             pgamma, 
-                                             qgamma,
+                                             pdist = pgamma, 
+                                             qdist = qgamma,
                                              shape = shape,
@@
 pvals_naive <- replicate(nrep, test_standard_ks(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
-                                                pgamma,
+                                                pdist = pgamma,
                                                 shape = shape,
@@
 pvals_copula <- replicate(nrep, test_copula_D2(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho),
-                                               pgev,
-                                               qgev,
+                                               pdist = pgev,
+                                               qdist = qgev,
                                                loc = loc, 
@@
 pvals_naive <- replicate(nrep, test_standard_ks(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
-                                                 pgev,
+                                                 pdist = pgev,
                                                  loc = loc, 

### 2022-07-22 Manuscript/manuscript.tex

@@
 \newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
+\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
 
@@
 The null hypothesis $H_0$ is that the population distribution is $F$.
-Let $F_n(\cdot)$ be the empirical cumulative distribution. The KS statistic is
+Let $F_n(\cdot)$ be the empirical cumulative distribution \eds{define ecdf}. 
+The KS statistic \eds{cite} is
 \begin{equation}
@@
 uses an alternative fast Fourier transform based method \citep{Dimitrova}.
-This issue with discrete or rounded is not the focus of this paper, though is a
+This issue with discrete or rounded data is not the focus of this paper, though
+ it is a
 common misuse that should be noted.
@@
 standard table when values of the mean and standard deviation are estimated 
-obtains extremely conservative results. This is supported by \citet{Capasso}, 
+yields extremely conservative results. This is supported by \citet{Capasso}, 
 who concludes that failing to re-estimate the parameters may lead to wrong, 
@@
 dependence and concludes that a test based on Monte-Carlo simulations performed 
-the best. We propose a parametric bootstrap procedure involving copulas to 
-account for dependence.
+the best. %We propose a parametric bootstrap procedure involving copulas to 
+%account for dependence.
 
@@
 the empirical distribution is serially dependent. A bootstrap procedure 
-employing copulas is a working solution. Section~\ref{sec:fittedwithdependence}
+employing copulas to account for dependence is proposed as a working solution. 
+Section~\ref{sec:fittedwithdependence}
 explores the case where a combination of the first two scenarios occurs. The 
-copula procedure can be adjusted for fitted parameters to be available as a fix. 
+copula procedure can be adjusted for the use of fitted parameters as a remedy. 
 Section~\ref{sec:conclusion} concludes with a discussion.
@@
 The null distribution of the KS statistic changes when the hypothesized
-distribution contains fitted parameters. In this scenario, the null hypothesis
+distribution contains fitted parameters. 
+\eds{what is the null distribution when not using fitted parameters}.  
+In this scenario, the null hypothesis
 is $H_0$: the random sample $X_1, \ldots, X_n$ comes from a continuous
 distribution $F_{\theta}$ with unspecified parameter vector $\theta$.
-Let $\hat\theta_n$ be an estimator of $\theta$, which could be, for example,
-maximum likelihood estimator of moment estimator. The test statistic is
+Let $\hat\theta_n$ be an estimator of $\theta$, which could be, for example, a
+maximum likelihood estimator or moment estimator. The test statistic is
 \begin{equation}
@@
 distribution with sample size $n = 100$. The p-values of $1000$ replicate tests
-are displayed in the Naive plot of Figure~\ref{fig:hist_fitted}. Each KS test 
-was performed using fitted parameters, i.e. the hypothesized distribution is 
+ of normality  
+are displayed in the Naive plot of Figure~\ref{fig:hist_fitted}. 
+\eds{how are these p-values calculated?}
+Each KS test 
+was performed using fitted parameters, i.e., the hypothesized distribution is 
 $N(\bar X, s^2)$ where $\bar X$ is the sample mean and $s^2$ is the sample 
-variance. Since the data is generated from a standard normal distribution with 
-seemingly all assumptions met, a uniform distribution of $U(0, 1)$ is expected 
-for the p-values. However this is under the assumption that the KS test
-assumptions hold, which no longer do due to using fitted parameters. Therefore, 
+variance. Since the data is truly generated from a standard normal distribution,
+ %with 
+%seemingly all assumptions met, 
+a uniform distribution of $U(0, 1)$ would naively be expected for the p-values.
+However this should only be expected when the KS test assumptions hold, and they
+ do not due to using fitted parameters. Therefore, 
 there is notable deviation from the uniform distribution.
@@
   the standard normal distribution with sample size $n = 100$. $B = 1000$ 
-  bootstrap samples are obtained for each test.}
+  bootstrap samples are obtained for each test. \eds{perhaps use density hist vs
+	freq. hist (here and elsewhere)?}}
   \label{fig:hist_fitted}
@@
 The KS test also displays issues in the case of dependent data. As mentioned, an 
-assumption of the test is that the data is independent. Unfortunately, real data
+assumption of the test is that the data is independent. Real data, however,
 is often temporally or spatially dependent and the results of a goodness-of-fit 
@@
 Equation~\eqref{eq:ks_standard}. However, since the data is dependent, the null 
-hypothesis is wrong and must be corrected. This is demonstrated with a 
+hypothesis is wrong and must be corrected. 
+\eds{null hypothesis or null distribution? or both?}
+This is demonstrated with a 
 simulation in Figure~\ref{fig:hist_correlation}. Data is generated from a 
@@
 P-values are gathered from $1000$ replicate tests for different levels of the 
-AR coefficient $\psi$, varying from $(-3,3)$. In the presence of serially 
+AR coefficient $\psi$, varying from $(-3,3)$. 
+\eds{how are these p-values calculated?}
+In the presence of serially 
 dependent data, the distribution of p-values no longer follows $U(0, 1)$ as 
 would be expected of a valid test. The results echo those of \citet{Durilleul} 
-that the KS statistic is too liberal for positive autocorrelation values, and 
-that the behavior is asymmetrical for negative values.
+that the KS statistic is too liberal in the presence of positive
+autocorrelation, and that the behavior is asymmetrical for negative
+ autocorrelation.
 
@@
 observations. The AR(1) parameter $r$ of the normal copula is set to match the 
-be the sample serial Spearman's rho of the observed sample. The procedure is as 
+sample serial Spearman's rho of the observed data. 
+\eds{What is the difference between $\psi$ and $r$?}
+The procedure is as 
 follows.
@@
 The procedure corrects the distribution of p-values for both distributions and 
-is shown to be applicable irregardless of the family of distribution tested.
+is shown to be applicable regardless of the family of distribution tested.
 
@@
 
-Similar to Section~\ref{sec:dependence}, the copula fix is not a complete 
+Similar to Section~\ref{sec:dependence}, the copula approach is not a complete 
 solution. Regardless of the true dependence in the data we assume an AR(1) 
@@
 generalized extreme value distributions. The results are favorable and show that 
-the procedure outlined as a fix for fitted parameters and spatially dependent 
+the procedure outlined as a remedy for fitted parameters and spatially dependent 
 can be adapted for various families of distributions.
@@
 the size of the test. A bias correction is required if the non-parametric form 
-is used \citep{Babu}. In the case of dependent data, a procedure using bootstrap 
+is used \citep{Babu}. In the case of \eds{serially} dependent data, a procedure 
+using bootstrap 
 with copulas to model dependency shows positive results. When both assumptions 
-are violated, that is the case where the data has dependence and parameters must 
+are violated, i.e., where the data has \eds{serial} dependence and parameters 
+must 
 be fitted, an adjusted copula procedure also shows positive results. The tests 
@@
 dependence, we assume an AR(1) dependence structure. Therefore, if the AR(1) 
-dependence structure is a close approximation of the truth, the fix can work. 
+dependence structure is a close approximation of the truth, the approach can work. 
 However, in cases such as AR(2), if the approximation is too far from the true 
-dependence structure the fix does not completely solve the issue. As well, tests 
-were only performed with the normal copula. It is possible that other copulas
-could provide stronger results based on the true dependence of the data.
+dependence structure the approach does not completely remedy the issue. As well, 
+tests were only performed with the normal copula. It is possible that other 
+copulas could provide stronger results based on the true dependence of the data.
 

### 2022-07-27 Manuscript/manuscript.tex
first two paragraphs

@@
 \author{Anthony Zeimbekakis\\
-\href{mailto:anthony.zeimbekakis@uconn.edu}
-{\nolinkurl{anthony.zeimbekakis@uconn.edu}}\\
-Department of Statistics, University of Connecticut\\\\
-Thesis Advisor: Jun Yan\\
-Honors Advisor: Elizabeth Schifano}
+%   \href{mailto:anthony.zeimbekakis@uconn.edu}
+% {\nolinkurl{anthony.zeimbekakis@uconn.edu}}\\
+  Elizabeth Schifano\\
+  Jun Yan\\[1ex]
+  Department of Statistics, University of Connecticut\\
+}
 \date{}
@@
 \begin{abstract}
-The Kolmogorov--Smirnov (KS) test is one of the most popular goodness-of-fit tests 
-for comparing a sample with a hypothesized parametric distribution. 
+The Kolmogorov--Smirnov (KS) test is one of the most popular goodness-of-fit
+tests for comparing a sample with a hypothesized parametric distribution.
 Nevertheless, it has often been misused. The standard one-sample KS test applies
@@
 distributions containing estimated parameters. For example, it has been 
-``discovered'' multiple times that the test is too conservative when the 
-parameters are estimated. We demonstrate misuses of the one-sample KS test in 
+``discovered'' multiple times that the test is too conservative when
+hypothesized distribution has parameters that need to be estimated.
+We demonstrate misuses of the one-sample KS test in 
 three scenarios through simulation studies:
@@
 For each scenario, we provide remedies for practical applications.
+
+\bigskip
+\noindent\sc{Keywords}:
+nonparametric bootstrap;
+parametric bootstrap;
 \end{abstract}
@@
 tests for comparing a sample with a hypothesized parametric distribution.
-Let $X_1, ..., X_n$ be a random sample from some continuous distribution. 
-The null hypothesis $H_0$ is that the population distribution is $F$.
-Let $F_n(\cdot)$ be the empirical cumulative distribution \eds{define ecdf}. 
-The KS statistic \eds{cite} is
+Let $X_1, ..., X_n$ be a random sample of size~$n$ from a continuous
+distribution. The null hypothesis $H_0$ is that $X_i$'s follow distribution~$F$.
+Let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
+distribution function of the sample, where $I(\cdot)$ is the indicator
+function. The KS test statistic is
 \begin{equation}
   \label{eq:ks_standard}
-  D = \sup_x | F_{n}(x) - F(x) |.
+  D_n = \sup_x | F_{n}(x) - F(x) |.
 \end{equation}
-The distribution of $D$ under $H_0$ turns out to be independent of the
-distribution $F$ and a table of critical values for $D$ has been constructed
-\citep{Massey} for various sample sizes $n$ and significance 
-levels $\alpha$. If the value of $D$ exceeds the test's corresponding critical 
-value the null hypothesis is rejected. The KS test is available in popular 
-statistical software packages, such as function \texttt{ks.test} in R 
-\citep{R, Marsaglia}.
+The asymptotic distribution of $D_n$ under $H_0$ is independent of the
+distribution $F$. As $n \to \infty$, $\sqrt{n} D_n$ converges in distribution to
+the supremum of standard Brownian bridge \citep{kolmogorov1933sulla}. For large
+samples, the tests can be performed with a table \citep{smirnov1948table}.
+Critical values for small samples ($n \le 35$) has also been given
+\citep{Massey}. The KS test is available in popular 
+statistical software packages, such as function \texttt{ks.test} in R package
+\textsf{stats} \citep{R, Marsaglia}.
 
@@
 has often been applied without realizing that one or more of these assumptions
-do not hold.
-
-\citet{Noether} provides a brief demonstration of the 
-conservative character of the KS test when using discrete functions. 
-There are remedies that allow the KS test to be used in discrete cases. 
-\citet{Conover} describes a method for finding the exact critical level for 
-discrete cases and derives its power. \citet{Gleser} provides methods for 
-adapting existing algorithms to provide results when $F(x)$ is discontinuous.
-The discrete KS test is available in various statistical software packages.
-The package \textsf{dgof} implements the methods from \citet{Conover} for 
-one-sided tests and the methods from \citet{Gleser} for exact two-sided 
-p-values \citep{Arnold}. The \textsf{KSgeneral} package provides a fast and 
-accurate method for when $F(x)$ is arbitrary, discontinuous, or continuous that 
-uses an alternative fast Fourier transform based method \citep{Dimitrova}.
-This issue with discrete or rounded data is not the focus of this paper, though
- it is a
-common misuse that should be noted.
+do not hold. For example, \citet{Noether} demonstrated the conservativeness of
+the KS test when applied to discontinuous distributions. The null distribution
+of the KS statistic is no longer distribution free. Computing the
+exact and asymptotic distribution of $D_n$ is challenging. Fortunately, the null
+distribution of the KS statistic when the underlying distribution is
+discontinuous has been efficiently addressed by \citet{Dimitrova} with an
+companion R package \textsf{KSgeneral}. Although a common misuse of KS test, the
+issue with discontinuous or data is not our focus.
 
